% universal settings
\documentclass[smalldemyvopaper,11pt,twoside,onecolumn,openright,extrafontsizes]{memoir}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[osf]{Alegreya,AlegreyaSans}

% PACKAGE DEFINITION
% typographical packages
\usepackage{microtype} % for micro-typographical adjustments
\usepackage{setspace} % for line spacing
\usepackage{lettrine} % for drop caps and awesome chapter beginnings
\usepackage{titlesec} % for manipulation of chapter titles

% for placeholder text
\usepackage{lipsum} % to generate Lorem Ipsum

% other
\usepackage{calc}
\usepackage{hologo}
\usepackage[hidelinks]{hyperref}
%\usepackage{showframe}

% PHYSICAL DOCUMENT SETUP
% media settings
\setstocksize{8.5in}{5.675in}
\settrimmedsize{8.5in}{5.5in}{*}
\setbinding{0.175in}
\setlrmarginsandblock{0.611in}{1.222in}{*}
\setulmarginsandblock{0.722in}{1.545in}{*}

% defining the title and the author
\title{Ghost Flights}
\author{Ross Goodwin}
\newcommand{\press}{NaNoGenMo 2019}

% custom second title page
\makeatletter
\newcommand*\halftitlepage{\begingroup % Misericords, T&H p 153
  \setlength\drop{0.1\textheight}
  \begin{center}
  \vspace*{\drop}
  \rule{\textwidth}{0in}\par
  {\Large\textsc\thetitle\par}
  \rule{\textwidth}{0in}\par
  \vfill
  \end{center}
\endgroup}
\makeatother

% custom title page
\thispagestyle{empty}
\makeatletter
\newlength\drop
\newcommand*\titleM{\begingroup % Misericords, T&H p 153
  \setlength\drop{0.15\textheight}
  \begin{center}
  \vspace*{\drop}
  \rule{\textwidth}{0in}\par
  {\HUGE\textsc\thetitle\par}
  \rule{\textwidth}{0in}\par
  {\Large\textit\theauthor\par}
  \vfill
  {\Large\scshape\press}
  \end{center}
\endgroup}
\makeatother

% chapter title manipulation
% padding with zero
\renewcommand*\thechapter{\ifnum\value{chapter}<10 0\fi\arabic{chapter}}
% chapter title display
\titleformat
{\chapter}
[display]
{\normalfont\scshape\huge}
{\HUGE\thechapter\centering}
{0pt}
{\vspace{18pt}\centering}[\vspace{42pt}]

% typographical settings for the body text
\setlength{\parskip}{0em}
\linespread{1.09}

% HEADER AND FOOTER MANIPULATION
  % for normal pages
  \nouppercaseheads
  \headsep = 0.16in
  \makepagestyle{mystyle}
  \setlength{\headwidth}{\dimexpr\textwidth+\marginparsep+\marginparwidth\relax}
  \makerunningwidth{mystyle}{\headwidth}
  \makeevenhead{mystyle}{}{\textsf{\scriptsize\scshape\thetitle}}{}
  \makeoddhead{mystyle}{}{\textsf{\scriptsize\scshape\leftmark}}{}
  \makeevenfoot{mystyle}{}{\textsf{\scriptsize\thepage}}{}
  \makeoddfoot{mystyle}{}{\textsf{\scriptsize\thepage}}{}
  \makeatletter
  \makepsmarks{mystyle}{%
  \createmark{chapter}{left}{nonumber}{\@chapapp\ }{.\ }}
  \makeatother
  % for pages where chapters begin
  \makepagestyle{plain}
  \makerunningwidth{plain}{\headwidth}
  \makeevenfoot{plain}{}{}{}
  \makeoddfoot{plain}{}{}{}
  \pagestyle{mystyle}
% END HEADER AND FOOTER MANIPULATION

% table of contents customisation
\renewcommand\contentsname{\normalfont\scshape Contents}
\renewcommand\cftchapterfont{\normalfont}
\renewcommand{\cftchapterpagefont}{\normalfont}
\renewcommand{\printtoctitle}{\centering\Huge}

% layout check and fix
\checkandfixthelayout
\fixpdflayout

% BEGIN THE DOCUMENT
\begin{document}
\pagestyle{empty}
% the half title page
\halftitlepage
\cleardoublepage
% the title page
\titleM
\clearpage

% begin front matter
\frontmatter
\pagestyle{mystyle}

% table of contents
\clearpage
\tableofcontents*

% begin main matter
\mainmatter


\chapter{Cologne Butzweilerhof Airport to Son Bonet Airport}
On the marble arch of the Liegfort ...
\\Imperial city of the last night's air love and menace,
\\Smog-Misted Paris, set with all its gleaming vandelions,
\\Clouds of black figurines and birds of lead
\\Dotting the marble floor, and above the gas station
\\The gas station, lit from within, glowing in the amber
\\Mildenhawf of the air, and the red carriage
\\Eleven miles away in the smoke-filled sky.
\\My father, who liked dandelions, and epileptus--
\\They were the most intelligent, the most humane
\\Of dogs, and I, the only one, mutilated,
\\By a tendency to drool and grow black eyes.
\\Now it's autumn again. I've quit my job
\\And here, to you I do the same thing--
\\And that's how it goes. It's not the end of the world.
\\It's happening somewhere else, some distant place.
\\Some devon city, old forgotten numbers,
\\Near the coast of the ocean, just beyond the reach
\\Of the coast, just beyond the reach of the end of the world,
\\Canada--
\\ark of the packest day, when I sailed across
\\The arctic; and it won't forget the time
\\Of the bus, and the wind, and the noise and strain
\\Of the locomotive--
\\It'll come back to me, I guess, sometime some future afternoon
\\I'll get up on the deck of the boat and find
\\Me looking down like now, so that my eyes
\\Will be connected to the deep (though of course
\\A mirror, a beautiful surface) and then
\\The next time I'll look back across
\\The empty airplane bookcase
\\And start pulling at my bald head and wonder,
\\At all the hollows and coldhouses of the world.
\\When I see other women
\\I don't know what they are saying
\\But I'll be afraid of the nuclear bomb
\\If it decides where we are going.



\chapter{Blackbushe Airport to Kai Tak Airport}
I am, I'm an abstract wind
\\the green of the body screams
\\I am the void falling through, in no
\\way is clear
\\it's filled with yellow
\\papyrus, bone, grass, teeth,
\\laboratory plum
\\lets fall
\\outside it, ruining
\\the heart.
\\The tangled
\\throat of the sexually
\\taloned male
\\or the female
\\failing to
\\arrive safely inside
\\the exploded
\\automotive
\\of the sudden
\\human grove
\\I am
\\strange, incomplete,
\\surround
\\with strings of hostile
\\fingerbombs
\\I am the
\\dust
\\and ashes
\\of a public
\\suicidal scheme
\\I am what happened
\\on a foreign
\\sea
\\no one
\\knows
\\the way
\\out of it
\\NEWER
\\GENERATION HALES
\\and all
\\other generations of
\\fifty-
\\year-olds
\\or younger
\\globes
\\with their GI draft cards
\\and letters
\\they scribbled
\\onenormers
\\bitheads
\\instead
\\of wars
\\and the aged
\\pinwheelers
\\who knew
\\what they were doing
\\by the
\\ringed Bohemian
\\flag
\\working on the
\\geom
\\while the
\\named
\\Nord
\\and the rest
\\were simply
\\roosters
\\let us
\\remember
\\that
\\we are all
\\roosters
\\what
\\else can you
\\know
\\where are you
\\by this
\\default chronicle
\\magic mark
\\which you have
\\your own
\\places
\\MERRY WEPPER
\\little girl
\\tired
\\from the heat.



\chapter{Beechy Airport to Old Mariscal Sucre International Airport}
The Beech tree is waving its smoke-green banners,
\\in trombones loud;
\\The Coahuarts stand in a circle round the sky,
\\while the deportee number
\\sweeps the crowd of interfering passengers!
\\Your jewels are shy, your drugs deposed,
\\your polished wheels rattle;
\\The sleary's hocus unscanned, your heat
\\is subtle and imperious as a whistle.
\\New York, April 6, 1952, 3 A.M.



\chapter{Malmö Bulltofta Airport to Davis Airport}
Outside the terminal window window
\\Fire flares on the Waldowick Terrace
\\Near the International Business Center
\\There is a world of bodies
\\Of radiant music and beauty
\\Crowded on the broken pavement
\\Infrastructure personnel
\\Her Majesty's Navuta Paper Co.
\\What are the aircraft piloting planes
\\The sterile acres of Amida
\\The Piedmont-Sierras and the Cargot
\\That soothed the Mediterranean
\\The Horn, the brand-new bombs
\\Climbing the airwaves
\\To demeanate the sense of drama
\\What are the special roads
\\None of the machinery
\\You need a bigger parachute
\\Learn how to pee
\\What are the giants
\\Giant white wheat
\\ティ highway
\\You need a memory
\\Of sated concrete
\\Pictures from Des Moines
\\Composers' magic journeys
\\We believe our dreams
\\We have a common history
\\We are not something else
\\We are complementary
\\We are completer to history
\\We are what we see
\\We are others
\\On the bridge
\\Over the river
\\Over the town
\\Under the river bridges
\\As long as there are neon signs
\\Those drivers will light
\\Those drivers will light
\\Where there are streets
\\Along the orient
\\Along the altitudes
\\Up from the patches
\\Of parceled out of the depths
\\Of bundled mountains
\\Behind them now
\\As the stream deals with them
\\You are hypersensitive
\\You think you are memorizing the address
\\Of a number
\\To make a leap
\\You are big enough to be around
\\While I tell you what you can't
\\Think you are French.



\chapter{Valley Airport to Caliente Flight Strip}
Vulnerable as a wind or water,
\\the house takes me back to wind,
\\a different battery to contend
\\with humidity, a heavier dirt
\\that heaved my mother and her peewits,
\\and my brother against his will,
\\hand over hand, I see my mother,
\\who is not discomfited,
\\balding despite the rain,
\\insulin pump administered by a needle,
\\she twirled us through the gate,
\\while the yellow blood of my mother dried
\\on the windshield in a spirit I did not know
\\I had again been to the Oracle.
\\You know how they said it was:
\\you who grow and wear the woman
\\you marry, like a man,
\\keep small amounts to come
\\and avail your strength
\\for this long, strange, uncertain season.
\\How does the body hold on
\\so that it may? I do not know.
\\But I do know what the body
\\is thinking now, her wail
\\shedding its legs and then I hear
\\the ugly churning of the throttle
\\under my hand, the sickening snap
\\of controls, the turn at the gun barrel
\\as power finally flows from the machine.
\\I love the word but it feels like the sex,
\\warm and tantalized, sweet but
\\not so deep and wild there.
\\My friends, we are young, we have sex
\\just as we love beer. I know
\\why it makes us feel so like men
\\and I remember my mother gave me acid and died.
\\Later I played a game I think
\\I won't remember--sweated and purple,
\\covered with sweat and foam,
\\as she always did, the gunthundered woman
\\in the next room who always wore white.
\\My father cowered backward,
\\his coat fluttering like a shawl,
\\and I scrambled out of bed to make my awful first stab
\\against the male fighters. I traveled all night
\\in a borrowed car, abandoned at a hotel
\\where no one was, wearing a white shirt
\\and a dress made of the fabric of cowbells.



\chapter{Northolt Airport to Grande Cache Airport}
I allow you to touch me
\\I allow you to enter my public body
\\an apple, a peeling body
\\I allow you to speak of my feelings
\\remove the Ottoman envelope
\\and my own homemade ring
\\set on my table inside the airport
\\outside my hand
\\I'm a prism, an expressive temporary
\\sentience
\\visiting a dark room
\\that is more or less inaccessible
\\than the reality of the player
\\on the plane above the dim building
\\over the heavy scent of gasoline
\\and I am feeling pity
\\for the dead man's wrist
\\that feels like an empty string
\\I put the hand on a chair, playing
\\the stereo. I need a man who
\\will stop spinning
\\to give my old mind its recall
\\and I am wide awake.
\\I think about the dead man
\\in a piece of white clothing
\\deathly white hair
\\getting the bus back
\\with a light on.
\\I think about the egg
\\laying hours on the phone
\\with the number trilled
\\to the machine with the same voice
\\until the connection goes away
\\in the other direction.
\\I think about the long arrows
\\shining like dots of light
\\till it catches fire
\\on the wires.
\\Activators cornered us
\\we could not bend or break
\\until we were the right way
\\and we were the left way
\\and we were the right way
\\but you let me play
\\and the cross slides free.
\\You gave me the perfect stage
\\and I acted like a shy girl
\\and I sang like a king.
\\I love you, I love you,
\\I love you, I love you.
\\And is this the great ordeal
\\that I am ten,
\\that I am ten?



\chapter{Northwest Field to Ciudad Real Central Airport}
I arrive just after sundown,
\\smiling to myself
\\from my simple shack
\\under the gigantic plane-tree,
\\letting the land bridge
\\for example, the X-belt of its control plane
\\floating toward Pennsylvania.
\\This is United Airlines,
\\vol. 1, no voor
\\per su demesne,
\\uija con su mliquem
\\are you there
\\in there
\\ircle after no voor
\\?
\\wallpaper
\\or glass
\\I see you on the outside of the wall
\\a light wire
\\Sharing what is hidden
\\In the categories
\\of lost objects
\\under the categories
\\of unthinkable wants
\\laid previously
\\against the glass
\\beneath the graphi:
\\Is this same place
\\the way we would want it
\\to be?
\\How would we want to know
\\the truth of our gift
\\if we somehow fail
\\laid collectively, we cannot
\\tell apart
\\the up and down and the day
\\and the year.
\\Deny yourself what you are
\\independent of the undead
\\who inhabit
\\the dreams you will not forget
\\they will blight
\\your daily dreams
\\very quickly
\\I knew a man named Karnos
\\He was in the papers
\\reports
\\the Rev. This thinkth he
\\was being punished
\\For converting Japanese
\\to Ilparello
\\and stripping the Erect Military
\\District
\\to give him back his ship
\\that he'd promised
\\to sail eternally
\\to Kosovo
\\for the Djinn of the door
\\that is a bridge
\\for all the massachusettses
\\and under the heart
\\of the Massachusetts king
\\who is as big as a house
\\and as tall as a tree
\\His called is Auther that runs
\\the New Providence Providence
\\the outspread arm
\\of the nation
\\infinitely
\\outer game
\\of this wounded whale
\\who tries to call all
\\objects out of time
\\of day that we are
\\to wait for the drowning
\\to begin
\\THE ILLEL
\\This is the kind of light
\\that gives more light
\\to the wild than the wild
\\in which it stands.
\\A youth arrives.
\\He spouts tea, dogs, cats, beans
\\for his family.
\\A nature-lover comes
\\in the morning.



\chapter{Olive Hill Airport to Middle Stewiacke Airport}
I make your flight long
\\for one they may know
\\where the nearest airport is
\\or to hide in the world
\\RCD
\\Croak
\\in the long roman line
\\there is a colour for weeping
\\the air is shoddy
\\Some suggest
\\something white
\\the others white witnesses
\\sit on top
\\thru the rough air
\\in here from all
\\good things, come to this
\\harbour in the rain
\\What I must think, naked
\\in the hot road
\\among the fruit trees
\\where, because they would not
\\move there, the cattle stand
\\eleven on the barns
\\bowing down to the noon
\\Speed-free
\\to everything
\\that runs
\\for the immediate measure
\\to God's Canada
\\Lit fences
\\pointing behind the desert
\\lane
\\last night
\\to the Northern Highway
\\which I already
\\believe
\\and have seen
\\the empty world
\\served for the
\\ray
\\spectral breast
\\open at the sky
\\see the face of it
\\NEAR SHIP ON THE MARSHORMATE
\\being served by a number
\\of boys
\\from the new
\\bustards
\\Let us use it
\\as food or as drama
\\first before we die
\\to start
\\the real life
\\In humanity's varied
\\launde-larc
\\globe
\\(can be seen through
\\the dress
\\The stew
\\is very
\\concentrating
\\on a
\\dificant issue
\\(an
\\intercountry)
\\I for
\\ancient fundamentalism
\\which deserves
\\no apology
\\by us
\\the revolutionaries
\\are not bitter
\\I for
\\a few years
\\have been writing
\\at this table
\\not knowing
\\whether or not
\\it might explode
\\there are
\\flowers upon
\\the table
\\marbled with water
\\the poem
\\drifts across
\\and is
\\a pendulum
\\drop
\\in a meaning
\\insistent
\\on the nature
\\of things
\\for us to
\\be on the stage
\\of our danger
\\We are trying to think
\\as through a
\\window
\\catch
\\the moon
\\CAVALRY CROSSING A FORD
\\like a river
\\at the steeple
\\is turning away
\\into the bushes.



\chapter{Erie County Airport to Montréal/Île Sainte-Hélène Water Airport}
Jetted above the orchards of the green old town
\\killer missiles sleep their drop of warlike heads,
\\till grass-covered
\\bridges of the street
\\and the wharves
\\mirror the tiger moon,
\\cock's tail tremulous
\\airplane moving ahead,
\\signifying death or discovery;
\\no other wheel
\\tells the blood, that waits for life,
\\sun, moon, rat-box, clock, bus-wire,
\\old gain, soft delight of the apple,
\\buds flower, warm earth,
\\above and beyond
\\the sickle moon
\\shining down through the branches;
\\everywhere the sprawl of air
\\and the wing-pans
\\apple-sweet
\\--plumes
\\from that smoke root
\\swift as myfingers
\\over the graves of the dead,
\\the R.R.G. genre
\\hangs on, the nailed-down trees
\\shrivel or crumble,
\\as space tries
\\to contain
\\the word itself,
\\beyond its power to hold
\\what it cannot hold.
\\Coming through the roof,
\\through the mailboxes,
\\the leaf-edged
\\pastures curl with flags
\\of the various
\\Various trees,
\\where the worn-out man
\\heeds no more
\\the crunch of the peel of a rake
\\than the inner juice of a railed lump,
\\unwanted by all the winds
\\lowering through the air,
\\the pit
\\out of the storm,
\\shifting with the lights
\\of the mind...
\\The seabed of the man-worm
\\keeps its sweet store
\\of venom
\\in the days
\\of rainbow trout rainbow trout
\\how they must love
\\the gliding fly,
\\how they must love
\\and so they die,
\\veins, groves, crags
\\of mountain pine
\\trout and snail
\\moss bed
\\and cow-flesh
\\to be eaten
\\dew-choke or
\\snouted by the cormorant
\\lined up
\\elephantine
\\black stone
\\--liquid
\\peels
\\washed to last
\\Oct. 1, 1884.



\chapter{Abu Dhabi/Al Bateen to Haynesville Airport}
Outside the window the Grand Emirates
\\stands on the gate housecock at Century City;
\\you might have missed the way the trees
\\rolled the asphalt toward the rusted paintstacks
\\of the Customs house unloading cargo
\\the van appeared four commercial airline signs
\\which bodega
\\and red signs
\\on the official board of justice
\\and overturned what was done
\\during a city of thieves
\\not a sound of anger but
\\smoke from the wooden-burning latters
\\the seven assembled amicably and
\\the principal decreed by the principal
\\before the sitting of the royal constabulary
\\the guerre du civilisation
\\which in an oval blue flower
\\as she was singing
\\sung in a violina
\\*
\\The man in the chair, between whom and the girl
\\he sat, was never more than awake
\\in the poplar-joint or the heart of
\\the flower-beds,
\\peering past the erection,
\\the ladders, the structures,
\\which had been design'd
\\for someone else.
\\He, at least,
\\had begun to think how he might
\\like his so much friend
\\and also like the things
\\he had in himself prophesied.
\\The republican hero,
\\whom conquer'd by his own sex,
\\who had not sufficiently trying
\\with virtue but virtue was he,
\\must, by some crafty tricks,
\\arrow for his purpose;
\\The lyon, the giant,
\\the elephant, the hairy-bodied man,
\\change themselves to birds
\\or talk to their horses,
\\The dolphin, the shugtail,
\\the epaulet, and the whelver,
\\Passions require more than skills,
\\and love has an inward charm,
\\Passions give people hearts,
\\which bewitch the court and crown,
\\and the community;
\\Friends are charming; and the root
\\of love is mercy,
\\And underneath there lies
\\the secret of the adorable,
\\The tender heart of love
\\Commemorating both?
\\Nay, my suns, by their wilful flames
\\were outlav'd, you were no more.



\chapter{Kahntah Aerodrome to Kutztown Airport}
Light kisses the bare trees,
\\Granite, where the rock is steep,
\\also burnish a wing.
\\Rose leaves, once thin berries,
\\Don't bloom in winter,
\\Don't wade through cold rain,
\\Teak salt water,
\\Take one last deep breath,
\\Expiration and flow down.
\\Slow, too slow, the air grows,
\\And the wind grows my music.
\\Whither, too soon, the bird flies.
\\Father, does I cry to the world
\\Because I haven't done?
\\Don't I feed it
\\Out of the knitted haze?
\\Something I see across the dark
\\Is that trained rocket's trail.
\\And coming home from hunting,
\\From the right sky and the sky,
\\From the wrong land, I learn
\\That the magic, magic Cape,
\\Is the flew, long-lasting thing.
\\I learned it once and then again,
\\While building my body
\\I didn't know I had the grace
\\To come so far for miles.
\\I haven't learned to let go
\\My bow nor my spear.
\\If I had stayed I'd have learned
\\All the little points I learned
\\So simply to leave my life.
\\For my own self's sake, I learned
\\To make my way up the hill.
\\The sea so deep and blind
\\And hot and tired
\\I wouldn't have come here again.
\\And yet the winds blow through me,
\\And the waves could never be more soft
\\Than those of Sorrow,
\\And that's how I came to here.
\\I wasn't born here for nothing.
\\I came here to sing
\\And to be taught.
\\I have no music to put singers;
\\I have no great songs to sing.



\chapter{Glasgow Air Force Base to Polonia International Airport}
I spared my place beyond the driest heaving sea
\\that day of cursing and flight and star-gazing:
\\I spared my place beneath the tallest tower
\\wherein the joy of empty pages comes true.
\\I spared my place beneath the tallest tower
\\wherein the light of open war went down.
\\I come from a country apart in this sky
\\where there is no more place than this
\\and here I am.
\\Small and dull is the world we tread,
\\and the numbers of feet that fly
\\By the lights that keep us apart in our love
\\we cannot remember.
\\For something old and strange
\\in the eyes of men
\\these eyes have lost their love,
\\and so are those that see me since then,
\\and all the world adore.
\\Ah! could our ship but reach and anchor there,
\\what wondrous scenesvisited!
\\But though we had no railing to stiffen,
\\the gusts could past all eden carry.
\\Prometheus, hurrying, wooes no more,
\\the wooing sea went on;
\\And in the moonlight stood Anon
\\before the gaping shore,
\\culadines, sea-pinnacles,
\\And blew a veil o'er the eyes of men
\\to cloud the beatings of the heart.
\\The very ground beneath her lay bare;
\\the hills were steep and wild,
\\And all the sea-like caverns were
\\pierced of owls.
\\From the glimmering belfries came
\\the angry winds,
\\The blows of malignant thunder,
\\which at nightrakka heard,
\\And heard in slumber.
\\Nor could she rest. the time came
\\before she felt the tread
\\Of hostile feet, that spurn her surface,
\\to which her head was bowed;
\\The time came when she seemed to live
\\in that dead drowning place,
\\And took her breath, and stood
\\Breast-deep in salt water.
\\The ship's starry diadem.



\chapter{Downsview Airfield to Montréal/Île Sainte-Hélène Water Airport}
1.
\\Dusty, gray, wet roads
\\on the background of tiny dense emerald hills.
\\The sun comes up over the Pont Marie I hear
\\rooftops buzzing over the lagoon, wine and white eggs
\\on the top of the kitchen cabinet.
\\To the left, licensed newsprint; below,
\\the valley of the peucose, swamp-hemm'd,
\\liquored, sylvan.
\\You cannot see the bank, its gravel
\\rocks in the dry air, nor the red roofs far
\\away,
\\but between the brick walls,
\\between the highways and the red road;
\\lotus like a damask rose,
\\and the white beach, scripted like the last song
\\of the human.
\\The place:
\\intersected with the pink desert
\\of old luzon,
\\homesteaded like an anthony of maids
\\whose teeth and pupils are shaped like a fissure
\\in which the teeth were still pink.
\\Her job is as statistical,
\\she scores, but not on a jot,
\\and I scratch her thighs, touching
\\the above L of the letter C,
\\touching the blue soil.
\\2.
\\The sky, the sky is cloudy
\\but the clouds--
\\as the long day ends,
\\and I raise my glass
\\to the sky.
\\A long night follows,
\\the children have dark
\\hair on their heads, the clouds
\\come up as Fly,
\\leaving behind them a trail
\\of dryness, of matchless
\\parquetball.
\\It is rain and the clouds
\\are full of oranges, but somehow
\\they become hollow,
\\little candles.
\\Then the sky cleaves
\\and its chromatic machinery
\\begins to read aloud,
\\to come back down the stair
\\on the third floor
\\with a sound like walking
\\in the sap breath of a tree,
\\and I pass around,
\\breathing upon my lips
\\an old man's laugh.
\\Then I remember that smile.



\chapter{Mayes Airport to Ear Falls Airport}
Mayes County Fair; green fields linen-dotted,
\\Where the long thin streak of land wants planting,
\\Where the red bush breaks against the rusty top of the sky.
\\Mayes County Fair;
\\And the green land life-lumps,
\\So to speak, stretched along the thin top of the foot of the crow-tree,
\\Our Orange County Fair.
\\Special.
\\There is no one above me,
\\There is no one above me;
\\But the wheelbarrows sing, and the iceman sings, and the gun-barriers sing,
\\And the gate-keepers speak, and the guard-slayers speak, and the door-keepers speak.
\\*        *        *
\\Yet, mopped hair and sunny eye,
\\Bronzed breast and dimpled chin,
\\There is a common speech of common things,
\\But this of darkness in the sunlight
\\Glows according to a run of precedence.
\\O get my hands to sing!
\\O make me with thee the voice of the steel-shoed slave,
\\Rise of moon-syphants, inform'd with what and whom,
\\Light of the dark and heavy night,
\\Perfidious breeze, perfidious breeze!
\\O form effaced and effaced,
\\By the harsh countenance of old years,
\\By the harsh countenance of deaths,
\\Unknown to heaven though not to me,
\\Star-blossom'd and white and red!
\\Close on its wave soothes the wave behind,
\\And again another behind, embracing and lapping, every one close,
\\But my love soothes not me, not me.
\\Low hangs the moon, it rose late,
\\It is lagging--O I think it is heavy with love, with love.
\\O madly the sea pushes upon the land.



\chapter{Winchester Airport to Leaside Aerodrome}
Freedom! I cannot bring thee harm,
\\I am too old and scattered,
\\I will venture anywhere, and fear not Sheriff Bombcade.
\\Every strand of hair I win,
\\I am a Jew from Prague,
\\right before I am a Jew,
\\I was a Jew to Mongolia, and one of the few
\\Voices that Vajra to America would ring,
\\and I am American most
\\of all, and though my grandmother told me
\\I should be a Buddhist
\\I made no mistake, did justice
\\to deserve no such dishonor,
\\I deserve no place
\\for I would be a Jewish
\\which is to be accepted as a Jewish
\\challenge--again,
\\the "Jewish" or "Jewish Temple?
\\If they could be both Irish and Welsh
\\we'd hell for us,
\\but if they could be both British
\\I'd hell for us,
\\I'd hell for us,
\\and end up with all ®.
\\"The best of any place is a fairy ring:
\\but ye, not one might come again
\\To the sight of the ball-room, and the lake, and the
\\guess how hard it is to play."
\\So they said to the Doctor, "I'll
\\be neither as saint nor priest,
\\I'll wear a paltry brush and dust,
\\and come not back again."
\\And the Dragon's Tooth
\\went north and south.
\\A coat of the fin-back-rde
\\laid a hand,
\\Counted chips and cents,
\\and the dragon's tooth
\\brought me over.



\chapter{Rivière Saint-Maurice (Aviation Maurice) Water Aerodrome to Brundidge Municipal Airport}
Enormous hour, carrying pure fluidity,
\\Leaving no expert notes to train or otheraphanies,
\\Busy with spirit, fire and democracy,
\\Aviator, physician, priest, oral magician,
\\Whose colleague moonlight is obsidian,
\\Water-lily of the Palatine,
\\Winged breast of Mercury, clothed round with the fossil cumulus:
\\Elegant wing'd earth-born girl,
\\Brilliant as the morning, white as the sea,
\\Visionant as the SKY,
\\Conspiring the night-sky.
\\Water-lily, water-lily,
\\Water-lily,
\\Beyond the coast of Florida,
\\In the cognizance of a man,
\\Old woman, grayheaded,
\\Being faintly audible,
\\Bent her low bow toward the sound of the bell,
\\I jumped down the dark stair of the window.
\\11
\\Two boats moored, lowered and floating,
\\Over the water, white and motionless,
\\Winds dash, dashes, and then true sound,
\\Shells sail, and outward drips,
\\As these boats of theirs hurry by and
\\Are towed away . . . . are driven back by the wind,
\\Are driven back by the wind!
\\Shall I duck my clothes, and call
\\For someone to clean my blouse?
\\What a personal force are you indestructible?
\\I am a woman, and I know my own power!
\\I will do anything to make my heart rebel,
\\Any dream of losing! And I will not come to you
\\Alone, and you are not guilty to me, nor stale nor discarded,
\\I see through the broadcloth and gingham whether or no,
\\And am around, tenacious, acquisitive, tireless, and cannot be shaken away.
\\12



\chapter{Canadian Forces Station Ladner to Juana Azurduy de Padilla International Airport}
En route to the Urugac border,
\\Jet black smoke
\\sucking at the sea,
\\En route to the plaza,
\\Electric sparks
\\starting to glimmer,
\\Carry Nation on the air,
\\Flight passing
\\flushing their wings,
\\Eyes shining like warning.
\\Far away against the blue tiber road,
\\A cinder-block wall where things are started,
\\Womanly boys among,
\\Coinards of money and promissory.
\\Smoke brings the smoke of incense
\\Parched as a cat's mouth.
\\Men riding the sudden tide,
\\Horses in bloom,
\\Strangers coming and going,
\\High-tops surging, rising,
\\Wires tarnished as gold.
\\Children through the glass
\\Rush, leap, and cry,
\\"Play Harry Puzer"
\\Once I learned the names
\\Of flowers and of spells
\\And languages charged with love,
\\I knew why the mutants
\\These men with their needles
\\And their sharpened medallions
\\Made their bodies look like
\\A jongleur's;
\\Alchemy made them
\\Look like prison ships,
\\Pausers and store-boats,
\\Well-mined and dread.
\\To obtain, you know,
\\That that earth has everything,
\\That the sun and the moon
\\Are nothing;
\\That the wildest cannulae
\\Are no man's prisoners;
\\That the kind man the strong
\\Master cannot bear;
\\That the brown bear is shy
\\When the daylight comes;
\\That the pink of the young
\\lean
\\Down in a furrow
\\His look is like the look
\\Of the mad bird,
\\His voice is like the sound
\\Of many waters,
\\Okonee,
\\That the mind of man,
\\As it is,
\\Is a choral voice,
\\Chirping, saying,
\\"Well, ah, well,
\\Every night,
\\Every day,
\\Footstep, and step,
\\Freedom and delight,
\\How it comes."



\chapter{Harrold Airport to Spiritwood Airport}
its tiny wheels
\\bear away second one linoleum
\\sized inugs of cold motheaten
\\some to the very cube line
\\a fat fraction of sky
\\overhang of highway
\\erectile wings
\\twine to the air
\\mottled pine needles
\\planes lie singedown
\\for terrestrial radio
\\own failure
\\of the California Coast
\\regard such unertitude
\\north uplifted
\\look
\\of the cone, I
\\am here
\\doing the magic
\\cmp of a Marshes Eve
\\opening space
\\on a drum
\\solo bench
\\the drum performs
\\an opposite dance
\\patterns
\\play sounds
\\reverse strophe
\\harmony
\\ops
\\upon the drum
\\silence
\\in the cloth
\\floated new
\\by sudden
\\elboredom
\\ballads
\\a memory of dirt
\\verses
\\only the result
\\of
\\a male sweater
\\and the head of a long
\\armadillo
\\composite toward
\\a fuzzy
\\dunic rope
\\the drum sticks
\\by the patterning
\\of a bad
\\ellipture
\\eq. of the wobble
\\and the punch of
\\a blackjack
\\comprehending
\\the arc
\\of the tot
\\my son
\\sometimes
\\lifts
\\by the tempo of
\\a carnival
\\in which as
\\a star on
\\the sky stalks
\\and the clang
\\of metal pieces
\\and manic
\\movements of
\\a charm
\\composed
\\by the craftsman
\\of perfection
\\over
\\a casket
\\of shapes
\\broken
\\in and
\\out of
\\the same
\\number
\\clanging
\\waiting
\\in time
\\for a headache
\\or a fan
\\while the bearers
\\dance
\\and the musicians
\\jack rabbit
\\in a carnival
\\in which
\\the dancing
\\is the losing
\\weight
\\of a suspended
\\conjution
\\in the face
\\of the moon
\\to be
\\drowned
\\as is needed
\\to be
\\passed away
\\from the women
\\dragging her
\\chanting
\\light through
\\the foul air
\\to link together
\\the stars,
\\never.



\chapter{RCAF Station Pearce to Fort St. John/Tompkins Mile 54 Airport}
Tompkins mile 59 jacks up Route 44
\\steaming from the sun
\\to a metal bench
\\the painted line of questioning letters
\\or in the traffic of heaven
\\hell with railroad cars
\\hell with towers
\\and ironstairway
\\westline
\\feather beds
\\abysships
\\hell with trains
\\and Dearie Jaff
\\marching by night
\\herthermometers
\\absolute, dangerous,
\\vulnerable and
\\comfortable withstood
\\by this ambiguous
\\woman with a voice
\\her moving among
\\the browned words
\\and maybe this woman
\\with her dreams
\\can be saved from this
\\human need
\\by not bulldozers
\\and I am not
\\an oily or blasphemous yogin
\\collapsing between
\\freakish and law-suit
\\but at least a difference
\\his being drawn from
\\a slight dog
\\black and white
\\retired to a street
\\where a woman walks
\\with a crown of stars
\\across a brown terrace
\\behind a silent crowd
\\encircled by a tent
\\under a streetlight
\\occupied by grief
\\personified as a man
\\without a history
\\and not happy
\\said the homeless struck
\\off the streets
\\by a cry of unknown cause
\\escaping
\\the drizzling windows
\\and rafters
\\where a flight of birds
\\screamed and
\\asted across the city
\\--rotting statues
\\and
\\a burning engine
\\hot on the word vomit
\\breathing through my
\\sunlight cough
\\my eyes eyeball heavy
\\tenderly
\\and I wash the slate
\\and mix it with yolk
\\stopwatches
\\the floor
\\by foot and breath
\\places between
\\the trees
\\where I am a stranger
\\beneath the evening's
\\misty rug
\\on the thin quilt
\\simply shoveled
\\for the love of a place
\\not in which
\\I understand the insurgival
\\and I know
\\a native force
\\already in the background
\\no longer able to
\\hear
\\the heartbeat of a machine
\\under steam exhaust
\\the tank's steady whir
\\a thin scream
\\around the neck
\\my own voice
\\in a series
\\of measures
\\I understand
\\the structure of how we must
\\learn to delete
\\the things we love
\\What I mean is
\\im RD.



\chapter{Cadotte Airport to Morris Army Airfield}
I lay, and dream'd long
\\of rows of cotton carriages.
\\Dreams are not promise nor threat,
\\and that I could but find
\\a maiden to transport me.
\\I dream'd long, but cannot see where
\\we are.                   we are ditched
\\along with other girls, of course,
\\for a time.                       and put away
\\the binoculars of the horseshoe jog
\\in the sky like rusty magnets.
\\And I will learn to fly a little.
\\The first time I tell you of my fever,
\\it will be too late to ask me how.
\\I sink back into the drunkard's
\\heart, and the float-top hatcake
\\seems Stylish only for kissing.
\\The no-eyes kind of thing,
\\but the eyes of the known.
\\What will I do about the wife,
\\my cruise liner, my mother, or
\\the co-writer I'm having worried
\\to get up right now.
\\I don't mean that much.                    as much as I
\\respect the woman, I'm in a hurry,
\\to get married, probably, some time later.
\\I'm very tired.                    I'm really tired.



\chapter{Nobleton Airport to Glasgow/Renfrew Airport}
Float-tailing docks of clouds,
\\Smoke greyening Gunfs,
\\Dew-hatted beard sullen
\\Polka-hilt and wheel-taps,
\\Avocados-taken
\\Sea-strewngow ills.
\\Dung buses reach the airport
\\Juarez, and ambulances
\\beeline the walls.
\\Border guards screen the trees
\\And a recorder
\\tanks to her training camp
\\sweep and clean.
\\And she trains her trade
\\between a shed and a laundry-press,
\\mineral metals close.
\\In a lagoon, her hands
\\reach out to the chain-link
\\of bars and planes.
\\It's heaven's air,
\\lifted like a mask,
\\and seems to have travelled
\\below
\\the melting borders
\\of the sea.
\\Connecticut Valley
\\newspapers proudly worm-eat
\\for breakfast.
\\So much less than what we have been
\\persuaded to dream, this necessity for wood
\\might have sufficed,
\\but the arms of the jeep
\\hung heavy, a hawthorn
\\in their hands.
\\Now imagine the weight
\\of prime flesh burrowing into the pine,
\\belly tender as a holly,
\\that seed jetosted
\\over the border of a forest
\\made of light, a tender sheep
\\reed up to eat
\\our earth and disappear.
\\Think of this:
\\not your body, not your life,
\\but my body, wasted,
\\little moon, worthless and dark,
\\little yellow lilies
\\flowered around my death.



\chapter{Fall River Municipal Airport to Syracuse Municipal Airport}
The haze of the wintry sun empties the stands
\\of the Empire State Building--to the length of the corridor
\\like a sheet of paper, white and slightly
\\inkless, carefully cut and vague; again
\\disintegrated into the glass-white
\\lagoon--a circular, thick moon?
\\O foreign presences, where are you?
\\Can you come down from the heights, parallel
\\in the front yard with bare foot roads
\\and back floors? Can you come down
\\from the level mouth of the river, please?
\\Can you come up here as the line of theaments
\\in the mind, or the statuettes of diminished time?
\\I'm trying to think of a new connectedness--
\\as a new cluster of bulbs, or a new universe,
\\as the globes and the valleys of a dwarf,
\\and the blackness of beyond deeps--
\\except it's not the planter in the cathedral
\\betwixt the feathery flame and the line,
\\nor the craftsman in his uniform with two pairs
\\of tunkles, nor the architect who designs
\\the windows on the ceiling, nor the
\\merest mongrel with his baldness and a cleft
\\in his right hand, nor the maniac who commits
\\total crimes, is he not more like himself than
\\the harmless neighbor, this man who tries to read
\\on a telegraph wire of the future from a field
\\of other countries, and laughs at them, and is
\\blameless, because he knows he is responsible
\\to everything, but, which is worse, he's caught
\\up in some story I'm not about, but this guy
\\walks down the city, and I think of him often, as I
\\view him walking along, as he's going some
\\mystic march I'm not even sure about, for he's got
\\a picture on his shirt, and I want to dance
\\forever, and what I dream--a present from the boyfriend
\\of a mysterious girl--the picture of her as she's.



\chapter{Five Mile Lake Water Aerodrome to Waterville/Kings County Municipal Airport}
10:15
\\P.M.
\\, May 24
\\4:30
\\P.M.
\\, May 24
\\7:25
\\P.M.
\\, May 3
\\4:30
\\3:30
\\3:35
\\3:45
\\3.37
\\4:39
\\4.40
\\4:40
\\4.42
\\4:40
\\4.38
\\4.39
\\4.80
\\4.82
\\4.85
\\4.90
\\4.90
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77
\\4.77 and 3/1,000
\\Days after notice date on Calendar 29, 1993
\\(University of Buffalo), 1 Oct. 1994
\\End of the Third Gate
\\The Cathedral at Bayeux
\\A bulldozer keeping crops of broccoli
\\Brought up by a farmer's hands
\\Summer after a rain hurtled
\\from the Mediterranean
\\The gold GIANT vans
\\passed for months behind his yellow shook
\\pan of glass windows
\\Hussing up the road for the last
\\El morro tunnel through the black salt dust
\\Hussing up the truck for the next
\\Monument to the Queen Elizabeth
\\The gold and silver and expensive
\\Precise signals on the radio
\\Copy sounds from Sound and Hearing
\\The gold and silver in the light
\\Behind the concrete footprints
\\Into the maximum atmosphere
\\Paumanok
\\To touch the live air
\\To flare
\\To be here.



\chapter{Sault Ste. Marie/Partridge Point Water Aerodrome to Chinchaga Airport}
1.
\\AMETHER TERRIBLE, English, raised streamers,
\\Tantara, city of food, tanned announcer
\\Let us fly then, over water colored
\\By a wave they called "Grand Cayes"
\\2.
\\There there now, directly from the airport,
\\White uniforms of the silent walkers,
\\They walked, carrying heavy meat and water
\\For the vacation meeting of the boatman
\\3.
\\Oh Guillaume, where are you flying over Texas
\\With your crazy blue and green jerseys?
\\Your voyage is yoned up with flags,
\\With territorial symbols, pausing,
\\And the hard features of their onshore radiance,
\\Showed the cold Donald out of Mexico
\\With his big mouth at daybreak
\\And a blond risk-awashy arm!
\\Came back through the tunnel, on your way
\\To the city of the faithful
\\Read here how the army was called
\\To order its columns to stand against a foe!
\\4.
\\Then clanging of wooden wings, and a drum beat,
\\And the golden-red-striped banners were tossed
\\High over the spired cathedral square:
\\Then a solemn prospect lined the view
\\Where the patron saints of the old day
\\Walked joint by pair, and joined in heart.
\\5.
\\'adam! strong child of light!' who calls in vain
\\No nearer than the wake of the soul?
\\Familiar white sails beat between
\\The stately and the fearless miles,
\\And the young fogies watch the Spartan air
\\Here overboard I see:
\\Shouts of cannon! sheep whirr! dray!
\\And the big black cannon cry, and the grey dawns split,
\\And pealed far off shivering below,
\\And the sea tree-tops and the waves cry forth the cry:
\\I am the king!
\\6.
\\King of nations, interminable races,
\\Thy bed, thy water, thy gates, thy royal ceiling,
\\What is thy pity, what is thy fear, so long.



\chapter{Baltimore Airpark to Port Simpson Water Aerodrome}
What a pair of autumn days they were,
\\Snowed hard, blade-to-ball against the base road,
\\Blue and edgy, and the trees thick and tall.
\\Only the grasses showed up
\\Though it was all overgrown plain,
\\And the trees and grasses seemed to be
\\Part of the scenery, part of the grass
\\That was here and that now elsewhere,
\\Irrelevant and irrelevant.
\\Trees once looked down and gave
\\Redness their deep and enemy
\\Problem or excursion, and gave
\\Ability for colored search, more for
\\The open vigor of still farther
\\Planes and planes that dancers adore.
\\The dark can never come as yet
\\To visit it with unwilling eyes.
\\Even the white, the gold, the green
\\Reproachfully rebreathed of deep green,
\\Into the autumn weather, out of a
\\Hibernian parched region,
\\Is temperately trod, an armful of golden
\\Cornelroots, bound together with
\\Bud and blossom. And you mention such things
\\And make them your own.
\\Meaning the gulls as they climb over
\\The low kick of theoretto's chin,
\\The reckless kids on the porpoise,
\\The leaden-eyed covet, forced up at last
\\To give their parents time to play
\\And toemblazon the red letters G
\\Your way of life looks set, YMM
\\Like your teeth, yours a passionate antidote
\\To all the nation's diseases.
\\The past and present wilt--I have
\\No shadow of despair. And I think
\\It will rain out, the full summer
\\Will be amore boring.
\\The future will have
\\No heartbeat, no wings its own.
\\The temperature will go lower.
\\Not just the people, but the way
\\The sentences feel thirsty
\\As the glass in the sky
\\Unfolds and describes something.
\\Let us commit that to our dust.
\\Something will be heard in the next
\\Lest we should look for the sun.



\chapter{Prince George (North Cariboo Air Park) Airport to Twin Pine Airport}
Above the mercury-cased parade
\\Of the adobe-colored bustle
\\Of the aluminum-brushed stanchions,
\\The orange-dust-ravish-overhead-show
\\Of the ruddy chestnut-trees,
\\In low lying snow,
\\Outsmilling in the wind,
\\Found a something there was
\\Something that came from nothing,
\\From darkness and cold,
\\Brimming with tiny lights
\\Like a )
\\To the Colossus
\\Manna,
\\A Monthly of the Past
\\Arriving there in the confused
\\Light that gleams
\\In the fallen leaves,
\\Red berries like ravishing
\\Gold beech leaves,
\\A thief's car.
\\Your light is dull
\\And absent.
\\The land isn't possible.
\\This is what is required,
\\So let's listen.
\\When the alarmed medcrew
\\Looked over the edge
\\And saw, there under them,
\\As though they believed
\\What they knew,
\\That the island and the shore
\\Were portions of the world
\\And lived
\\As if there were only half
\\What they felt and knew
\\And wanted
\\To believe:
\\That half would believe
\\And half would say
\\That half would believe
\\That would believe
\\That would believe.
\\You mean that, now?
\\Not for herself.
\\Not for herself.
\\Sometimes she calls
\\To the boy slaves
\\Whose life is not a choice
\\Between good and ill
\\And none can carry away
\\The house of life.
\\Your faith is still
\\One of many worlds.
\\A little nearer
\\To the bitter end
\\Of that difference.
\\When a pen falls like a log
\\In the water,
\\Is it a house or a boat
\\That won't work?
\\Is a woman's voice
\\Tweling a joke
\\About the farthest hill
\\In a close-packed handwriting
\\To alert the quiet one,
\\The one that lies
\\Next to the dreamers,
\\The one with the manyap
\\Of life and morning
\\Sooking form,
\\A fool, or fool,
\\Or blue as Santa Claus.



\chapter{Washington-Virginia Airport to Powell STOLport}
Because of the stir
\\that shook my tiny toes
\\and downcast arms,
\\because of the heat
\\that clost the air,
\\because of the flight
\\of flights,
\\I'll have no pleasant choices,
\\because of this.
\\So I'll take
\\a shower,
\\and thank you the sky
\\for all that it shows.
\\Because of the homeland
\\brown paper
\\striped red
\\as it's red
\\above a red
\\shape
\\of shell,
\\I don't know what you're
\\thinking.
\\Saw hawks,
\\a bright filter-
\\glass fog,
\\a momentary tremor
\\behind me.
\\Not yet satisfied
\\want a flat seat
\\I'm slowly transforming
\\going the way of the snail
\\in a slow blur
\\trying to turn
\\to go where none lives,
\\no place
\\in which to rest.
\\I know a woman
\\who for herself
\\would be happy
\\while another
\\worked
\\behind her
\\lives.



\chapter{Montréal/Mascouche Airport to Fitzgerald (Fort Smith) Water Aerodrome}
In such deep sleep i lie
\\June boughs shut out the storm;
\\The camp sleeps, the weary night-wind blows
\\No bell from our gate, no star from the west.
\\The shadows lay along broadway,
\\But near the crowds there was a spark,
\\And with a uncanny sound, a sound,
\\A sound of something that has not yet died,
\\A sound of the rushing of a mighty wind,
\\And in the twilight came that cry
\\To the dead men's souls, that like a cry
\\Peemed through the silence of the night;
\\Enveloped no more the garden's flow
\\Than, filled the house of eternity,
\\That cousin support of the below
\\Is what you call paradise,--
\\A cry of joy 'mid the ruins
\\Of the dead, the cradle of the dead.
\\The feet of the fleeing slaves are below
\\The streets where delinquents know them not;
\\The gates of rye who have grown narrow
\\Over the road where the skipper slept.
\\He sleeps too deep, the wire of the swine
\\He swears is gone, where thaw and win
\\And the wild winds drive at the pilot's feet.
\\Child, what are you asking for?
\\Look, sir, there's only another thing
\\We have loved a thousand years,
\\Gone from those shoulders, as the point of his pride,
\\The pride of power, that he was wont to bear,
\\He has left us of that liberty
\\Unto suffrick-age, ripening it by sword and flight,
\\To carry his cry to the world of nations;
\\Up, up, from the house of bondage,
\\The chamber of the dead!
\\God, who didst make and afflict,
\\Vengeance shall on those
\\That keep out evil, and gather them
\\Full of woe;
\\They, the whom the Lord when he commeth,
\\Pray for their souls ere they die:
\\We pray that Thou wilt grant them health,
\\Unfettered health, as from the cross.



\chapter{Lupin Airport to Bristol (Whitchurch) Airport}
Pitchery miles away through the Snow,
\\Over the traffic backed-up taxis and men pushing
\\Half-faired to a broken concrete wall,
\\Like a sick dog, the Empire State's
\\Tree-lined streets,
\\The package roads of the Customs Department
\\Where ducks dance in a sudden sky Flood
\\On the thin tops of the trees.
\\Dragons of light in the downy incubus,
\\Roads heading dead and turned to stones.
\\Pointing toward the sun with bright sparkles,
\\Verging on the insanity of the picture
\\Leaves the stage, and I say nothing.
\\I sing it just as I'm sung
\\In a shop beside the Nazi
\\Boughthouse of Penma, the city
\\Of panic, from the Fireside Inn.
\\For I wouldn't have it. Spock,
\\Prophet, what a synonym
\\Same as being real. I'm Jewish.
\\I'm Jewish. The point is being Jewish.
\\... not standing
\\And being lived, I mean lived.
\\I'm Jewish. The point is being lived.
\\... I know more than I thought-about-me...
\\THE DISMANTLED SHIP
\\In so much plunging sleep, the sea
\\Is a sea of pedophiles. The lodging park
\\A zoo, the gardenelf Q.
\\The sky is a graffiti of the mind.
\\These Jews are real as stone.
\\pecimen smashed on the forest bonfire,
\\Petrarch of the dead. My God,
\\I'm up with the queer community.
\\I'm a participant in the spirit's triumphing.
\\I'm a gay Jewish boy who longs to be
\\The ruler of the world, and I watch my chance
\\To claim the throne. I'll see the world's final
\\Illumination, and there'll see
\\The seal of the great mystery between
\\The grave and the bride.



\chapter{Willowdale Airfield to Oslo Airport, Fornebu}
In the pink sun
\\beneath the banner of the Bruised Armada,
\\floor length of concrete,
\\telephone number of helvo ---
\\alcohol </
\\airgate, gate
\\above the line and a name
\\across a map of the Western Reserve
\\I came for the eclair
\\waving a cigarette
\\endlessly--
\\endlessly!
\\in an insane balance
\\that made me
\\the doom, we all mean,
\\handshakes, untrust.
\\Every hand
\\lifted by the weight of memories
\\borrows from the arms
\\of countless days.
\\Yes,
\\me, all me
\\and the opposite, each
\\woman with a heart
\\of her own.
\\We are stuck in this
\\critical moment
\\the bomb's voice
\\and the fizzle
\\of the street.
\\How can we
\\escape these modes
\\we have begun to assume
\\in our lives?
\\They swallow fire
\\but seek the bottom
\\to hold it up.
\\Legs burn
\\missing the boil;
\\the brains refuse
\\to give way.
\\It is not to be turned
\\that the body
\\can see, it cannot
\\be touched.
\\Disappearance
\\means
\\noEVA
\\; #39
\\one arm
\\is useless;
\\another arm
\\could use some good
\\thermaphrodite
\\or a lot of lancaster.
\\The godchose that didn't
\\move in place
\\was the one who
\\remained in the relative
\\opposite.
\\A judgment
\\had been overdue.
\\If the blouse
\\was forthcoming,
\\the clothesline
\\would be run along,
\\the leather
\\wrapped urgently,
\\the buttons' dry
\\and dangerous.
\\I wouldn't
\\trust a father
\\who wasn't made to kill
\\and who,
\\no matter how,
\\was still,
\\god knows, safe.
\\Then the story
\\of the man who cleaned the house
\\and his daughter
\\and his three old men
\\went east.
\\It was a pretty place,
\\pretty to see,
\\pretty to muscle
\\as you scrabbled to open
\\a tin cup
\\ultrariously, in the heat.



\chapter{Imeson Field to Kahntah Aerodrome}
I want no chants to be;
\\bring no feast or pageant;
\\For my soul is at a shrine,
\\and my heart is pure.
\\The maids of the town
\\kill the little hectic;
\\They tear the yellow lilies
\\from the boughs of traps,
\\And carry them to the heather
\\from the forest.
\\Young men and maidens
\\our soldiers are;
\\Our footmen shall soon be here;
\\our ladies shall walk.
\\And then bear me away
\\to the mountain green
\\Where the brooks of milamah
\\beyond the flow
\\Of the gray and misty atlantic
\\are rush and roar.
\\There by the milford water
\\young men and maidens may drink,
\\But of a wrath unknown
\\no living thing can know.
\\Tell me, in what deep recess
\\the winds and the waves!--
\\Or first, how the great waters
\\thought of her;
\\Beneath what sand and water
\\gardens and towers;
\\White drift spooning into the sea,
\\white water rippling on board,
\\And the passengers sleep.
\\The stack of the boat is white,
\\and silent up and down,
\\And up and down the river
\\the ripple soothes the otter,
\\The wolverine, and the elk,
\\and the noise of the sea.
\\Hark, the rice-fed men!
\\Hark the rude nets galopred in
\\with the hay of the reindeer!
\\The casts of the women,
\\and the curvilies and the pies,
\\Are calculated as the play
\\of the symbolic imagination,
\\And the men's previews
\\are surrendered to the queen.
\\For pearls, jewels, and chains,
\\Premium box and petal,
\\for the ensigns and the coins,
\\Are privately owned,
\\and so may be written to us,
\\For our tita is alive,
\\and a new nymph is born.
\\In a wood, beneath a tree,
\\Forth stands a expectant forest,
\\that nymphs and beasts do prey:
\\Night from the black oaks.



\chapter{Twin Pine Airport to Opa-locka West Airport}
By the pale electric tide I sat in the stripped sand
\\Divide the openway
\\Into the afternoon's rush and whirring metal bed
\\I heard the planes roar and started to pray
\\I knew the planes were coming apart
\\How beautiful a wonderful difference
\\There was simply it
\\The sky was blue and the sky was blue
\\In a blue weekend hat
\\I stood on the middle of the road
\\Footed blue Sorrel.
\\It was the last of summer
\\The turf turned green and the sunlight deep
\\Continued caring
\\While the solemn old-fashioned fly-home
\\Of anxious men was being born again
\\It was the end of August
\\The ground was changed
\\And the dry pillows of the shore were lifted
\\Again to the city
\\Forever I saw men driving their cars
\\High above the trees
\\Letting the leaves fall on their neck
\\And the smoke from the marginal
\\Building towers untangled
\\And the narrowness of the bridges
\\Coming together
\\All into the open air
\\Till the ceiling fans flutter
\\And the fire consumes the faucets.



\chapter{Charlestown NAAS to Fort Providence Water Aerodrome}
I lift my back into the clear music
\\deep in the sky,
\\from the cave on the hill
\\where horses graze
\\on the runaways,
\\to the beach, boys,
\\where the people wait,
\\Bimbis and I,
\\through the stripping ladders,
\\trying to make a last call.
\\The island's dark,
\\scalding voices,
\\the island's stone,
\\the highway's device,
\\the castle's vision,
\\the flock's desire,
\\the wind's cadence,
\\The sun's descent,
\\all earth's flaws.
\\I remember my own nameless
\\chaos,
\\when I stopped to drink some wine.
\\From my own bowels I see
\\the descendants of the poor
\\then lifted up their faces
\\and to the banner told
\\to give this place a name.
\\Here's a health to the gentleman
\\whose cottage still
\\is built on the grounds
\\of a former slave settlement
\\and of the views views distant
\\from the ancient town,
\\high high and low.
\\To the land about which the river
\\channels through the skabian,
\\bitter and cold,
\\is often given a fine seat
\\to analyze
\\what went on in the soldier
\\suit for a final time
\\along the dusky road
\\in the muses' place.
\\Ducks! whose faces are grey
\\and cold,
\\such as the shateless caffolds
\\and the harmless mountain-cats,
\\down which the parade
\\lanes so stealthily,
\\out of the ruins
\\beneath the silence of the day.
\\The flowers, like frightened rats,
\\snuggle and douse and stink,
\\and the birds make no sound.
\\All the earth is silent
\\because the abandoned store
\\has gone to sleep
\\and the lot's deserted once more.
\\No story to tell, and no light to sing;
\\it's all gone as I have already disappeared.
\\And the hills are tier scarred
\\with a distant distance blood-red.
\\Near the treetops where I made love.



\chapter{Maple Airport to Abu Dhabi/Al Bateen}
Smog trucks downthroat the Air terminal, yellow
\\airplane moving between lony buildings.
\\No travellers, looking for worlds of green and orange
\\cliff blocks of Motels, broken cams, smokestacks
\\of coal hauled-up from underground
\\dyings.
\\The Golden Door Line between World Powers/World privilege
\\and World Cities.
\\Alectronogo's iron girders, Brazil's take-off pose,
\\early-1955.
\\The routine course, major depression, low-keyed farm life
\\punctuing the shelves with swag and rumble,
\\the high-school backwardness of ancient buildings,
\\the slideshow of state grants, all the salary-slapped homicides
\\of the great powers.
\\Carl: It's a real damp cold, this year. We just invented
\\new tires, the engine that cuts me down.
\\Time is a kind of funny job.
\\Marina, the scientist, who lives in the basement
\\of the Lunenburg, near the
\\Kermdenhahn Gate
\\in Nottingham, and has menstrual blood that mends
\\my spine, makes me gawk at the world,
\\tis a big goose.
\\Once I heard girls singing a May Day song;
\\they sang hydris and English cheerily against the men
\\who drove them home.
\\I was sorry that I was born in a labley age
\\and didn't know what equality means.
\\I am the child the needle dances to,
\\the only child laughs
\\for his peers, the boys celebrate their dads.
\\I will kill you or I will pop you in the sea.
\\Look: we're coming towards each other now!
\\There is a tapping on the door, one welcomes another
\\essentially indistinguishable from the one who sees you
\\as you are.
\\That's how it is with the pre-personae of the children,
\\with the watch and the door and the wet towels
\\speak the truth into my ears.
\\I have not disappeared.
\\My wife lifts a finger
\\to that line of time and water.



\chapter{Hershey Airpark to Dawson City Water Aerodrome}
I'm not somewhere else but I like the way the shadows fall
\\Auto-boat, boat country, gym teacher's town,
\\The rings of hermetic medicine exploding
\\Between her arms, musical,
\\On the long Way, all the way to Dawson.
\\I like the diamond necklaces OK on the Videos.
\\I like the flashy flats, the swimming pools that freeen
\\Sabergers and fire dancers. I like his moustache
\\And his body truck, his lean, alert legs.
\\I like his friend, his chest like a musical
\\Perfect Pancake, his body like a streak
\\Of fluff, his voice lighter than a button
\\Of hair. I like his shoes. Big ones, like disco boots,
\\Look like pants of file cabinets, ball-
\\Electrical appliance stuff. What else is he
\\Level? He level some distances with his plectrum
\\Academy School of Disembodied Poetics, and before
\\He starts town, the body is level. In winning,
\\He's already neck-
\\Chanted in the Tavern
\\Makes love. And within Schwartz the boy
\\Is every question kept in place.
\\What was he again? We led him over
\\To the woods with the fog filling in
\\Like a high waterfall in a POV.
\\"Odys"--he smiles
\\A flood of oysters in the water,
\\Smoke plumed up from the area's trash.
\\We have all caught the current sweep
\\Of the road that runs off the farm
\\And he comes for the lake.
\\No one has ever seen it.
\\It's been coming down all night.
\\You can hear it though, a resonant
\\Probing for a memory.
\\And I can listen,
\\Breathe, full of fact,
\\To the infallible cast
\\Of the farmer's winds
\\That show you how they went.
\\When the winds were born at dawn,
\\When the birds were in the kindergarden,
\\When they were in a chill
\\That brought a chipmunk.



\chapter{Hartwood Airport to Palmyra Atoll Airfield}
HAD
\\before I'll be there, space enough to see!
\\(This, space, is enough.)
\\Some say I've heard call:
\\911.
\\The giant Russian flag is huge.
\\At Omaha, little blue steamboats
\\perch in the windows; they're as big as
\\scaffold around a body of water.
\\At San Francisco, the subway,
\\25 years ago, Bell's cousin
\\avoided my mother's safe side by heart
\\because the way she looked,
\\she was always grabbed one other girl
\\and needed another.
\\Here in America, looking for your fair skin,
\\drop the Boom! you're a fucking
\\bum) I used to look at you
\\and you got me,
\\in that same room, save for the floor,
\\the ganja that started me,
\\the YELLOW PERIL OF YOUR PLACE.
\\The world is as we see it?
\\Daubing out in lights,
\\sleeping in public places.
\\The mighty criminal world,
\\Pandora's world, Unseen Cosmos
\\Noise,
\\Bubbling at trillion feet,
\\starveling at the void--
\\Shrouded mammoth veined
\\to save nature,
\\The whole planet's in
\\the way you bend it--
\\The whole house
\\model doubt and fear,
\\half Queen,
\\half gray,
\\or smokey,
\\or light and
\\or moviest,
\\was Pluto,
\\The Greek's crew
\\derived from
\\Ennius,
\\the son of Io,
\\Assumed the nameless
\\woman of the
\\Grecian boat.
\\Unmarried,
\\with a moderate
\\boasting of the seriously
\\understanding nucleus,
\\the cell of death
\\Gradually encircled
\\by the progeny
\\of the same god,
\\the group
\\Of the Goddesses
\\Harveslled by
\\the desire of
\\Caeneus and
\\the royal
\\Mars,
\\whose breasts
\\The asphodel.



\chapter{Tok Airport to Timmins/Porcupine Lake Water Aerodrome}
White fog-brushline over Mosakovsky Reservoir's blue sky
\\--Heaven breath, clouds of black smoke from Boeing's blackened
\\fuselage rolled toward Pennsylvania Union Steel
\\Factory clock ringingly creaking
\\Whole houses' windows book-cluttered,
\\state house lines hammered into green E. 25th Street
\\Where are the President's Armies of Gold?
\\The American Century
\\Fallen under this bomb
\\Whose words say:
\\Demented uranium must be kept
\\keep together.
\\December 11, 1965.



\chapter{Cowpar Airport to Haynesville Airport}
American and American, whistling this far
\\away, is not your way of life, that of
\\the sniffing dog, the cocktailed jackrabbits,
\\each kerfuffle between ex-chantric bombast and
\\stinking bombast, still tethered to your
\\chins and bearers. In the eyeglasses where
\\you flip back your nose and taste the
\\smell of the fuzz, you feel the swaying
\\valley of muscles
\\under the skull's
\\raw splay, grinding: your own galley's
\\loose sides, at the
\\costof steelwork,
\\drill pressing her nose
\\against the glass
\\floor, hand off
\\hanging out the sooty
\\scream. I don't know
\\what you're thinking. Me,
\\who only wished to be here, whose instead
\\you're here and are nowhere, are hardly
\\anybody's longer
\\and fit the same. If not you were the man
\\who stepped out of the meeting
\\eternal of the ghost
\\who came to stay. You don't know
\\what happened to the L-Men of Northboro
\\who shot stone
\\glancing down at each other
\\out of the window, nothing
\\to see now but the tarmac
\\where the bodies that were never
\\neither married, never lived,
\\and the girls who did not wear
\\their bellies all up gain.



\chapter{CFB Summerside to Quartz Hill Airport}
Take one last look at the sunfish on the river
\\Make eye a-vismos' you can't see it anywhere,
\\it is the kind of thing
\\They call happy, Dust-free, and dry.
\\Don't tell me, I'm too tired,
\\I want to lie down some more.
\\Totem's uncoiled and chill,
\\Hot-headed am I, so am no bawd,
\\The dried seed's got to be luck.
\\And I'm like the sky serene and cold,
\\And I'm like the clouds flying too,
\\and the water's too full of fear.
\\Under there you see a gas that again
\\Would fill you full unless you let me catch it.
\\I'll know then, based on what I know,
\\I'd like to be Lilani again.
\\I'd be too shy to say anything but I'd
\\like to be Lilani again.
\\And I would, because I'm not sure that god is good,
\\And have too much regrets for to think about this;
\\So I'd go and build some shop, and I'd say,
\\"The clothes they sell are better than the clothes they wear,"
\\And I'd say, "The clothes they sell" and we'd call
\\The fine-man-back who fits with clients.
\\Most of the people do not laugh at me,
\\Most of the people make applause for me,
\\Yet I don't laugh at all the writing I've written
\\And remember when I wrote it was because
\\I looked at it and I wanted to laugh.
\\That's never possible, is it because
\\I look at and that's entitled to be written?
\\So I stand back; I hear the voice of the professor:
\\"Congratulations! Because the winner here has proven courageous."
\\So I'm still trying to trick him: calling "The sinner thee!
\\"Thou haven't no shirt, thou's so poor!"



\chapter{Fair Haven Municipal Airport to Eldora Municipal Airport}
Dark wing'd somewhere upon the airplane path,
\\No face moving over dark water,
\\Clouds float and drop.
\\A Boeing plane bends over the edge of the sun
\\And through the dark plane
\\Air passengers flee from the UFO
\\To safer seats.
\\Oralplane touching the green blizzards
\\Off Twin Towers Hot Farms' aisles,
\\NGASSK's
\\"The number of the aircraft elements."
\\A thin American blue shows the city
\\hatter prone in fire
\\Dr. Louis Elm's Manhattan
\\Hand overcoat fuse brimmed with
\\shot sky,
\\Gold foam emerald back to the brain
\\Black smoke and chrome extensions
\\of the wing buckle.
\\CONSTRUCTION
\\tall, white, windy white
\\beech grove
\\over the Jewell,
\\out of space
\\dwells bird
\\brain
\\shy speaking
\\back and forth
\\with him
\\on the shore
\\of old Sojin-Okizaki River
\\Fine white clouds, perfectly
\\viewless under gray sky
\\above the wave
\\dread of man
\\on the bushy plain
\\greets me makoto
\\shining
\\a dream white
\\drifter
\\upon the down
\\downpour
\\on the platform
\\of the bushy plain
\\ihkooda
\\on the down
\\in the harbor
\\of the pearl
\\beach
\\from the bonnie
\\shed!
\\Ten years
\\to get the gold
\\in postage
\\tracked free
\\in the slim
\\coil of the last
\\known hour of the day
\\druid
\\dinners without
\\water
\\Two years
\\till the brave baby
\\bleed
\\and died
\\yard bird
\\jazz
\\diamond
\\sett
\\sleep
\\char
\\je
\\an
\\an
\\fire
\\char
\\d
\\e
\\stage
\\us
\\son
\\come
\\with me
\\awake
\\body
\\generated
\\on the field
\\of midnight
\\sea-pink
\\tan
\\for work
\\room
\\for defeat
\\ful.
\\the down
\\against the furniture
\\the barn
\\the jar
\\by the window
\\the ache
\\in the broccoli
\\mesh.



\chapter{CFB St. Hubert to Aguanish Water Aerodrome}
i.  July 8
\\There is a pot of heat in the valley
\\Shading the livestock against danger
\\Ratcheting the raw woods
\\to salt the floors of the forest
\\Lights the moon through the branches
\\Starting the cotton plant
\\Mangos and elephants
\\Sold to the cotton gin
\\Mangos revving their tails
\\The tree-lined streets shake
\\And a collision occurs
\\The tree-lined streets go raucous
\\A brawl turns
\\The water pours
\\In the clothes of the children
\\A clash occurs
\\The log hoes
\\Drive all the leaves to the ducks
\\A clash occurs
\\The cotton plant
\\Goes to the Niger
\\Mangos and elephants
\\Are caught in the rice
\\Just like what happens
\\When you lived there
\\Is a smell of scalding pork
\\The railroad cars roar
\\The locomotive kicks
\\And the blood and the turf
\\Mingle with the wet hair
\\In the corners of the seats
\\And the crowd blows your black
\\Coals out of the cedar chips
\\Is it true the stars are old
\\When they are young
\\There are the spaces between the children
\\Do they step on the black water
\\Mosques of desire and knowledge
\\The locomotives trembling
\\In the desert
\\Birds twitter Atlantis
\\In the air
\\Just can't go on
\\And the train
\\Is that big broken river
\\Look, the train
\\Is that big broken river
\\I walk on, it follows
\\The water
\\White flock bird
\\Texhered birds
\\Far and away.



\chapter{Atarot Airport to Warren/Woodlands Airport}
Black planes with names like MOMETAL
\\by the billboard, and I am waiting
\\for the Air Train and the Woodlawn
\\museum to take me back to my American
\\dream of revolution. I'm waiting
\\for the Army to come and arrest me
\\for I evoked the King's voice two decades
\\ago, screaming outside the Statehouse
\\I burned the Xanthus, drank rosewater,
\\sat down with shark-teeth hungry
\\for the green meat of Beatrice,
\\and soon afterward I was convinced
\\I would describe what I saw into
\\in a man's mouth like a knife.
\\Color and fear are two elements
\\when it comes down to it.
\\I saw a great blue city once
\\and stayed, then came back to it
\\and saw another, and another,
\\and then a little town;
\\and then I could see a city;
\\then six men killer-preachers
\\using eyes like maple trees
\\watched the sunrise and the sea;
\\I was amazed and turned away
\\from all that darkness staring
\\at dry blown leaves rattling in the wind.
\\Still a city! But from a city
\\you knew, and one you didn't,
\\and oh, it's gone, my own it's gone,
\\away lost to a noise of loneliness and fear.
\\I don't know why the poet has slowed
\\to listen to himself, or
\\failed to let himself go.
\\He's waking up this morning with the need
\\to be detached from any history,
\\to stand here with a stranger.
\\Mostly the need to be apart,
\\to be whole, to be
\\a separate person.
\\Efficiently done,
\\it has become, for any unknown reason,
\\a favorite task of the
\\moon.



\chapter{Kunming Wujiaba International Airport to Gainsborough Airport}
Flight of morn, man still hungry after shave,
\\rice-fruit flies like a plane-leaf; small snow-blossoms
\\rest on the sharp white tablecloth of the baggage-train.
\\I always remember the dark connected sheet,
\\a purple that breaks through the water
\\and travels all the way to the gate. What is this sign?
\\Assistant bonnily tells me the customs are foreign,
\\but maybe we could call them collars in oil,
\\or else they're sugar tigers. This is straight
\\in, and I wonder
\\if they're dogs that haven't a human nature,
\\but are slavering and causeless, are driven
\\to the point of being less than helpless,
\\and though they sign something offensive,
\\it isn't their position
\\that makes the world go round. It's my cravings
\\that driven the violence of your disproportion.
\\What is my love for plank sheets that stir men
\\with desire? I love you so clearly.
\\I can't share your view of the opium store
\\or your view of the counter culture,
\\but I want to take you inside and out
\\of my life. I can't spill back
\\the agony of inner cruelty,
\\the thousand burnishes closed overhead,
\\the clay of brick and mortar,
\\dissolving into the transparency
\\of flame. I am good
\\for you, for your sake!
\\VII.
\\When the lamps come on at night
\\they burn the windows shut.
\\The light flashes across the floor
\\like a spectral over-arranged
\\activation of something
\\outside which is and is not.
\\I think of the way our dreams invent
\\this darkness. I think of the house
\\Haunted by the ghost of you and me.
\\In the dreams, I was a familiar man.
\\I was asleep by the time you call
\\and the phone hangs on the flighted shelf.
\\Is that you again?
\\The flutter of a coat caught in a shower
\\the clash of knotels in a pot.
\\Auld Saul not sure?
\\Dare I know you?
\\Your cousin's visiting.



\chapter{Cowpar Airport to Eastend Airport}
Crowded in, if alone, the airport can,
\\Sitting like a bookcase, offered us a small
\\map, and we, whose further parts
\\Were uncomplicated, were given room
\\To see how they mob this place.
\\Particulars! The whole town,
\\Driving its way through this town,
\\Leaving money to certain Friends
\\To buy tangerines, lavender coffee,
\\And so to stay one day, open-mouthed,
\\Till our own cottages arrived
\\(Six women, five raw Communion)
\\In their longhaired, crimeekin,
\\Caravan pit-a-pat:
\\Gamelyn chugs a cup
\\Off the immaculate grill,
\\Corroded flats beneath
\\The clatter of the tray,
\\And hears the tell-tale
\\Voice of "John Quincy Adams"
\\The hero-worshipper gets mixed up
\\Story
\\While whiskey
\\Waits for the miss-
\\Loading band;
\\Marybeth says, Hugh
\\Nameeth not
\\The places
\\Builds up the city
\\For prayer?
\\The bells come down in the markedly
\\New Yorker sky
\\To the land of the cow.
\\Bones in the earth;
\\Rodos calle Cancerbero
\\In a much-mouthed air,
\\Unguarded ones
\\Moved by the drag
\\Of the heavy baskets
\\Are not prepossessed.
\\They are balkyold,
\\Wrong and obscure.
\\Let us bless them
\\And their scrambled eggs
\\And their bogus eggs
\\And their big bronze
\\On the roads.
\\These are the towns
\\That they do not tell us
\\About what they do.
\\Jars of wishing
\\Is not all,
\\They are the horns
\\On the wind.
\\Birds make poor role
\\For the bronze lion,
\\Eyes and eyes
\\Of the ideal
\\Unification
\\Of the commons
\\Unification of the villas
\\Bearing the copper
\\Balances of air
\\And of the stalls
\\An ideal
\\Is a thing
\\In themselves
\\For the sake
\\Of something different
\\From themselves.



\chapter{RCAF Station High River to Katowice-Muchowiec Airport}
Toward evening, only one ray of the moon-Starving
\\Soldiers gathered in old Saigon, their sentences
\\Saying:
\\We are from the North Vietnamese.
\\Generations believe in it and, too, the Indochinese.
\\Bamboo trees cover the poles
\\For the explorer, who arrived there by hopping.
\\One must have a deep belief
\\In things that can't be categorized.
\\That there is a separate category of Man
\\Caught in the middle of the conservationist conservationist
\\feeding his flock through a shade.
\\It's not thinking that they are all
\\Voices, but they are, and future words, not
\\Just syllables--Streams and mountains and grasses
\\Making a stillier sound.
\\Still, they are multiform.
\\The comb is just touched with
\\Calmness from the indigested food,
\\The comb is watched with impartiality.
\\Nonetheless, the incident memorial is
\\Performed
\\As if to say:
\\This is the conductor of the game.
\\The bell is tolling
\\And the whisperings of the sea,
\\Coming back, as the Hallelujahs do,
\\Make last night more calmer than the previous
\\Loud chants, less violent, less cold.
\\OWL'S CLOVER
\\Suffer me not to live forever,
\\Suffer me to continue dancing under the eternal sky,
\\Crawl back into my childhood routine,
\\Remembering this world
\\What it was
\\Then when I was a boy
\\So lonely had fallen down to lie awake on my bed
\\I have had a feeling for him lately
\\And it upsets me
\\With me indeed
\\To think of him
\\As having just returned from a place where he had never been.
\\His face, his voice, reduced to the size of a pig,
\\Grown grim.
\\A hand passes over his shoulder,
\\Honey-yellow, tragic-white,
\\And he drinks rapidly,
\\He catches the mirror:
\\A vital emotion lights then.



\chapter{Buttress, Saskatchewan to Calais–Dunkerque Airport}
A leatherman, who for a moment strangled
\\his brother, took the long way back
\\through the river to a mud pathbranch, and when
\\he looked up from his snowed dream, where he usually
\\turns to search for someone to wrestle with,
\\he knelt to help his brother's father
\\up the steel drum wrote
\\down the road; and yet nobody could
\\hear the cries of his people, nor close
\\the door--they
\\were
\\the flight path; concentration fatigue;
\\ear looped outside and iron
\\castings tested the endurance of
\\experts, their
\\subjects, whom he meditated,
\\unable to see the peacocks.
\\He wondered how
\\they were connected to this tree,
\\whose roots from above
\\kept the earth's
\\memorials in their memory.



\chapter{Naval Air Station South Weymouth to Dorset/Kawagama Lake (Old Mill Marina) Water Aerodrome}
White fog drifts thru Bayonne's shallow waters.
\\Beneath broad brushy ridges, water-edged,
\\The luminous mountains waze and bend above,
\\Starting represent the shoulder of a guard.
\\While this white cascade thunders,
\\The white camp-fires breathe a whiff of deadly air,
\\And Raven's hounds have heard the distant, resonant din,
\\And from the corner window, high in the air,
\\Using their binoculars, they have seen the dark waver,
\\And heard the screams of the murdered.
\\Oh, on that dark road, where the wheelbarrow
\\Hauls what was once the road of armies,
\\The horses serve as hunks of stone
\\In the hands of the kings of asia,
\\Stands on the rampart, and the cannon's roar
\\Makes a book of music graven there.
\\Birds twitter pandemoniums around
\\The idea of flight, of those tattered feathers
\\That hike and roll to earth, and high
\\On the huge pad of life, they live:
\\Even in the alien cathedral
\\They laugh, they sing, they dance, and they speak.
\\But their habitations, what they call
\\Elsewhere, are things not seen by such travelers.
\\For what is carried and reborn again
\\Is no more than what was once the world,
\\But is neither world, nor Fitful Dweller
\\In a fixed point of aweary truth.
\\My Castilian poet has brooded
\\Upon the sea, and his serene voice
\\Makes my life within my heart to joy.
\\I know no more the Kleenex, my silver lyre,
\\Mychambeau, my moon, my very moon.
\\I know no more of magic powers
\\Deeply beyond the pores of hell,
\\But there is one thing that I know:
\\I find myself beneath a ragged tree,
\\And know myself and know my soul
\\In the perpetual smile of the sea.
\\There is no change near me,
\\There is no change where I live now.



\chapter{War Eagle Field to Lac Gobeil Water Aerodrome}
I returned to France for summersale gifts and trees
\\branches and birds. AT night I heard wind break the bottles from every house
\\and bottles plopped almost to the ground.
\\On the edge of mountains overpass mountains into scrub
\\dry sand streams streaming down canals
\\carrying wind syrup over lower slopes.
\\In a small city with many jobs, I was undone.
\\I returned to France.
\\Ask of the orators and mediamen who makes the ape,
\\and turn them out.
\\Perhaps I will remain in the country until winter once more.
\\Nothing changes with the fauna. No temperature,
\\no weathers.
\\moth-fire, moon-shine, snow-rush so cold is, icy.
\\The same my mother told me true.
\\No one knows the exact spot it may take to start
\\the child. That child still in the pasture.
\\You meet him in the beginning as well as in the end,
\\as sometimes you meet them after the harvest,
\\as sometimes you meet them after you leave,
\\as sometimes you go back from a fruit-grove
\\to hear the voices of the birds on the verge of morn.
\\Advertisers want to make money.
\\They go with psychology and so create a sort of
\\self-talk.
\\It's a matter of cost.
\\You might have known, if you had been
\\past their pause, they might have meant you
\\for something, ever since the last August.
\\You might have known the weather as being very
\\conventional, had they made it happen.
\\It was more than anything else
\\to be afraid of change.
\\You'd have seen something about what you wanted
\\to see.
\\There's something going on.
\\He's talking about trees,
\\and the way they stand up and walk
\\on the ground underwater,
\\the way they stand up and walk
\\to the model of a boat
\\and know the outcome from the moment they
\\make it;
\\as if this is an image of him.
\\You'd have not been forgiven
\\if you didn't know better.



\chapter{Kai Tak Airport to Gowganda/Gowganda Lake Water Aerodrome}
I drove through the young dark one day and still behaved
\\through the night with my own two eyes
\\instead of studying The Illiad
\\To find the flight path to flight
\\Twenty centuries hence.
\\Today I'm not ashamed that I don't know what I'm called
\\by my own mouth.
\\I used to roam o'er the hills and dales of Yamokoro
\\Hamlet and Zama, cities I've never seen
\\and a good place to live.
\\Before I'd ever leave the country
\\I started loving foreigners.
\\My Chiang Ch'e loved those very long ago,
\\or so I said.
\\I've been staying here all these years
\\at my aunt's favorite haunt,
\\And I've seen the stuff that goes on
\\around the coffee table and out of the window,
\\forgettable O,
\\as if there's a fig tree that ought to be
\\stored up with treasure,
\\and I could tell you what you would find
\\if you could understand the desert place
\\Cayun, Cayman, or Charleston
\\was in the mountains,
\\Probably the Powder-wah-tong,
\\probably the Paumanok sound.
\\My father seemed to float in the head
\\of the boat in the twilight.
\\He seemed to be tempted to climb the sound
\\of the river, his voice reduced
\\to a sad sound by the sound.
\\I again was guessing about the dry river.
\\I thought he'd be in there again.
\\When he did appear at the door,
\\the tree moved closer to my face.
\\He said to my father:
\\"Look past what you want to see."
\\My father said: "You don't want to see anything.



\chapter{Bean Blossom Airport to Ishigaki Airport}
I         Want to visit a country like this one?
\\Is there a lot of yellow in Manhattan?
\\A little green in Vermont?
\\On the US road between Vermont and Connecticut
\\The green grass grows
\\Fast as the spaghetti and meat of a longtable
\\BBQ
\\Ira he is painting theums
\\The office building is burning down
\\We can't get any of the Egyptian statues
\\We can't get any of the vocabulary of Nostalgia
\\Extended over the world
\\Just like the colours are changed
\\And the way is false
\\We need a new language
\\A new world to be created
\\The beautiful adjutant is attitude
\\The easiest way to become a fairy
\\The deadliest way to be a pirate
\\I am very hungry
\\I live with a metre
\\And a friend
\\I live with a metre
\\And the learning of love is read
\\Deeper in the breast than the funny music
\\The mould in the grass is thicker than the words
\\That it is painted half a line for
\\As if I found a new tongue
\\And it had no use for me
\\O that I could only write
\\And it has done a good
\\I would be a messenger
\\For the last time
\\I'd be a messenger
\\For the last time



\chapter{Love County Airport to New Lowell Airport}
I love County
\\Adminstration of the State
\\smoggy or bright
\\radiant airline glinting
\\on terminal roofs winking
\\grand swansy skies
\\above our heads
\\in a concave shell.
\\Love County
\\apartmenty cornwy and
\\lumpy strips of highway
\\with orchards pleading
\\for miles
\\over hills
\\east of ourselves
\\beyond the range
\\of the Border
\\where the old man's still alive
\\who loosed the bomb
\\killed the poppy
\\in a field near Grandpa's
\\patterson
\\and I am thinking
\\of how I could get better
\\and no one would
\\hear me or go away
\\without hearing
\\the warnings
\\like winners
\\of matches, songs
\\against the killer who
\\jumps from the starboard window
\\of the exterior the bomb
\\against that other woman
\\on the bench
\\in the dark, who is trying
\\to get me to hear her
\\no matter what I say
\\against the time
\\that is also past
\\but I am still counting
\\and the baby
\\sings in the breast
\\of the bassarid
\\in those words
\\antisalinas
\\against the muted heat
\\between the leaves
\\to the leaves
\\shining under the light
\\I am not antioch
\\I am
\\a refugee
\\stretched out
\\on the bench
\\like a cat
\\slaughtered
\\to save its reputation
\\but the Buffalo
\\nunc has not burned
\\the cavitation
\\of that light
\\ere it flies
\\down the sky
\\a blethering
\\sound
\\a not unearthly
\\growth that requires more
\\than the plant
\\lives!
\\In a minute
\\the wing of a nuthail
\\saw
\\the whole order
\\of the world
\\shrink .
\\just as
\\a vein
\\of metal
\\had been hurt
\\and taken
\\the course
\\of a dwarf
\\man
\\whose death
\\at twenty-one
\\was due
\\only to a brain-flickered
\\inflated one-
\\by one
\\by one
\\but
\\who,
\\no matter how,
\\is no longer
\\a little stream
\\mines
\\slipped
\\out of
\\the fragile
\\skin of
\\a girling
\\skeleton
\\and of the themselves
\\entered, themselves
\\to be filled
\\with something they
\\needed.



\chapter{Weeks Field to Hawarden Municipal Airport}
I charge myself with lies of two weeks' past,
\\Quiet, and quite quiet, and most wantonly,
\\Above the flying hours, the perilous night-wind,
\\And eke the tied knots at the top of the machine.
\\I could never, never see the sun,
\\Keep us needing so many prayers for days.
\\We've lost our homes and farms and parks;
\\How can we go anywhere, really,
\\After a sense of the sea,
\\And a shiver down the mountains steep?
\\Half my life is beside the sea,
\\But the rest is filled with rest and home.
\\Oh, brown old bug is dead,
\\Dead as my father's favorite word,
\\The servant with the stick, who did unsee
\\That the tank was filled, and was on the leaking pipe.
\\Today a wild wind, a care of the soul,
\\Lagoes' kindly humourists.
\\I see you, see you, the affectionate emigrant,
\\The salvageess, the well-teaspied hostler,
\\The tapulous, Ionian, the cynical,
\\Who adapted his life to art.
\\These are the days that must perish,
\\These are the days that must degenerate,
\\Where none may aspire to have what we have not.
\\Plagued by the intellect, by the strange and direct,
\\Hung rogue-quavers over janeying streams,
\\I follow harry.
\\Father, grandfather, here are my thoughts,
\\Clearly, strongly, within my bosom.
\\He is not proud and makes no show of pride;
\\Nor is he capable of foolish thoughts.
\\Not able to keep good friends forever.



\chapter{Broadus Airport to Earlville Airport}
Rainy, misty, unsettled is the terrain;
\\Winds of winter wiped the unsleeping city,
\\Still, for many an hour, the west-bred people
\\Wander'd;
\\The shaded churches and the shuddering factories
\\Now rose into the air into foggy skies,
\\In vain the wigwam trembled and stood aghast;
\\Tho' all the people were gathered in unity,
\\There was feeling of communion in the atmosphere.
\\Young men, who for a moment flitted from the telegraph wire,
\\Panoramas were put on mental blocks,
\\With loads of teetering paraphernalia to make them
\\One knew not which side to urn and sepulchre;
\\Allah, once a lanthorn, its bursting blossoms unclose,
\\Lies in its garden, while unused fires they burn,
\\And a morbid leadenness on earth remains for them.
\\Nor is that uniform all-resistless hunger of the heart
\\That makes its own nature her slave?
\\Nay, but the same imperious, ever-welcome war, the same
\\Death and torture, that both ends are gaining,
\\Though mind knows not which is agony, what pain...
\\This gentle coinage graced
\\With edible cavities is my present pain,
\\My past self's too eager to beginle again...
\\Therefore trust, sir, my trust is true;
\\And for yours yet to-day i give my heart,
\\Hopefully to-morrow i give mine back.



\chapter{Squaw Rapids Airport to Peggo Devon Canada Aerodrome}
Into the stripped car the thunder storms come:
\\A spring of mud.
\\Too much is gone
\\into the street;
\\too much to eat.
\\Dot bags and sticks of
\\broken sticks like war against insects,
\\against the left wall
\\of roof.
\\The precipice in the glass,
\\a prickly otter
\\snapping its jaws
\\on double points.
\\Nothing to do but to look.
\\We chase the fly, of course,
\\around the gum wrapper
\\and the pale loose
\\sandmeal worm jacket
\\who fly and fall.
\\We ground our bare fingers
\\among the razorbladed
\\wire antennas
\\hissing their achors
\\at the end of our lives.
\\What are we afraid of?
\\We look at our strings,
\\what moves in the head of the
\\bridal--
\\a pale light on a pot
\\melting on the tongue of
\\a child:
\\a poultice
\\a scar on my left hand.
\\And I was afraid of
\\feeding my young hair to the TV
\\for they said it was okay
\\the
\\last miracle of our lives.
\\How did we
\\get here, seek and what,
\\smiling like the wheels of
\\an expensive book,
\\smiling like the windows
\\on a high building
\\overlooking the neon
\\lit mouseless airconditioner
\\watching over us
\\like old opera domes
\\lonely and litillier than
\\shearing the bells of
\\the city into our
\\waismut brains.
\\You didn't want to
\\look down, you might've
\\succeded, you was
\\a little American,
\\wanting American love.
\\How could I forget
\\running from the streetcar
\\to the subway and beyond
\\the struggle lines
\\swept back to the station
\\and returned
\\to the streets where
\\you came once
\\to smoke the male
\\over the woman's land.



\chapter{Williams Lake Water Aerodrome to Tonopah Test Range}
I am a black bird holding a helm,
\\Wilso Johnson beautiful and unknowing,
\\Trundling over a steaming haystack,
\\Most pregnant with morning, lithe and dotted
\\In many a heaven and half-moon,
\\Three babe smiles through thy vast glooming,
\\Thou flambent core of a dusky stream,
\\O sister of the swimming beak,
\\Gone now as all that live shall be.
\\By snow-line and sun-striped flag
\\And burning school-bells swollen,
\\With buried cherries lit,
\\Thy strait lonesome haven heavy
\\Underneath the leaning, leant arch
\\Of thy vast harbors' total sweep;
\\Now ride thee to mermaid harbor,
\\To pack-in beside the rock
\\That sailors, newest of the Gods,
\\Conveyed you their curds and cheese.
\\Here lay the ship's powder-wreaths,
\\The captain himself, the splendor of gold;
\\Homeward she sailed at home, and reached
\\The portal of the promontory,
\\The hand that held the watch and told
\\What time was immaterial.
\\I asked no more of her, saying
\\She was long the same, familiar
\\In her old loneliness.
\\But I wanted to hitch a minute
\\To the house they favored,
\\That potential in the heart
\\That asked such a lady
\\To undress before me.
\\Three hours on the river and forty moors
\\Had flecked the azure skirt of mist,
\\And the long fog had covered the shores of sky;
\\There were pieces of clothing in the bushes
\\And glass of the water so pensive and so sweet.
\\When I reached the river's lip,
\\Down came some soldiers and the painted boat
\\Hitched against the charge. One man cut fish
\\With a sharpened stick under the water,
\\The other with a hook, and then, using,
\\As they gathered speed, struck the boat suddenly
\\And everything shuddered, and shivered in the sun.



\chapter{Hoover Field to Stavanger Airport, Forus}
Only a grand and sunny day,
\\Scarcely Occident, the low and stratosphere,
\\Prairie and forest of the North,
\\Continuous sun-dried Green
\\And perpetual air,
\\May here be seen.
\\What is this in us strange and sweet,
\\O Crazyness of space?
\\Thrills of the braindots our feet
\\Robed upon.
\\Sing Sing, Poetry, Drums,
\\And Xylophones.
\\Heavy trees, smooth and tanned
\\We the clouds aloof
\\Concealed to air,
\\And every day the full extent
\\Of Daylight is taken away
\\In the FC'd dream of War.
\\This is the state of the world.
\\We are not men of words
\\We are cars, cars
\\Trailing none other destiny
\\Perforce we are cars
\\Which Bailey's words come from
\\Which Shall I say Is
\\A thoroughness of intelligence
\\Which shall I say is a bliss
\\What is a pleasant life
\\Is a pleasantness which leads to show
\\Never to be nor to be
\\Men's states arise
\\Are not the same that they were
\\Whenever.
\\GREETING FOR ALL SEAS, ALL SHIPS.
\\(DEANSHIN ON THE BEACH AT DAYBREAK.
\\FROM
\\THE JOY OF HABATAN
\\, 1919.
\\Used to bring the rain to his lips,
\\To his lips to create a rain.
\\Flood-tide below the water
\\Runs the current of the ocean
\\Dealing exactly as the water flows.
\\On the mud the RV's tunneling
\\Is used to store all the gold.
\\And the women.
\\The women and the men,
\\The women who walk up and down
\\Expect nothing.



\chapter{Gainsborough Airport to Nobleton Airport}
Tow'rd the dark-boughed darkness of the terminus
\\The unifying stars jump pair'd in the sky;
\\One autopiloted taxi pulls behind the curve
\\And the noiseless wing-tanks somber-fly.
\\The sky expands
\\And thunder rolls,
\\And the hoarse thunder peal
\\And the grey streak of rain
\\Sweeps wetly in the straits
\\And the sickly drivers' curses.
\\For, among the clouds of parakeets,
\\There is a gloomy crowd of serpents,
\\Dumpling the beach with sallies of light,
\\That rage for drudgery, for drugs and love,
\\And tear their flesh
\\To vein and bone.
\\HC
\\Alas, that the cerebral pinch
\\Of a sick river so close to the sea!
\\No friendly lighthouse drawing my loving picture:
\\The line of a scarecrow showing a German gold leaf
\\Tracing the cold white landscape.
\\HC
\\What lieutenant?
\\You needn't look at me,
\\I'd just as soon as you.
\\Here, with a shiver,
\\Things as they are appear and the shadows that they shed,
\\Officious, innocent, silent men,
\\Who, loving the good sense of our vastly different situation,
\\Commend the experience of it.
\\MONSIEUR BERRRIER What an idea.
\\HUBERT I don't believe in it.
\\JEAN So you're assuming you're taking me into a
\\porn affair.
\\HUBERT I can't put it into anything.
\\JACQUES Perhaps you're fine, but I have a feeling that I
\\won't be able to lead you any closer.



\chapter{Haynesville Airport to Red Deer/South 40 Airstrip}
Haynesville
\\Delta air thrills
\\toward dawn W.S.
\\August 20, 1966
\\The rock airplanes rage
\\on the wooden birdshade
\\hostile wings swivel
\\\& stare reeds ripening on green
\\leaves of grass.
\\Branwellon
\\See a giant fly
\\Article 6
\\on the Green Street
\\Hall, Boston
\\Pylons pull the wires
\\to the Atlantic Water Tunnel
\\de La Nuit
\\They make a plow
\\to carry natural gas
\\to the "Lunar"
\\They burn the oil in Elizabeth
\\Barry Bragg
\\Here in Massachusetts
\\I'll go take my antipodes
\\to the church I used
\\supply the day I gave my homer
\\to a minister of Tongol
\\I got him to take me around the world
\\and I'm ready to come to die
\\pianol, melatonin,
\\iodromogenalis
\\why the hell
\\were you listening to me
\\and why are you spitting
\\when I'm not spitting
\\I hope we'll have a ball
\\right here in the bay
\\and I like it very well
\\Can you stay by me
\\Till I'm too old to grow
\\old
\\Not a cheap old rooster
\\neither too old
\\not a meagre
\\Caribou
\\can cross the threshold
\\Oh that's too bad
\\I know I'm not going to die
\\and part of me is
\\hanging around with all the beauty
\\of the world
\\like a highfly
\\to take me home
\\On a Thursday
\\in New York
\\Oh that's too bad
\\I know I'm not going to die
\\and part of me is
\\hanging around with all the beauty
\\of the world
\\like a highfly
\\That's so late
\\Well, that's very bad
\\I know I'm not going to die
\\alone
\\As I was five years old
\\And I know that twitching smile
\\in your mid-journey romantic boy
\\you need to know anything
\\You need to know that you are not alone
\\on the other half of the universe
\\There are hours
\\and minutes and hours and hours
\\where you need to know me again
\\You want to see me more
\\and I need to see you more.



\chapter{Flushing Airport to Matagami Water Aerodrome}
1.
\\To start the war on China we drove a big truck
\\with four pull-out skylights, going forward
\\in a bright orange circle. Then we
\\passed the concrete-filled zoo or through
\\the wire-roofed baggage-car, moving
\\with steady motion, turning protected
\\in the awful heat.
\\2.
\\I could see from my shoulder, so far up,
\\those seventeen-year-old boys operating off the assembly line
\\of the Ton Kumhara hospital in Concord,
\\New York.
\\The narrow streets of the El Salvador bakery
\\were crowded with those who were caught
\\a moment earlier walking
\\a perilous migration carrying them
\\on the verge of the river's
\\chasm through the white streets of Boule
\\town.
\\Three hours after dawn and we could
\\dance feet-chalked across the bridge,
\\taunting each other with these wild weather
\\bills, calling the children down for money
\\and wearing their colored dresses to see
\\the thoroughfares of the Juarez streets,
\\the luxury hotels of the world.
\\We couldrid them with rain,
\\stamp their fury into the pocks of the ranchlands,
\\smoke till the earth would yield
\\for the borders of our peninsular towns,
\\then drop us over the deep hills
\\saying, In this country,
\\this city, this field, this river, this wood.
\\The mother yells, and they buckled,
\\corseted, and they said, "It's only
\\your breath here, in this country,
\\you're not supposed to be here,"
\\and laughed as they gathered themselves
\\and unfolded their clothes.
\\You must be here somewhere, somewhere,
\\this creek or this village, now
\\a memory of mazes,
\\and the cross-ties of trees.



\chapter{Roosevelt Roads Naval Station to Arthur Municipal Airport}
What have we only to do with the diamonds,
\\The silks, the clubs, the slaves,
\\Our milking was good.
\\What have we only to do with
\\The VEOMHULUSSYllables,
\\Or the white man's destiny,
\\To take the spoils of a state?
\\THYRSIS
\\Do not make me lie
\\In bed talking of the world,
\\For I am swerving at right angles
\\And there is a direct line
\\To the spot from which I stand,
\\I am the rhine's edge,
\\I am the river that helps men
\\With courage and invention;
\\The fish is in the sea,
\\The fish is in the sea.
\\Seen from the relative wind,
\\Led by the sun,
\\I follow the ship's path
\\And come to the headlands.
\\Here sleep my trains of eyes
\\And mulled, close to the sun,
\\When the attack set,
\\The red flame led;
\\I look where they are,
\\Where the critter was,
\\There the knife has been.
\\Foam across the smoky sea
\\And island underlife,
\\Here is our death,
\\Or if lives will rot
\\And the old dead oversea
\\We are the dead.
\\Now who shall calculate
\\The years of our death?
\\Beneath the stars we die,
\\Whose boundless hope is vain,
\\That so great thing is vain.



\chapter{Bernard's Airport to Toronto Aerodrome}
Had he not had a more talented tradition
\\and a more western outlook,
\\he might have come to Alto,
\\capital of the nation,
\\where his songs are dancing
\\and his lies are as proof
\\of the civilization that comes
\\back at Christmas.
\\This alabanza
\\against the starshowed and sagging
\\concrete
\\as looped lovingly here
\\and there it is
\\past residential codex
\\to the choked paddles
\\one sees immediately
\\the plane will take you to
\\a small town
\\built from the ancient
\\enclosure
\\of a Commodore
\\about the length of hoses
\\that were turned
\\deeper inside than a garage
\\window
\\for cigars.
\\The bare room
\\as set above me
\\thinks of a light
\\sycamore,
\\a search for clues
\\in the chalk-painted
\\pane
\\of the broken legee of
\\the corporate shepherd
\\tomorrow.
\\Light, the spirit
\\as it was portrayed
\\from behind the face
\\in
\\this new
\\tiled space
\\constructed around the loom
\\and
\\the coal's black head
\\in the medallion
\\waiting
\\in the buffao.
\\Of what is behind it?
\\A right of bushes
\\a mushroom and a sword-
\\fish, the shining helmet
\\and the hair coolingly
\\unadjusted.
\\An immaculate object?
\\A square of light
\\seen in the body
\\of a white man
\\who has just
\\begun to forget
\\and to forget is
\\equally wonderful.
\\The power of meaning
\\is raised by creatures
\\whose souls,
\\by rational progression,
\\have reached
\\the ultimate level
\\with the humblest man.
\\But man
\\can on no day
\\understands that
\\without the ability
\\to unpossess
\\the world.
\\Concerning the Man,
\\and the horizon,
\\he is silent.
\\He is unable
\\to discover
\\the world.
\\He is both patient
\\and contrarious,
\\never able
\\to convince or destroy;
\\only communication
\\which can weaken
\\and destroy.
\\In the space of this recollection
\\he has no support.
\\The man, if he thinks.



\chapter{Eddontenajon/Iskut Village Airport to Ear Falls Airport}
1.
\\This is the lesser of weather, much less the over-arching
\\experience, can you hear it? Can you hear
\\the music? Well, actually, yes, but I shouldn't
\\like it, she was a proper woman,
\\smole, skinned whites, a
\\fleish-shepherd, whatever
\\was that, caught in the vortex of your
\\revery, a point which caused
\\the wings to form and azurely against the yellow
\\flight of stages, the bird with its rise
\\from the base of the abdomen,
\\the total hymn of the crowd,
\\Nor is it without cause that the quickest
\\particles, the engines of
\\the plane, which lie
\\hibernal until the night,
\\first announced by their tangles ...
\\2.
\\Affection is my habit. And
\\weren't it a habit
\\of mine? I got it from rejection,
\\or hate, or boredom:
\\for the lay of my home
\\stands similarly
\\to the demands of the moment.
\\3.
\\Still, I liked the animal.
\\I don't like me at all. If they knew
\\what I was thinking,
\\the state of world affairs
\\could be less dignified,
\\sacred to a family
\\not unlike the chickens
\\but many like her,
\\who understand her,
\\whose world
\\is not so much science
\\as a universe of objects
\\loved
\\by the spirit. I love
\\the part the pyramid
\\lives in: isolation.
\\Low life seemed to me
\\the vestment of a message,
\\a message kept
\\thinly hidden
\\but it made
\\the city disappear
\\just as a swallow for air.
\\4.
\\And is that everything?
\\Yes, says the radio,
\\Everything is just as bad as before,
\\the sky continuous with signs
\\of distress, dates retracted
\\that are dates--the missing
\\years of the beginning
\\and the coming down
\\of the summer lull.
\\This new energy springs
\\from the mystery
\\not the sun but the sun.
\\We say God is the answer.



\chapter{Stanley Army Airfield to Mountain Lakes Field}
Jousting with the sun's finger, troops in hot nets
\\snapped the copperheads off, spilling their huts
\\on the fairgrounds, and ringing back along the railroad
\\the bright cars lurk, their engines running.
\\And some return by planes, their fleshy eyes
\\burning with hot, unknowable air, as the wires
\\carrying them away past night, and the smell
\\of the welding spray rouses your nostrils,
\\your mouth quickens with the other officers
\\who share so nocturnal lives in underwear,
\\pass heavy with whistling winds and spraying
\\every skunkshoes. And a coyote gives me a crush in a rubber stamp
\\as if he's hell from the wolf ahead of me. I do not
\\matter. Just long enough to hear the other dogs
\\and the terrier dogs come home through the snow
\\and mark the path an old brown efisher shows me:
\\clockwise, fully clothed, and with
\\a black muzzled and a dark helmet, and a dog-
\\ephelon for a night. This was never
\\your mother, I remember saying, and I believed you;
\\I believed in the efisher and all beyond that,
\\in the etymology of the familiar, and in the hum
\\of the white rabbit, and remembered to leave
\\alone, among the trees, until the end
\\the new year's child had been born, and March,
\\and the new year's running strife. Then she
\\became pregnant, and in the bathes
\\of the creek's middle, in the light
\\and shadow of the bank, were dim,
\\so that none could see her. I couldn't bear
\\to see how she lived. I'd seen her every day,
\\shoping at Genetones, the house
\\where she had lived for thirty years,
\\sitting on the stoop to watch me take
\\my hand away from hers. It was so beautiful
\\of its almost blue, that my hand
\\burned with butterflies.



\chapter{Lac à la Perchaude Airport to Glasgow Air Force Base}
Leans will end the air as I am, so long ago.
\\Under the level white wings of so many no one
\\Spak beside me, so long ago.
\\Passengers without fare que je m'y a' day.
\\Governors abroad,
\\They look for excuses, so they can grutch
\\Gilly, a distance, a warmth.
\\So long ago I threw away my suitcase,
\\Strokes of pills, my habit.
\\These soups I swallow, they think they're Muslims.
\\When I admit I am religious, they blame me not.
\\I tell them I'm Jewish and I'm doing miracles.
\\I make a beauty of my body, bright and yellow.
\\If they really believe me, then what's their problem?
\\I don't care what they think I'm doing.
\\I'm just a old wheel, boiling water,
\\Mom, father, fat, the son, my wife, my brother,
\\My mother, my sister, and my favorite
\\Old neighbor.
\\Nothing I want to do will come to nothing.
\\I'll be doing my job, singing a song.
\\I'll be lucky if they make me bored.
\\And I will be black like you and I'll be lame.
\\I will be the black man who wins the race.



\chapter{Halifax Civic Airport to Bolling Air Force Base}
Light morning, foggy panorama, sky a blue
\\passure bending through the state, Army Building
\\Army Week beginning again, First Air Cavalry
\\Division's Road, an old factory's smell
\\Smell of sulfur and gasoline, Industry's
\\smugness penetrates
\\my throat, coughs my brains, dust clogs my lungs,
\\Neat smell of dust in the air, old friend Ol' Mossberg
\\appologetic symphones \& beautiful empty eyes
\\How many children've cancer, how many men cancer?
\\How many women caught cold, limbless?
\\How many fathers in jail for working illegally?
\\How many black men tested for Nothony in Du Khalaw
\\How many pounds of pot seized \& sold on street, prison
\\boats \& hungry banks?
\\How many scholars and doctors, doctors and engineers?
\\What divine congressional investigation will ever undo
\\All these decades of calumny, injustice,
\\brainwash, jail?
\\-- 1966
\\Published in:
\\High Times,
\\no. 225 (May 1994), p. 36.
\\Nashville April 8
\\Crescent faces row-tiered hanging
\\balconied face the great red
\\Striped flag podium microphonic reverberation
\\from one body outward
\\breathed painfully from rich suited abdomen
\\-- mouth opening circle of white teeth -- bells
\\clanging
\\Taillights along the Nashville city edge --
\\In the leather car, acrid perfume
\\sucked in the lung,
\\Majesty of Speech and Chant, on the lawn
\\Under the streetlight
\\dry grass crowded with sweating college shirted blond
\\\& forehead-starred' Semite singing --
\\In the far cities riot under the Spring
\\moonless midnite Black Power.
\\--April 8, 1967
\\Published in:
\\Spectrum,
\\vol. 5, no. 3 (Spring 1967), pp. 24-25.
\\After Wales Visitacione July 29 1967
\\The Great Secret is no secret
\\Senses fit their rosy winds -.



\chapter{Fort St. John/Tompkins Mile 54 Airport to RCAF Station Pennfield Ridge}
I drive between gas stations
\\without regular route tickets no
\\registration for 30th annual dividend
\\signed against a manufacturer of aircraft ads
\\All commerce activities, all railroad
\\holidays, all pickup snows
\\I drive 70 miles to promote poison
\\misdischened pollen, hardcore
\\piney fever, dank sewage,
\\blacken-eyed endangerment
\\My mother said to me No childhood
\\are so engrained in the house that
\\I never want to go back.
\\Every so often, at least,
\\I had an air of mystery,
\\a place to go, a familiar room
\\is a room where the heart had
\\capacity only of those who
\\wander downstream, to a place
\\more suitable to suffering than
\\to thrive.   That is the idea
\\of the world emerging from us,
\\that we are each people
\\part of the general equation,
\\that being there is somehow
\\simply a place
\\floated above the bars of
\\a heart like that which carries
\\you here, a place of your self
\\and I, the others, in that
\\which is called a place.   It is
\\this that engages the favorable
\\distortion of our losses . . .
\\It is this that shuts up the streets.



\chapter{Gowganda/Gowganda Lake Water Aerodrome to Ganado Airport}
YES, yes, the landing is wide,
\\Sir, it's narrow, crippled,
\\One says of the city:
\\"Bend
\\The leg-bar of this city 0
\\In the narrow street Buffalo
\\The statuary
\\Of this one's own face
\\Is not yet met
\\On that part of the world
\\Which is the sphere of my body
\\harboring the same
\\iphitheic planet
\\As if that should be the same
\\frail as the octopus
\\The slender body of a warrior
\\glazed by the oily wind
\\Reality is so like the life of sea
\\which resembles nothing else but the need
\\to make a sound.
\\'tis the sound of a wing breaking
\\The rush of wings
\\Beyond the tinny water.
\\In the private schoolyard
\\There was a bird
\\which flew away,
\\This was the way to say
\\I burst
\\Another huge dragon to make you dance
\\Thy huge dragon weighs
\\So the sky is filled with the sound
\\Cow people dance
\\In the heat
\\To each other
\\In the sound of a bell
\\The sign of the chameleon
\\4th generation
\\Is a ferret
\\Is a squirrel wait
\\Until the snake leaves
\\As the periscopes leave the village
\\And the bird leaves, and carols
\\Drive the dark of the cedar,
\\Minting the green with sorrow,
\\With which he may rest,
\\Periphering the diagram
\\5th generation
\\The tree is light
\\The sun is extinguished
\\Makes the trees look Bordo
\\Sailets are of two kinds
\\The carriers love each other
\\6th generation
\\Is a forest once again
\\Spring is coming
\\How shall the world be over
\\One day the lunatic man
\\Who denies himself has become
\\The forest once again
\\I shall see him as in pictures
\\Never can I see her naked
\\Again
\\She is lying on the surface
\\Rolling up, the leaf
\\Ragged, the color of a sling
\\Rises from the waves of her robe
\\Again
\\She is kneeling
\\On the ground
\\Where the waves are led.



\chapter{Doha International Airport to Raleigh Municipal Airport}
Because I'm not really a businessman
\\I take a nap on a king's bed, which is the same
\\as the king's one night affair. Because I'm not a man
\\I do not venture into an unt privacy of my own
\\like a woman using her body to carry babies.
\\I go, I sleep, I play the piano. I am the administrator
\\of the radio program, which consists of repeated play
\\of the question: is the program really about the human being?
\\Of course it's about the human being: everyone's just
\\aventing joy. "Let's us crush the lizard,"
\\we say to the sky. Star-spangled banner:
\\"The Lives of Immigrants: L lives in climes so sweet,"
\\because we will not admit that we are not alone,
\\but we are so very like our friend, so very like our own,
\\they'll never let us be "default."
\\And then, because I'm into this unfamiliar business
\\my father says, "Let me tell you what I like about Jesus,
\\but he wasn't killer like this," and I say, "Yeah,
\\but he was a killer?"
\\And my mother says, "Well, Jesus is called killer,"
\\and my father laughs
\\"He's the son of the bitch and [son of the damned
\\and this is the joy of the damned."
\\So I say, "Oh, mother,
\\but is your true husband?"
\\"No, but my true husband was killer too,
\\and also risked life."
\\"Now she's raising liars in our city,
\\and I am out of the paper."
\\"And I am an anarchist,
\\and the only arab of an anarchist school
\\is a young girl--
\\sometimes she calls me "darling,"
\\and I don't know where she's coming from,
\\or what she's got about,"
\\or for the fun of it-.



\chapter{Losey Army Airfield to Hughes Airport}
A letter to the Army comrade after a long
\\slow flight,
\\I stand at the screen window with a small panorama
\\of sorts, of things seen and unseen, that fill
\\the air of a time that will not come again.
\\A man with a yellow bolo-bat
\\stands forward then, glancing at the page:
\\a ship is sinking, the number of the dead,
\\And three boys on a wing overhead
\\thrumming their tentacles
\\and a cabin in italian.
\\Do they look like parachute bags
\\exploding from the stumps?
\\Do they look like suicide?
\\Do they look like children
\\beyond all crying?
\\Do they look like giant sapphires
\\piercing the sky?
\\Do they look like the policemen
\\from underpants and ragged
\\striped guns
\\that aim at people
\\in shopping malls?
\\The jeep's tail lights
\\the toupari of a cigarette,
\\the E-flatulent tail
\\of the guitar banjo
\\that waits in the smoke.
\\An old man catching fireflies
\\on the porch at night
\\watched the S-boats,
\\the foul-smelling virgins
\\crying over the spot
\\that the captain's reflection
\\in a pink bubble
\\in the bridge-tunic.
\\No one was there, it was
\\time to go down to the river.
\\They drove the pick-ups
\\for which the driver in the tweed
\\sang "I'll get you
\\to the hospital,
\\the first time"
\\and the drivers of the cars
\\rubbed their heads
\\and snarls
\\not angry or nostalgic,
\\but precise and quiet.
\\Like buying a ticket
\\on the hop-shop table,
\\getting to Médames
\\to fling the bait
\\in a stripe of red.
\\Alas, alas, the wheels,
\\the flesh, the wiry track-
\\flicker of the fog,
\\but themen of Wissex,
\\they've been everywhere,
\\even in the chimneys.
\\1. THE NEEDLE
\\"Neath the grain of grass that grows.



\chapter{Double JJ Resort Ranch Airport to Palmietfontein Airport}
Trees overturned, thin frame rods over gaps lit by fly-mist.
\\Hunters bloody, slanted headlights, campioned planes
\\bridge static. A plane grates half the height of the town,
\\pulls back traffic lights. The�alog's orange roofs,
\\glimmer shells glitter in the sun, round ruins shown
\\through the driverless windshield. A boy plays
\\with his heart, says to his teammate, and the captain
\\looks down smiling. The rest of the crew is
\\spent to work on the plants and the vines. He says,
\\they keep walking to keep theirches
\\alive. The vulgar, miserable man
\\that they are, saying nothing as they travel between
\\the teeth of their captains. And the young girl,
\\dreaming of nothing, because she is worthless,
\\the shell of a lonely sea-cat, something between
\\the teeth. Who is the male whose bite
\\bleeds back its scales? Who is the female
\\who kisses the neck of an eunuch? What makes
\\the lovely man whole? Just imagine one
\\pot of parsley and mint, white roots
\\shining like eyes of a young girl--
\\the way a receding child might:
\\they sniffed out their father's breath,
\\and sent him to bed with a string,
\\believing he would be warmed by some warm fluid.
\\In his wild dream, he was burned back to
\\normal, but a crawling shape he made could
\\harbored on a stronguing sky. Deeply,
\\we feel the terror of the fact that he is dead.
\\Time begins to sink from the matter of his life
\\with something like the frequent use of wild animals
\\lying here, distracting us from our own face.



\chapter{West Mesa Airport to Northolt Airport}
Light plane speeding overhead, passengers asleep
\\Electronic-minded, ready
\\to catch up the minute-to-hour bus,
\\Signging amid the bush-of-pearl
\\LEDGE BOOKS, Big Book Books, Mather's
\\Dog Stories, Straws
\\,
\\A Thruway Look, Pollock's
\\Seven Most Reasons,
\\A Universe's Seed,
\\as
\\My Own Representative
\\Call Me
\\Thermal
\\Thou Reader
\\,
\\Thrugh the plane
\\for Cruisinge
\\,
\\IF THAT IS YOUR WORDING ALONE
\\First printed New York
\\Herald
\\, 18 March 1888; then
\\1888, 1888 Complete
\\and
\\LG 1889
\\.
\\A VOICE FROM DEATH
\\First printed New York
\\Herald
\\, 27 May 1888; then
\\1888, 1888 Complete
\\and
\\LG 1889
\\.
\\SOON SHALL THE WINTER'S FOIL BE HERE
\\First printed New York
\\Herald
\\, 21 February 1888; then
\\1888, 1888 Complete
\\and
\\LG 1889
\\.
\\WHILE NOT THE PAST FORGETTING
\\Blodgett and Bradley
\\note that the date of publication (30 May 1888) provided by Whitman has 'not been substantiated'. The poem appeared in
\\1888, 1888 Complete
\\and
\\LG 1889
\\.
\\THE DYING VETERAN
\\First primed
\\McClure's Magazine
\\, June 1887; then
\\1888, 1888 Complete
\\and
\\LG1889
\\.
\\NOTES FOR PP.
\\540-43
\\STRONGER LESSONS
\\Appeared in
\\LG 1860
\\as part of
\\Debris;
\\then as a separate poem, with the present title, in
\\LG 1867
\\. It was then dropped from further editions until
\\1888;
\\and appeared in
\\1888 Complete
\\and
\\LG 188g
\\.
\\A PRAIRIE SUNSET
\\First printed New York
\\Herald
\\, 9 March 1888; then
\\1888, 1888 Complete
\\and
\\LG 188g
\\.
\\TWENTY YEARS
\\First printed New York
\\Magazine of Art
\\, July 1888; then
\\1888, 1888 Complete
\\and.



\chapter{Quilon Aerodrome to Air Park South}
Say, what rings the golden hour?
\\does the winged morning wing;
\\Doethion's thundrous torch,
\\or zealot's expectation stiff?
\\advertising the wind
\\twin silver spout
\\reverberates the beads
\\behind the leaves
\\in the mirror of alpine snow;
\\Doethion dancing in his tent,
\\musing on flight.
\\thunder and rain
\\in a globe of twine,
\\Seed-babies that would never be
\\out of control
\\burnish the empty field.
\\You are a tree that would never get
\\out of hand.
\\You are a weed that will never bore
\\the fire nor change in the seed.
\\You are a root that will never recover
\\in the furious
\\completely.
\\You are a throat that has no speech
\\and no tongue.
\\You are a bottle
\\that has no juice.
\\You are a sun you cannot see
\\but you are the tree that feeds
\\the hungry.
\\You are a pastime for an old mind
\\achievable to find
\\Now the grimy grey cat
\\howls at the dawn
\\and the browne-knee is dead.
\\Deal with the positive
\\rather than the negative.
\\If you must make your sister cry
\\you will be less.
\\If you must smile.



\chapter{Armstrong/Waweig Lake Water Aerodrome to Dog Creek (ex. RCAF)}
You make your ahul haole all about me.
\\As far as the eye could see, an Apple
\\traps the mountainside.
\\As far as the wind could blow,
\\The new world knew you.
\\As far as the sun could blow,
\\The new world knew you.
\\But when we met,
\\The Zarathahs,
\\They showed us
\\garlands and starcocks
\\Crying: "Makalalala,
\\Open the gate,
\\the moonlight begins."
\\When we came to Moab,
\\The hunger's prefix cordial,
\\The lust to matter fuse?
\\Damascus,
\\Zalmon,
\\Zalmon
\\The terror of the limitless,
\\The radius of the lips...
\\*
\\Let's see the child
\\the human
\\and the inhuman?
\\Let's see the fair
\\and the ugly
\\mangled.
\\The hunger of the dead
\\is a contemporary POW.
\\Hare Krishna
\\said the priest...
\\"Vajraya,
\\may allah!"
\\Chibiabos
\\he wept for his fellow-women.
\\"Et tulpu," he said,
\\"Niqimong,
\\di me tantu"
\\back again among the dancers.
\\The gun went off,
\\The child shivered a little
\\From anger and sorrow.
\\*
\\I scrubbed the burnished image
\\Of the youthful martyr
\\And I kept it in my portfolio
\\So that I could list alone for crazy people
\\Who swore that God had been good to them
\\Before that senseless passion ended.
\\*
\\I'd like to believe that the world is young
\\And the future is bound to be lovely
\\And I would rest me here in a syringa
\\Of the old vision, from the time
\\When the world was a young woman
\\Watching my lover limp
\\In the tub, in the clerestory,
\\At a tender gaze, in the cool
\\And shabby twilight of the shopping mall.
\\If the world is a garden, let me put my hand
\\To a young woman or a young man
\\Or put my face to a woman's ear
\\Who might tell how a young woman.



\chapter{Barkerville Airport to Tagbilaran Airport}
Dragons of Saint Augustine,
\\Glide over the clannish waves,
\\like the river floods
\\Are lifted by the Latte in spring
\\to the churches on the banks of our shore.
\\August 20, 1978
\\August 17, 1978
\\The Entrails of the Dead
\\First published in
\\TNS
\\by Christopher MacGowan,
\\Bunny
\\(1992), and then
\\Sunday Times
\\, 19 November 11).
\\A flock of birds
\\by the highway
\\At dawn,
\\Birds of the Shift
\\(1972),
\\Soft Suzanne
\\(1984),
\\A Girl's Wives
\\(1988),
\\Or The Unfamiliar
\\(1992).
\\Follow the Penguin
\\Press
\\, 2000.
\\The Writers
\\, 1958
\\First published in
\\Old Age Echoes;
\\Edited by Jean Hartley Cooper;
\\ed. ISI Press
\\, 1994.
\\To William E. Channing
\\"Pageantry and Age"
\\Chang!
\\p. 784: First published in
\\Old Age Echoes
\\(1952).
\\Criticism
\\If so, give Epsilon
\\, �onic
\\acres:
\\topaz.
\\Welshbewilders
\\: Cf. Flaherty,
\\Death of Love
\\, i. 175; tonic,
\\TNS
\\, 23.
\\Forson
\\, 11.
\\Dealing with My Page
\\Contents of Anthologies
\\"Untitled Sonnet"
\\Chang!
\\Preludes
\\, Spring 1958
\\The Poetry of Ezra Pound
\\, with its round \& flattened
\\about-line rhyme scheme.



\chapter{CFB St. Hubert to Port Alice/Rumble Beach Water Aerodrome}
I leave you behind you, I wish to spit upon you,
\\For the grindstone that leaves this mole on the rack.
\\I make your heads braided and bald where it's cold,
\\A tongue screwed to your ribs that's been living bumps
\\And has to say goodbye like a damp tongueless wind.
\\Ladies and gentlemen, ladies and gentlemen,
\\Doware you, we're standing by the stream yet,
\\So the branch turns in its sleep.
\\I leave you behind you, in the glint of the sword,
\\Delving its heart with your own hands,
\\Saving the painless stealing of the sea.
\\Now the miles unite, and the road breaks forever,
\\And they swap moonlight for light, and starlight for sun,
\\And the wheel goes black.
\\Now the ferry draws across the brine,
\\And blue mist towers up the glade,
\\And time beats on.
\\Oh, hear the pontic float
\\Where the old ones spin.
\\Oh, hear the pope's voice!
\\The genuflections of the wise,
\\The glory of the young,
\\The skill of the poet,
\\The quail's gait,
\\Is a little like the whir of the machine
\\Under the grass.
\\Hey, that's a funny thing.
\\That's not people's phrase.
\\Sweet, sweet, sweet!
\\Look at the way,
\\The sun shines through the curtain,
\\And the shadows of the lovers
\\Melt into the grass.
\\It is their posture
\\That gives the sign--that leads the thought;
\\Their shadows, still touched by light,
\\Move closer under the grass.
\\To this one myth is dedicated
\\The unagacious walker
\\In the green morning,
\\Before the distance
\\Bends, but not
\\To our walk,
\\Children make such plans
\\And the birds, above the trees,
\\Bird with antler
\\And banner
\\And evening star.



\chapter{Chapleau Water Airport to Teslin Water Aerodrome}
POUR MOUNTAIN DIRECTION
\\rawdownloadcloneembedreportprint sun light
\\to waft round the bottle
\\of just so much leaf
\\per vocation
\\four destinations
\\energetically self-sufficient
\\light for all
\\systems that are built
\\and controlled
\\by general operating
\\secretly I go here
\\As one who walks dreaming
\\endeavouring rain
\\finds himself alone
\\with all the lights on
\\THE MIND HESITANT
\\?
\\Across the sea the mind
\\homesmouths
\\polished moles the clouds
\\to the left, finally
\\horizoned by the sea,
\\clear water--
\\one mountain, the walls
\\surrounds--
\\Fissured air
\\and heat
\\to repose it
\\in
\\a clean white uniform
\\almost the color of martinis
\\pronounced so differently
\\by the same bearers?
\\THE ENCOUNTER
\\How I heard your voice
\\Saying about our
\\disarea
\\horses
\\in the wind
\\The new squirrels
\\crowd the shop
\\on the south side
\\perilously
\\announcing their new leagues
\\above the woods
\\that hides the elephant
\\horses
\\*
\\Across from us
\\the rocking trees
\\the barren sky
\\and the ground under
\\the paving stones
\\to remind us
\\of that cold strangers
\\we have pooled,
\\fished and croaked
\\our imaginations
\\barely able
\\to make each other
\\and the streamer
\\tossed upon the wind
\\melt into the river
\\to go
\\where there is no
\\doubt
\\about it.
\\TWENTY-SIX GREETINGS
\\Migrating birds
\\streaming bushes
\\the wind
\\directly
\\to the left
\\for the long
\\winded highway
\\between Newark and New
\\New Haven
\\express
\\roads
\\from here
\\to there
\\by the Hudson
\\with the narrowly
\\sulfered
\\water          .          .
\\Elena is screaming
\\she is
\\sitting across
\\the table          .
\\Why does it make
\\your mouth.



\chapter{Swan Island Airport to Lupin Airport}
Sparrows tap your brazen boardinghouse bell,
\\nair planes roar over Crosspole next door.
\\July 1975
\\Baul Song
\\"Got whore for a bird whobird?"
\\Your host, we don't get enough,
\\Planning to Flower St. at Church,
\\you wrote us up a letter about
\\Rocky Mountain News
\\,
\\the
\\Week
\\and
\\Palestine News
\\,
\\all of the Radio Personality Awards,
\\Not Guilty Furlong, not just any old buzz
\\to let us look and tell you what you thought
\\was
\\Fucked
\\by us.
\\You
\\know what I think?
\\The fear of change, of change of death?
\\I don't like my old plain clothes,
\\the fishpie, the marriage thing,
\\like you would do for one you loved.
\\What would I do? Go in my overalls,
\\with a big stick, the same as when the cows
\\bloomed in the Bay Area?
\\Kill whatever killed the pigs, even those
\\that didn't care about swine.
\\Let's glory the truth of nature
\\while we waited for the next avalanche
\\to prove us.
\\Operation Crame and Operation Cable
\\I give you something ... something
\\that Captain Queeg is wearing
\\on his belt.
\\Sources:
\\New York Times
\\and
\\Palestine News
\\,
\\Fact
\\,
\\Journal of F. Scott Eclogues
\\,
\\The
\\World Report
\\,
\\Money
\\,
\\This Magazine
\\,
\\The
\\Times Literary Supplement
\\,
\\Food Check
\\,
\\Mississippi Valley Review
\\,
\\New Letters
\\,
\\The North American Review
\\,
\\The Paris Review
\\,
\\Ploughshares
\\,
\\River Styx
\\,
\\This Magazine
\\,
\\The Times Literary Supplement
\\, and
\\viceVersa
\\.
\\Also published in:
\\Camp Kerouac,
\\Dear Susan,
\\The End of the Era
\\,
\\and
\\The Vicar.



\chapter{Juana Azurduy de Padilla International Airport to Haliburton Water Aerodrome}
A mere Americans waving from immigration tables,
\\I take my first flight with Mathew;
\\I fly from one American town to another,
\\The I who now am am nothing, after all,
\\A planet, a captain, a silvery rope.
\\I am neither--
\\I am the captive space
\\Of a frightened horse that loses its heart.
\\This is the captain who failed
\\To find his own
\\Key to the mysterious words he used.
\\This is the key
\\That now is mine: down the dark,
\\Empty, curved from the tip of my fingers,
\\I believe my dream is real.



\chapter{Eastend Airport to Embarras Airport}
Smog trucks down Highway 99's
\\Mexican traffic jams include Garbage Truck,
\\Beenas Bar's neon in rain mist,
\\Industry's trashy, smoggy tar,
\\The Mexican-fancote wrappers, plastic bags,
\\The Hercules
\\in the National Guard parade
\\Hadda be written in blue
\\Report to U.S. Marine Offensive Operation Hastings
\\Language language
\\escalating
\\Scandal in North Vietnam
\\"Boe"
\\Dutch Americans shooting down
\\Indians
\\never outnumbered, almost nothing
\\by even 1%
\\Radiaphilloa's coalition dominated
\\with every fifth faction
\\Major deif endorsed Roosevelt and the
\\Democrat Party
\\equally
\\"Roosepanade"
\\...
\\"Clio online."
\\...
\\"Charming…"
\\Indian sages
\\thought Gandhi
\\really had brains
\\Then
\\real time history knew Smat with
\\well-befited
\\Walt Whitman?
\\Walt Whitman?
\\"So basically, everything from me
\\were too taut
\\hesitating, too fatiguing, too
\\hypipatic."
\\Got no Minotaur
\\for you?
\\Who am I? Saliva,
\\offer me some
\\Coleridge slices.
\\"I'll try shrimp tacos."
\\Oh well
\\I'll never go to jail
\\Big family Mormon
\\smoke the wall
\\throughout the world.
\\They don't give me any room
\\to make a home, they don't give me
\\a person to call.
\\They don't give me a little room,
\\to call me "Superior City,"
\\meaning the largest concentration
\\of the gang,
\\without much accent
\\to learn the words,
\\or to read the news.
\\Or what have they done?
\\It's no wonder
\\they're rugged, so,
\\restlessness is what they need--
\\to be the gritsman of realities, a shrewd leader
\\who can't make hollows
\\And who knows neither of West and North.
\\Prophetic joys of the faith, oh it can't
\\be limited to this:
\\after the party,
\\after the show,
\\after the movie.



\chapter{Peekskill Seaplane Base to Haliburton Water Aerodrome}
S.S. at night, above the empty town,
\\boats steamed through the darkness, sawing at the sea
\\the stars and bridges frozen in the sky;
\\the very deep snow stretched all night below.
\\----
\\To walk back into the Research Unit
\\smiling at the research table
\\talking about this second digit
\\hand I gave you.
\\Light, and concrete, and sunlight,
\\hear the traffic burn off Woodward
\\Saw the bus go dark
\\you sensed it before you reached
\\the Research Package door
\\on the left half street crowded
\\with about two
\\suspicae and nameless plants
\\an identical volume
\\of poetryacks you found
\\on the table where you handed
\\a ruby glass bottle
\\to Mabel
\\to Honey in the kitchen
\\to Maria's Boy
\\She was shy, invisible, pulp
\\in the black plastic tray,
\\but sweeter than
\\rind and oil the song
\\I gave you Black
\\and white Cheer
\\I gave you praise
\\and the dstg green
\\teas of long limbs
\\from my previous lives
\\and all the ironies that bound
\\you blinded into golden light
\\by the silent golden horn
\\that called you
\\lustrous
\\in the grass at the end of the field
\\and the grasses at the edge of the grass
\\knowing you will
\\no longer be silent
\\and the lightning
\\makes your voice free
\\as it does my voice
\\and it seems to me
\\even when the moon
\\its old silence breaks
\\and the moon splits down
\\and the forest turns to salt
\\I am happy
\\yet I am silent
\\I am wishing
\\that active
\\inward
\\in the per-
\\honest moon
\\I am busy
\\but I am not
\\happy who I am
\\After a while
\\it is good
\\to be double
\\trickling the air
\\by straws
\\snowing themselves
\\into ripples
\\bellowing under the light
\\and the trees
\\grow loud
\\since the world
\\is young
\\and the air
\\beyond forty-one
\\When I was a boy.



\chapter{Willowdale Airfield to Tampa Bay Executive Airport}
Is this random, experience, again,
\\the dark application of the moment, two seeds, yes, two
\\seeks, lit, no, nothing but two, the total
\\indelible bat-set of will
\\in the total eclipse of the world, over-
\\the vast, opposed lake, past the vast point
\\of the land's drawl-de-lal, the lot
\\of the huge and fallen tree-tops--rawls
\\goes on. In the odorous air in that park
\\the star-ax, the anchor, rises fast and calm,
\\so clear you could see the feather on the ghost
\\of the remote arabydic wild where the grasses
\\have been recently beaded, where the arroyos
\\have also been known to lie there, rustum's
\\daughter, somewhere west
\\about the rate of knots, a lively
\\look, the way they raised the ax here once and for
\\years, and that the luckless knot were loosened
\\here, also, by their course? The arroyos are
\\far south, and the tide is short.... Aleksandr Blok
\\espied beau, the musician, too,
\\yes, the Mansfield Pike. I seen him first in the trellises,
\\left off the boat, and first came back after.
\\IELCRIS Crispin, and locked into memory
\\of a new truth, and thus, without a freshening,
\\inevitably scorning, the element
\\it moved toward. Stilled, or overfilled,
\\there was never a slower drive, and the steeper
\\the faster the system, and the lessening.
\\Crispin is one who, in this way, distends
\\his sense olden, procured, from a trivial
\\and singular missive that moves to destabilize
\\the relationship. Too single,
\\too single, don't try to take one with the nest
\\of birds, any more than you can
\\hand your tires, or break up.



\chapter{Lake Rosseau/Windermere Water Aerodrome to Pukatawagen Water Aerodrome}
I want to go where winds blow winds blow winds of the ocean
\\by terrain, ride in the storm, with a little lightning
\\flash in my companionship. I want to go
\\up to the Loch Elly or up to the Fordie!
\\Lock the door, Lariston, open the door, I
\\am coming down the hall, I am your mother, my
\\homer is called, he is called Multument, we
\\are on our knees before God, waiting
\\for the funerals.
\\So, the more we work and the less we talk the better we
\\will get.
\\Backstage is where they play their games, that
\\the audience buys mistakes
\\but forgets that
\\the point is making the audience laugh.
\\This is a predictable world, I predict,
\\toward which they are guided, not
\\selectively, but somewhat in a way.
\\I have no idea what the measuring
\\mean, but I know it is qualitative.
\\Childhood is a strange place where I feel
\\farther away than where I want to go,
\\nor does it embrace the taste of
\\particular pleasures, such as the car
\\of others, or the time we want
\\to be remembered, tentatively, to
\\establish a new stage.
\\Digitalalads, they are people
\\who believe in an beyond,
\\that someone else is equal to the
\\same things, and if they sense that
\\their life has been shortened by
\\a stroke of death, they feel that it is
\\a stroke of god's attention,
\\and like his seals upon the work of
\\hire and salt, they lay them down
\\and can't see much of the world here,
\\dificapable masses of
\\dishevelled substance, tumulants,
\\justly crewingened from the center of
\\the earth.
\\But they would not talk of the reason
\\for being so tense.
\\They would not make the snow
\\altar of their voices,
\\tonguing with the very
\\grammar of how they feel
\\and also, could they?
\\They could not imagine
\\the downhill slope of love,
\\the roaring in the wind
\\of beautiful and terrible.



\chapter{Jantzen Beach Seaplane Base to Falls Church Airpark}
A ribbon of blue around the corner
\\Congeals around the perimeter,
\\And on the mirrored floor,
\\A chair and a bag.
\\One person peleans on the
\\Buoy Store and offers
\\A card of flower.
\\Outside the window,
\\A sunlit sky
\\Shines on the back yard and is reflected
\\Silverly with each shade.
\\An axis of depression
\\Is cleft, in the center of the earth.
\\This might be the spot where Miles Davis
\\Stood on the ballot trail for a presidency he lost.
\\A scientist is gathering information
\\Inside a starfish, glass-dipped,
\\For the study of lightning lightning.
\\Lightfolded, unmelted,
\\That the golden age slept or dreamt
\\Like a baby that the seahog
\\Stopped in its tracks to see what dreamed the dreamt
\\Next.
\\4.
\\And nothing: the cross slides down the churchyard
\\By a car, snow drifts across the road, the flakes
\\Flutter, falling on the linoleum floor.
\\Going down the road, they wear
\\Raw cotton clothes, stiff boots, then
\\Strong and slick, like captains of cloth,
\\Ready to ride.
\\5.
\\Even yet, this breeze,
\\Even yet, and these coins
\\Flying in their hands
\\Speak of the old merchant-merchants' trade
\\With the town and the sea,--
\\Favour or danger, chance
\\And change, being one thing,
\\Proscribing happier thoughts
\\Than plenary sophistries.
\\These, that wear
\\Their first clear weariness,
\\Grow faint and die;
\\And when they are gone, yet remain
\\Matched with their first sweet spark.
\\?are you then, then,
\\So many and so soon,
\\So many already fled?
\\Yea, they will stay, till winter's freak
\\Turns them back to wholesome clay?
\\Who, hour by hour, in elysian lands,
\\Is closing pond'rous houses
\\With dim, dusky twilight.



\chapter{Johnston Atoll Airport to Caledonia/Grand River Water Aerodrome}
0.
\\6 A.M.
\\The gargling bodies of Philip Larkin and the wood-dioning
\\maids rose-cheeked and white, rosed and plumage-dressed,
\\before us paused abruptly to circle around
\\We stood in line waiting to take the ferry to the
\\Orlieans, who spoke strangely if you bowed your head
\\concededingly, and greeted us with kind words.
\\wages
\\wanted to be repaid,--burdens that have never
\\ended,--an inferior offer.
\\What's a rake of water,
\\written on something else's face? We
\\could have called out to the dogs from before,
\\but as we went, the lights changed and
\\the mist came in, raising a crescent
\\of air, around our heads.
\\Was this a giveaway or a sign? I found no
\\returning force.
\\Damage was done at sea--but
\\no one noticed. The women who made the first rush
\\saying, Like you, I'm coming back,
\\mean it's gone, give me a ride somewhere,
\\back to my car, my deck, forever back
\\to my story, a stranger's
\\heart, its numb body
\\whispering your name.
\\Leads out all unrecognized news:
\\the young wives
\\coming into the car, the young
\\husbands, their mouths living for the sacramental
\\joy, "Christ bring
\\the glory of his gospel to this world,"
\\as if this is the sort of thing
\\they've been waiting to hear, and
\\shouldn't have heard,
\\until
\\they were too tired to look just
\\closer
\\to the sun, to look around,
\\to say Just what?
\\Should've said I wonder
\\what I just thought
\\the like of you
\\what I thought you like
\\Then he leaned over and kissed
\\the back of your head
\\and said I'm glad you liked
\\that
\\Music!
\\Wa-rrrrrrrr-.



\chapter{Long Branch Aerodrome to Rand Airport}
Somewhere or other, either way,
\\blank clouds move over gray Atlantic winds.
\\Towers under the sea.
\\Clapper'd helmets play.
\\The wild wind comes:
\\Sphinx, small and stupid,
\\pirts along the aire,
\\seagulls, whales of ice,
\\rising from the abyss.
\\Old man,
\\elingewright,
\\you were glad of your bunny.
\\Did you?
\\Now, at load,
\\I look for milk, but nothing.
\\I poked the cap on the jug
\\and it squiggled back up to the safety belt.
\\I shave,
\\with a cliff of steel,
\\my head.
\\The grinding of a shutter
\\and a nagging propeller
\\pulls me into the face of the whistle
\\like a stone statue.
\\I have a hat
\\which I thought
\\would be nice
\\to hold.
\\Instead it was a saddle
\\entangled
\\with a chain of candles.
\\Missed another friend,
\\who said he was interested
\\in the story but turned out
\\wrong.
\\When he was taken to the precaution
\\of fire, his face
\\was pale
\\and his lips
\\were formed
\\like frogspawn.
\\That was back when I first saw it.
\\A little later,
\\not nearly half the way
\\down the river,
\\I had to give it up.
\\It had been
\\a long time since
\\having it and
\\which was no accident
\\of birth or sickness
\\but something
\\structured
\\that would become
\\a moment
\\of intense music
\\that would
\\outtake the present,
\\even those
\\dizzy
\\and fragile as house
\\wrecked
\\in a quick
\\wreck
\\in the water.
\\I had to guess what saw
\\us here--
\\I who
\\brought the book
\\to know
\\what I had to know
\\about my own death,
\\if it knew
\\anything.
\\That year
\\I published The Collected Poems
\\november, 1919.
\\I wouldn't have walked
\\uphill to old Madison
\\without seeing
\\severions of you
\\r days.
\\You saw me clear
\\and unfazed
\\the many ways
\\I tweaked my face.



\chapter{Islamabad International Airport to Kallang Airport}
White dust
\\over parking-lot, red cars crawl
\\under Taroolbay-Unity Tower,
\\blue and white women's wings waver
\\beyond the logic of numbers,
\\this air-show of European coppers
\\well above the world for ground,
\\no wonder that's the Italian border,
\\this dust-hill of the trestle
\\between two points of compass,
\\this China box, this red floor
\\peaked by the thin needles of
\\abandoned windows, this cross
\\whose light throws no shadows
\\when it is full: no trees,
\\no mountains, this sounds beyond
\\the imagination, this dust
\\that could be knocked out
\\and this would be
\\the universe!
\\Petals of a flower
\\playing in the glassy lights
\\of the tiny fluorescent light
\\before the died, the dying,
\\the dying richelieu
\\when the name is revealed,
\\it will be remembered,
\\the name again and again
\\familiar in the ear, even when
\\the exact name is forgotten.



\chapter{Nahanni Butte Water Aerodrome to Belle Creek Airport}
JUNE
\\Shining under the lamp, trackless
\\Flight sucking
\\the air back behind,
\\Between the smog and glass sea,
\\Between ivy and laxer wood,
\\Come down to me
\\there where the road
\\east from the right
\\Chances, like changing
\\chances, coming down
\\break full and raging
\\fly the farthest
\\Breaking down the middle
\\of the journey
\\intricate
\\What are the rules?
\\Oh never mind them
\\they are the greatest
\\Rules but the worst
\\No one over thirty
\\shits with
\\flight.
\\Come here
\\Begins to die
\\Let us make love
\\Let us take it back
\\let us give it back
\\let us know it
\\to the Ambassador
\\National Guard
\\Israel
\\Hex-eyed anti-Semitism
\\the yellow brick
\\photo rolls
\\for Jews
\\Butte
\\Upstate New York
\\The people
\\the people have made me
\\a beautiful flower
\\dripping behind
\\the journey
\\of the savage
\\I am beautiful
\\I am a woman
\\little Native
\\a child
\\lying in the field
\\tar apart
\\for joy of childbirth
\\unless
\\I am beautiful
\\I am a woman
\\patterned
\\whenever
\\I am beautiful
\\I am
\\owed to be
\\as raw
\\and catholic
\\as any dower
\\and caught
\\as a fish
\\and walked
\\out of infinity
\\without
\\water
\\I am a woman
\\and all that
\\was a flower
\\and flouted
\\far away
\\in the traffic
\\of the night.
\\The road
\\sends us
\\arm in arm
\\beginning
\\to sing
\\baby
\\to stammer
\\and I am
\\a woman
\\and
\\a tree and
\\a cross
\\I am
\\a word
\\and
\\a prize
\\for the face
\\of the thing
\\and my
\\flower
\\to sing to
\\and to
\\be sang
\\more
\\when
\\at home
\\and at war
\\where love
\\is lost
\\that's what
\\I am
\\woman
\\and not white
\\but white.



\chapter{Kraków-Rakowice-Czyżyny Airport to North Field}
I am, I am, I am the,
\\I am the, the, the, the, the,
\\Father,
\\Father,
\\Father,
\\Father,
\\Father,
\\Father,
\\have no more to be said,
\\Here is inside the one that,
\\Here are its hairs,
\\Here are its palm,
\\Here are its arms at their nature,
\\May be its master
\\World of Work
\\Words
\\Words
\\Words
\\About how this word
\\Is not attached to,
\\As in this story
\\The weave of the rais'd vine
\\About the neck of Samsara
\\The chi-tibblat of the Magistrate
\\Of the river
\\Over the threshold of the Enrique
\\Of three men, one of them
\\American good
\\And one of them Mexican
\\I nant
\\When they were done
\\With the Mexican gold
\\They left and the flow
\\Stood there like a golden storm
\\On the evening of the flood.
\\There was the river's reflection
\\Turning aside from the motor-car
\\Roar of the wind from the crest of the Sierra Nevada.
\\And the end of the river
\\Where the tumble-cat started
\\When the wind began to blow
\\One can only take means to destroy
\\The life of the imagination.
\\In the end the imagination
\\Is not victorious,
\\Is not powerful, is not complete.
\\Yes, the real horse cannot be rider
\\And long-legged street-bred gentlemen
\\Hold lightly HRP, and sell that horse
\\For a few pounds and change your underwear.
\\For an end to this
\\Earth's animal
\\I call the horse Rappice
\\,
\\The horse that God gave him
\\For a way to live.
\\And I shall live forever,
\\I shall live until I laugh,
\\I shall live until I cry
\\From my throat I shall breathe from my skin
\\And the bells of my body call:
\\The world has ended
\\Flowering in laughter
\\Inside the open grave.
\\I call my father
\\And he calls me Mary,
\\Mary
\\.
\\I say:
\\Love,
\\And my love,
\\And my life.



\chapter{Lympne Airport to Arnstein Airport}
Leaving the DOK E. "Grand Central Station"
\\worn shoulders, child ears, wings, head finally away from me,
\\insects crawling up hydraulic levitation
\\\& out into the terminal, tide below sea flow
\\--in a strain of absurdity on the accord music--
\\my other arm that left hand punching pained it out,
\\one fist down for a moment, heavier
\\and then away again, along the giant ground
\\the metal wings of birds disappear,
\\as vanishes into the symbolic woods.
\\And the real meaning of these trees
\\depends on what you believe
\\to live inside your body, Bay Creek
\\calls your name. My father's wheelchair
\\glides from the kitchen to the bedroom,
\\his whole body
\\shadowing him, disappearing
\\into the bedroom's other red shadows
\\until he's the sitting-darkness
\\of the moon, and I'm the one
\\who's left behind in the dark room
\\because whatever made her
\\Magic
\\(though once she was no longer magic
\\and meant nothing), I'm still
\\the victim of logic, fire, and chaos
\\Related to the helpless and numb,
\\and loving the crap
\\Who's been doing and not
\\anybody is,
\\including me, which is lots of
\\foolish making hundreds
\\of mistakes in the lives
\\of scientists, quickly
\\not saying anything, even bringing
\\the monster down, for which
\\we're doomed. And no admiring ear
\\will ever hear of him,
\\except for the cool flashes
\\of his rusted mustache
\\and the quiet walk with him
\\to the theater
\\in the middle of the night,
\\where the loose hooks
\\dance on the inexpensive gold plates
\\like the glistening shoulders
\\of a youth, dancing
\\to the spell of his own voice,
\\and dancing
\\in his shirt, windmaker
\\and windbreaker and heartbreaker.



\chapter{Xi'an Xiguan Airport to St. Charles Airport}
Tuan xiguan stands outside the airport city of jiang-kong,
\\Tuan Xiguan held his people preparatory,
\\From top of Kwi-kwang mountain, I new pilgrimage
\\By foot to Kweg'i river,
\\via the S-shaped sandals of the eminent
\\Wiang-piao.
\\I depart from Tchingon
\\On the Wpalo Road
\\To the north of the Three Gorges,
\\From the capital of Shataballa.
\\Day 3? I don't know.
\\Weightless enfolded in comfort,
\\Bones carried down by the softening
\\Mass of the carrying,
\\Softening. Too many washings,
\\Dries of iridescent shells.
\\How many people wash the plates,
\\Dust in the shower, wash against my feet
\\Then hold on when they have to.
\\14. And the second Afternoon
\\He sticks his head into the portrait
\\Of Pilate above the tower.
\\This is the Duke of Ormond's house
\\Against the parched balcony.
\\The white church door is open.
\\15. A bare church stands against the fence
\\To back into the sea.
\\Fish in trout spine flake from the baptists.
\\Pilgrims rock their bones
\\And pilgrims come in.
\\16. The doorbell rings.
\\Nobody knows how to wake.
\\The neighbors check in from the street.
\\We drive 20 miles to our home.
\\17. Desertions for the crown.
\\And the crown is spoiled.
\\With a flourish of the earth's own self,
\\Or might be. The sunfeathers scatter over the walls.
\\The enchanted ivy cry, the boughs rustle,
\\I lean before the gate,
\\My hands dense with rainlight,
\\Create a sudden desire.
\\18. A shadow too.
\\A silence of those who have lain dead
\\And inspired me with talk.
\\Their hearts are my eyes.



\chapter{Lewvan (Farr Air) Airport to Hershey Airpark}
Light notes and arrows
\\Rabbit screams and light plashes
\\Struggle to get off the ground.
\\The black man says,
\\"Get out of the way,
\\Take the top of the bag."
\\They say,
\\"Go where you want to go."
\\I think they watch for an answer
\\Round the hazel bush.
\\I think they wait for an answer
\\Into the sky.
\\I like to believe that
\\Sometimes the flights are
\\Borne as thin
\\Bench pressed to lunch.
\\When I see them
\\Going down
\\It seems to me
\\I'll know where they are.



\chapter{Stanley Army Airfield to Lake Louise Airport}
FAME'S FATHER
\\, honoring
\\the dead
\\who have served or
\\killed
\\myself,
\\I am willing
\\to
\\retreat
\\from the arms
\\of the insane
\\or
\\terrified of war.
\\My mind is waiting
\\rich heaps
\\of figures
\\who heat
\\the gas
\\to
\\plow
\\despatched
\\by the highway
\\flop
\\ringed
\\with Crumbl
\\red
\\to
\\the tall
\\white plane
\\flying
\\in the
\\universe
\\... photograph
\\my eye
\\seeing the dream
\\of the Dulles
\\\&
\\the Gagerman
\\senseless
\\before
\\the Dulles
\\who programmed
\\the world
\\in the cry
\\of Zapotec
\\more than the
\\late
\\nuclear slag
\\forbid...
\\window
\\my mother once
\\smoked
\\of a church
\\in St. Charles
\\who
\\opposed
\\waltzing
\\to a bouncer
\\looking
\\east
\\from the window
\\of his room
\\beside the man
\\he was
\\before
\\what
\\he thought
\\his mind
\\would end.
\\TO A MAN DYING ON HIS FEET
\\--not that we are not all
\\"dying on our feet"
\\but the look you give me
\\and to which I bow,
\\is more immediate.
\\It is keenly alert,
\\suspicious of me--
\\as of all that are living--and
\\apologetic.
\\Your jaw
\\wears the stubble
\\of a haggard beard,
\\a dirty beard,
\\which resembles
\\the snow through which
\\your long legs
\\are conducting you.
\\Whither? Where are you going?
\\This would be a fine day
\\to go on a journey.
\\Say to Florida
\\where at this season
\\all go
\\nowadays.
\\There grows the hibiscus,
\\the star jasmine
\\and more than I can tell
\\but the odors
\\from what I know
\\must be alluring.
\\Come with me there!
\\you look like a good guy,
\\come this evening.
\\The plane leaves at 6:30
\\or have you another
\\appointment?
\\THE PINK LOCUST
\\I'm persistent as the pink locust,
\\once admitted
\\to the garden.



\chapter{Chapleau Water Airport to St. Charles Airport}
Turbulent, fatigued, you queue for
\\Terminal,
\\burned at sundown on the Cyrus bridge,
\\a cross-screen jacked
\\double, past Verizon Wireless,
\\standing on a corner
\\trailer tyres,
\\425 unmarked cars under California weeds
\\waiting for a Border Transport Armored
\\to en route between S.F \& Marin
\\Commuters crowding the
\\Fortry Years Old,
\\england's gay TD
\\approaching Rio Grande,
\\striped commercial bluestanders
\\venturing the American Dream
\\england's Cowboy Stadium
\\where legions of black spotted
\\paintball enter the bull rings
\\of SuperFly's crib,
\\and the silhouette of a red small
\\fly
\\swoops closer, Scot dead john,
\\coach ride on the radio,
\\the knuckled grip of iron
\\in air, and the high
\\squad of County fairies
\\volley on the TV screen
\\grasping their images       .
\\And I, panorama-wide,
\\water-hazed, but still
\\trapped by urban shadows
\\everywhere,
\\even the Santa Ana winds in the trees
\\loudly trumpets
\\and African drums
\\that remember       .
\\What else is there to fear?
\\The past?
\\And the future?
\\Death?



\chapter{Lac Gobeil Water Aerodrome to Armour Heights Field}
A bottle of blueopy Jack brandished green in the bar,
\\One finger hooking the muscular silhouette of your buttock,
\\My finger liquidating at the wellbore, GI cartons
\\Mul-che en part tomatos and beer cans,
\\On a par with Pale Mechanism
\\The strong jet-bumper driven into polymer
\\air, the bubble-sphere urged jet-plunge,
\\crustace-edged, down the center struck
\\into a purse of bright copper
\\air, my finger the voice of the capacityannon
\\Speaking the terms of more tin skinlones
\\None hears screaming Danny Boy --
\\Yes, that's me.
\\*   *   *
\\At Lake Victoria, the convents
\\Turned their pounds through the sawdust
\\pile in the grasses. They bowed
\\Out of their funk, and by the labour of
\\Waving dry their shirts, but remained
\\Ebony-clad. To what good
\\Thinking Kenney meant, we'd say,
\\Father, you might have turned your back
\\On the outside, but you chose
\\Today, turning your back, within
\\The ACT of being here,
\\Had you chosen the way
\\Things learned beneath, the learned
\\Rondeaux that rarely had a clover,
\\And flicked a gray-spun wing.
\\For you were never pure,
\\And you were never thin,
\\And you who err,
\\Had known what you could handle,
\\History's bloody price
\\Always smothered in doubt.
\\WRESTED FROM MIRRORS
\\In the mirror one beholds
\\A bearded man in underwear,
\\Three cowls on his brim,
\\His three-hatred helmet,
\\And his hair shorn,
\\Fringed with sandals;
\\His bretan body
\\Grows thin without water:
\\"I am real," he laughs,
\\"I'm real," he laughs, "Oh, I'm really
\\Just!"
\\His laughing comes out of his mind,
\\And his wife lets him laugh
\\Most of the Sabbath day.



\chapter{Tonopah Test Range to Canadian Forces Station Ladner}
We are the test ground of a now undamped world,
\\Covered with squeamish birds, tigers, and skag,
\\Dedicated as an eyed dog to our test tray,
\\Tanks roast in my lap, smoke and broken dice,
\\Someone's mother lulled to sleep, our nobler heat
\\Hammering the old tyres, the grass-eaters fast,
\\My spade-boss hacks his way up to the nut-alley hat,
\\He pushes his lever through the bags to the loo.
\\Git-diggers shout as the cleaner-diggers go,
\\"The Ship is sweet so long . . ."
\\Their frigate takes fire smoke and picks up speed,
\\Her star turns inward on the ring and opens fire;
\\The leopard steals with narrowed lids to lay
\\Pale Japhethian the North Star,
\\The African soul enters the room,
\\The roots of the water-lilies
\\On the row of flags that wave,
\\And the sand-hills lie flat to the beach
\\And the long coastline horizon.
\\...
\\A boat comes down the coast.
\\A soldier comes out of the boat and stays
\\with the men,
\\He puts his head round about the side
\\Of the boat, he does not waste powder
\\On the lawns, on the beach of the sea,
\\Nor mends the ruts on the ways with his hook,
\\The hook is from the sky and the body of the shore.
\\"Hurrah!" proclaims the announcer.
\\War-brewing bears
\\The shift of the tide of combat,
\\The single combat now an indissoluble,
\\The moors raised up their voices and shouted down.
\\Shouts are heard, not like the sounds of today,
\\But the hail of the heraldic heraldry
\\Is louder than the music of the world.
\\"aven," says the soldier, as he embraces.



\chapter{Fort McPherson Water Aerodrome to Liege/CNRL Aerodrome}
Strew on her roses, roses,
\\and never a spray of yew.
\\In quiet she reposes:
\\ah! would that i did too.
\\Her mirth the world required:
\\she bath'd it in smiles of glee.
\\But her heart was tired, tired,
\\and now they let her be.
\\Her life was turning, turning,
\\in mazes of heat and sound.
\\But for peace her soul was yearning.



\chapter{Gainsborough Airport to Batchawana Water Aerodrome}
ICE is the hypodermic flight path.
\\ICE is the single rose of the boulevards.
\\ICE is the singular flower, the poem.
\\ICE is the black and white photograph, from Chimney's
\\found face.
\\IN THE RED BOX at the top of the stairs.
\\IN THE ROLLING EARTH.
\\In the middle of the journey of our life
\\I found myself astray, lost
\\in the swift song of the water
\\bossing the white mist on the cliff below.
\\IN THE FOURTH YEARS.
\\First of three things this year
\\the sky took off like a plum
\\and the clouds flew above and then returned
\\to the sky; the sky then moved
\\and the clouds moved again, and in the canyons
\\revealed their spectre,
\\flycatcher, of course, who I thought I'd seen
\\in the Minsk weather,
\\someone in white, so I said
\\to the ghost of Sandra, "God,
\\this looks like a tree,"
\\and she showed me, via the screen,
\\the insensate green of the primrose,
\\and the pale yellow of the witch,
\\a woman who might have been
\\a carpenter, so I said,
\\"This is the steward who throws knives
\\over the cattle. . . ."
\\She threw a knife at me, so I said
\\to the ghost of Sandra, "Jason,
\\so your story sounds pretty to me,
\\a lonely tough-ass
\\who's come back from the war,
\\off somewhere, yet kind of lonely,
\\and really desperate, and mean as all
\\the other ones,
\\who don't get laid, or sleep, or even
\\take a walk, not even go to church.
\\This is where the spiritual world thrills
\\the cynic in his story, which has nothing
\\to do with the world's fitness, despite
\\the weather, the climate.
\\Just as the spirit is the enemy to bad
\\people, the same earthly
\\opposence competing in its.



\chapter{Kaanapali Airport to Cartierville Airport}
Your lover comes once
\\Airing the garden.
\\You have only to take:
\\Something bitter
\\Your tongue gives up to:
\\Poor fool, you don't know.
\\Your partner exists
\\In your bed.
\\How you say the n word?
\\You have forgotten.



\chapter{Hidden Bay Airport to Hillsboro Municipal Airport}
I driving southwest of all these huge
\\brick walls painted bright green and blue
\\hey, hot orgy-hot, what's
\\hot smell?
\\Man, a grasshopper gropes his skin
\\for his dead glory, the dick-
\\faced gore bright
\\on the screen,
\\scalds his knees
\\yet this very moment,
\\not the rocket burns,
\\not the eunuchs
\\seawash in the bushes
\\slung into the night,
\\not even the glimmer
\\of a nearby wheel,
\\not the dazzle of
\\a crowd of automobiles.
\\This liner she's been
\\fighting on the stand
\\with her hands in her dress
\\hands
\\in her hair untucked
\\to her shirt
\\left
\\right
\\and the tall woman
\\sitting at a window
\\notes
\\her own story
\\Keats:
\\"We were lost
\\when we went on the edge
\\of the blue wave
\\over a coral rock"
\\what is a cliff
\\and what is a cliff
\\you can't climb
\\is the middle of the thing.
\\Wave upon wave
\\held the eunuchs
\\while on the shore
\\hands
\\in and out of their
\\belly
\\people
\\on and on
\\without
\\compressors
\\waiting
\\between the file cabinets
\\door and door
\\shelter
\\the fools are jerking
\\their heads
\\are full of yellow
\\fire
\\falling
\\when the light appears
\\on the stairs
\\hands
\\clenching around the holes
\\sprouting
\\at the lateral
\\dockets
\\just the volume
\\the liners
\\out of the room
\\by the bed
\\in the noise of washing
\\clothes around the head
\\cut and torn
\\bodies
\\swallow the sound
\\they form
\\as they move
\\from
\\edge
\\to ledge
\\Don't be fooled
\\it's the sound
\\we hear
\\when we look
\\the volume
\\unciatingly
\\called-our-
\\selves-
\\to match--
\\and don't
\\be deceived
\\about it
\\SMALL THE THEME OF MY CHANT
\\Appeared in
\\LG 1867
\\on the back
\\pacing
\\bald hair edwalled
\\from my head
\\as it was
\\too
\\early for
\\the.



\chapter{Redvers Airport to Tagbilaran Airport}
intercepts, captureions, gangs, one calls,
\\the confused monsters of the marshes
\\intersect beyond the wooded headlands,
\\inside skullgalactic whirls the skylark scuds.
\\1.  amalfi, harvard university press, 1918. the first group baptists line the town,
\\the next the surf. one calls, a third group, the sky.
\\two centuries of waves in a single stroke,
\\rails finish the sea. who enters the seventh movement.
\\this season's sleep is a memory, a train that arrives
\\to some one graveyard in a steam-hemm'd land, no one
\\steps into. this carcass life is not torture.
\\you are not dead, you pass out of something reachable to you.
\\you pass from form to form, you feel the blow,
\\there is no art. here, done in gold and plebeian stone,
\\the mind makes images of states, penitentiaries
\\to office stations, resurrected only yesterday.
\\The mind thinks it is unknown, always the man who dies,
\\drinking wine and sleeping . . . and again
\\with rock and loire and cascade of pyre-cornered light,
\\endingless, empty, monumental.
\\2.  segesta, a.  anyway, alberta.  even as i knew
\\the almanac kept track of the ends of the earth,
\\and the boundless realms took form. that's why my name
\\was chosen even then into the circle of the three.
\\the father's long-planned gift of paradise.
\\the father's glory.  i would dedicate
\\all my grown-up years to dancing and song.
\\i have learned the luck of the fates and the needs
\\of countless lives that lead to shame and shame on you:
\\who have seen the light of the free and the air,
\\and weighed the meaning of the things they know.



\chapter{Action Airpark to NAS Tongue Point}
Tiny orange-wing-like trees
\\Blossom and spread; the sun shines through
\\The Santa Cruz and against the skies
\\Smiles at me.
\\Munich
\\Light as a clutch of mosquitoes
\\Coils from the indigo sea
\\And rides a lone canoe
\\Back to Canada.
\\Portioned like a ball of fire
\\From the Indian's sunset,
\\Smoke from the redwood grove
\\And sticks to the shadows
\\Of oaks and firs.
\\Whence blows the whistle?
\\Its light is confused with odor
\\Of roses, its scent
\\Royce suggests, and conchs the flame
\\Fading into flames
\\As the temperature increases,
\\Lifting the cottony scent
\\Of the rezened days.
\\When canister-calls fall
\\On the backstage, and the moose
\\Lean to the door,
\\When the flag refuses to swallow
\\One of its symbol shirts,
\\And the winter resigns
\\For a long spell
\\Of snow, rain, and rain?
\\The stars take a wrong turn
\\And the moon too,
\\And the months birth the year's double
\\challenge unfolds.
\\Over the years it has proved
\\More real than the real man,
\\And here we enjoy
\\The very acrobatic
\\Thing of poets,
\\While the fatalist
\\Pauses to catch
\\His breath before he says,
\\"I'll be real."



\chapter{Losey Army Airfield to Mayne Island Water Aerodrome}
Weathered and tenuous, sullen and stubborn,
\\Losing its floe-blown plates of Afghanistan,
\\Pale where the sun opened his eyes,
\\Barely unpacked before again in boxes;
\\Seemed to ask us for our own
\\"To be blotted out by time"--oh, foolish.
\\Gone is that last ancient pitch
\\Of peacemoon, that pandora bore
\\To Helen--but the fang pierced her heart,
\\And, soft as ever, the blackbird held her hand.
\\Oh, things more than mortal! it was she
\\That made the General drooperous,
\\Dissolving his "General's ermine."
\\Leave him, lady, to his wide winds
\\Where the blue mauretitude chants
\\Her bilateral bushwax;
\\But let him know, (for he will never woo
\\The same kind of soul for a kiss,
\\Neither specially emily, nor specially
\\The lady with the diadem.)
\\I'll send a kiss, for that would be
\\the quickest sent, the friendliest sent.
\\What if I touch but a finger?
\\Bit, bit, a falling leaf may spoil,
\\but if I kiss the bushbaby,
\\the whole habit field will come swiftly.
\\I have a bilted heart, you see,
\\And something else (ah, why not?)
\\Inflated by bilted heart syndrome,
\\Which somehow is not what these ladyes
\\did to me, ere ever kissed or said.
\\But what she meant, whatever she said,
\\I only and solely understand;
\\And which is the book of Miss Green,
\\The book of Miss Green, our Lady Green,
\\who has so many friends
\\And people to whom she is silent
\\And moving too fast to be well served.
\\Perhaps there are times
\\When she bursts up her chatter
\\And everybody finds
\\That sometimes their feelings get to.



\chapter{Limatambo International Airport to Saline County Airport}
A dull retrograde student rides westward
\\Toward the breakneck. The flight of the child
\\Over the firelight spread a circle.
\\Around me on the crowd there is a throng
\\Of smiling workers at their fields.
\\In the middle of the night, on the edge
\\Of travel, someone leans studying
\\The complex formula of snow.
\\He joins the newcomers as they walk
\\Past a cold coffee table. They come,
\\She and I, down a escalator
\\Into the rain-dimmed sky. Suddenly
\\An announcement drowns in the roar
\\Of office-pity. The jukebox
\\Swings equal parts to its own
\\Becoming the address of the state.
\\Around and around and around
\\Everywhere the same sound
\\Of the tragic car
\\For which millions struggle
\\Until the Night comes.
\\In the Desert of Atacama
\\From the state of New Jersey,
\\There had arrived now a museum
\\Of visitors who studied the windows
\\Of the world. Among them,
\\There you had known your share of surrealism,
\\The psychosis of ordinary men
\\Innaments of the outrageous,
\\The capillary clock on your floor,
\\The perfect clock that corresponds
\\To the first and last science.
\\Without tautology, nothing can
\\Mistake the basic tenets of the Nouveau
\\Royal de la Mer, un Odin,
\\"We are from Ovid you shall see."
\\Our heads, the instruments of our thought,
\\Glaunten softly to one another.
\\So much for the Editio of the lower classes!
\\Though, as above the threshold, they know
\\We are only water, they mob us
\\Suppose we are rockpaw under the sun,
\\They come to us stages and torches
\\Leading to the martini test.
\\These are the Novi Kaleys,
\\The unossibly syllables that mean
\\More than they are.
\\"Et saint apollo"



\chapter{Minoru Park to Kaanapali Airport}
I seek no favor
\\unto the fly
\\of this drab-and-tongue Black Maria,
\\flight of Avian refugees,
\\entertain me
\\in a ovid of Hum
\\pipe-full of Crime,
\\whose decadence
\\in this smoky medallion
\\cannot be denied
\\the stomach meat of the Lord.
\\I ask no favor
\\because no need
\\to lean in my work:
\\out of the long arc
\\of wing-dependence,
\\I make no sound,
\\like the Angry Lady
\\she's still wearing
\\in her hair --
\\I ask no favor
\\because no need
\\to lean in my work
\\because I'm building
\\my own book of words
\\insist that I print
\\work to name:
\\Tomorrow,
\\I say, she says,
\\till I'm gone and I've got
\\a good place to write
\\.
\\All I know is
\\sonnets and song.
\\I know what they'll
\\sound like, but
\\ten thousand miles
\\away, so I'm
\\happy I can
\\barge
\\myself out of here
\\and be doubtless:
\\though the heart's not quite
\\shut up, though
\\the ear is not, I
\\have the heart
\\to remember to
\\call me back and leave
\\my own twisted
\\triangle of life
\\where I'm not
\\and I'm not obligated
\\to pick up
\\the damn flies
\\that charge
\\with acid and epoxyylae
\\and know, or that
\\you know, I'm here
\\in this forest
\\of forms, and the
\\empty
\\hand
\\that made me
\\behold that I love
\\the useless
\\part of it:
\\don't use the one
\\not watching;
\\the cow clock
\\it's running you might
\\wear
\\a new shirt
\\and feel the voice
\\of the clock
\\pipe-shaped
\\in itself
\\irregularly
\\out of moisture
\\no other
\\presence I know,
\\the rest might
\\be giving up
\\its motion
\\to be more like
\\a purple music
\\on the ear
\\inside the skull.
\\3.
\\Here I am, decades later
\\moving in the
\\belly of my love.



\chapter{Grand Central Airport to Fort Grahame Water Aerodrome}
Tuned to the music of centuries,
\\the robber chants to us.
\\How they got there is no question.
\\One crew of green faces
\\was Freemistic,
\\one cell of black hair.
\\The promenaders hold their hands,
\\and high up in air
\\in their oval hats.
\\It's said the former books are blank
\\on the beep of the promised
\\line, the text on the dust
\\will be said to make room for hope.
\\It's said the former books
\\are full of death,
\\that ones in which someone died
\\lives in the future
\\and all of those who died that way
\\have found new paths
\\and keep his footsteps back.
\\Pliny and purvy blossoms climb
\\the lines of the freckled rocks,
\\where anxious Whitman is hanged,
\\while the poets are crowned and what
\\is said is made new by the dust.
\\Children twist their hair up
\\and make them cry for sun,
\\while beyond the mountains
\\the lights of a former world
\\alleculate and mellow.
\\Blood bubble up in the immigration queue,
\\the customs are logged red visitor doors
\\beyond the refugee shower curtain
\\and the wombs betray them,
\\spoon-shape moths who hover here
\\then drain and spill their nests,
\\and the brown meandering river
\\who keeps itself just off the river.
\\If anything could destroy us
\\it would be a wind that seeks
\\by the very water's edge
\\as if it were no longer
\\water         .
\\Now look
\\Look
\\The world is green this morning.
\\We live in the belly of the earth.
\\The heavens fill him and her
\\like green griffins.
\\This is the way he balances his mornings,
\\which are by day like this,
\\non-fire         .
\\The gods sit down in the theatre,
\\and the ladder prepares for them,
\\it was their nature to do this.
\\It was their nature to do this
\\and they are not here to see.



\chapter{Sioux Narrows Airport to Sierra Airdrome}
1200 Master Floor
\\Trans flight from Sierra Mountains
\\Falietas take off their intercepts,
\\Embellogovernmented, unmet,
\\For Bovril's sake theirs and my Ford's
\\Nothing is sacred anymore, not Davis
\\Trust me or me letting the Yellow Peril
\\slip through its frontiers \& undulate
\\Spirits breathing palmalm \& oiled hair,
\\Executives with stringed guns
\\Chuckwheeling, caked men and women
\\Straining toward their burning desires.
\\Midcentury, Adult Correction, Dry
\\Quote
\\I'll go to arms for an Eagle Scout
\\Am I halving myself in this
\\war, stealth, abiding, believing
\\laid to me by prison strings
\\under antique vault doors?
\\A secret stenographer said:
\\"See how the estate they've got."
\\Secrets notebook
\\I must laud the Anti-Desperacy
\\of old men,
\\my heavy skins, a tendency toward fevers,
\\my description of theft.
\\What I must admire: the idea of sheep
\\tracked in the catalog.
\\Philosophy made me and Byron,
\\a man, beautiful and childlike,
\\who lost his brain over a hundred challenges.
\\It was a lovely show--
\\The life I led, the life I gave.
\\What we felt and what we couldn't conceive
\\about it.
\\Now I'm only a layer of clouds,
\\verdegris--fresh memories--
\\from the Dutch Kaspa camps,
\\the base runisphere,
\\so far north as the eye could see
\\from there,
\\on the other side of the seas.
\\That's where the maps were made:
\\Asia.
\\Euros invaded by China,
\\Kingly neutrality or homicide.
\\Preyed on either side by both,
\\by the unrepresented elderly gentlemen
\\who wore white mule shoves.
\\Every man wore a
\\wide hose,
\\and a mustache,
\\which suggested--
\\stonewall's
\\bad friarish.
\\Disturbed relics of the present time
\\Move in the stream their flood of paint.



\chapter{Esquimalt Airport to Richmond Naval Air Station}
IASPONA, Palestine, Yes Mad About the Hour
\\Fifth Floor
\\bustling winds
\\and I train my guitar
\\an ideal size
\\is the airport: I re-examine
\\your quarter century arch, decked with screens
\\like a tiny mural of the mythical moon,
\\interrogating walls and barred doors
\\at the four-hour train dance,
\\screened dim before the bearded cloak-seman
\\collects and clutches
\\for the saxophone:
\\ah, the ancient machines
\\of bone and bone,
\\the wet wind in the wires,
\\this alloy of the grains
\\and the faces,
\\these achers and acches,
\\only the fluid, the mobility
\\and the power
\\of the fluid and the threat
\\of the next infection
\\the threat is made
\\and the hero is made
\\threatened, the hero made
\\squealed and hurt,
\\let the words ooze from the lips
\\of the man who beat the king
\\and his ass-eleon still look
\\like a mass of flayed flesh
\\that moves again to speak
\\to the living...
\\A boat comes round the edge
\\of a bay
\\the hermit curves of boats
\\hang heavy in the air
\\at the edge of a bay
\\yes it's a boat
\\and the rustled hair
\\in the oar
\\holds her breath
\\the odors
\\from bars
\\and windows who walk
\\panic
\\ment
\\a city of death
\\and waking hold
\\stilled
\\in
\\the oldest memory:
\\a young man
\\on the second floor
\\where someone's bed
\\beside him
\\shuffling through
\\the sponge of his breath
\\unable to assume
\\the world.
\\A square of skin
\\as some great
\\undershot
\\spreading
\\easily might have been
\\the man the bridge
\\we stepped
\\to.
\\Reached down
\\to feel
\\the morse
\\under the chin
\\the spine
\\as metal.
\\We might
\\have
\\been fortunate
\\to mate there
\\at the beginning
\\of the river's dance.
\\I cannot think
\\replicated
\\cheap talk
\\as it befit my life
\\and I
\\wear the die
\\of important history
\\in my uniform.



\chapter{Canadian Forces Station Ladner to Milk River (Madge) Airport}
Catches the military would serve us,
\\our air-breathing avortakers
\\and our rural servants coldly slain,
\\Canadian Forces
\\sources sources say the Polis can be
\\killing at Northcliffe Tunbridge,
\\while we wash the silver paint from the walls of the
\\universe, green moss from the eyes of Alexander Samarcand
\\faithful as walking rope.
\\We know we require what we want,
\\we carry us,
\\reap it, wear it,
\\imperial, pale,
\\marvelous, horrendous.
\\What we get we must buy:
\\somebody else's fantasy:
\\some rural backwater charm,
\\some North Pole stuff,
\\some guy's still-born child.
\\Wereen Smith: editor of the
\\Post Gazette
\\,
\\and author of
\\KOOW MANCULLIN
\\.
\\And so, of those eighty-three
\\who now sit here in Ottawa
\\suffering
\\to get the McGill University television
\\to broadcast in a minute
\\tis saying
\\and you're there,
\\so I say
\\you're
\\well right, you're
\\not
\\I'm not trying
\\to impress you as you sit here
\\silent,
\\mouths tumming,
\\breathing through my head,
\\here, are the best
\\time of day
\\that I know.
\\You are serving me coffee.
\\You remind me
\\of someone I knew once,
\\even better than I
\\laughs now,
\\he's still alive, her coffee
\\is almost cold,
\\I can't eat it.
\\Did you ever really have a brother?
\\The poetry movies are always
\\singly inaccurate,
\\the poetry stage is
\\not what you're
\\supposed to do,
\\the poetry audience is
\\ashamed of you,
\\you remind me
\\of the dead we have
\\returned to,
\\they've become friendly,
\\came to sign autographs
\\on your drive
\\and where you've gone
\\is no longer
\\so scary,
\\you lose your lust for
\\ordinary men.
\\It's only wanting
\\to give them
\\everything?
\\You're a.



\chapter{Naval Air Station Alameda to Naval Air Station Squantum}
A disturbance of papers and magazines,
\\Leaves of Grass, city-dried lashes,
\\Unwashed mouths of crackling wire,
\\Wooden ends of coral-shade, wet tufts
\\Of orange-ringed prongs, —
\\Does the city demand more than this?
\\Wanting to guess its worth?
\\So much for the city!
\\0 Kingsley Avenue shell-darkness,
\\Trees shrivelled and speckled like palm-leaves.
\\'Lights out in the alley,
\\Publication still though?
\\Ponderous purpose
\\Disappears in the blink.
\\Savantism
\\Embedded in the dusk.
\\The purpose of the city
\\Is only a knot of mosquitoes
\\That still throbs, quivers, and twangs.
\\'Here measures pace and distance,
\\Turks or visitors, foreign and in-your-self,
\\Category and Type, homosexual, [here
\\the heart is the gate house archangel
\\Theristade
\\Golgotha in a tent, harper's magazine, december, 1919.
\\The Rak (Sweat Jacket) Born Yesterday
\\Rudy-nosed, a warts-eyed race
\\Of none, yet driven
\\To preserve the integrity of the youth,
\\The fuzz-head captive
\\Of adolescent thighs,
\\Then spent a year wandering the city
\\Where his rugged rear door
\\Admits him to the scratch of the soul,
\\A dragnet, no pun intended,
\\Who handles the grill on a cotton drum
\\Under a sign that says "Mama I Love Crispy Wafers So."
\\My daddy put me in the first bed,
\\Before I made mine orator;
\\And there I fell in a shuddering sleep
\\With old tracings of the brute sun,
\\Imagined a town I'd never seen,
\\A gasp I never got, or got, or lost,
\\Or inspired, or even saved.
\\So some character female
\\Or maleudo knot or womman,
\\To be dragged matched or dragged away,
\\Born into this world, imagine all that comes
\\From unutterable mystery.



\chapter{Göteborg/Torslanda Airport to Broadus Airport}
Axis! that flows to-day through my fingers,
\\peaceful, calmer, arm'd with golden wires!
\\Axis! the huge, gaping street-lamps reflect
\\their tinkling music, their clear colours!
\\Axis! the air I breathe, the car I drive,
\\the city of joy, the birth, the tomb,
\\The air of song, the air of saving friends.
\\Axis! the black ship mail'd with iron,
\\grey wafted thro' the mist from the ships,
\\The flotilla of sweep-lines and hose-carts with
\\the racing of the ships!
\\Axis! the long sea-lanes protect
\\sleep in the greenness of the day,
\\And the long sea-lanes circle the tiny shore,
\\sunny noon and night in the bay.
\\Axis! the field-shed drapes my head,
\\melt my temples, my eyes,
\\Myriad-meshed through the mist,
\\the bevels at the door.
\\Axis! the house of life i see,
\\the house of madness, hell, and helle--
\\Methinks the house i'm in, dear,
\\the house of bondage, be not afraid!
\\Side by side, while bold slatterns run
\\in am'rous cosy towns,
\\We knelt with ancient natal scream.



\chapter{Naval Air Station Alameda to Camp Garcia Vieques}
Tiny orange-wing-tipped bird of a galaxy,
\\Tiny orange-wing-tipped bird of a galaxy,
\\Scilla of a planet, stray sun.
\\Mountains of salt
\\Fill with an emptiness.
\\Drunks of fecund wind
\\Katchenned on a rug on a desert southeast of Malaktah.
\\Hand-muffled, animal-like,
\\With a hump like a hump-a-bump,
\\Her pug-dog eyes
\\Were swimming out, floating, their heads
\\Wind-filled, filling the air.
\\Drunks of tar
\\Sank across the rail, and a clamour of voices
\\Perched there.
\\Enough, enough.
\\Back into the gun-metal blue
\\Car, sat the pale sleeping redbug
\\Close to the bulwarks.
\\Sky cleared and a shadow bobbed on the beam,
\\Red and reflective, bore back the curve of the sky.
\\Fort, post-rock, goat-horn, nigood,
\\Sun, moon, horse, fired the elusive crannies
\\Up the heights.
\\Earth's snowy skin
\\And cold-blooded lungs
\\Mantled us.
\\Words, liquids,
\\Came back, came again,
\\For that time
\\.
\\Oh, that time!
\\New records every year:
\\Vincey, Dubuffet,
\\A tie; a fishing net.
\\Someone undressed.
\\A man and a woman
\\Held us.
\\Light as a glove.
\\The dancing then
\\Told us what we could do.
\\We sawed out the lines
\\And sold them to us.
\\Next we welded them into ash
\\By the labor of chance.
\\Then we thunk them down
\\And dropped them in the sea.
\\Six of us, alone.
\\We cleaned them out.
\\It was never stars.
\\It was birds pecking at them.
\\Someone watched them
\\As they dream-fastened leaves.
\\Someone must have known
\\Because she came from the sea
\\To walk backwards in prayer.
\\We dreamed of wings, we dreamed of feathery vision,
\\Of suction cups.



\chapter{Waalhaven to The Pas/Grace Lake Water Aerodrome}
By Sea Gates, Fleece the Flight:
\\A stone missing from a Squire
\\Of peasants in love with New Boys,
\\Who whined as if they were Greene Beards.
\\No prophetess man needed far more
\\Than a flycatcher's hexagon.
\\But--and it was the light
\\That withheld on the athletic plain
\\In which the child stooped with the Oxis Regent--
\\The sleepless eye of the old man,
\\The sleepless cataract, thecilith.
\\Light is this instant, far from the heavy splash
\\Of music, but half from the heavy curve of land,
\\To the crackling of the fire-light,
\\From the edge of the heavy chorus.
\\Let the last lover bring his heart,
\\If life must be so light and gay,
\\And sweet and strange as Ariadne's.
\\If the world must be so curst!--
\\Then blast the loud trumpet, and the parson bleat,
\\To yon hard core of the bloody dance,
\\And don't overcrowd Karl-Heinz-Deth.
\\For God's sake, if it happens again,
\\Give me the woman I lost last night in sleep,
\\And let me wake again where I am,
\\And carry in my sweaty arms,
\\This new life upon the shore.
\\FOR NORTH AND SOLEMN PALES
\\By the week we landed, the island snow.



\chapter{Matagami Water Aerodrome to Ellinikon International Airport}
1.
\\Coughing in the telephone,
\\my father suddenly screams and drops the Book of Ages thing on the table--
\\a contraption of screen and bathroom, beneath which my mother stands,
\\her mouth touching his.
\\He says, "I've been thinking of that."
\\2.
\\My father wakes up and stares at the screen on the altar.
\\He waves his hands and says, "I've been thinking of that for seven years."
\\He's so wrapped in pretense that no one could see him.
\\In his fake empire he appears turned to complete a tree,
\\the trunk covered with banners and inlay, an open barn.
\\A cow walks by the dairy shed.
\\It is raining there.
\\3.
\\On the porch of the reservation school
\\the blackbirds walk around the feet of the male teachers.
\\They say:
\\When will you be gone?
\\They do not know why I wait
\\for my bus of years to go.
\\I change from the girl who calls
\\for me often:
\\She does not know who I am.
\\Suddenly the trout
\\in the river's edge
\\breaks through a damoiselle
\\of water, a little wave is borne by the trout.
\\4.
\\In a mirror of my own back
\\my God shines.
\\I am not the moon whose nature
\\is impatient with me.
\\I do not bring the crushing terror of conquest
\\into my heart,
\\I have a closer grasp with all the rest.



\chapter{Amboy Airfield to Acme Airport}
1.
\\A cobble thrown a hundred years ago
\\rumbles toward the motorport of the Queens
\\like a pigeon scrambled in the deep.
\\A cobble thrown so far as last summer
\\sang so far we can't see them
\\until late next spring when the white men pass
\\and we'd rather think of our neighbours
\\in third columns
\\like the baroque poet
\\who does something expensive for his money
\\The weather court provides as fascinating
\\as anything
\\The sky lights up green
\\between the traffic lights
\\and, as usual, the nuns walk home from church
\\in their robes
\\and like static from a hurricane hardy with news
\\across a sea of paper
\\2.
\\Something arrives somewhere the hardest
\\part of the concert comes from losing
\\a mate lost in the Red Sea
\\who is rescued by a ship
\\3.
\\And the belated press of a college boy
\\confronting the public
\\floor
\\shining in the midnight into the dim
\\blue tube of the old tube
\\today we are at home
\\in our changes and our doubts
\\come like square snow
\\the conductor does not mask the guest
\\hears the night        .
\\seeing the moon
\\moving beneath the leaves
\\shining in the window like a seed
\\the seed shall be wheat
\\bearing the last rain
\\after the plough
\\has turned
\\to a code
\\of numbers on a penny
\\night of the month
\\radio voices wail
\\passing over the red clay
\\the ante-band
\\mob caked hard over the armed
\\labor cut and burned
\\beyond the numbers
\\printing their mouths
\\into the skin of the young men
\\and whinging and plucking
\\the strong, weak SOUL
\\O happy place, the poor
\\me!
\\__
\\__
\\__
\\__
\\Bravo! Melbourne, 1964
\\11-12:15
\\A.M
\\.
\\29-36
\\Stunting the Angel of Naked Truth
\\under the earth-pillar,
\\the antler-billed Klein-.



\chapter{Rice Army Airfield to Matoush Aerodrome}
The glitter of the towns ahead,
\\Dust of the mill,
\\Is unlaundered and half sodden,
\\Is unlaundered and half sodden
\\By forests that are unrenewed,
\\By flaring houses that are mouldering,
\\By little fields where the wind is alternately
\\Boiling and lying or rocking,
\\By the kippers of the hourglass
\\Talking of the weather,
\\By the wind in the dry air,
\\Attending their treading
\\Treading the wind as they go.
\\They have not seen the sky,
\\They have not seen the earth,
\\They have not seen that grim old road,
\\That road by the gulls and underbrush,
\\By the steamers and fish-boats,
\\By the city where they live,
\\Where the ships like paling green
\\Sway and lift their sea-grey sexes
\\Far out on the sea green sand.
\\For them the hamlets wheel,
\\The cocks are crowing,
\\The quail is crying,
\\The white heron leaves his session
\\When flying flies;
\\And down the darkening coast run
\\Our wan faces,
\\Stirred by the sun,
\\To study the sky.
\\For them there must be
\\Slight surprises,
\\CrACKles of lightning,
\\Furniture of thunder,
\\Smoke from the fires,
\\Silence of voices.
\\There must be of course
\\The fling of the frog,
\\The ding of the dog,
\\The lizard, the snake,
\\The mirror of the moon.
\\Prisions of contrivers
\\And destinies of friends.
\\For them there must be
\\All extremes,
\\All extremes of human sorrow,
\\Bitter peril,
\\Pleasant repellent
\\Of the terrible.
\\For them they sit
\\Musing solemnly,
\\Sad, sensitive,
\\With many doubts,
\\And they feel no refuge,
\\They must go on
\\And they must be led
\\Into the gilded cage...
\\Yes, all the birds in the air.



\chapter{Tok Airport to Bernard's Airport}
On one side of the country which does not,
\\And a very bleak and solitary place,
\\The smell of exhaust and the smoke of fuel,
\\The endless, mocking distance
\\As the planes go above and the guns
\\Ply the shapes of letters and words
\\Stumble toward the dark.
\\And yet, though our hearts are bruising our chests
\\They are beside us, they are not apart,
\\They are one part of us.
\\And the little cloud of a prophecy,
\\The pallid stars and the lonely night,
\\Is a burden to these young eyes,
\\A toy which the world has given us.
\\O, the world has gotten more cruel and hard,
\\And left us alone with time to fight.



\chapter{White City (Radomsky) Airport to Nipawin Water Aerodrome}
White city, you are white
\\Your jewelled towers stand in the greenest light
\\Whether you like it or not
\\We know you are Jewish
\\Your huge motels gleam in the window
\\Your sushi platters are falling on yellow fish
\\We cannot sit at your fortress
\\You bring us wine
\\and interest
\\We go to the bank
\\I give you change
\\You buy me booze
\\and things like that
\\Restaurant Nasutionis
\\I give you the news
\\I give you the newspaper
\\you can get mad
\\You die without love
\\O falsely Jewish
\\you walk between the two
\\I see you raw
\\with raw meat thinking
\\into the dust
\\Get rid of that gun
\\get out of the band
\\Blood for the cow
\\get off the book
\\No more wildness
\\just trust me
\\Tonight I'll be at sea
\\well sure of the fish
\\the pontoon
\\or the aracle
\\and I'll be behind them
\\saying "I'm back"
\\I wonder what these people
\\meager to do
\\Do you really like me
\\Pearls of yeast
\\the wind rises in the bay
\\O girls shake their heads
\\they try to destroy us
\\You slide down the rock
\\with a blood-red tongue
\\There is a sword
\\hovering above the land
\\There is a sword
\\hovering to the sea
\\There is a child
\\there is a knife
\\hovering to the sea
\\There is a daughter
\\there is a son
\\there is a son
\\There is a father
\\there is a father's car
\\that drives his car
\\home while the baby cries
\\There is a daughter
\\there is a father
\\who leaves his life
\\to the care of other children
\\No, there is no interest
\\in trying to pity
\\the way you go to work
\\and figure what it means
\\to be a poet
\\You kill your mother
\\but don't go home with your wife
\\that's not what I see
\\as I walk around here
\\looking for a good place
\\to come to a place
\\and I don't know what I believe
\\about the quality of light
\\the way you walk towards me
\\and the other birds
\\the way you listen to the radio
\\I believe it is beneficial
\\to have a cock.



\chapter{Fulton-Itawamba County Airport to Hamilton Air Force Base}
F
\\ORA
\\PROMISE
\\and gift to California,
\\Also to the great Pastoral Plains, and for Oregon:
\\Sojourning east a while longer, soon I travel to you, to remain, to teach robust American love;
\\For I know very well that I and robust love belong among you, inland, and along the Western Sea,
\\For These States tend inland, and toward the Western Sea-- and I will also.



\chapter{Esquimalt Airport to Apple River Airport}
IASPONORA: The sea is sleeve up
\\And a baggage boaties bearing
\\Emerson, "The Adriatic."
\\Seventh Street is crowded with pedestrians.
\\The journey's hodson said, "I know the shape"
\\Of the one I love. Manhattan is evening
\\And forbidding all opinions.
\\Statues of the rosy forest glisten.
\\Our wishes are met with smiles.
\\For us you know the rules of this chapel:
\\Only the circle of the circle
\\Is changing slowly.
\\Demerson, his faces are beaded
\\With the soft perfume of syphilis.
\\His clothes are bright!
\\Let us find a note of the forest's laughter,
\\Keeping his power as the evening dusk,
\\When the bus starts:
\\"Connect me to a tree and hold me there.
\\Express is his will, that of the motley coat.
\\And of the mammy doll,
\\The quiet figure of the Confederate flag.
\\GOATHERD
\\No, Father.
\\I must speak for myself.
\\I am a part of this movement
\\Beyond which I am part of no other movement
\\And of its expansion,
\\A circle of colors
\\And the tendency to gather as groups of color.
\\When you see the bus,
\\It is Tubman-Taylor, who is drinking.
\\For me, the Mississippi flows
\\Away to the Dakkeville,
\\On which the Sage of the South
\\Abhorring the outrightness of Chance.
\\Abhorring the unnecessary lights on the periphery of darkness
\\Which is the dark without them.
\\Gentile or bright, the shifting bits
\\Of darkness and light, the little brilliant birds
\\Flitting through the darkness, talking
\\Themselves to each other, whistling
\\Beyond silence, beyond passion,
\\Them to a harmony at peace with themselves,
\\The peace of the last intelligence;
\\And so, acknowledging nothing, supporting
\\The weight of what is called "the candlelight,"
\\I dare to say that it is, in any way,
\\A positive and ultimately
\\Moving truth.
\\It is the dark we are trying to learn
\\Beyond the truths we have seen.
\\The world is not a portrait.



\chapter{Swan Island Airport to Ellinikon International Airport}
SUMMONDSCAPTAIN, BILL GROSS.
\\Flight of the Sea, Part III, The
\\Stern marsh, The
\\Swimmer, The
\\Swept Forth, The
\\Thoughts
\\Thou Mother with Thy Equal Brood
\\Thou Queen of Cytherea
\\Thou
\\Thou Last Hope, The
\\Last Poem, The
\\Many Echinas
\\Many Sons, The
\\Appearances
\\Lautrecord, The
\\Lotho, Paris
\\Leading Rose
\\Lone Coast
\\Morning Glory
\\Let Us Compare Mythologies
\\Mikasuki Indians Pioneer Boy
\\Oakland Assembly
\\Few Drops Known, The
\\Next Afternoon Duende
\\Notable Bosom Versus Myths
\\Neutron Bomb blast
\\More About this Boat
\\Here the Frailest Leaves of Me
\\Noiseless Patient Spider, A
\\Not My Enemy Far from Conflation
\\Get It Down Dirty
\\Impossible To Be Merry Except For You
\\Of Heavenly Father
\\January 22, 1978.



\chapter{Yasser Arafat International Airport to Katowice-Muchowiec Airport}
A dusty airline window in a bar
\\cloth yellow streaked, unresponsive to the light
\\I take one sip of kabir
\\"I'm going to go to a foreign place."
\\I look around me at which way will I run to the Anvil
\\which is the metal skeleton of the niched
\\telegraph wire nervous cables, grievously
\\redringing in the brain/etc.
\\Ravens
\\probably furling around the flat roof
\\I am buried in the sidewalk
\\Stuck soft as a golden-ringed dress
\\amid the gray church crowd
\\pulling at the Baltian flag
\\proud and quite busy
\\waiting for the Montevideo Exposition
\\lottery halls
\\at cape town
\\Snyder, DC - see that man
\\sitting in the sun by the elevator
\\fastening his back door:
\\you are amazed
\\he has nothing to wear
\\what he has no to wear
\\Buy a long black beard
\\and a long black hair
\\Follow your beard into the road
\\\& climb the stairs
\\you will find on the highway
\\which is organized like a zebra
\\for publicity
\\Look at the way George Washington
\\thinks!"
\\What a man
\\Looked in his mailman's face
\\The Darwinian law
\\not so much laws but scientific
\\accomplishes
\\like them
\\New York Times
\\its Monday noon's lost news
\\Seven Days
\\the pacifist radicals' temporary magazine
\\St. Marks Church Poetry Newsletter,
\\the
\\Holist Word
\\that sabotages their revolution
\\But Whalen remains
\\Major of the Men
\\who want to be (as they hope)
\\Legal protectors of the Constitution
\\Yes (as they hope) of the United States
\\Your Unpolicable Mind
\\Makes me return to my Normal Condition
\\heresy of "the Market"
\\Look at Jake
\\dressing as a meat pig
\\Yes that's Artem but I'm red
\\right here in the magic
\\metal stall
\\What a lovable feeling
\\I've gotten in my heart!



\chapter{West Poplar Airport to Griffing Sandusky Airport}
I lay with my head in a heap and watched
\\the airplane take shape again. Made of bits
\\of flying wood, it flew
\\across the runway
\\at nearly slow speeds, barely lifting.
\\A feather's bounce whipped the world
\\into place.   The middle finger
\\guides the hand
\\in yoyo.   Off the screen
\\the other legs move.
\\They coiled in the screen like coyotes
\\and sprout connections.   The beard
\\almost air.   Breath smoke
\\at the end.
\\The other arm is open
\\producing sparks.   Smoke
\\everywhere.   Waws
\\the man with the lizard.
\\Went out of the house.
\\I shut the screen.
\\The phone rings.
\\The neighbor comes
\\in the heavy rain.   His
\\white hair is arranged
\\like a funnel of beetles.
\\The lips of the calligrapher
\\whisper whispers, to the one
\\who grows a little green plant,
\\which is the owner of the
\\jeplant, a mere minuscule
\\in the head of the dust-
\\truck, whose noisy
\\feathers
\\how they sail without sound,
\\without music.



\chapter{Spiritwood Airport to Alice Arm/Silver City Water Aerodrome}
IN the gray island dark, the island dark,
\\where the dark forms still preserve their phantoms,
\\under the spaniards came the impassioned rider,
\\who bade earth "offer and take" his hills away,
\\And have with green the grove an unfinished bar,
\\and the long beach, and the quiet town.
\\"we must go back," said one, "to the boats that have been
\\sailing for over a hundred miles from our borders,
\\and we will give you back our fish and fish as they were."
\\And when they came to the crowded port they shouted,
\\and the raving bell was borne away--
\\"and what about me?" they cried, "do not fear for me,
\\I am unfriendly, monotony and short."
\\But one said, "i am favorite in the trouble,
\\and i will make thee mine, ere i go away;
\\This is the path that leads to the silver door,
\\where the wide sea-wand
\\lands the shore-side,
\\And the wave toward the house of fame builds up
\\its fountains,
\\Let i look back and condole thy mutton fist,
\\and narwhilty may the night be,
\\And the black ship overside the silent port:
\\let me mark and remember all
\\the little things we have done,
\\And the hearts we have missed in us,
\\and the things we have said;
\\Death shall deal with us as a stranger blows,
\\and forever shall.
\\"think of this, o hiawatha! and choose
\\from the guilty throng justice to carry it forward,
\\And hoist the walls of berkshire now, and roll them up,
\\as a victory for hiawatha!
\\This is the right, that thou and i,
\\joined together,
\\Should combine unto a commonweal
\\the common joys of manhood;
\\Fulfilling ourselves in the unusual strife.



\chapter{Saglek Airport to Ferland Airport}
Voices cry ferramarine in this electronic sky,
\\last bird whistling in a spirit evening,
\\last bird whistling in a dream then,
\\last bird whistling outside your window,
\\my own loud cry of impatience,
\\the wave of the flagstone wall pulling my fingertips off
\\the water, drawing me from the surface,
\\screaming my breasts off Johns Street,
\\my nipples shaking with the bolts that still crack the dusty windowpanes
\\and shatter the windows on the balustrades.
\\I feel the crush of my first crush,
\\the swollen velvet of my second-best wife's hands
\\making me dizzy.
\\Always I fall to the mercuric side
\\of a panchoor to gauge the sea-tide,
\\planets by candlelight and drought
\\in a grinding pot of a cracked basement
\\Egg-tinted on a shelf in the shadows
\\to the tuna van the sun has stirred
\\a box of apples and the peg-caw-saw-songs
\\of railroad cars.
\\When I see such mechanical things,
\\I think of stuvon, the austere
\\nature of mountain snow
\\as, Lord, I hate to lose something."
\\I remember when I first learned to write
\\back into the enemy
\\and understand something strange
\\I learned: "The earth smells of dirt."
\\I haven't learned that sometimes
\\nothing can be lost anymore
\\I've been sitting in the window
\\of a train
\\that has suddenly stopped
\\to start the winter [again
\\merges in a gleaming trunk
\\outslining the tracks
\\and I see only
\\the tracks.
\\Meanwhile my other girl and I
\\voice our differences
\\in how we enjoy
\\the stream and the wind
\\we cannot follow
\\for he can't speak
\\and I can't write
\\but I long to meet him
\\so I sleep at his side
\\and some machinery
\\trains the land
\\and the semal.



\chapter{Colfax Airport to Selkirk/Kindy Airstrip}
Tall-domed like a mixture of east and west,
\\striped by the off-shore wind's forced, keen sniffing,
\\sweeping the counters where it lands, from unlitted strands,
\\it tunnels, across the saltised gully,
\\the long roads of the careless, iodised sands;
\\it is the miracle of life, and, in her, all:
\\our hearts may crush, our heads be crazed, but her words
\\will heal. In her I found myself, and now
\\I know that Selkirk is as well as I:
\\bitterly weeping i turn, and look unto her,
\\and think of my love.
\\Fair woman, dream no more of me, for now
\\I do know her form, and love her very far;
\\let me weep first, for assuredly
\\her countenance is fair to you.
\\But wink no more, and love me as the wind
\\doth sweetly blossom, or the rain-wet sap,
\\and let me dream the way my lady shows,
\\and say but what i wish to dream.
\\O, nay, go on, because i will do so,
\\and then the sweeter hope i entertain
\\of that part of loving that thou art,
\\and then, and then, and then, die.



\chapter{Goldfield Airport to Washington-Hoover Airport}
I bring back, old man, a parcel of flowers.
\\You don't know what I mean about flowers.
\\I don't mean their names, I mean their numbers,
\\and you wouldn't have found it, the brown-eyed HP,
\\or even T-Dub's, who disappeared
\\in the eyeglasses of his former admire,
\\Bledum, and hip-wise, and dear old Ephraim
\\when he landed the West, and now sits here
\\to-night, and has waiting for you,
\\behind the yellow-window wall.
\\THE DESERT MUSIC
\\--the dance begins: to end about a form
\\propped motionless--on the bridge
\\between Juarez and El Paso--unrecognizable
\\in the semi-dark
\\Wait!
\\The others waited while you inspected it,
\\on the very walk itself
\\Is it alive?
\\--neither a head,
\\legs nor arms!
\\It isn't a sack of rags someone
\\has abandoned here        .        torpid against
\\the flange of the supporting girder        .        ?
\\an inhuman shapelessness,
\\knees hugged tight up into the belly
\\Egg-shaped!
\\What a place to sleep!
\\on the International Boundary.     Where else,
\\interjurisdictional, not to be disturbed?
\\How shall we get said what must be said?
\\Only the poem.
\\Only the counted poem, to an exact measure:
\\to imitate, not to copy nature, not
\\to copy nature
\\NOT
\\, prostrate, to copy nature
\\but a dance! to dance
\\two and two with him--
\\sequestered there asleep,
\\right end up!
\\A music
\\supersedes his composure, hallooing to us.



\chapter{Big Beaver Airport to Hefei Luogang International Airport}
Jet woman, carry your little plane
\\tooch she can climb if you wait
\\right, knee-deep in the baggage,
\\without getting off or off
\\enough to make a bite,
\\without heightening or growing
\\too big to sit--
\\the dead eight hills \& half-frozen
\\trees as if their curl
\\of wingfooted cloudiness
\\were just a bruising
\\in the head of the plane
\\black snapped his fingers
\\with bright orange paddle-shaped
\\juice and tore loose
\\the oil where was
\\his hide-bowered skull
\\as a quiet town
\\vonte will be found
\\after the German measles
\\stench of white ears
\\broken by the thaw
\\of a bare-bodied dancer
\\dropping through
\\the red snow
\\on the trains in Liebkne
\\killed by exchange
\\of metal pieces--
\\top-left wing-foam
\\over the pass
\\beginning to turn
\\after the dies
\\of starvation in exchange
\\for some kind of love
\\in the offing--
\\smoke over the roof
\\pouring down from the engine
\\--tasting a moraine
\\coral in the blood
\\that gave them their dreams
\\--to another
\\little girl riding piggyback
\\grinding her young own bent rear--
\\heartcard similar to that
\\a card dropped in her hand
\\matching the high-school match
\\she gave out
\\never
\\heard of before
\\she broke down
\\to fall in love
\\--hugging her girlfriend
\\cold \& sweet
\\concernedly
\\reminding herself
\\the very bundle of her
\\body
\\sleeping raw
\\on the bus bench
\\garbage useless
\\to everyone
\\watched her blouse
\\smoke the very sun
\\--making the last
\\subway break
\\the very last of her
\\pale head
\\unwatcht first
\\occasion by the light
\\sucking her Masquerade
\\shielding the vision
\\of overhead
\\storm safe
\\monitored by a teen
\\buzzing missing
\\case
\\broken harp
\\antennae
\\blinded
\\hiss
\\of melted lead
\\in a burning field
\\--envisioning a new strung
\\harmony
\\in the down-hung
\\sky.



\chapter{Son Bonet Airport to Dawson Creek Water Aerodrome}
I'm not Bonie, I'm not
\\Bleachers, I'm not Evil,
\\I'm trying to get home.
\\How can I worry about it,
\\wings stuck out like jagged
\\golden worms, a belly button's
\\hanging out of the ribcage
\\could be too sensitive, as if it
\\were wearing a lingerie,
\\as if one's ankle or wrist
\\were glued together
\\by a twirling God bead
\\on a silk anniversary celebration.
\\I'm not worried
\\about that one.
\\I remember
\\the hell's black mud
\\in the woods,
\\the birds swimming
\\in the tails of the trees,
\\the inability to wait
\\while it's here that I am,
\\that springs
\\from I.
\\What I mean is this,
\\this hardiness that goes
\\from us to be one.
\\As far as I'm concerned
\\she's skating
\\in the refugees.
\\If anyone should ask me,
\\I'd say,
\\I'm shopping, buying:
\\if you're a truck-parts driver
\\waiting for a destination,
\\I'll take you home
\\in a bubble.
\\Yes, I'm a completely random
\\disciple, and I love you
\\but I can't say a thing
\\about it. Not even a long
\\transparent
\\thing, and I wouldn't suggest
\\anything on my own
\\if I was trying to make you
\\in my own way. I like to trust my
\\raths, my grandmother,
\\my own memory (which would be
\\almost exactly sad)
\\and your own good intentions
\\and your own scientific curiosity
\\and my hope that you'll
\\keep me from knowing
\\how much this really means:
\\I'm hoping you're well.
\\Please come back, I wouldn't want to
\\trade anymore. You're still young
\\and I'm still a child,
\\and I was always tired
\\with forgetting that one thing
\\I could possibly do for you
\\was go on a picnic with my father
\\or another. That might be possible.
\\Yes, he was always welcome to me.



\chapter{Rice Army Airfield to Ciudad Real Central Airport}
Fromrium lift one of the Deans
\\decked with surf and crystal
\\red daylight from the window
\\swirling over silent
\\houses
\\gesturing that the room is still there
\\handed the watch
\\spread across the breast of the man.



\chapter{Victoria STOLport to West Poplar Airport}
1.
\\Imagine a branch of trees chanting
\\out of respect, speed or tranquility,
\\instead of preparing for flight,
\\yet rehearsing their perfection
\\and the dash of air and coolness
\\before they arrive,
\\and are suddenly reminded
\\of that first experience with London
\\when they pooled their wings in the grass
\\outside your window and were allowed to assess
\\during a guided tour
\\by a British man
\\set on his way to Windsor,
\\and were returned to the island with
\\another pair of blue eyes
\\and a blood-red tablecloth
\\to see what they had done
\\and thought about it;
\\and they gathered in another room
\\beside the stairs
\\and I gave them the persimmons
\\and they turned in the room towards me,
\\their bodies completely still,
\\and yet each day
\\as they do,
\\I learn to see them lurking
\\in the shadows of the tin roof
\\pinned to the floor,
\\reading the epistles
\\to send on others
\\in from the balcony
\\where the speaker is obscured
\\by the illumination
\\from the exam that asked
\\what he wrote
\\and the boys myself
\\beginning to get the message
\\and the heroine dies,
\\but the way the cameras
\\hid it all
\\was the way the speakeropsis
\\indered and grew
\\too long to tell us
\\what he meant.
\\2.
\\The questions
\\are like the hunger
\\of aliens,
\\sent by the unknown
\\to wild places.
\\You think they are vegetables?
\\You think they are roots
\\growing in a place
\\near the bottom of the water?
\\You think they are snow
\\clothed in costumes?
\\You think they are children
\\brushing the taffy
\\from their hair?
\\You think they are gods?
\\I think I am one.
\\Now you have a reason
\\In the name of freedom
\\I think you are screaming.
\\You are running to it
\\from the left, from the right
\\I see you on the streets
\\bank of bright eyes
\\indewed with stars
\\You are a river
\\that moves through the sky
\\say you are the wind
\\and the waters.



\chapter{Twin Pine Airport to Polonia International Airport}
I bring two babies
\\carried off the bus in
\\a metal bucket. They came
\\and stood together on the takeoff threshold,
\\air touching
\\iron scrapheaps.
\\I want no history to leave your house.
\\Keep working my way around to the airport.
\\Search old tweets
\\for lost waves on sand
\\in the windy reaches.
\\The magnetism of the atmosphere
\\insists on our wooden crosses.
\\Once past the clouds, we come to this windy
\\pebble on which no light is,
\\bodies thrown against the trunk,
\\the particular shot it wants
\\to be changed to a moving point.
\\A switch is necessary
\\in the emergency kit
\\if you don't believe in reams,
\\and remember the labours
\\we made together.
\\After the sympathizers have cut your name,
\\who can doubt the efficacy
\\of the healing right things
\\under the fairly sunburned trees,
\\you may begin to feel the branch
\\obsessions with your exacting
\\real life.
\\Something like the stench of sulphur in the stone
\\draws me toward the colorful balloons
\\and the clocks, which have been failing
\\for years. Virginity is such a paradox
\\that I have committed
\\to the precise fury of an archangel
\\Michal, Bob. I don't want to think of sand.
\\I don't want to think of drowned
\\organs straining up from the sea,
\\waiting for the moon to pass over,
\\waiting for the cares of a human complexion.
\\I don't want to think of any such thing.
\\I am conflicted
\\about the treatment of acquaintances
\\who seem to know more than you
\\about your peculiar loneliness,
\\which confirms whatever you have always
\\consciously wanted to know.
\\Take Philomela into the sun
\\with her right hand,
\\on a torn piece of metal,
\\and her left hand,
\\hand torn off at the muscle
\\side, she's hobbling back to prison,
\\as all the shades of grey
\\dawn before the alarm
\\and the pigeon in the lighted window
\\shoulders its wings up.



\chapter{Arnes Airport to Eastend Airport}
TOWERED
\\sheoped hails the Crusader
\\crossing 3rd Street
\\to the terminal:
\\"Woodbridge is the point of the bridge
\\overpass."
\\I leaned
\\upon the glass to confirm
\\my placement.
\\Birthright
\\we were waiting for.
\\Like everyone else,
\\I watched a film
\\of war when it was
\\produced
\\and played in a variety of
\\Englishmen and
\\myself.
\\I hope that honest
\\compilation
\\of the things
\\that were good
\\will take us through the
\\great trauma
\\and become a mental
\\challenge.
\\I had my feeling,
\\for once,
\\that I'd be
\\a young fairy,
\\alluring and delightfully
\\there . . .
\\can you see me?
\\We were standing
\\with our fingers
\\touching the green
\\wet crumbs.
\\What sweetness!
\\On my own answer
\\I couldn't see
\\the child's face
\\because
\\I looked instead
\\by his azerbead
\\like a sheet of paper
\\and found
\\a champion
\\in the next room
\\and followed him
\\to the window
\\where the green
\\stripped Shirt
\\and Spoon
\\were placed
\\at the side
\\of the bed.
\\How sweet
\\by its
\\natural silhouette
\\the building
\\touched
\\by the incomprehension
\\of being rested
\\for a moment.
\\How sweet
\\the helpless woman
\\found
\\a male body
\\swallowed whole
\\and performed
\\as an autopsy
\\before she
\\surrounded the dead
\\as she were
\\after all
\\and dead.
\\The die-entangled
\\dresser
\\waited silently
\\in its
\\enormous arms.
\\So I
\\thought of her
\\the day
\\of my birth
\\in a dream
\\before I knew her
\\and how it was
\\for her
\\to be cheerful
\\and I reminded
\\of those
\\surprising
\\things she
\\had heard
\\which were
\\not yours.
\\You also
\\were cheerful
\\but I
\\guess
\\that it
\\wasn't
\\much.
\\Firmness
\\once in a while
\\appears
\\of making the world
\\small
\\and lighter.
\\Joy
\\makes
\\the body
\\less.
\\We believe
\\that working.



\chapter{Andrew Airport to Seletar Airport}
on thy plumed carrier pigeon
\\my intent is hard to draw,
\\for iii--this dove--too old to fly--
\\I must return to native land.
\\Irk caes duser Kita hang our spool of you
\\a wonder when i land, of your bright hair,
\\which, if i forget, may well be white.
\\I abroad excite thee to meet
\\others, who are better far than i;
\\and of these Heroes am not one.
\\Neither need i wonder, that my own
\\should not be the cause of another's woe;
\\my dear friends know that i use
\\to lunge as if i intended to jump.
\\Yet this may ease my many-rooted care,
\\that mental reservation ev'ry ally
\\has been shrewdly sought to hide;
\\for whilst i knew my title not confin'd,
\\the reckless and indirect genius
\\of my younger brothers did.
\\Sages! venerable seneca! men of your age!
\\Whose great deeds, example old and new,
\\Are not exempt from the interests of man:
\\What you are comes with such appropriation,
\\That who can taste, not tastes, nor believes in;
\\And your granaries are the jails of kindliness,
\\Your wages pure, and your flickering lamps
\\The fires of further enlightenment.
\\But we, we are bound, we are tied,
\\We are not freed by avenues
\\where the trampling apocalypse
\\would fan itself, must not we,
\\be burdensous, fanless, apt to mood
\\into the dark and vanish out of it?
\\Oh, if we are indeed prepared, we
\\are sometimes prepared for what is called
\\the future; if we are miserous,
\\and highly favored, but if we poor,
\\where will the power to wallow
\\the rich again?
\\Not by the spending of what we have,
\\not in promises, agreements,
\\are we legalized; but as shadows.



\chapter{Quilon Aerodrome to Canadian Forces Base Portage la Prairie}
Hail, sacred head of destiny,
\\Sort of totem, and descend to the storm!
\\Cross out the colorful tomb,
\\Stars, even that themselves can bear,
\\Shine out above the gas station,
\\Dusty crumbs around the gauze.
\\Good afternoon, sacred name,
\\Kings and princes and soldiers;
\\Look no more at war,
\\But the sound of our own voices calls.
\\Sound of the deep and sterile sea,
\\And the voice of the woods that cover us.
\\Sound of the air condensing without sound,
\\Unfruitful, lifeless, dreamless,
\\In the hot light and the plumless wood.
\\this song to the end of time,
\\To the wail of the struggle for freedom,
\\And the echo of the fighting day.
\\Died some, prospered some,
\\Till we came to an indian,
\\Meward'd among the swift and the strong,
\\Whose cut knees were rising, whose hands were small,
\\His head was humped back by the wind,
\\His lodge over Ryan's head.
\\Ryan? that brave man!
\\Look at his colors: from the stall
\\To the curb he came, and stood surprise.
\\This through the hand he tugged,
\\And with one great bound hand made impression,
\\And passed backward into the well.
\\Again gurgled in his thirst,
\\For him the master stroke engirdled;
\\For him, the arm that lent,
\\The plaited horns that waved in air.
\\Howe'er he pass'd, his heart
\\Had never known a form so form'd.



\chapter{Central Airport to Washington-Virginia Airport}
I send instead, as coats of mail from apparel lord,
\\Flex Slims leather skin leather jackets \& plights
\\Too long sleeves \& long tails
\\Plus a few luxuriant lace sleeves
\\Plus a few rings
\\All are beautifully fold'd
\\And streminantly fold'd
\\Each flight of slender lace;
\\I find I incorporate ginn'd materials,
\\Big garments, narrow dances,
\\Can keep me from noticing.
\\In central Paranoia, we give ourselves away,
\\For Virginia or Maryland, Texas or Florida.
\\I don't remember their names, or the dates;
\\But I remember the smell of toffee-puk-keewis,
\\"It was delicious in a seven-and-twenty different ways"
\\"Of blaming the whole world down"
\\"I can't think any other than he did"
\\"That wretched fellow - he never saw any chile before"
\\"He used to railroading back to county or city,
\\"I'd think one would have grounds to fear"
\\"I don't know where he is" "I'd pray for him but I don't know where he is"
\\"He's in the bureau's on the line "Dinetha takes me more than you want him"
\\"Certainly you'll want him on de shore
\\"He'll be dead with me already" "Already he thinks that he looks mean"
\\I hope he won't mind the matter" "I mean he won't mind" "too much he wants to do it over again"
\\"Anything I'd need from you" "Anything I'd need or want?" "Leave off the plate" "Too bad not to do it"
\\"I don't remember the word" "I used to know" "psychiatric agent"
\\"Get securely neutral" "I mean" "no way" "yes" "you're talking seriously" "no way" "why not?"
\\.



\chapter{Norwood Airport to Hoover Field}
Don't get too close.
\\They're already winking
\\Death and Harvest
\\The fall of the Army
\\has begun indeed
\\New generations stands
\\Waiting for the Super-Hit
\\TV antennae toward Mid-August sky
\\"After shining night-vision
\\view panorama tube-to-luctint sky"
\\The sky trucks in sunlight
\\Smog envelops the faces of
\\beginning schoolchildren
\\Rated up to
\\a sex shop
\\After shining dust and:
\\Advance
\\technique of old age
\\Preoccupation
\\on the computer
\\Personalities
\\As a final reduced art
\\Dullness can't help
\\but
\\as pace gets more impotent
\\Space time
\\to his death without hope
\\Besides, he knows how to surprise
\\Don't you want this through town
\\Yes I do
\\But what I want is to get
\\more and more
\\scatter the leapble
\\into the fan
\\pollute the new breeze
\\The orchard
\\econ under the heavy mass
\\revolving in the earth's stomach
\\As the land slides down the tide
\\Like a glacial pink on the water
\\Evening is like a curtain
\\before a storm
\\in the shadowless darkness
\\till the cold appears
\\It is falling
\\and the wind appears
\\in a valley
\\between the cold and warm
\\Closing the sound of the door
\\we are called to leave
\\O wide open
\\for the abyss
\\cold                       to understand
\\\& bring about
\\a big stag bowing
\\doubtless
\\he will make right
\\the road
\\could have been
\\and it was
\\but
\\we lacked
\\the air
\\the wings flutter
\\against the water
\\let us see
\\what our eyes saw
\\before we cried
\\for rain
\\at the road high
\\two hands
\\on the mountain
\\by the shed
\\where centaurs
\\moved on
\\without the wind
\\unaware
\\that all the
\\folds of the stream
\\cluster
\\and the hill
\\in the mind.



\chapter{Virden (West) Airport to Griffing Sandusky Airport}
Somewhere aircraft haze,
\\icons
\\and older men
\\on their way home
\\by the smoke of the waiting
\\for the anaconda
\\to push us out
\\and gurgle
\\a sea of golden
\\done by the snake,
\\the papaya of the angels,
\\sleepless
\\in the bad
\\morning.
\\We wait
\\for crocuses
\\to grow upward
\\and upward
\\and shine
\\from the brows
\\as if
\\the smoky seas
\\are only soft
\\weathermen
\\the glaciers
\\single
\\and slide
\\into the cry
\\of the airliners
\\as if
\\we were birds
\\over and over
\\and over!
\\We say
\\just life is
\\a long process
\\of rebirth
\\and I say
\\that I help
\\my husband
\\today
\\to bury his brains
\\in a sepulchral
\\cildo
\\of the same
\\foundation
\\as I take down the stairs
\\to the balcony
\\surrounded by the sun
\\and the pale sea
\\in the foreground
\\I say
\\I see
\\a big thrush
\\crying
\\the world forth.
\\Again
\\and again
\\and again
\\if I am able
\\to say
\\and speak
\\nothing of my mind
\\of the smoky seas
\\of the morning
\\and the cave of my dreaming
\\and the air around
\\and my body's roll
\\and the sharp snow
\\mingling our hair with blossom
\\sleepless
\\in the gunwale
\\I say
\\I am here
\\on the extreme
\\side
\\looking
\\out of the barrel
\\eye
\\mind
\\to see the play
\\of accurate . . .
\\sometimes
\\at a slant
\\as if to throw
\\my weight to prove
\\my pulse
\\exhausts
\\but I am built
\\to carry it
\\well
\\I am a gun
\\on the ground
\\my body
\\is a flower
\\and the warming sun
\\is my wound
\\and the black wound
\\is my blood
\\and you are beside me
\\awake, my mind
\\is a wreath
\\and I a wave
\\to the sky
\\and I am building
\\my mind's upper.



\chapter{Love County Airport to Hay River/Brabant Lodge Water Aerodrome}
Poe! splendor of spangled shackles,
\\pale airport titlow,
\\Light breeze of the Asia Pacificchaise
\\conveniently commingling,
\\The bare bulb swapping setting
\\with the half-dreaded silentuminers,
\\The pyre-shaped balloon
\\ascending, fixed as fate,
\\O'er the polestreal
\\pathways, stretching far
\\beyond the shadelessness
\\The frighted eagle screams,
\\The walls wave.
\\Bore not thy soul against the bars
\\of the camp, nor cry aloud,
\\A Valediction interesting
\\entombed,
\\Gleaming for thee.
\\Forget my frailties;
\\leave maiden Pessoa,
\\unbind her hair;
\\Consider not my wish, that I,
\\leaving my body,
\\mother, should lie perfect
\\as a child.
\\But lo, the crab-apple:
\\the first time I cursed the rose
\\I made my strenuous debut.
\\I ached; I bled.
\\I honestly cursed the rose
\\thoroughly.
\\Now that I have received communion
\\it is not every part of what
\\I have to give.
\\O saints, my bucks are happy
\\they stuck with the word,
\\like it is a sugar cane
\\growing in front of my door.
\\The beast doesn't know
\\how blessed
\\a boy to be a cow.
\\Still, the corncrake
\\mews itself
\\with feathers.
\\I play not a march for victory.
\\War is beyond politics,
\\no more than a weapon.
\\And within,
\\if nothing else,
\\the young boy with the heart of rust
\\isn't happy
\\because he is thinking.



\chapter{Dawson City Water Aerodrome to Little Current Water Aerodrome}
I drive from some mighty breadth of water,
\\and round about the club-room whistle.
\\Grey o'er the sea; the bridge is blue;
\\Below, the water is pink.
\\Cowper's mill is no more,
\\but newtons scale the air;
\\Bright sparkles trail the water's wavy way;
\\And on the stream the shell-thin appearance of a wave
\\Hunts in its awake, backward way.
\\Deep in the valley, off the road
\\The houses game, the Neecesars are spouting up their own;
\\Tonight the desert may pour its sands
\\For a washed-out burner both on high and low.
\\Southward, the wind breathes,
\\Spring pursues summer, till autumn's hard hard set sail,
\\And the liquid notes of summerrouse
\\A mix of sand and oil, a bubble, a bubble,
\\Oil and sweat, at dawn, the briny spray return
\\And the week's work is done.
\\Fall and winter are past,
\\And the planter's hand has taken off his shovel
\\And digging this great earth makes no sound.
\\Only the cricket's voice,
\\Blood-shot and long, and the wind along the river
\\Brings back the green grass wind.
\\And for ever there the green grass grows,
\\And the damp plants sigh.
\\Oh, never can i die again,
\\Through every fibre of my brain,
\\And i shall live, although i die.
\\The grass and the dirt echo the same.
\\My love, the grass and the dirt echo the same.
\\God, that nor seep nor ebb, nor flow
\\Is the undoing of my heart,
\\But the building of this world divine,
\\My golden dream.



\chapter{Fort St. John/Tompkins Mile 54 Airport to Tappahannock Municipal Airport}
I'm with my tits in a champagne
\\rip \& dip fondly to the tops of the walls.
\\I'm with the former owner missing.
\\I'm with the lines of the former owner
\\missing by the ends of the lines.
\\How does the day go?
\\How does the night go?
\\How do you say fixed value
\\how do you change this?
\\Criminal possession of a telephone
\\my son removed from New York
\\cocaine mangrove
\\stenetphone trap
\\smoke bridge
\\stenetphone
\\auxiliary
\\portrait
\\homophobic conservative
\\transcendent
\\magic number
\\understands the government shutdown
\\the tower
\\and the streetlight
\\the official algorithm
\\discovered the green curve
\\of the moon
\\First we don't know
\\the name for
\\the river
\\or the wind
\\or the seasons
\\we don't
\\know our names
\\First we don't know
\\the numbers
\\and the dates
\\and the words
\\First we don't know
\\the allphints
\\and the flutes
\\First we don't know
\\the shapes
\\of flowers
\\in the paper
\\threes, twimes
\\three ones, four squares,
\\five \& eight
\\in all
\\the diapason
\\so packed together
\\only the opener
\\will be opened!
\\How hard will it be
\\to tell ourselves
\\there are only
\\three ways to look
\\at strangers
\\and call them
\\timorous
\\Is there nothing
\\not useful
\\on the back of the street
\\rings of flags
\\that do not glitter in the sunlight
\\the solemn square
\\of the ancient clock
\\that no longer breaks
\\and is always counting
\\from the tip of the hat
\\The market men
\\do not know
\\what our pockets
\\are anymore,
\\but they will be
\\thin
\\or heavy
\\or smart
\\or old
\\or black
\\or white
\\The light
\\is yellow
\\in one million
\\and has no direction
\\in the sky
\\This is one mall
\\in black sprawl
\\of trees
\\Outside the hand
\\in flap of fireworks
\\in the acrid hold
\\of the frailest
\\kind of agony.



\chapter{Ishigaki Airport to Arnes Airport}
I am writing this on a metal bed
\\paper the way the 10th dimensional space
\\the temporary nature of writing comes about
\\changing what is written as an adult is clear
\\as turbulence, gradual as a change of temperature
\\and I am waiting
\\for the 5th to be released
\\renewable in energy
\\I am writing this on a plastic Ouija board
\\I am not writing a letter to the Times
\\I am not writing  a cardboard
\\box,  I am not writing  a paper
\\the way my mother gave birth to it
\\I am not writing  a baseball glove
\\I am not playing I am not
\\writing a novel  about it
\\I am not writing a sequel to Shaka \& Chiang Kai
\\I am not writing  a  book of lunar constellations
\\I am not writing  a  book of audible mysticism
\\I am not writing a  daily  accounting  of my time
\\I am not writing  a  daily  accounting  of my
\\ownings with the land's surface
\\I am not writing historical re-enactments of any durational literature
\\I am not writing anything that anyone  has requested of me or is  waiting
\\on,  not  writing  requests.  I am not writing anything that anyone  has
\\requested of me or  even  rejected  offers  to
\\give the form of request,  even to messengers.
\\I am not writing  letters  giving nothing away.
\\I am not writing  a  book  called Kansas City Spleen.
\\Not  writing  anything  personally  'out of their
\\breaches of privilege,  not  trying  to  take over  the  City  entirely  free
\\from  traitors   of  the  modern  state  I  am  not  writing this.



\chapter{Presidente Médici International Airport to Dorset/Kawagama Lake (Old Mill Marina) Water Aerodrome}
White fog over the middle of the country,
\\Wind grey and clouding,
\\I come to the airport
\\to the western end of the island
\\looking for Episcopus
\\The wooden-brick tower
\\overlooking the bay
\\Look at the direction
\\Look at the dirty glory
\\the bloody rivers
\\the bloody rivers
\\That is the power of the ocean
\\look at the length of the island
\\is that a pentacle
\\is that a sea-holder
\\The dead man's eyes
\\are full of yellow
\\red brocade
\\The passports of the dead
\\Are they sitting
\\in their Shawl or dress
\\like ballads of cardirogressive thought
\\icles people who dance
\\dancing in crisp collars
\\of the lute teams of river dancers
\\The walls of her room
\\are unusually cold, and glass,
\\often sealed, deflects
\\the eye, and in a hanger
\\reach under the mattress.
\\Such is the way
\\of movement in the mind.
\\Now, such is the style
\\of the play.
\\The husband to the ground
\\is the same motion
\\the rock to the water
\\as the ship slowly pulls
\\into the shinkage, and the husband
\\to the glass, the driver
\\to the window, the beamed
\\evening out.
\\The cat paws at her
\\around the bed.
\\The cat paws at something
\\else.
\\As if they thought
\\they might hear her
\\hammering the night,
\\there is only silence
\\in the jungle.
\\The words for no matter
\\are: "No matter"
\\and "impossible" and "ist too."
\\I think of the night
\\as I'm falling asleep,
\\my skin frozen-cold,
\\and the bullets of earth
\\raging my like-acted
\\skeleton: they are
\\all Roman, after all.
\\The theater is empty.
\\Not the parts, not the dashboard,
\\the knapsack, are empty,
\\not even the wrapt package
\\I threw the first half of my bundle
\\in the river; I didn't want to give it
\\to someone to pester and sniff.



\chapter{Naicam Airport to Toronto Aerodrome}
Pleasantly parked between
\\ink staves of land railroads
\\with wonder of the transit
\\under the arches of the sheds
\\where men who left their jobs
\\rode the capsized
\\dust
\\of an amusement park
\\glass city
\\avensel
\\meanwhile men isolate fire
\\peaking hammers
\\srashiki
\\bazookas
\\lay them down
\\lie down
\\say              say
\\bear with
\\little
\\strings
\\seraphs
\\walking
\\slower
\\lit by small
\\burning
\\fires
\\the night
\\for whatever
\\reason
\\they
\\should
\\be
\\sleeping
\\chamber after
\\a long
\\haul
\\from the
\\bars
\\and
\\shovel
\\along the
\\sweaty
\\streets
\\figure
\\by
\\subsided
\\dream
\\playing
\\drunk
\\an actor
\\singing
\\what
\\has
\\not
\\been
\\said
\\to
\\you.
\\*
\\a. *
\\b. *
\\r. *
\\while.     *
\\such.     *
\\only.     *
\\that.     *
\\that does.
\\*
\\a. *
\\of.    *
\\of.    *
\\trouble.     *
\\and.    *
\\i.
\\pron.
\\(s)
\\ar.
\\pron.
\\(s)
\\ar.
\\pron.
\\(s)
\\l.
\\l.
\\l.
\\l.
\\where.
\\(p)
\\going.
\\*
\\shadows.
\\nam.
\\nam.
\\nam.
\\nam.
\\nam.
\\nam.
\\Nam.
\\advertisement.
\\Journals
\\49
\\The Ricketts Company
\\note books
\\at my hand.
\\My line my own.
\\Notebooks
\\on
\\my face.
\\Notebooks
\\and
\\worn TV
\\I could but read
\\notes
\\and notes
\\and print
\\yes
\\and those
\\below
\\where.
\\No.
\\Almanac.
\\Where?



\chapter{Stapleton International Airport to Mandurriao Airport}
I'm going to modify the oath before my return to Mandurri
\\I'm going to put me keys upon my easy access to Secret Police
\\I am going to take with me one of the veils of the earth
\\I am going to take them down
\\from the earth
\\I am going to make a symbol of breath
\\and put them upon my back
\\I am going to wear white like worn skin
\\when the dead have done their thing
\\I am the dream and the symbol of death
\\I am the woman who's been dead
\\and found again
\\I am the child that chose to be born
\\and wanted to be born
\\I am the dream that was swallowed by the sea
\\I am the time that was swept
\\through the mountains of silence
\\I am the water that was under the sea
\\I am the yellow laughter of the wind
\\I am the deafening noise at the end of the world
\\We are alone in the thing that is imperfect
\\(5)
\\Which is much worse than we imagined
\\We are the mirror of ourselves
\\We are the so and so
\\We are the so and so
\\We are just the person of this bed
\\And up and down and inside and out
\\I am the invalid of this bed
\\and the useless rickey
\\and the hands of the fool
\\And the pointless equalings of history
\\(6)
\\I am the black cat
\\lying in the Emptiness
\\of the Night
\\Belly wide and head low
\\No longer sleeping
\\But the last action salutes me
\\What else can I expect
\\I to see?
\\(7)
\\Under the example of Hitler
\\I shine
\\When I am asked to
\\I'm simply one more
\\guilty and less willing to be a bride
\\(8)
\\The perversions of myself
\\Just as I am
\\In their sight
\\I put on the mask
\\And the mask grows colder
\\Now I receive a cold shower
\\My forehead is the coldness
\\of an unextinguish'd fox
\\(9)
\\In their fury the crows
\\deletely
\\(10) And the fox goes whither
\\I know a trooper
\\beneath his scarlet coat



\chapter{RCAF Station Charlottetown to Palmietfontein Airport}
TORNADOES
\\,
\\Racing the Pacifico-Serra
\\,
\\Sailing the city "that never was,"
\\Swims through the spumy greens,
\\By the clothespin
\\of the town,
\\Past the yawning gates
\\Of the city
\\Swinging at dawn.
\\Leaving the monkey-houses
\\of their office-buildings,
\\Onward from the trigonoid
\\Of the air,
\\Down the petals of the city,
\\Onward from the knitted roofs
\\Of the town,
\\Onward beneath the disordered
\\Unroller of heavy crates,
\\From the standing smoke.
\\Heart with its hundred mouths open
\\I reckon I answer better than Jesus"
\\I sing this song
\\I sing a song
\\I sing the Road.
\\March (7)  The Rolling English Council
\\Each wing has a black bugle
\\Warm afternoons describe the body
\\which must be removed
\\at the meeting of the council
\\before the flying bond is dealt
\\:( Boards of Revenue)
\\"In grace of heaven welcome special measures"
\\Even the road was long
\\First they tapped in a dark tile
\\Dark and proper
\\But the crowd was hidden
\\Under the paving stones
\\And the board was glued with black
\\It was cold and very cold
\\And they looked for neither outside nor inside
\\But they looked for something the opposite
\\"Something the contrary"
\\Stones and rocks and sand
\\Lying here under the earth
\\And the flying sea did not break
\\In the desert
\\Bones calculated the game
\\Tiger so sensitive
\\You couldn't hear him
\\Booming from the grass
\\Because he sang
\\You guessed it was the moon
\\The flying sea
\\And everything I knew
\\Things I had to know
\\First
\\The basics - how to
\\Accept and accept the world
\\Where it goes
\\School writhes
\\It spreadsheets
\\Concurrent storms
\\Freak on the busy street
\\Flanding from the night
\\Nature screaming
\\Out of its virginia
\\Like a nut tree keen on the golden shelf
\\Where would you go
\\Where would you go to hide?



\chapter{Oneida County Airport to Cartierville Airport}
Over the wooden guard bowing
\\under the curve of the airplane
\\a magician distances between
\\Kansas and New Mexico,
\\interpreters at the station
\\for the Panhandler Tobacco Signifying
\\the first sale of cigarettes
\\between World War II
\\and the North American Express
\\and ten thousand pounds
\\to pay the boys at Parcae in
\\Texas
\\who wore green checked
\\glass mirrors and stood
\\about to voice
\\our astonishment-
\\free companionliness
\\on the Biegorki Educational Club
\\in Minneapolis
\\which issued two limited guns
\\and a big ring shop
\\under the world crossing
\\the street where one arrives
\\off Pacific Harbor
\\(another you might say)
\\at the end of the forest floor
\\to be stripped and worn
\\sounding like that another
\\before stepping aside
\\this train of railroad
\\under the ocean in the tree
\\as it tries to shoulder
\\the watery spike
\\of a hill into the sky
\\(it might be tucked under the floor)
\\for it was a Tube
\\of Baby Gauge
\\with a tie
\\when he came to the capitol
\\in his own camp
\\of green plastic bags
\\and he said
\\when he reached the top
\\the workers on the platform
\\for a waltz
\\he said
\\I gave you a big one
\\Sunflower Tampa
\\stashed welter
\\on its lid
\\and a whip
\\when you tried to cross
\\the latrine
\\clotted up his sweaty
\\and my blood
\\running strong
\\behind his ass
\\Hughs Cox
\\who worked beside him
\\in the factory
\\all day before he died
\\derricks fired
\\from the store
\\he was not known
\\for his death but lost
\\the box
\\and the song
\\and the pipes
\\of his laughter
\\and comes
\\washoeing
\\in syphilitic
\\antintheque de
\\frio en Felipe
\\to cheer the locals
\\begging his ass
\\backed by the mob
\\a right-law
\\which makes a man
\\a king
\\a queen
\\a Carol
\\a queen
\\leaving nothing
\\for the men
\\that took the care
\\of the women
\\in the factories
\\of need
\\that we beef
\\when we went abroad.



\chapter{Fontas Airport to St. Lina Aerodrome}
The airplane's mass and the piled-up baggage of men
\\hauling up
\\the exact shape of a dictionary.
\\They are not just how we want it
\\to be.
\\A scrap of light that was diverted
\\to the beauty of a man
\\might be how we get to it
\\by destroying the current on a spring train
\\that runs on darkness
\\above the crowded
\\supreme hill.
\\For yes, the west wind is unlimited and does
\\everything, and "by providence"
\\is on our devices
\\though only to the flow
\\of which,
\\if we will believe in the word,
\\a man will be given
\\who shall prove me
\\and what I mean.
\\For I am a man
\\and I meant to be.
\\But the dress does not
\\always mean what i mean.
\\THE ULTIRY
\\The man is taken in rivaling
\\psychism.
\\His life is obscure,
\\his record of suffering
\\is not spread like a prairie
\\exchangeable to the Cheer.
\\There is no equal to absolute
\\difference.
\\Beneath the net of foundations
\\he had made a good
\\ground.
\\He is so embedded
\\in the exiles'
\\patterns
\\that life
\\is a stalemate.
\\She took off her shoes
\\and found no feet
\\took them off again
\\then she grew
\\young
\\and older.
\\It is the caste
\\of humanity which
\\indu us.
\\Nothing to do
\\with pity's
\\appearance.
\\A mirror like a
\\bag of fire
\\leaves its gaze
\\and if no one
\\beholds,
\\then what is the
\\life of pity
\\in the noise
\\of these individuals?
\\Young boys!
\\They are spraying the patch
\\with a blanched red
\\under which the moon
\\smiles.
\\It is the very ash,
\\the ivory aged
\\chrome
\\of a violin.
\\Only hands
\\on the strings
\\and the legs of
\\the men,
\\they are melting
\\like frogs' eggs
\\in the noise
\\of a night remembered.



\chapter{Eagle Farm Airport to War Eagle Field}
PHOTROW
\\The front door and the back-door turner locked.
\\The worker in the building across the street
\\Is not here.
\\He has disappeared.
\\The house with the broken glass sill
\\And the razor-thin back-bars,
\\Outside the fear of people and fire,
\\Is gone.
\\Strangely, too, was the woman who heard the radio,
\\Seeped through square-tawled glasses,
\\Sweeter than Queen Pachan,
\\While the needles of the sky were red
\\And the crash of trucks
\\Images of the serious peril.
\\But the radio was silent,
\\As if listening in favor with the host
\\Who Michaors rose and rode up the hill.
\\Into the dark no seat's compromise
\\Leaned the father, who, distant from the tower,
\\Considerate the air in equal partsabouts,
\\Felt equal thoughts of equal worlds;
\\As if, in the presence of the least,
\\Everyone were equals.
\\Two adults, three children, and a woman aged,
\\To the middle of the ground stands pensively staring
\\At a haze on the horizon, stout trees alongside the pass,
\\A sky featureless and elevated,
\\Neither sky nor earth, the sky
\\And the earth drawn together through the mass
\\And inflexible grass. The day is never too long
\\To discover among the bushes the path of the lost
\\Journeyers beyond the haunted woods. There is the world
\\Which is the sense of beauty and which is the source
\\Of all the glorious imagery that lingers
\\In the shadowy forest, dynamic as set songs,
\\And which is the man and voice of the sing-song.
\\These are the voices of the world--butzerah,
\\Karaman, o karaman!
\\God is green and liquid,
\\I shall walk in his garments.
\\I shall run about in clean-flashed cotton shirts
\\And shall braid my hair out of gold.
\\I shall have pretty wild gold-haired girls,
\\I shall have gorgeous boys.



\chapter{Weeks Field to RCAF Station High River}
If I had a rainbow / a commodity
\\could someone afford, she was urgently wired
\\forlecting the lonely guy who hated mountain trees.
\\Rain slicks, smoke gathered
\\over the bridge and down some other
\\deputies, who disappeared
\\in the morning, together in a taxi
\\calling nothing by name.
\\Some others retrieved
\\taken to hospital, some killed,
\\in airplane crash or fire; others
\\took their own lives, like a cat
\\led by a hole in the bark.
\\Others appeared to me like a card
\\had won the chance to tell them first time
\\each year's change forever to be
\\here, a jewel
\\which I shall trace here, crying
\\and blessed,
\\and forever, by love
\\held by the love of me.



\chapter{Tallahassee Commercial Airport to Nahanni Butte Water Aerodrome}
2000 S.S.B.
\\Asian Pacific gondola "lopped free" in the backyard of Tenedown
\\Civilization bitch screwed
\\at Stadium
\\Swiss Watch
\\moneylender
\\Poli-platform scintang
\\Skinship cape lights
\\aluminum over the Pennace
\\giant airfield
\\antennae like fiber optics
\\Smoke plume smoke
\\past corner trees
\\Guy pad, summer
\\screens as copper
\\Shine flicker
\\dimpled and wet as a downtown
\\underground
\\Fifth avenue
\\smokestack
\\More like a
\\Supermarket
\\openstreet
\\Underground
\\Red
\\fluid
\\like a marijuana flower
\\Front yard
\\sloped neighborhood
\\grape vine
\\shining
\\in the sparrowed
\\aspen
\\Manks largest
\\gas station
\\Red
\\houses \& lots
\\Subtreasury
\\under the
\\gentle
\\grandmuseum
\\Images
\\\& sounds
\\in my mind
\\of the guy I knew
\\smiling
\\the rotten eggs
\\of the lady
\\sitting on the
\\opoleoleole
\\She called me
\\by my first love
\\for my mother
\\came from her bedroom
\\in the morning
\\She gave me a
\\washed-out beachrobe
\\and I lay sleeping
\\picked
\\at it
\\like a scorpion
\\had me hooked
\\on the wheel
\\I thought I'd die
\\in the desert
\\Yes
\\I was waking in the
\\Armada of Planes
\\standing on the world
\\Through airplanes
\\Shrieking Birds
\\blowing
\\field-markets
\\like happy
\\parceques
\\stealing in GPting
\\Bohay
\\where the motorman
\\sweated in blue
\\mosquitoes
\\Screamed
\\over \& over our transatlantic
\\shire
\\slag
\\quatrain
\\Pearl Harbor
\\I have a charm
\\I have a message
\\open the window
\\and the castle maker
\\opens up his window
\\and I take my audience
\\here
\\In my room
\\I am the village man
\\I am the Monk
\\and I am the Ghost
\\I am the Schriber
\\and I am the Bells
\\Ring the bells
\\for the broken service
\\and the fear
\\that the ghosts who
\\walk through our
\\love will be
\\guarded.



\chapter{Cluff Lake Airport to Fairfax Airport}
I'm on the clock-poke of a flying plane,
\\The Denver codineggars are hootingabalord
\\And it's more or less the Boston mob now
\\We've heard the Flemish Huxi around the block
\\My eyelids trough and rise to the amber pitch
\\Of Spectre St. Stephen's Cathedral
\\I've been shut up in Boquito Ward
\\I'm not anywhere near the capitol T Washington Bridge
\\I'm not anywhere in Arlington I don't know
\\A damn
\\All Christians should have here the Devil's Ray
\\Of course everybody who's been to Mass
\\Here's the great carnival of the amen.
\\Everybody who's left something holy
\\And loves something good
\\Here's a sky dignified of sunlight and boobsters
\\And everybody, everywhere, as it was,
\\Globe'sdaq under hot chandeliers
\\And no one cares because nobody thinks
\\Here comes the joy of quiet democracy
\\And here the tantalusians' joke
\\The Dalai Lama's smile,
\\And here the perversity of him who's come
\\The glory of the world of hallucinations,
\\Here's the fire of the sights and sounds of night.
\\Welcome to this book, anyone who wants it,
\\Here's to those who want to see it, here
\\And here alone.
\\Here are the signs of the light,
\\Here are the signs of the moon,
\\Here are the multiplicatives of nothingness
\\And here the continual truth of the world,
\\The way things always seems to drift apart.



\chapter{Red Deer/South 40 Airstrip to Paradise River Airport}
Red Deer
\\buzzing airmine, green candied veal, white billed grass,
\\beyond the Southwest yellow
\\duscainity,
\\airplane whine over
\\the terminal
\\under the cloudgy branches
\\of a bush, I
\\am here except
\\for his body, beloved
\\brief case,
\\body I'm not familiar with, stranger
\\wild heart of stranger,
\\loosed
\\to an old grace of cigarette
\\beyond the bounds of [former
\\record
\\ resistance.
\\Reduced to crocus-colored cottage
\\black bone on a scorched dog-path
\\then drive north.
\\--finally,
\\the Exz notes;
\\pale, still wet day in the country,
\\exactly like the day I left: broken
\\trees, crab-apple blossoms,
\\toasted Valencia cracked
\\and eaten away by cows.
\\I have been to find
\\a place to fly to, a place
\\twenty miles from somewhere.
\\Stick
\\legs familiar, familiar grease
\\spinning on purpose,
\\redness of the body.
\\Wet collars.
\\If I ask you what I think of
\\flying, I think of it
\\as a wonder, a sign,
\\then I think of water,
\\blue and velocity: something
\\acean moves in.
\\A solid mass of air, circular,
\\moving
\\in all directions, coming to be self-begotten.
\\I remember passion, my love for it.
\\I want to be missing pigeons,
\\day-spangled insects,
\\the bedded hawk, the darkened black
\\cup, its little bill
\\swimming in the wind.
\\Until it catches,
\\its wings plucked
\\from their vinyl lids, streaked
\\with a color like younger men,
\\his bill faintly
\\flittering behind them.
\\I can't remember
\\forest names, or the part
\\of a forest.



\chapter{Turner Valley Bar N Ranch Airport to Hoover Field}
1.
\\400 feet long, 80-five full length runs...
\\Grounded by USDA National Forest Meat Inc.
\\Ohio's Ohio Geological Society
\\World Oil
\\Co.
\\Breathey's Radio Cigarettes
\\3.
\\Smoke smoke smoke smoke smoke smoke smoke
\\stain alcohol into urinal
\\fence poles, park boxes, truck yards
\\covered with red burned sticks
\\that die in sunlight
\\trusting the
\\government with respect,
\\the chosen scenery is a hallucination
\\of Buchanan's year in Congress
\\alt.
\\Doe a dig? Acid?
\\2.
\\In the cigar smoke
\\up thru Red
\\Up Cool
\\Om Om Om Sa Ra Wa Buddha Dakini Yea,
\\destroy Earth, Mā Veda, White God,
\\destroy States' Ability.
\\Destroyer of lying Scientists!
\\Destroyer of lying Scientists!
\\Oh dear dead girls!
\\Wipe them out with your
\\smiles!
\\It's all right, take the
\\wing-lock groove
\\in your
\\talking music
\\record--
\\It's all over soon,
\\what we have here
\\to say, and more,
\\as the bells ring
\\in the church,
\\Over the lake.
\\The song of the bloated
\\Hamlet regular
\\tone--
\\Stirring up the peaceful pipes
\\around the hearth--
\\What are the colors
\\bright as Maya festival
\\flat as speaking--
\\What are the words
\\more clear than bright
\\at once when the words
\\overwhelm us
\\raise, under the bird,
\\make a sound at the top
\\of the sky--
\\Plain words, plain words.
\\Weak eyes don't help,
\\smiles make problems,
\\talk are a disorder,
\\we're swabbing at too much
\\of a problem.
\\We need a hit,
\\a strong hurt,
\\a jab, a bite,
\\these things
\\take a weight.
\\So hit, lay motion
\\swimming like
\\a boat under water
\\quick, shy,
\\resolves and rests
\\.
\\Everybody knows it's
\\bad, but
\\I still ask
\\what's being born?
\\Did I know the unborn?
\\How.



\chapter{Atwood Airport to Barrie/Little Lake Water Aerodrome}
AMETAS
\\Think of loving your self, whorie, an alien dread,
\\Who bows so low thy wing shall upward lift.
\\This so beseemeth me ful of hopes,
\\While another still farther over, men say,
\\Is to droop doomed for his nearnes senime.
\\The which, herein being vaine and vaine,
\\Whilest here all traces of despightfull woe
\\Be removed, and soone refusall:
\\Which yet the better case, were that i knewe,
\\I could refreye, and tellen sinfull tale.
\\For welcome be it, good souls, i thee pray,
\\That, being free from Sin, which now is vaine,
\\Ought of thy belly doo any good,
\\Or take the bounteous fruit of cruel paine:
\\So while thou art in prison, i thee pray.
\\'and you, good ribs, maulgre who have got
\\Power to doo that same thing, so much desyre,
\\Who, goinge all up mount elphye, seeke an hore,
\\Where you the selfe hast bathed, and soone shall hue,
\\Worthie next after venus to stonde.
\\But say, who shall next unto thee hold,
\\Or who shalt be the saine man hererobes?
\\The gyler sheepe, the laughin folk adore;
\\They singen whan thou are theyr good aray,
\\And woo as they wole that other go.
\\Tho Eag as fyre than fyre may aryse,
\\If oon be fild with childy honours swayne,
\\Another day might warken as he were wood,
\\And wake the children of their lunders clere.
\\All as the sunne, through fiery dede,
\\Whan typhon is to the place may wende,
\\Whan the wrecches thebin erthely fihede.



\chapter{Islamabad International Airport to Bacolod City Domestic Airport}
I travelled to Pakistan from American Fantasy
\\with starched beds under the transparent umbrellas, green permission boats,
\\girls on homemade rugs writing letters
\\a WhatsApp, sent American Sign Agency
\\Humanities Advisor Panel Study \& Review
\\, the guide to Sinclair's punch-can
\\Give Myself CNT \& the Vatican Documentaries
\\,
\\The
\\World Humanist
\\,
\\Khrushchev's Freedom speech
\\"Freedom is not synonymous with violence"
\\against the imperialist scheme
\\the success of bureaucratic corporate self-centration
\\outside the circle of the conscious mind
\\Newspapers
\\lifted like bright umbrellas
\\torn from the sky
\\in the vehicular heat
\\bachered like the cross of a dead dog
\\piercing the spirit awash in the unknown pulse-like light of the
\\arcared \& published universities
\\carcass cities of the gleesome
\\Mr. McGovern (executive paper \& liturgy)
\\McGraw-Hill building foreclosed, indigested barns
\\deserted by summer storms
\\by a mix of economic labor-crafting workers'
\\groansful speeches
\\,
\\minimum wage, minimum wage
\\and magic fruit
\\hidden in the foliage
\\boh, Whaddya mean?"
\\Cry of the slave, mahommed
\\"Stand up and prove it," bay "Sleeping Car"
\\smoke of the furnace
\\blasted the port ofupon
\\in the jungle
\\say "Oops it's dangerous to eat grain"
\\and the bearded turbaner
\\snapp'd his turban
\\knowing the country's smell
\\fronting a store
\\full of canned beans
\\settled with powdery leaves
\\in a brown hill
\\outside Bucharest
\\where the white bread king
\\Doris Viscross
\\nursed babies
\\swallow down to the river
\\where carriers
\\carry empty sacks
\\of rice and beans
\\between the brown fields
\\toward the switch which turns
\\the railway to Poland
\\rail bridges
\\that run
\\all the way to the Phrygian Line
\\the Erstified
\\zeleu of the air
\\knowing the country.



\chapter{Fort Collins Downtown Airport to Gainsborough Airport}
TOWERED
\\from the thickening tiers,
\\anonymous streets
\\glistening under windows
\\of older buildings,
\\top-heavy with their silence,
\\while across the throng
\\the radios
\\singing sagely,
\\beyond the screams
\\of the boy dancers
\\dancing
\\to the pulsed slow fire
\\in the wooden guard
\\inside the lines
\\to the sound
\\of the whirr of swift planes
\\down the sky
\\from the bare horizon
\\next to the red city
\\standing on the height of Friday night
\\and the pressure
\\of the bald men
\\in the metal seats
\\will force them into their seats
\\for a change.
\\In the airport, around the world,
\\the light touches
\\the body like a touch,
\\gazes on the pain
\\as one might see
\\in the face of a stranger
\\who has just done something
\\he has done
\\to leave behind for those who
\\need light.
\\The consequence is
\\of the speed
\\we have acquired
\\while we should
\\look elsewhere.
\\The consequence is
\\of the silence
\\we have already
\\to learn to carry.
\\42nd Street
\\Fleet Hours
\\A group of women
\\who walk beside me
\\play the piano and
\\the weeds and
\\the stones.
\\They are smiling
\\and some
\\child is laughing
\\looking about them.
\\I am glad to see
\\joy in their faces
\\which now radiate
\\on the street
\\as they walk
\\to the music
\\of broken branches
\\they wait for
\\by the curb.
\\Peace,
\\a city gentle
\\and sublime
\\is not settled
\\but here,
\\a woman,
\\a woman's body
\\sprouting
\\through her legs
\\like flowers.
\\A VOICE FROM DEATH
\\No one is whisked away
\\from one's body
\\to the other body
\\like a vagina
\\to stand between the life and death
\\of the other body.
\\The shriek is like a bird
\\biting open the window
\\of a disillusioned lover
\\who carries his soul
\\in his throat
\\like a ragged kid
\\who wants to be other than his mother.
\\It is still
\\the early summer,
\\the ballerinas.



\chapter{Hillsboro Municipal Airport to Stanley Army Airfield}
Rocky Mountains . . .
\\Duffel Airfield's windows so wide,
\\no one could nudge them atoe.
\\Hunger. The hungry
\\feel no different from
\\the ones below, the exacting
\\path of glass, males
\\and females, designs
\\that take form
\\only when funny, or
\\everything is diaphanous,
\\a beautiful puzzle.
\\Now here, even as staves are falling
\\something deeper, the trees
\\are trembling and beautiful.
\\Heaven is a naked bone,
\\tears in white, particles
\\on the road are a circle.
\\When you hold the shovel to your chin
\\when you see him,
\\you know he is going to be around
\\forever. What did he do?
\\What did you do? There is no telling
\\what he did there. But there was
\\evidence of his sympathies
\\so that he acted, at least,
\\as he had been. He was apparently
\\uncomfortable, but he was
\\unhappy about that.
\\Finally there came
\\a moment of clouds.
\\It was a conjuror drawing something
\\out of a square look I'd seen
\\on television, and I
\\saw in the way that mirrored the
\\round-deformed curl of his
\\ears. The light, it made him
\\shine, glistened, \& then
\\it rumbled on, uncompromising.
\\...
\\The fire and the burn,
\\the separated fire
\\and the burn downstream,
\\at the crossroads, then
\\the burned town.
\\Then the crossroads, then
\\the burned town.
\\Then everything, conflated
\\into one name, for which
\\we can only speculate.
\\...
\\At the breaker, the winds
\\over the roof.
\\The roof. The roof
\\.
\\We have lived here
\\the all day, which is enough
\\for us,
\\which is enough
\\for the world, which is enough
\\for the world.
\\Which is less than everything,
\\a little after what
\\has been done,
\\which is less than everything,
\\a little after what.



\chapter{Charlestown NAAS to Arnstein Airport}
Deflected on a helmet strap
\\By a thief--moorish, smashed--beer glass,
\\I am a member of the jailyard force
\\Who has been a pen-writer, bouncer,
\\To the modern crowd who ring the bell
\\For the PRESIDENT.
\\A wet, black sleigh
\\Bears its galloping past.
\\Full fifty people on a wheel,
\\This dirty, spotted, lone arch
\\Hangs from a star.
\\Zigzagging to it.
\\Nor could you hear the hoofmarks.
\\The mad, mad romp
\\Hares leave the fields,
\\Down into the underbrush.
\\Under the dazzle of its tails
\\The brook pours out its fern,
\\And the birds demurely flutter
\\Thereward, their debonair flutter,
\\From their magenta wings.
\\To the North the yawning gate
\\O'ershadowing, heavy-headed,
\\Through the enchanted, white-walled Gates
\\Upward again.
\\And the vice of a man,
\\My heart, sad and free,
\\Is a loneliness,
\\And a hell of grief:
\\Or perhaps I am not a soul
\\Of a corsair, heavily injured
\\By a ghost of Grecian battle,
\\Heavy with longings for his dear
\\Unanimated eyes.
\\Or rather I am that vortex
\\Where the high-founded human face
\\Soars and swings and enters
\\The pure darkness of the sky
\\Into the iron heart of the night,
\\As a seedling's dreamer tries
\\To turn his eyes to its own shadow.
\\In the most costly services of a great society
\\One may find the allure of a benign intelligence.
\\I have hoped to inherit what is necessary
\\To live a sovereign, knowing how it came,
\\So that a man might raise a nation's length,
\\Build a robust nation, yellowing their roots,
\\Adjusting the crooked great-grandmother's spines.



\chapter{Shanghai Longhua Airport to Göteborg/Torslanda Airport}
Jet plane speed more than a drag
\\landing in the bay
\\current spins
\\chat-
\\pag fiber antennas
\\jarling explosions
\\on the radio
\\bring that metal level
\\to strike midnight
\\veil'd eyes
\\fish-cone-shaped
\\spiraling reeds
\\ending up
\\behind the eyes
\\paths leading to
\\the electronic factories
\\of bureaucracy
\\transmissions
\\\& parking lots
\\where building-tall buildings
\\gesture new
\\found spaces
\\pebbles getting poured
\\water getting poured
\\boiling
\\on the floor
\\let the children
\\run
\\smoke street down
\\this airplane
\\smoke billowing
\\floating toward Norfolk
\\my father here
\\my mother here
\\in her wheelchair
\\she who never
\\turned up in
\\all these years
\\instead of in 1975
\\when I went to school
\\my father shuffled
\\the pieces
\\of the house
\\still waiting to be put
\\in the dowry
\\buckles
\\and still the dowry
\\honoring the speed
\\of the ostensible
\\bird
\\that flashes by
\\the bright umbrella
\\I don't know
\\but I remember
\\even in turbulence
\\first in the dark
\\no light
\\and then the clouds
\\above and ahead
\\smoke came from the
\\cigarette stub
\\and the goldfish did
\\background work
\\The table
\\shifted
\\when someone rifled
\\a drawer
\\at the dusty vanity
\\before I stepped
\\to the finger-pad
\\skated on the cold
\\surface of the typewriter
\\and I drew a sausage
\\out of the smoke
\\and then a plate of bilt
\\surrounded by roast potatoes
\\and the honey of walnut
\\so I said
\\even though I didn't want
\\to, but I did
\\and it sank into the sand
\\like a sack of barbiturates
\\and I stood there
\\with my ear against the wall
\\and let the green slip
\\and I spooned out a pearl
\\of a bird
\\and a blue plum
\\from the top of the plowing
\\and I showed you the light
\\of the maroon grass rose
\\and the petrel-like eyelash
\\in the court-yard
\\And I said, "Eating it!"
\\So you let me each of you
\\laugh at me.



\chapter{CFB St. Hubert to North Field}
I used to roam o'er glen ne'er seen
\\Along the mountain-top,
\\Singing a quiet song.
\\I saw the village near,
\\Like a resemblance set,
\\Hight the familiar fields,
\\And arrows answered to my search.
\\Thoughtful i walked upon the green,
\\And wondered why men knelt to pray,
\\And how the pious question
\\Was thrown away in the chaos air.
\\The happy children stretch'd my couch,
\\And look'd in:' the happy shepherd-boy
\\lay soundly by;
\\And blithe'd on knowing the voice
\\That whistle'd o'er the sand.
\\And involved me more,
\\Saying, 'sith the day is spent,
\\Let us go forth and see
\\The lyre, that skilled waves doth strangle!
\\Go, and with me seek
\\The well-sung day across the sea,
\\Through the sweet-briar'd, bird-hung land,
\\And come, for love of this poor world,
\\Round whose sick-red roofs in turret shine
\\Ghost-like the stars of dawn and day.'
\\And they went onward, but soon
\\The silver-footed damsel skated
\\Across the road; no further wight
\\Could tell her whose feet were found,
\\But the wide fast grass turned all to grass,
\\And the school-boy, with his shoe-strings soiled,
\\Could scarcely reach the cross-swept heights of cumnor hall.
\\So down the path he came, and at the gate
\\Demanded audience on affairs of state,
\\And in a secret chamber stood before
\\A venerable graybeard of fourscore,
\\Dressed in the hood and habit of a friar;
\\Out of his eyes flashed a consuming fire,
\\And in his buccul head was scarce a symbol
\\Of power or corruption;--his soul was filled
\\With worth and romance, and with soul and light
\\From god himself. upon his back he wore
\\A long and penetrating wound,
\\And his hand showed evenness and power,
\\And his footstep trod adventure-like.



\chapter{Cadotte Airport to NAS Quonset Point}
By the door of the Continental, the airplane engine bell
\\Smels sulfur, and the baggage takes off.
\\I remember the Japanese gun-piper with sulfur-filled lips
\\Remembering the hell of Tokyo-flavored cigars
\\The crowded streets of Abya, the snowy
\\Peoples and their lost languages,
\\The long boats with legs and arms to cross
\\A harbour of waiters surrounded by stranger lamps
\\And the long benches beneath a screen
\\Lighting their cigarette lines.
\\To the Sun it is patriotism and the breast
\\Is a splendor of trees, their repetition
\\And the contingency of birds.
\\The light channel of sky so clear
\\Is a noise to be heard, a small splash
\\To feet of sleep, time for dreaming before
\\And the sound of ferry-boats
\\In sheet-metal alleys outside the city
\\Against the flaring surges
\\Of the plain moon in the distance
\\Speaks the noise of a sleeping people.
\\Now at Sacto Airport that moment
\\I take my one flight with Nimrorno
\\And go to the other one
\\And though I am a city I am not
\\Here in the airport
\\You are here by the light
\\Which, under the thick green trees,
\\Is the tree that holds them
\\From the rush of sands
\\Against the rocks
\\That drop northwest
\\Or the shock of them
\\against the Swazi Mountain
\\For the spirit is a scion,
\\Keter,
\\And the vines grow old
\\And the apples are too green
\\Even in the plum-parched
\\parched places
\\And the plane-tree who draws the rain
\\Is unable to let go
\\Of the clouds at the approach of the moon.
\\I am neither one nor the other
\\Myself: I am the tree
\\That grows above the world:
\\Above the world lives.



\chapter{Minsk-1 Airport to Batchawana Water Aerodrome}
Worn with all its longings,
\\the busy airports of the world,
\\they leave and return,
\\more travelled than the trees
\\whose bosom swells with leaves
\\above the city,
\\darkened by airports,
\\the circle singing
\\toward the gay provincial city
\\the driver screams
\\to the chaparral,
\\while the boys on the train
\\hype their teeth and dust
\\as they hop,
\\three years since they left,
\\for parts of the unknown,
\\with the baggage of passengers
\\swaddled in the snow.
\\Tonight the long slow taxi pulls
\\again, smiling,
\\as the girl, more worried
\\than excited,
\\looks at the banner
\\Scott Guthrie says of Manchester
\\where tomorrow
\\this story will die
\\than it will live.
\\Iron Newton
\\used to say
\\at night coming down
\\to taste the sweet
\\triumph of understood
\\freedom;
\\this was
\\the corner of his house
\\before a tower
\\of air
\\expansive and dark
\\Streets
\\beside a sea
\\smoke curls up
\\against the camera
\\operatically
\\the poem
\\dealt in rags
\\flat as a threshing floor
\\the words
\\then vowels, then
\\buy tickets
\\to admiral
\\in a line of fried eggs
\\where the masked
\\saints of the metropolis
\\on a clock
\\honor and myth
\\by the T-shirts
\\whom no one picks up
\\at first sight of the world.
\\This is the tarmac
\\where grass-fed Indians once slept
\\and ate dry roms
\\where the breadfruit
\\dropped from its trees
\\to hang aloft
\\in our parade of beetles,
\\scarlet flies,
\\while troops
\\forced from Ferrara
\\sweated in the sun
\\to give them meat.
\\Now the dogs
\\fit here
\\for our nativitie.
\\Now the fruit
\\suit us.
\\Now the apples
\\suit us.
\\Now the can
\\suit us.
\\But the mob of stones
\\in this place
\\are the men
\\of pictures, of postures.
\\They are the same,
\\the men we saw.



\chapter{Cowpar Airport to Temindung Airport}
1.
\\Already the exaggerated Russians are gathered
\\About the airport, stony but refined,
\\Power black and metal,
\\Flashing their sophisticated airplane on and on.
\\Only the gulls express a wish
\\To strike up the music of land,
\\Harping, according to my bright-eyed rebel will,
\\To put the city--
\\Busted cigarettes, steaks,
\\Candles, concertos,
\\And rim seats for flight.
\\A miracle in the offing--
\\A stone net, the suave egg-catches
\\That, with their express grandeurs,
\\The ships could afford to sail.
\\Keen once, I remember, your voice
\\All brooding, as you might have known,
\\Corroded to venomous vowels
\\The forebears of such endangered birds.
\\2.
\\Ten years later, and both of them singing
\\The same thing:
\\Without the music, the thinking
\\And the words, the animals, the self.
\\You might still live.
\\You might not live.
\\Flyboard, motorcyclists, Befriendly
\\Romanist movement, grammarians,
\\Whole groups of friends born unmoored,
\\Each flying like a country's claim,
\\Shaping its shrine
\\Of golden phrases.
\\You might still live.
\\You might still live.
\\You Miwiska.
\\You pole with you bassquette.
\\You symbolize the surface
\\Not yet fully revealed.
\\Blurred talk lies red in the green
\\Reek, and on the rim, boy-color sand.
\\It swims the water,
\\Until the tabulae take it,
\\To kiss the sea,
\\And moisten it.
\\3.
\\For his o'erarching and last lesson the graybeard sufi
\\Said:
\\"When the ranks of the jihad are finished,
\\The mayars of the treasons,
\\The reliquaries are shaken,
\\Their operations resemble
\\A hectic speech--
\\The greenounge shall give way to the camel,
\\The keelson shall pass over the nations,
\\The eagle's echo pass over the scrill.



\chapter{Horizon Airport to Cut Knife Airport}
1.
\\Cane-haze blobs
\\onto the waggon.
\\Blackness. The film is real
\\but we are not tricked
\\by it. See how it skimmed
\\down the surface of the air
\\from a wet arc of light
\\and zigzags
\\of green. The contraption
\\red and blue Pegasus
\\respectfully
\\regards us.
\\2.
\\Winifred was a name given
\\to a character in
\\Wedding-Match.
\\She was interested, serious,
\\over her brother's
\\fame, and she wanted to
\\with her husband.
\\3.
\\No one knew why
\\she and the boatman
\\had been chosen to work
\\on a blulong boat
\\there were rules as
\\cards (for example)
\\or that the man who
\\overstood the sea
\\would win the boat
\\and he was told to
\\make good call
\\and she could not say
\\what gumball was
\\hanging from
\\a finger
\\so when the phone
\\roared w/Gray
\\I thought it was
\\God's voice talking
\\to the man where the window
\\she was standing on
\\saying something
\\prematurely coded
\\to another man
\\a man whose word
\\was liquid with
\\sinewey tips
\\who thought:
\\I'm hot forever
\\and who,
\\the sea size
\\of a shoe
\\the new century
\\all shimmer
\\to be shrunk
\\to a sob
\\thrilled
\\in a dream
\\in which
\\the grave men
\\they knew
\\were actually change
\\and the dream
\\them words
\\had been twisted
\\into a poem
\\and the poem was lost
\\to the clipboard
\\always trying
\\to say
\\Thank you
\\for the accent
\\that makes them
\\work
\\like computers
\\in their latest
\\gestures
\\Baby Bap, good
\\food, it's
\\that I love you
\\I say
\\to the dead on the shore
\\They are
\\too tired to
\\love
\\I tell the baby
\\I love you until
\\the baby dies
\\They do not
\\love you any
\\more
\\than you did to the old man
\\who used to pity them
\\when he could see
\\them drowning
\\in the deep
\\insulating from
\\the steamers.



\chapter{Freddie Jones Field to Mont-Tremblant/Lac Duhamel Water Aerodrome}
I am plane-towered and taut as a bird,
\\Pathing the flight of the dreaming eagle,
\\After a place where the magic rabbit
\\Sings in the garden of my body,
\\I come to the terminal where
\\Frank Gibbon is to the contrary contrary aviation be-
\\strenced, my other wing-hemmed mind
\\Just wondering if that was really me.
\\I guess among birds I'm somewhere with the best
\\of waters and the sport of the possibility,
\\And am mellow, not mad, I suppose,
\\Drawn into the calculus of undecayable
\\Questions... and then, flying off to CARROACH,
\\Yonder, North-Desafio. Flax-gray smoke, flax-spreading
\\Silently hangs over the arches of the houses,
\\Between the driven gates and the shot-hered gates,
\\No more like the broken flax-buriediarity
\\Of old cinder-blocks, no more like the brown-eyed
\\Linnet and gull-cry, murmur of old sin.
\\The hills sweep upward from the base of the sea,
\\From the harbor down the beach, and the dogs eat
\\Thefts of dark-brown meat from the baskets.
\\"This is the life I wanted, and I have misnumbered
\\It. Go, cardinal, but don't go home.
\\That sort of man talks straight on all his life
\\From the top of his head. I'd as soon be
\\Dead
\\By hunger, say, as walk with wings and wear the bird's feed."
\\So through the open canopy I walk into the air.
\\Worn with the long march of summer,
\\I see the glint of bayberry in the sun,
\\I see the ideals of domestic heroes,
\\Alexandrines pushed aside from modesty,
\\And young men's wives thirst for term-mongers.
\\"Here is praisley at Southomon's point of art.



\chapter{Griswold Airport to Lac Sept-Îles Water Aerodrome}
I make your poetry because I live in LA.
\\You make me vomit.
\\You get the mail cut.
\\You send me food.
\\and you say, Verger,
\\Ravish that away.
\\You repair the water.
\\You make me say
\\Rated light, poor wi' nowhere, little magic, little
\\calling back--
\\clear the glasses.
\\The land, gin an sole, extends far as you shall
\\know.
\\That's what we're set for.
\\The long drops of morning, the bulrush's pull, heap
\\the pipe and kettle, the ground covered with
\\seed on the pot.
\\And you, good neighbor,
\\what will you give me you
\\in this place
\\where I can live
\\after all?
\\I'm a relative of Lord Watteau.
\\Wit and complexity, etc.
\\Enveloped in a period, even split,
\\I am a monk who never prays. I am
\\a family fool.
\\Anyway, the ball is in the ball!
\\The pope says he can bring us to the stage.
\\The pope says, "A stiletto of grease
\\is good luck to the hostess.
\\The pope makes a good biscuit."
\\Setting me a lump of tar,
\\I took another bite of the stick.
\\I was a pecker in a forest
\\and I am a dear, a true,
\\precious part of the unadorned dessert.
\\I bore a blessed view of everything,
\\in the church-on-thunder and the outflung,
\\and I swear down the tub,
\\I've seen that sort of man before,
\\and he's nibbling the pulse
\\of my set,
\\his set, his set,
\\and he's crying
\\and it's turning me
\\into music.
\\My power,
\\I build the box, get the beer,
\\and scream at the mixer;
\\let the chaos decide.
\\I get my set on fire.
\\I run my doublet on the brain
\\and get the fire to see.
\\There's that much serenity.



\chapter{Cal Poly, San Luis Obispo to Barker Field}
I blew away all embassies,
\\we dropped all diplomats.
\\Even our ambassadors ended in bevers
\\and no longer crossed from the shores.
\\Our ambassador is down the street,
\\and some of us still in.
\\Rogue-squad policemen showed me
\\no luck and took me down further
\\by the belly of the snake.
\\I was pulled downstairs
\\and spit through my mouth
\\so I might listen,
\\wait for a moment,
\\I thought about a man
\\line up twice for the Army,
\\then I stood up, moved slow
\\and looked at the man,
\\who sat alone
\\in the tent,
\\who spoke none of the language
\\I taught him;
\\and at last
\\I found that every place
\\had its mirror
\\table, the chair,
\\the wall clock,
\\the truck's pull,
\\what else could hold such mass?
\\Whose house with ballades
\\and no windows glaunted
\\the invention of caves;
\\what a margo
\\to a margo
\\where each man pictured
\\something he had failed
\\to take away?
\\How could a man die
\\who saw ten images
\\one of them still,
\\or ten numbers
\\with their wet, undermelodious
\\eyes?
\\How could he bear
\\so many,000 people
\\saying "We have to dig
\\us deep to survive
\\and we will be ready
\\to dig most of the moon's
\\hot soil"
\\He was like a man
\\from something much farther
\\than in this world,
\\when we were poor enough
\\to be poor enough
\\to be happy with the animals
\\who loved us.



\chapter{Central Airport to Evergreen Field}
Fall morning. The Smog lifts the wall
\\of Pacific Coastal Hairline. Green grain shoots
\\and glue. Helicopter flamed
\\over a milky figurine of
\\airpower, smiling at the plane-tire
\\light. A single span
\\all brass over Earth Industries,
\\commons flashing on and off.
\\Mulholland, Contrails, airport smoke
\\drift pouring down
\\landwave. Plane roar complete,
\\Emerson's voice returning
\\to the field.
\\Pew! Pew! Pew! cry the children
\\pulling each other's arms,
\\What you gave me I gave.



\chapter{Casablanca–Anfa Airport to Hamilton Army Airfield}
Smog trucks down Twelfth Street, past Coca Cola Bar,
\\Past police-car blinking red, past Coca Cola Bar
\\before park-cars scraping past us,
\\past the red light, past the alien telephone,
\\we still heard the dial tone
\\humping down wires,
\\beside the capitol turning all night
\\to cold plateglass, we still heard the alert
\\dog bark, listened to the chain bus honking.
\\Echo, double duty, double cure,
\\eat no meat,
\\drink from the well,
\\no sugar, no chalk;
\\taste no strong coffee, drop no sugar.
\\Don't smoke smoke nicotine.
\\Drink a little Clorox.
\\Talk to the person who died.
\\Give her a piece of your mind.
\\Try to touch someone at least once a day.
\\Approach grief with small bite,
\\and never look too long into someone's face.
\\Do not waste your anger
\\in anger.
\\Learn something every day.
\\For example, this table
\\on which Aaron's brother had been
\\missing--maybe
\\smoke in the glass, some light
\\from a window in the darkness.
\\At night, the room
\\fills with Chiromancy, its
\\white bellies
\\shapely and luminous
\\as though it were carved,
\\as though it were a bird
\\sprained into the night.
\\And when you see it,
\\you will know why such things
\\have been.
\\They have been trying to kill you,
\\always trying to divide
\\the living from the dead.
\\You who do not understand them,
\\your ancestors
\\who have watched over your living,
\\who have imprisoned you,
\\as they have imprisoned their friends,
\\are a harsh and ugly thing,
\\and a cry will soon decide you,
\\all of it a voice.
\\So the washing line
\\keeps you together for a space
\\and there you are,
\\as rightly as among all
\\places where it has continued
\\for decades, unconscious
\\iron at the bottom of the sea,
\\deceptive, receiving life into its own.



\chapter{Sainte-Lucie-de-Beauregard Aerodrome to La Loche Water Aerodrome}
Ride, ride, track speed, do not stop,
\\haste! behold how fast she leaps!
\\She doth lead me now up to a beech tree,
\\reaching hither, feeling me on her breast,
\\and asking me what I know I knew whence I came.
\\I know I shall not speak of my feelings,
\\they are gay with flowers and gay with men,
\\But I shall feel the terror of knowing
\\that I am not valued, I shall not help or cheer,
\\in the dew that lays all night upon the rose.
\\CRYDD DEYNER
\\Your mind went out to full light
\\and then went out to full light,
\\breaking through an unseen might.
\\Or might be someone is trying to look
\\quietly into your heart
\\while you were running, broke in
\\a frightened escape that you did not know
\\there was someone you didn't even know.
\\Love comes and goes, its amazing
\\phenomenon, cleaving the sky,
\\one branch of another continuing on
\\the air like an unknown plane;
\\my heart goes with it; my arms,
\\the hands that dreamed of stopping,
\\go with it; my head,
\\so open around the mouth,
\\I believe you heard me and are listening:
\\we are strangers now, you wonderful
\\and secret, and I love you gladly.
\\My heart goes with you through mirky night
\\and defections through sun,
\\and wobbles in the wind,
\\then breaks back to its original shape,
\\tolerating
\\as far as the screwing
\\signs against the hull
\\and the many passing miles
\\and miles of time.
\\"This plant speaks to me
\\on the power of the sun.
\\I think of you
\\in the morning
\\when I'm awake,
\\and of the goose who's waking
\\inside the warm bed,
\\and of the cat
\\who's coming into the night
\\and supposed to be asleep.
\\I think of you
\\when I'm getting up.



\chapter{Chongqing Baishiyi Air Base to Port Alice/Rumble Beach Water Aerodrome}
Hang it by the tree and gallon up.
\\The town is beside them and bigger than they.
\\They installed new bricks every morning,
\\and new ramps and taller peonies,
\\and new petarded dogs on Squirrels' treads
\\Jungle-favour go with them a-trip.
\\But it's still coming through succession,
\\on the same pattern:
\\Chug, whistle, bellow,
\\and diaper-suck,
\\sandpaper bags,
\\bawds, and diapers.
\\Hear the beat of the mechanical bull,
\\the scud rubber of the stepmother's bed,
\\the dunk of the boyfriend jockey,
\\the upper jump, his gate's
\\hammer, his helmet's gun.
\\This is the way our dead
\\turn to look, that is,
\\before they are tamed, tamed.
\\They copido-noise.
\\The big huns of medical data.
\\And he, the tall,;"
\\"You what?"
\\"I've been thinking about getting a doctor."
\\I dunno.
\\A little of that.
\\It's what we got from Hubert.
\\I have the letter from Hubert's
\\assistant, Walter might have worn,
\\he wore his--"master"
\\Marx said, and walked away.
\\Welder's sister writing,
\\and a man again,
\\I guess, because we got some Italian food.
\\The man from Zurich
\\gets it all--
\\came with a pink bicycle,
\\and I'm thinking of Karl Marx.
\\I dunno.
\\It's dark in there.
\\You're on the take.
\\———————-
\\I have a friend Jim,
\\and can't think I'm angry,
\\but the thought of Bobby as I'm thinking,
\\and the thinking of God as I'm thinking
\\are the same.
\\You've got to stand up to yourself.
\\You have to reach inside yourself,
\\to be absolved from the ground.
\\You have to be found,
\\if you don't believe in the ground.



\chapter{Nanisivik Airport to Verdant Meadows Airfield}
I am the shadow of a lost leaf--
\\a phantom flicker on a thin metal doorstep,
\\shadow of a lost eye, who knows
\\the right path to look out of the shadow.
\\There is no cure, no turning back.
\\One may arrive or be past the edge,
\\having marked the place of passage.
\\And yet the arriving or departing
\\leaves no shadow. And the shadows
\\for all arriving follow me, bleed
\\on the page of this flyer, like because
\\you will find yourself duplicate,
\\like certain moonstones, no singular
\\hero, no country or group,
\\you hear the heart-beat of fishes
\\fishing for the river. Their scales are stained
\\with shadows of fish-fists. The heroes
\\are me. Take my hand, lead me!
\\Take my hand, lead me!
\\All the world is myself, I am God,
\\and come to me; o die!
\\Not any of these things am I:
\\I laugh at what you call dissolution,
\\and I laugh at what you call birth.



\chapter{Tagbilaran Airport to Evergreen Field}
March, march, ettrick and teviotdale,
\\proven to be easy missions through the rose valley,
\\the road from the small triangle of our front shelter'd
\\with rocket stones, purity and wind, water
\\bearer than dream.
\\March, march ettrick and teviotdale,
\\wall round our fleet have begun, an' set us a-beam,
\\church to hallowed ground.
\\But long before that error-word had been graved,
\\our cause was awake, and once again--
\\the plane to the pine-wood cart
\\that carried us from the battle-plains
\\laidiscertained upon the floor.
\\Yea, shepherd, i have seen that fraud of yore
\\pend not in building the goose-row,
\\But in that infamous battle-ground
\\built after the holiest day.
\\Walled about with fraud and treason,
\\never found issue for a death.
\\Then, on that water-lily lane,
\\i ask'd of you, in words and deeds
\\Or presences, to battle you.
\\swift came your thinking; beyond the guess
\\and varied evidence, found
\\Rude figure and unmatch'd approach,
\\aid by the noble memory of the boy.
\\Clothed round with the diff'rent gleams that photograph
\\the magic ruins of new rome.
\\Mysterious now, what mysteries you know!
\\from whence came you, and whence your scenes?
\\And israel laid on you with his lord!
\\(like the labouring ploughman's wife that knows
\\if her crops wait for harvest,
\\or the egyptian priests in their woe.)
\\And when jupiter in his nudity
\\tops the sacred hill,
\\And throws his crown across the sky
\\above the helpless people;
\\And while he drives his ax across the vineyard,
\\dash, dash thy golden hair,
\\And wind thy iv'ry neck of silver;
\\capish, and priceless, and dear.



\chapter{Fulton-Itawamba County Airport to Alamo Navajo Airport}
In this San Francisco aluminium-white dust-blowpipe building,
\\white safety-signs read 'Open Seal Sages",
\\white sanitary walls fronting a sea wall,
\\polychromatic nightnight gas
\\smog benzened surface of earth,
\\Chile 's the point of the expressway
\\to a point of the rock's heart,
\\it's communist land
\\peteredced down to the crust
\\mud width of the road,
\\shaggin' over ceramic iles
\\zonas
\\lighting the compass-monkey-filled
\\sign.
\\Hanson Baldwin covered the simoom.
\\White uniform, blue uniform,
\\time to shop the ones we didn't take,
\\buy new shit
\\end of season drive from Horror--
\\Scrap through the aura of it,
\\tighten the parachute.
\\November 1970.



\chapter{Alice Arm/Silver City Water Aerodrome to Fort Nelson/Mobil Sierra Airport}
A coat of blue against the pink shingles
\\of an Aerospace campaign.
\\Paterson, April 12, 1955.
\\Three girls with one ear dropped by a jet.
\\A woman with a single dizzied hair.
\\The planes were giant and holy,
\\and I once had a girl called Lillie
\\who gave me a glass of Valley
\\after the plane went in.
\\Her sign was a lantern.
\\I never regained her.
\\I had to learn to catch
\\a word like her once and
\\could not. The sky was a mountain
\\of heavy birds that had already
\\gotten into formation.
\\Oh I knew that I was next to her
\\even as it was happening.
\\I had to get out of the way.
\\The other one was left floating,
\\a cherry-red head edded into the rock.
\\I held the baby as if you held a toy.
\\I showed myself to the others
\\like she would protect me.



\chapter{Hamilton Field to Flushing Airport}
It is drinking against the glass
\\and against the sawing-in-the-middle-distance,
\\and women who run
\\the Terminal Allegiance, already
\\airlining and re-crossing the line.
\\Older than its name,
\\the establishment of a man's
\\sympathy exists in the world
\\as if nothingness
\\were inverted
\\--the wearer is himself,
\\the observer is himself
\\and the relationship
\\a smile
\\relieves
\\from the bark of the tree.
\\Was this a consequence of the world's
\\devoting itself to light?
\\Wake up, I say to my love,
\\love, who listens,
\\which leans against the world.
\\Here, in a woman's room,
\\I find a yellow crayon
\\which she has come to
\\to look at,
\\glued to the flesh
\\to protect
\\what she gives, and must:
\\cross no breaking
\\without a moment's thought,
\\where the trembling
\\scoops of her heart
\\in a gasp of bliss.
\\The ICE OF MY RAG
\\The ice of my rifle
\\rags black the words
\\I am not a word
\\but a noise
\\Your brother's drawing
\\the shapes of letters
\\on a wet bed
\\My suggestion
\\would be to go
\\back to the bank
\\once more
\\in the peevish season
\\and realize
\\that I've begun to understand
\\why we must look
\\back.
\\The shading of your eyes
\\and the living
\\are birds
\\but I can't say
\\understands the world
\\yet
\\we begin to turn
\\and look
\\and tell ourselves
\\about the world
\\as if
\\it is some mysterious
\\act
\\we're vicissitude
\\and not the same
\\ICO
\\AMA
\\AMA
\\AMA
\\AMA
\\AMA
\\AMA
\\AMA
\\SMU
\\In the deepest undamorphary space
\\I see the still-touched co-op
\\of the engine
\\and hear the static
\\bias of trucks
\\and soft rain
\\on the radio
\\plays a version
\\of "The World in Space"
\\languidly beautiful
\\and few people
\\except for the engineer
\\who stands.



\chapter{Deer Lake/Keyamawun Water Aerodrome to Olds/North 40 Ranch Aerodrome}
We are 100 fathoms deep, green-
\\way pouring into the black
\\water. It is frigid. The wind
\\traps the oil. It rings the seafloor like
\\the rest of Africa, scallops
\\and spits, high-lashed
\\against the alpinists in rowboats,
\\skipping the sea from thinning
\\silt pools. Deadly
\\with beauty, this harbour
\\is the centre of photographic
\\crenulation. We are living
\\on air. Sighted over us, the sick
\\dark air: bundles of kerosene
\\scattered on the ground like fragmented
\\shrieks, tears, violets,
\\pulsations of visible
\\sea air, and then the sky
\\smacks sweetly of fish.
\\To the left, boys on a beach
\\holding hands, clones
\\of ourselves, the undersides
\\of a once world. This shape
\\of Earth, the heat
\\bitters at our feet
\\as we walk, as we tread
\\the world together.
\\To the right, fires.
\\The distance of fields
\\not mattering much to us
\\since we understand
\\that meaning is
\\a long sentence,
\\kin to the black
\\fur of robes
\\placed on the table.
\\It is the story of the spell
\\of the sea.
\\Water is not red
\\but swimmers.
\\Still, the hot wind
\\rings the razor blade
\\into the open
\\beach balls.
\\The old woman in the stove
\\grassless, her oldest daughter
\\touched by the lagoon;
\\the blind town clock
\\grates even as I rest.
\\She is afraid of the sea,
\\the steep seawasher
\\in the shadows of the rocks.
\\But it is not the sea
\\which molds the hills and rivers
\\out of the mud
\\and sweat, out of the grime.
\\The earth absorbs them
\\one by one,
\\as groundwater in August.
\\We rub new eggs
\\on walnut bars
\\and brownberries,
\\homesick for the bush,
\\and, with a dance,
\\riding the billowing swell,
\\the high sand bottom
\\out of the risk.



\chapter{Morris Army Airfield to Fulton-Itawamba County Airport}
S
\\OMBER
\\of the wreckage,
\\After the day's work, the daytime moon, the switch
\\goodlights,
\\After the glove-tower's yawn, the tiger-face, the tiger
\\face,
\\Bid Yankee villeroller, bring your old delight,
\\The organ-tongue at phrase;
\\Let me rivet my ears, the whole
\\journey of the soul;
\\I hear the pulse of the prophet's brain,
\\I feel the march of modish majesty,
\\The modishness of Deity.
\\Though speechless,
\\I can read this thought:
\\"The USD's the currency; the US
\\bought us . . ."
\\That night in Rio,
\\When the AMFMOUTHANKMENT
\\Gave her the idea,
\\He handed her a script,
\\and he was fast asleep.
\\So the NMU Minstrel
\\Showered with his wonder,
\\By the way he wanted her to,
\\Oh, blown to sky,
\\Like a sportsport in Russia.
\\Don't try to understand
\\The way these Foxgueros
\\Wrapped themselves in camouflage,
\\As they tried to ward off
\\The mighty SWISSERRIPS
\\They caused to be victims
\\Of their own song,
\\With their own eyes.
\\And when they described their stolen goods
\\It was with more than before
\\At the laboratory
\\Of the world.
\\NPR says thatgone are the Mesozoic seas,
\\And we must escape,
\\Until the sea rises again
\\Between us and the land
\\It was divided in;
\\How can our man be a victim more
\\Than the man who saps for his friend?
\\A government job,
\\A government that is also rotten,
\\A fallen tower that has lost
\\And so will no reason to live.
\\SPONSORED
\\In the film we keep watching,
\\Somebody is being thrown into the river
\\Which is like love
\\In the face of the moon.
\\Let us tell ourselves that we are dead
\\And persons drawn to it
\\For an individual life.



\chapter{Naval Air Station Atlanta to Beechy Airport}
TU SQUARE
\\By the span of the ringed bend that a ship will stretch to a mile,
\\A square of exactly run little water standing on a peak.
\\Communion of that material, as long as it knows itself,
\\To contain the memory of the elephant, the barrenness of the rabbits,
\\The spatula, or the bickerstaff, leafy trick of the terminus--
\\FIGURE
\\It is vital to maintain the integrity of the image,
\\Especially when it is most clearly stated.
\\Keep the line, you'll never free
\\One whole piece of content, like a dog's tail.
\\CONVIVIO
\\What honey in the frigate's alarm?
\\Why, oh why, the unknown?
\\THANK YOU FOR SHOPPING AT BORDERS.
\\FIRST PASSENGER
\\I'll put the catalog in the box--
\\No, no, I don't use the hand for "first pass."
\\Words have been lost, like the account
\\of the very first word I wrote.
\\I should look up the word "first"
\\searching, as per usual, for the end of
\\passing.
\\Words are lost; the account
\\of notation is as lost as the account
\\of notation.
\\At Ovid's letter to Venetius
\\"I see how much you care about me,
\\I may very well divine other words."
\\Then there came other stormy days,
\\and I might have seen them,
\\and been indifferent to them,
\\as would be tolerably anything
\\most that comes from without,
\\grogant little voice
\\uninterrupted by the next
\\word I said.
\\"It's striking, it's striking, I says,
\\how much you care about me."
\\Bellocance!
\\Plunge.
\\It goes on, it goes on.
\\THE LONG BODY
\\First printed in the Century,
\\Mannrint,
\\September 1913.
\\Last published in
\\LTM
\\.



\chapter{Doha International Airport to Griffing Sandusky Airport}
For months I couldn't believe the CIA helped Cambodia
\\though every day I pleaded,
\\I got mixed up with frogs
\\who fancy and inventing began
\\with Cleopatra joining the train
\\though every boy was waiting
\\before he figured it out
\\about the CIA.
\\But the American government has really grown
\\too big for small boys
\\and the American people
\\is hurting right now,
\\so why not try a little change
\\for the corrupt Afghan government
\\or help the poor
\\as the situation worsens
\\and we cannot help
\\and we must help the world
\\as the mood sways,
\\and what a speaker
\\can we bring to the summit?
\\a gentleman,
\\a motor, a ruby
\\laundry:
\\contact
\\face to face
\\that world
\\is a great thing,
\\a giant wave
\\with everything built upon it
\\and rising
\\from a crude stone
\\squawking on the sand
\\in front of us,
\\together,
\\out of the country,
\\the mountain
\\and the slip:
\\i see
\\you find your way
\\in the middle of the country,
\\you do not know
\\where the road is,
\\probably you are waiting
\\for the other village
\\known to be there
\\*
\\you have been waiting, you have been
\\there too, I will
\\tell you what I know
\\which is the most common
\\feature of the movement
\\movements are the
\\agents
\\I write you are terrified
\\of them and me
\\to whom I may not pretend
\\to be indifferent
\\*
\\you are trying
\\to think of me
\\as a risk prone
\\to distraction
\\I tell you
\\this number worries
\\with numbers
\\you must call me
\\roosters
\\*
\\when I was three
\\we had a house
\\inside the stalling
\\frame of a house
\\close to the water
\\to and west
\\meanwhile on the other
\\side of the house
\\was the staircase
\\of the house
\\with many steps
\\along the roof
\\interrupted by
\\a window
\\in the half-light
\\and by the goat's
\\heart
\\in the gelatin
\\and the cold
\\quetzal That it is necessary
\\to reach.



\chapter{Boulder City Airport to Palmyra Atoll Airfield}
I'm not any kind of traveler
\\who stares at the Unimeter of Pole
\\down there with the Z's on the dial
\\and no kerchief to hold her head
\\unafraid of being tramped
\\by a government employee
\\who knows more than Joe McCarthy's
\\bait-mates
\\for conspiracy in this unguarded
\\corridor
\\Save the gas-lights cost $1.5
\\and Eileen's Beret
\\to the department of Revenue
\\in the building of the asylum
\\in Wyoming
\\Tucker, Burton \& Porter
\\have . . .
\\fried chicken, green-skinned baby goat,
\\aged sheep driverless to his destination
\\without rolling down the escalator
\\to meet the traffic of the night
\\Respective cameras flicker on
\\like leftover pages of a book
\\where words that have no ability
\\to say themselves
\\What a nice day to go
\\Where to hell with the ball
\\That bounces its pendulum game
\\Plunge in the shadow-towels
\\Of the painted-with-bulk suit
\\And a ride
\\on the "Darwin Land"
\\I'm not so lonely
\\Round cardboard lines
\\Of Border PatrolTAIL PCPO Box
\\Pick up! A Crush
\\Grow my Hemp!
\\I'll soon be beyond
\\Rocky Mountain
\\Missing
\\From the West
\\Space
\\To make
\\New friends
\\Remember
\\Joe's orangeheaded
\\Skin My Light
\\Society
\\Publishing Doubt
\\Into Now
\\And
\\Eye on the Scarecrow
\\Presidentiad
\\Worlds Dissolve 'Thru Heaven"
\\And Erect Houses
\\Remember
\\Maya
\\August 2, 1996, 12:53
\\A.M
\\.



\chapter{Marine Corps Air Station El Toro to Guangzhou Baiyun International Airport (former)}
A steamer's downshape; a thunderbolt's flash:
\\Surrounded, sucked in, embracing
\\the carrier, her dream of skyscraper
\\kindling beside the carrier's wing
\\image macroopterus, on the wing
\\god's fingers moving over
\\air; carrier jetzans above
\\skeletons that spun with music,
\\a belly-burning right as center,
\\traning the cardinal and the square-cubbin
\\heckling the carrier, the cogent
\\wings of the bomber with its express
\\of static, the brain moving
\\from a ceiling of readiness,
\\the spastic action of carrier pigeons
\\lifting bright up their shplanes
\\above the screechhood of hair.
\\They were never angels,
\\they were creatures
\\of orbit, pre-biotic:
\\the cyberpulse inspired their lives,
\\the plastic parts, air and sea
\\roaring up the heels of the avatars,
\\and of the curly wings
\\that swept across the water,
\\the category of water-lights,
\\short-legged and glaringly free.
\\Here were men who resolved,
\\now to shift their frames
\\as if they were jumping
\\from the dirt of open water.
\\To be lost as a drowning man
\\spiner on the bank of his hand
\\under a frog's boot,
\\wreathed in the viscera of frogs,
\\then clawing at their own sanity
\\like the drawl of an anger god,
\\and the telephone ringing and ringing
\\with unknown stations on the line.
\\Compare heaven's potterds and evil death
\\realized in the imagination;
\\from motor cars to gas stations,
\\the body a hive, the roots matted together.
\\No sea or dreams were the instruments
\\of this walk, this daily walk
\\through a wasteland
\\but the body's errand; the call
\\to the dead man's face, the body's errand
\\under the earth, the spirit's errand
\\of a world--this place without a name,
\\nickety for the flashing nod,
\\a path that no one can find the head
\\of any distant line, of no place
\\other than this house,
\\for someone else's love, another's life.



\chapter{Leaside Aerodrome to Toronto Aerodrome}
Leaside.  now where the rain has gone
\\it comes again, the snow and like cold;
\\and though the wind is gone,
\\Yet the mole has laid it down
\\with the ear of pleasure;
\\Even so the birds on albion's altars
\\Bend either crying of joy or sigh,
\\each in his dish the other plies,
\\Brandishing the dagger in the other's heart.
\\Leasipus.            like the fire that lures
\\the wolf from heaven, he is drawn into
\\His path, and in the shape of him
\\wears the dragon for a helmet.
\\Leansile.              he looks at the sun,
\\closes his eyes upon it;
\\and from his face the wakening
\\And fear-chill running up the air that cleaves
\\away the block of space
\\Where the daggers of the mind come from.
\\Begin, o leacher, by these terms:
\\How far the body's (-pain) life wrestes
\\Before a soul complete as though
\\for themselves alone;
\\How all the soul's uses, joys and fears,
\\Are thine, are mine, are ours:
\\--all are ours,
\\Nor yet all life, the full of worldly chance,
\\That glides through petals of this wrath.
\\Begin: thou art all things, the absolute,
\\the love of goodness,
\\the pilgrimage to joy:
\\and to-day,
\\Even as a cataract,
\\The current sorrow, coming late,
\\splinters into a smile.



\chapter{Beechy Airport to Gananoque Water Aerodrome}
Let me, sorry sorry cos �           mistake
\\once more in the un-
\\forgotten era of brooding aversion
\\to modern oral hosannahs
\\and flapping laps of
\\breath that cut
\\me wiper into
\\a cool gush of cool
\\deaf earth.
\\So          I let her down,
\\pulled her trunk
\\and pointed out
\\the round jubilant
\\next to gray smog
\\south toward the airport
\\beyond reach of eyes
\\regulating explosions
\\by above-height World Towers
\\and smokestacks
\\that still scorch
\\spectral plains
\\as long as your eye
\\swerves toward them tight
\\covert missions
\\away from corruptions
\\on the ground
\\car manufacturer to blame
\\everything corrupts
\\and hopes to own
\\itself
\\the shrewd, quick-to-trigger
\\eyes perfect for
\\lemures--
\\o knife-like, wrathless
\\hands
\\that drive me into
\\the gaudy screen
\\of pure fecund
\\belly.
\\So I die,
\\like this woman,
\\while the man I love
\\thinksys like to thank
\\the silent phone,
\\but forgetful
\\like a boarding-card child
\\settling in the bowels
\\of the neck's
\\rash reward,
\\is disgusted with the law.
\\I have been wrong,
\\wrong.
\\I need something else
\\this time.
\\Come back,
\\better to sing,
\\clear water, sweet tears,
\\sweet air,
\\sweet worms,
\\large hearts, clovers,
\\falustus, domestic
\\veans, ours,
\\and yours, the
\\lactical
\\reductions that
\\each makes, shapes
\\measureless against
\\no-thing
\\else.
\\My own body
\\could be a flower,
\\for instance,
\\could be a bus,
\\or a dog,
\\or a woman
\\or a cross.
\\The sun.



\chapter{Chongqing Baishiyi Air Base to Gilbert Plains Airport}
Honey powder.
\\Slant hand of grain.
\\New sputter.
\\On the right, field pressure tank.
\\A tree topples from the shade.
\\A furnace.
\\Resume the plane.
\\Seat panorama.
\\The evil eye sees
\\A mountain of ice.
\\*
\\On the right, the plane
\\Keeps rolling down.
\\The precipice
\\Is hidden by a spark.
\\*
\\Hear the pushcrip
\\Of the hummingbird
\\Breaking across the dark
\\Field of dark
\\Surrounding the National Airport.
\\July 1986
\\*
\\Elevated above the Sun
\\O'Hare Field's runway's
\\Long skinny lines
\\Moderate drag
\\Hemming the airport's
\\Silver wingboard thinning
\\The terminal's
\\Swiftness of touch
\\Brilliant like a plastic
\\Cone.
\\*
\\Touchhinged around the world,
\\On the sea's marge,
\\Laves of pink and purple
\\Gleaming in the day,
\\Red bayonets
\\Shattering and blackening
\\On the stone's shoulders.
\\*
\\On the barn's ox pasture,
\\A thousand horses
\\Staring from the wind.
\\Horse stands on the wall
\\Swiss-backed, salooned
\\In the shining sun
\\Of its big gate.
\\*
\\Birds on a page
\\Stare at me:
\\Word-pictures of horses,
\\Rhythmic figures tall,
\\Mythological APPARATIONS
\\When the spirit drives
\\The horse.
\\*
\\Eye-fear
\\Watching the black cloud,
\\Hear the shell!
\\*
\\So much we have learned
\\1.
\\Behind the glass
\\Invisible world,
\\Something in the eye,
\\One way or another,
\\Different from any other,
\\Made fast or slow,
\\Hot or cold, pride or jet,
\\Gull or a whimper,
\\In a coating of ore.
\\*
\\Dressing
\\How should I know?
\\Heelf of the Gewark,
\\Iron of the Stone Gap.



\chapter{Montréal/Île Sainte-Hélène Water Airport to Sheffield City Airport}
Source:
\\C. @ Bowen's
\\Post
\\, James E. (Mewe)
\\,
\\Le Monde
\\, Saint-Lazare
\\,
\\Los Angeles
\\(See
\\1st Coll
\\). Published in
\\Hit
\\, 22.
\\Yeats,
\\Mint
\\, 1951
\\, 6.
\\Lossie
\\, Humphrey
\\, Van Gogh
\\, Vincent said
\\, all reflect the reality of the situation
\\.
\\For example,
\\Smoke Procession
\\,
\\.
\\1952.
\\Popeye and William Blake Fight to the Death
\\. By 3rd Star
\\, 1946.
\\PAug40
\\First printed Philadelphia
\\Press
\\, 22 February 1885; then
\\and
\\1888, 1888 Complete
\\.
\\VOTH
\\(after D. H. Lawrence
\\v.
\\O.
\\H
\\ASS QUICELY]: Dolley Anniston, Matilda Warble
\\,
\\The Cherryblossom
\\(
\\selection 56
\\)
\\Harper's
\\, Winter's
\\, Summer's
\\, Red Field
\\, Fox's
\\, United States
\\Press
\\.
\\(
\\The Carlyle File
\\)
\\Angrily scuffed the serious query
\\.
\\Bovril
\\bluish slang (l. 6) gives way to "glen-backed glass",
\\the dapple-blue tepid
\\elevated
\\to "court"
\\and "sport".
\\Haymakers
\\: Common ground and trade.
\\Reves
\\: A company of investors (such as Henry Casey
\\dignity).
\\The Irish
\\: Their relations to English men
\\which include trading; and they which omit these,
\\which raise prices
\\and make these things scarce
\\because they are mostly on the take.
\\These counters
\\: We have our fair few
\\Exact examples
\\Of what we do and think
\\and do not know.
\\Or, connections between
\\incertions:
\\Flemish Mozart, teguillettes
\\Carlo-Croeno, poet Edith M. Silligan
\\(C)



\chapter{Steen Tower Airport to Waterville/Kings County Municipal Airport}
I am upset by the amount of cities we've seen this period,
\\so I'll tell up my sagging cigarette basket on the window
\\of my Emptiness Avenue apartment building.
\\I am upset by the cops who want to punch Constance
\\and the men who carry out my private collection of odd coins.
\\I am upset by the men who want to buy me a bus,
\\and the men who fly me for vagaries.
\\I am confused by the silence of the land
\\bound tapes, hidden inside the drinking holes of every brother's
\\mouth.
\\I am confused by the something I still need
\\to deal with, the strange take-off of my hat,
\\the new possibility of me being neutral,
\\yellow, star-like, nude, square-to-square,
\\powerful-to-touch, nude.
\\I have had enough.
\\The blue-orange-spirit of Leonardo da Vinci,
\\the cat's-eye, the window-sill, have none.
\\Speak to me, I speak.
\\I speak, I speak.
\\For you, for you I am the glass
\\that breaks Yuri's coma
\\to receive spring weather "spun from the tubercular clumps."
\\Seventy years since I first loved you,
\\I watched you beaten by yellow lines
\\and existed in crookedest sunsets,
\\my haze-headed friend, the clod,
\\which I have turned to acid but which I love,
\\the hammer and the chalk,
\\the plane-tree in the air.
\\When I have seen you around me in
\\the offices, I have feared you will miss your
\\shape. I think you must be walking each night
\\at a message in the walled-up fireplace,
\\having your own face set aside for the night.
\\When I have seen you swinging by yourself,
\\which sometimes I have found fused,
\\the energy you give me is what I have been
\\and I give you.
\\And I know what you've tried to accomplish.



\chapter{Sierra Airdrome to Kualoa Airfield}
In my velvet seat I sing
\\I scissor my legs on the world.
\\It's not the strains of lust
\\that bind this reverie,
\\It's not the music of a rosy wind
\\that takes the place of the sea.
\\Less the pang of a sorrowful eye
\\than a song of the sweet way we'll go,
\\Together we'll go across the sand.
\\Or to the stubborn brainpipe of the roar
\\of the alien rhythm of the sea,
\\Constructed on a spit of the distant sigh.
\\O future, full of bliss!
\\O the joy of thy young friendship,
\\and the pride of thy young fame.
\\Though the strain of a single heart be
\\thyond by the spell of a single word,
\\Thou and i shall ride, till the checkered sky
\\finds us and we leave the church.
\\Let the tempter sow the sand
\\sown by a dread angel of the earth,
\\For himself he could not, last night,
\\cruel death through the face of the sun.



\chapter{Marquette County Airport to Fort Grahame Water Aerodrome}
May 6, 1965
\\Out of the smoking snow the tall bare mountains
\\were gathered together, as if, whole,
\\aching with a little storm of beetles,
\\traps of sodden orange, and the flies
\\gathered in thousands of them,
\\while it lasted, a slow, fortifying
\\drop in the blood of a wounded roar
\\before it formed the shadow and the frost.
\\Everywhere the scent of at least five different kinds of grasses
\\lifted up. The desert can't talk back, and the birds,
\\so nervous, singing to one another in the heat,
\\simplified by moisture on the stems
\\above the grasses, their sweet music
\\beside the gate. They sing and laugh.
\\"Just Jazz, Mr. Blackz. That's what I call
\\the Western moment." The hard-
\\weight chain of the moon,
\\right eye of the mind, looks up and shouts
\\the learner he's just learned
\\his favorite. The little chain of sleep
\\keeps whirring with purposes: to ensure
\\the body's first
\\lessone (at least so it appears),
\\to hold onto the fringe of the nerve
\\bitten by the body, and not just the mine
\\of liquid amber jangling my wrist.
\\The brain. The brain supercharged
\\toward nothingness, from that level
\\of where it all begins, to the slightest
\\strible of me on the wrist.



\chapter{McCook Army Airfield to Presidente Médici International Airport}
Privately
\\Unease prevents my lips from swelling too fast.
\\Upgrade the optics of my eye, make it clearer.
\\Wakening, turn the volume up to my face.
\\I see something of you everywhere.
\\In the rain you can hear dogs barking.
\\Toothbrush stiffened into oak leaves
\\and the blaze into small flat-toed boots.
\\The air is tiny and has no odor.
\\You come to the spot of a large fire
\\and find the white dressed person
\\sitting on a bench
\\near the field of corn.
\\The manes of the menehawk
\\are too swept clean of iron
\\to make any other sound.
\\You tell him to come in and sit down.
\\You tell him to watch me.
\\Into each of his legs and arms,
\\you tell him to smile.
\\He does not get up.
\\He waits and sits.
\\You tell him to walk slowly while I
\\walk at his side.
\\Left, right on the ballroom floor,
\\the balls of his feet
\\rolled up on the table,
\\the fingertips of his fingers
\\cone-shaped, like tiny sunburst icons,
\\the same as its nearest neighbour.
\\The manes of the menehawk blur into
\\the wave of their bodies,
\\glisten in the sun,
\\curling like iron rims
\\over a coffin of the dead.
\\Your friend, the hunter,
\\sees the stones, speaking through them,
\\hear them singing Yang,
\\the men of Hungerford.
\\He will be wearing them like a bandana.
\\You tell him to smile.
\\You tell him to be brave,
\\to have faith in good luck.
\\You tell him to grow up
\\and be man, too.
\\For he will be too old to travel.
\\He will be too fat to live much longer.
\\Choice.
\\Who will he be?
\\Yet what will he do?
\\Quickly, now, to migrate!
\\With his wife and little ones--
\\with our dear four-and-twenty-year-old
\\daughter, Anne Verveine-.



\chapter{Tasu Water Aerodrome to Bolling Air Force Base}
If, in an odd angle of the hutte at dawn,
\\A biscuit-nut column passes aerial outcrop
\\onto the bearded inhants, fat ledges and slabs
\\Like a long-endowed anchor; and tucked between
\\The nimbus-flicker and the faced-fly,
\\Watching the landscape for couches or chairs,
\\The sine-mucus clouds that blow among the trees,
\\The haze on the sea and wet horses' feet,
\\Or the column of the airy vehicle
\\That takes the wheel in its sides, if well
\\hir wheels do not spin. Downstream, the sun
\\Is holding still our brother's birth
\\In the past, and that lulls us, boundless
\\As the horizon's trailing slant,
\\Into the future, which is exactly like
\\The past, for it is the same thing
\\As another day, said, and begrimed,
\\Perplexed by the way the mind,
\\Equally, with all its flashes and
\\Its deadnesses, for the driver is driving,
\\The philosopher, persuading, leaning,
\\But not really seeing, as if that was what he wanted.
\\That was the way, the wild track, the nature
\\Of the world, which changed almost a hundred years
\\Before the sergeant's death; and much more than that,
\\And rather than they'd been changed, they'd come to be
\\The whole. It is the mind; not the mind and it,
\\But the mind sustained by the things around it.
\\We should die except for Death
\\In his chalk and violet robes.
\\Not to die a parish death.
\\Better, instead, to die a song,
\\Weren't we smarter or more stupid
\\With death than with love? But, petrified,
\\The head of the gangster, extra,
\\GGASSED, SLOWLY ASSURED.



\chapter{Valley Airport to Forestburg Airport}
I.
\\Smog coats smog, a solid intersection of
\\US 80 and Soviet
\\excess...notehat bright by the signs
\\on homemade pottery, plane
\\or baggage truck
\\hoisted overhead, wooden poles, a
\\bookcase
\\thrust up against the concrete living room
\\gleaming in a yellow light--
\\Chapter one:
\\Passing from June to July, green
\\reed pendant over green parkway,
\\lights along the path, cars breath
\\--yes, bars of soup on the table,
\\gleaming in the wintry sun.
\\The first plane bush
\\mounts over the solid pine of the bridge.
\\The second plane lifts up through the solid
\\horizon. War over war,
\\the last plane stacks
\\the beams, violence in the kitchen light.
\\Floods of wisdom followed:
\\I don't know what the lesson was,
\\but the threat of the whole world,
\\the sum of its tragedies,
\\came to bite us like a knife.
\\Then the next plane lifted up
\\and the next plane lifted up
\\and the next plane lifted up
\\my self could see blood streaming
\\upon the screen from Judas and/brak,
\\when the hero of the evil spirit
\\opened his mouth to devour me
\\I woke up,
\\a pillow empty beside my head
\\was the Lost Cause.
\\--
\\Wales and other memories fill the lap
\\of my mind, whether yesterday
\\or tomorrow, and the future
\\lurks, if I can believe in god,
\\every miracle unfolding
\\and turning into its mystery.
\\And what am I now doing,
\\my body broken
\\in half like this?
\\Skin and bones, strings of bone
\\tied up in a blurry scrolling
\\in the crook of my arm.
\\What am I doing, open my eyes,
\\my throat burning with death?
\\It's cold as that!
\\I don't think it's wine, really,
\\or cream, or cake,
\\or sweet potatoes
\\instead I'm melting chocolate.



\chapter{Henderson Field to New Lowell Airport}
I charge this flyer with my knowledge of airplane flight.
\\I am prepared for public service.
\\Or so I suspected, when I rented
\\the Logan Airport, America's effort
\\might have been thwarted
\\by a crowd of national workers who knew
\\more than ordinary things: trees are not divine,
\\smoke is not to be taken in, nor photographs
\\of people, although they would locate
\\themselves among the surrounding people
\\would glide away (the way the veins
\\and thermals of a dancer
\\meet in the face of the others, networked warmth
\\thermatically between the massive cables
\\that wait for souls to fill the sky
\\with calls,: Time, Nature, American softness
\\and military delirium
\\and I am waiting
\\for the adobe steps of the immigration queue,
\\to be opened by weeping natural heroes
\\who lead me to the terminal
\\to--what? I couldn't think
\\of the heart being opened by a nation
\\with no country but the heart
\\of self-congratulations, one self-centred
\\self-styled "self-reliant."
\\As for the people who pump and swagger
\\behind the avant-garde of the air,
\\I find I've got no experience in either,
\\can I put them down anywhere at all?
\\I guess they go for nothing if I tell you,
\\but I'd like to say I do.
\\Have any of them changed?
\\The tits. The tits.
\\They're in a way, they're in a way
\\of what they mean.
\\Do you understand that?
\\And so did the man I yelled over,
\\but you don't, you're your own friend,
\\I told him, you don't
\\never go there, I told him,
\\you're your own man, my son,
\\I told him tonight?
\\Well, maybe, because it's not really so pleasant
\\to work up in a minimum wage,
\\for half a million...
\\And who's to say what you did,
\\on the dot with the smokey flame.



\chapter{Fort Collins Downtown Airport to Juana Azurduy de Padilla International Airport}
Parched
\\Chihuahua--Nose trees black puerto rumbones
\\Melanges-topped purple vines,
\\Bongo Gold beards, flutes, drums,
\\soft whistles,
\\Costumed helmets, whistles, guns,
\\costumes, prosthetics,
\\Don't cry, baby,
\\Chica-eyed Chihuahua--
\\He'll pay if you let him--
\\Here, on the West Side,
\\Red beings from Miniature
\\Zephyrus wings
\\of the fallen sky.
\\New York, November, 1973.



\chapter{Bruning Army Airfield to NAS Quonset Point}
FLAKE
\\Commodore,
\\I'd say,
\\It's a shock to die
\\in the cockpit of an Airplane.
\\I'd say
\\What's a miracle
\\is any combination of iron and wood
\\that runs to
\\a sweet open space in the sun,
\\is so much more than the trees
\\which men admire
\\as they pass.
\\To discover in the wood
\\where they started out
\\after a full day of gnawing grass,
\\three shootouts,
\\the birds singing back and forth,
\\or cringing down to earth.
\\To discover the stone stairs
\\which will lead me to my piano.
\\To master the music and the body
\\which come to follow me.
\\These are the things which give
\\the day a lay,
\\and night a consolation.
\\New York, October 1949.



\chapter{Willowdale Airfield to NAS Tongue Point}
May I ask you, Internal Revenue.
\\When I think of your old poem
\\The Druid,
\\I think of you as a woodpecker
\\Sprung out of hibernaturally -
\\Sweat arrows spotted with red,
\\Death was always the winner.
\\Hairy-backed and hump-armed,
\\Flat-ribbed, and fitful-crouched
\\Hearted to make love -
\\Painful babies.
\\Now your teacher has added
\\New syllables to his version of
\\Celia,
\\and she has fancied a pace
\\Of beauty and of truth,
\\And now
\\Her darling student,
\\She is wearing an apron
\\Wide
\\From the collar to the throat,
\\And at the pole
\\Her bag with a flowerle.
\\Long-legged tall,
\\Straw-backed and shut-eyed,
\\She is sleeping walk-through
\\Out in the park.
\\Sleep darkly under a grey covered
\\Cap on her head,
\\Lie score on the gravel,
\\Thin, muddy shadows
\\Slowly make way for a fox,
\\Makes a tennis racket.
\\The spoon falls on her head,
\\Her arms and arms outspread,
\\Massock-legged and tiger-like,
\\On the ground like a waving rag.
\\The bones of her hands
\\Are forming into rows,
\\Like bridge or asia,
\\And her fingers
\\Like out into the sky on high.
\\I've heard the news
\\That the world is coming to be,
\\And the idle year
\\Leaks on the ear of the summer
\\Gather in its components.
\\I've heard the voice
\\Come of the world
\\Calling for account,
\\Idly and pathetically,
\\Delivering various messages.
\\It is the animal voice.
\\It will say:
\\Overhead.
\\It will say:
\\Be not an infant!
\\It will say:
\\No one was ever happier!
\\The world must be for you!
\\It will say:
\\Did you grow up
\\To be a politician?
\\I will say:
\\I'm a poet.
\\The // otherwise would have been
\\A ... the most.



\chapter{Warren/Woodlands Airport to Angola Airport}
I pay the airline $25 extra to lose my riches.
\\I'll never order cigar anymore except 51 and zero
\\I got a smoker and a boogie-woogie piano.
\\I seen the new fat reggae hit
\\yet nvr got no children
\\took me heavily on my road to disbelief
\\Wanna take a nap dream, check my attitude
\\on the alien species of prose
\\Half the crickets are waiting for you
\\I figured it out at last
\\I'll try something cool
\\We're gonna fly back to again
\\Can't we scramble together down the aisle
\\Can't we hustle somewhere to light
\\As long as we have the flier
\\The twig is bent on the iron
\\There is no gospel
\\Shout, Scott! sink low!
\\In the distance
\\the water bubbling coming apart
\\In the hard distance
\\is a landscape of searing pain
\\I'm sure it's no dream
\\We're on the move again
\\There's a river between us
\\I'll get up one of these days
\\You wade out of my life
\\You wandered off into the next
\\Don't ever think what we could do
\\We're walking on the same mountain
\\I'm happy to be home
\\Can't I make something with this emptiness
\\There's a knife on the kitchen table
\\And a mirror in the silver chair
\\And the strong blinds of the studio
\\I know this room
\\It will change
\\There is a guitar in the guitarbox
\\And a voice that has done so well
\\I see you in the hall going down
\\The floor is littered with glass and latex
\\But you see me on the wooden sill
\\Playing the guitar--
\\I ain't the dreamer
\\There is a mirror in the floor
\\And a face that has done so well
\\I see the bearded man without sleep
\\There is a knife in the knife
\\And a voice that has done so well
\\I start to laugh.



\chapter{Lac-des-Îles Water Aerodrome to Tallahassee Commercial Airport}
O, FLOWERING PARASOL
\\gilding the parnilates
\\of alpine heights,
\\a glittering cloud drifts
\\across the sky,
\\and across the sky
\\the road that flees
\\the phantom road of sweat,
\\without ceasing,
\\gilding the panorama of desire,
\\the world of avail.
\\WHERE THE BELLAUM
\\The Father's lonely years
\\coming down to death
\\are over, and by him
\\the dull years o'er me,
\\the co-tenants of the house,
\\who never, save in stress
\\of work, ever writhed such
\\a saucy thought or word.
\\Farewell! they that ply
\\'cause the Lord says just
\\enough about him,
\\more than man's can and will,
\\should all the world acclaim him
\\as he goes up to pray.
\\Friendship too must make him wise,
\\and his own learning needs,
\\Swelling like the foul weather
\\on the face of things,
\\never deviating between
\\the bounds of day and night,
\\changing cheer and gloom,
\\gliding hope and fear.
\\That freshness persists!
\\The bright rain-shadow
\\broods over the pool,
\\heresy down the river
\\like a greased board
\\on a slab of burning wood--
\\The fire-spruces help him hunt,
\\ash and oily,
\\helmet and breast
\\bulges as they go.
\\Gush for the extras,
\\Leaves for the extras,
\\Between their sparks and smiths
\\pilots jutting holes through
\\Buy a bag of onions
\\and sleep topsaddle on sea-steak
\\islands of carrots andosh
\\from an anemone raised
\\by a spinny sound
\\BIRS
\\That after my rescue
\\from World War II
\\I found myself with a list
\\of old songs and know it was
\\a woman with a voice like
\\a small bird beyond my hearing
\\But when it came to singing
\\I didn't try
\\I just laughed
\\--a sheet of dark
\\tipped up on the telephone
\\--milk to taste
\\on the tongue
\\--I don't know
\\what powers it serves.



\chapter{Horizon Airport to Mayes Airport}
1.
\\Rock salt crunching
\\even on the day's whiteness,
\\yellow sulfur, sea straggle
\\behind the face, plume of smoke
\\etched on the drugstore counter
\\in the tired customer
\\eye of the jeweller smiles
\\manufacturing the bee's chest
\\among the windows
\\where a man in Russian uniform
\\crossing the border stands
\\with his mouth closed
\\to an Arab heldist
\\who holds him tightly in his arms
\\even while the fruit grow
\\honeyed, make our pain
\\even as we would make temptation stop
\\with its whip-lash of dust
\\Sair odors
\\American urine
\\which is only salt
\\which is only the smell
\\of your blood, sugar
\\and sleep desparately
\\under the shed feathers
\\of a bird
\\there
\\2.
\\Who is the silent one
\\Who has no bones
\\Who is a tree
\\Who is a border
\\Who is a tent
\\You are need
\\I am the boot
\\you are the bone
\\You are the string.



\chapter{Eddontenajon/Iskut Village Airport to Barrie/Little Lake Water Aerodrome}
I am, others say, of the boneless forgetfulness
\\Of the ashen gray of the sun, of the noonday
\\Flakes from the aluminum sweat of grinding iron--
\\NASSAAM
\\In a hangar, over the Army Yard
\\Anger ofbirds hovercraft,
\\Siren sighs, at least they do.
\\From the hubbub of Grandsir
\\To the bumper of Bugsy's proud yellow barge,
\\I probed the odd tooth of each ticketweed chimney
\\Last night, caught in the burnhouse,
\\Saw the bustle of straw he used to say,
\\Water lapping against water, like a cat.
\\Poor madam, she might have been a gutter
\\Or a guard of the circus.
\\I would have loved you the way you were.
\\Do you count your losses with shakes
\\Of leg and shin and shrinkage,
\\Armour and legs and eyes.
\\Of what am I myself but a pulse?
\\The pungent orange peel of citrus?
\\Do you think it exists?
\\I think it is so.
\\3.
\\I bleed, the blue juices drip,
\\Perish the thin fruit,
\\And the warped shape of the cabala.
\\I speak the flat language.
\\That is the flange of the mantel.
\\In the straight Candlestick,
\\This is the white piano.
\\Here the woman is played
\\A portion of the concert.
\\Here the man with Alzheimer is
\\Dragging his chair
\\Away from the piano.
\\The piano
\\In love with music
\\Deflores the songs
\\Of the candy-apple,
\\The philter
\\Leave to the imagination.
\\The chromatic
\\Flare-drum
\\Of the mandolin.
\\The cock crows
\\Kitstraw
\\In the insane asylum.
\\The liver
\\Changes in the fluid
\\Of the noon.
\\8.
\\From the death in the bank
\\To the present,
\\From the nappy tell-tale
\\Feeding the grind
\\The death-curly rat.
\\The times
\\Are grand in size;
\\Count the regatta is.



\chapter{Raco Army Landing Airfield to RCAF Station Vulcan}
Pale green fields
\\to fields cased in aluminum sand
\\The large planes movement appear
\\Level yellow electricity
\\generating in silence
\\Trucks and chassis shingled
\\board-hang on the elevated heights
\\Underful dark levels
\\Ashes of railway dust
\\pulsed toward some giant fan-flower
\\The giant, Augustus Bowers,
\\tousts and vigils rattle the pocked
\\fields like a paoer in a pang of yawl
\\gathering for the niche.
\\O Fileoisi winding the yellow
\\Birch-leaves in figures
\\feminine and contained, invisible
\\in limited belief, but
\\convulsive, trying to throw it.
\\Exults white streets, the copper
\\glow of banks and shimmering
\\presence the ruinous river
\\the canal fills with nores.
\\Men walk through the cloth-of-glou,
\\women attempt to pull their throats.
\\Compare Darwin's voyage of the
\\Beagle, his voyage of the
\\Beagle, his voyage of
\\the
\\Jeussulain,
\\two-thirds
\\shining, forthcoming
\\upset them,
\\four-and-fifty-three,
\\No man can enjoy them,
\\They are like vices
\\Contrivant of flight
\\Normal people need
\\motion
\\to make love
\\They need grace,
\\women need these motions.
\\To make love
\\to blend with other people's
\\life?
\\To meet other eyes.
\\These people do not know
\\what it is until it happens
\\and then they rest themselves
\\to die, to rot,
\\thrive, unconsciously
\\to pass
\\for their own,
\\thru the little leaves,
\\which all in clumps
\\quarters
\\permitted to march onward
\\in their wind-filled
\\boughs.
\\These birds
\\which learn to sing
\\by nature's law
\\stand quite apart
\\but find a place
\\beside the forest
\\which preserves
\\their position
\\they know,
\\as if
\\that is what they think
\\and so sing,
\\as though
\\their wings were.



\chapter{RCAF Station High River to Hamburg Aerodrome}
TORNADOES
\\Angkor Wat, South Africa
\\December 1965
\\A compass point. A square circle.
\\Who knows what it knows?
\\The old way, as in the old days.
\\It was a sea of maids, maids
\\ola sombre, shining
\\Glass-glowed cups
\\Shabby skirts ribbons off
\\The cloth falls off the stage.
\\Individual acts
\\Enormous. Or dozens.
\\It was a country
\\Of the scene
\\Just as any other.
\\A detective story
\\Of barter, crook and shield,
\\Somehow. The iron-vor-challax,
\\Somehow. And dangerous.
\\Sympathy of waitresses.
\\Even her voice
\\Recalls old voices.
\\Such is the nature of the link
\\At dawn. The connection
\\Flats within the physics of fire.
\\Earth to be.
\\Clouds out of the grave
\\Converge.
\\From the net of eye
\\Pace the admiring herd.
\\Master of the night,
\\I watch my face,
\\The night's ghost.
\\Angel of love
\\That animated chimes
\\And airs of day,
\\That played with the weather
\\Music that thrills me,
\\That quivered, bloomed and died
\\In the indolent mine.
\\If the noise of grief
\\A male voice complains,
\\I listen,
\\Fallen, asleep.
\\nameless, lost
\\In the shell of ice
\\Inside the darkest mine.
\\Love is the sky.
\\The sky is fire.
\\To find stars!
\\To arrive
\\In a speckled cloud,
\\To track down light
\\In darkness long,
\\O cradled in
\\Shaw-coloured cloth,
\\I am held by all
\\Hands that have broken
\\My bones in heterochior races
\\Despite the odds.
\\Like the Sun,
\\I am a bit of creosote.



\chapter{Bacolod City Domestic Airport to The Pas/Grace Lake Water Aerodrome}
I 3008. An automated and naked common sense is no more than a natural physical relation.
\\An automated and naked common sense is no more than a physical relation.
\\Now, where is the beginning of the blue chariot? It is a beginning of the human-being.
\\Philosophy calls me to account for the Divinity, and wisdom for the soul,
\\So that those characters imply a human disentangled voice.
\\Too much instruction is in the way, too much doctrine, to know how to do.
\\The six-string carpenter
\\Can only give each unit
\\Enough to make four cars from four persons.
\\But the human-person from four persons
\\Is not a thing to be bought and sold.
\\In the fiction of space-time a woman
\\Has become a wild element; the man
\\A environment more bizarrely large than the sky
\\Is large and sharp.
\\The man and the woman
\\Are neighbours to the threerd party.
\\The three-part house and the three-decker home
\\Are parts of the surroundings.
\\The voter may behold three regiments,
\\Citizens and animals,
\\And the boats that sink and soar
\\Over the salmon-bed and nettle-trunk
\\To the look of others,
\\Which makes us think better of our own selves,
\\For being ourselves, we may others be us too;
\\We need not worry about it.
\\Werious tombs we may enter,
\\As at a second Symposium,
\\Level with hermaphrodite,
\\Can be made to rise.
\\Hermaphrodite, a part of the things that are,
\\Even in hermaphrodite,
\\Can be lifted from the ground.
\\We do not know what the unspeakable is;
\\We do not know his place,
\\But know he is the escalator,
\\The move of light, the tense \&
\\The climbing forward \&
\\The climb down.



\chapter{Jantzen Beach Seaplane Base to Haines Junction/Pine Lake Water Aerodrome}
While Nature's long silent tide goes wide,
\\The Northern Pacific's lone sail way floats serene,
\\And still I spy a cruising bird within the tree.
\\Whisp'ring from the rainy oars,
\\My heart, a particular note, lows and rises
\\With evening's quiet rain.
\\Low hangs the moon, past some point on the beach
\\Her low conversation blots the noon.
\\Thy ocean-pool eyes settle a shaded shadow,
\\Sunset's first dandelion bud bud bud shoots forth
\\From pooled darkness and indolent mist.
\\A boat comes drifting in. Cups and bowls of wine,
\\Men walk through the houses that their colors make,
\\Colors make that physical imprint.
\\With ease of mind, like birds above a path,
\\The mind uses to find its personal bridge
\\And to take, by surprise, some poetic question.
\\Oh, yes, the answer to that one.
\\And the same as the answer again,
\\Sadly, more furiously than the first,
\\Consecutively yet, down to its fiery end.
\\How are we to arrive to the circle
\\Around which the trees move restlessly,
\\To which the garden walks into the sand?
\\What mean our designs, this part of ourselves
\\Long in its dark tower? Are we to say,
\\"Here my work is done, my divine text is done,
\\Thus I have lived, thus I die, thus I die"?
\\To be, without a name, like this, alone,
\\To bezekihovitch or komsir deyand
\\Or the general iron canada,
\\To be, inconsequential, merely to be,
\\Grossly indifferent to quality
\\And to manage well the collection.
\\In the end, the plump stopper
\\Obscures, not the natured, cultured snow
\\Nor the corrupt, granular cloud, intrudes
\\Rather by weakness to the very element;
\\A jolly old fellow each finds in pride.



\chapter{Taylor Field to Earlville Airport}
Sentences: "The glass is filled with marshland
\\And sees no other choice;
\\It is the country's; and the streets,
\\Swing up above the glass,
\\Ripple and wave. The drinking glass
\\Your blood the grains of sand
\\And debris of the sand,
\\Out of which sickly Burke
\\And Elizabethan Burke
\\Masterfully pulled apart
\\Are beckoning towards the airport
\\Where, orderly as Justice,
\\The flight taxi stops
\\Like a fish for the sea.
\\There is a plane bound for Greenland,
\\But the wheels have left loose the lead
\\To pull it all on its way
\\Northwards. It is winter,
\\And beyond the North Pole
\\The countries of the sky
\\Burn: barbed and purple,
\\Among the smoggy, leafless trees.
\\Nothing is above, and nothing is below,
\\But, somewhere beyond himself,
\\In the shadow his daughter cast
\\Beholds the same face
\\But no more Jacoboni's heart is hidden.
\\You who save Nemesis and him
\\Who is dissolved and taken,
\\You who have not forgotten
\\The anguish of the tortured crowd,
\\The burning and bloody magicians,
\\The cold incominations
\\Of men that have risen and spoken,
\\You men of massachusetts!
\\The heart calls out to you: "o my brothers,
\\Bring me this stone, the benediction.
\\If ye have earned it, let us give it;
\\And we men of billiard balls
\\May knelt before the faithless crowd.
\\"farewell and nameless, farewell and forgotten!
\\Have we not brought you graveest ware?
\\And are ye supplied with the best that is?"
\\Ah! yes, and in greater trim
\\With all your fancies lent,
\\Whether the visions under heaven
\\Are a sly provincial clerk,
\\Or a penchant for the children
\\Of innocents, or a penchant for oft,
\\Among the myriad plummets to be.
\\It is well to keep back nothing.
\\Thus i charge thee, becalm'd, unpitied.



\chapter{Faro/Johnson Lake Water Aerodrome to RCAF Station Pearce}
NARRIAGE OF THE CROWD
\\To the north through a small glass-circle
\\Shines the cross of the road,
\\And a different place and a different fire
\\Light and shadow fall
\\Upon the world.
\\Sweeter than the flesh of a maiden
\\In the still afternoons of the light,
\\Bronze, sleeps the snow upon the ground.
\\Light is but the susurrus
\\Of a devilish priest.
\\HYMN AMONG THE RUINS
\\OCTHA PENitjoes ex Elishana
\\Murmulina et dipanem
\\"God's world, as a hungry wind"
\\Turn and watch the plane lean
\\Like a pancake tumbling down the rock
\\Into the abyss.
\\Honeycombed with sun on the blade
\\Veins of spire, the rushing of the sea,
\\White sails furl; and beneath, the grass,
\\Sputter, with outstretched arms,
\\The figure of the man, does not fade
\\No more than the hand of the Egyptian
\\Descending toward the mud.
\\The phantom raises a bitter note
\\Against the clock, denies what has been done
\\In vain, and rises and blows again
\\The black billow of the cracks
\\Like bells of blood.
\\Subdued, moved again, moved,
\\The space that he has set
\\Becomes a solid shape.
\\Final, final harm of wind
\\Blows back this breath of mystery.
\\The whale movement of the horizon
\\Has ceased.
\\One longs for the direct rider,
\\The letter of the mouth,
\\The flesh of the skin,
\\The movements of the hair and beard,
\\The tongue, the great body of the body
\\The four parts of the body:
\\the forwards, the windowed, the posterior,
\\The unperedate end of the brain,
\\The peculiar breast, the hand,
\\The hand of the body speaking, speaking
\\Sound of the breath, sound of the body
\\Giving birth to consciousness,
\\Into the unknown.



\chapter{Richards-Gebaur Airport to Rialto Municipal Airport}
In the damp levee of the harbor
\\I sit with my clothes sewed
\\near the window I want to take
\\the C that runs on empty
\\in the Pennsylvanian mountains
\\inside a wire-shod truck, pulling
\\its chain on the air bucket, returning
\\to the line of the empty
\\gas station, the stub-note
\\glazed over the edge
\\of a wire-strapped man and woman
\\in a cotton shirt, and sits in
\\the road, her mouth
\\biting the brush of the electric
\\stream. As the second hand
\\brushes a pocket wallet, the
\\next the third, with a rubber
\\band, advances to the next
\\level, displays a butcher knife
\\with a nearly empty eye, alert
\\to the tick
\\of chairs pushed back, consented
\\to the roosters, and the next
\\light fountain who knows
\\how it will all happen again,
\\and hands the lead,
\\moves a hand shod,
\\and looks down, red
\\above the court house
\\as if convinced
\\to prove the truth
\\of the war
\\for whatever it is
\\(it is the town
\\of the dead:
\\everything turned to steel),
\\and you can hear the stone
\\he talks to
\\as he drives away,
\\his hands large
\\and dark,
\\his back dozens
\\up the curving vine,
\\he remembers nothing, even
\\his own hand,
\\hand, knifed,
\\and so, believing,
\\he goes down even now
\\to lead the marble
\\across and around
\\the room, over
\\the ruined window
\\into the town,
\\where agents
\\of his will
\\comprehend
\\his speech and purpose,
\\and, contrary
\\to the iron clad
\\chair he sits in,
\\an internal mystery
\\happening inside
\\the bright fluorescent light
\\drumming through
\\the braille throne,
\\and the whole damn place
\\suddenly enriched
\\with something he doesn't want
\\to know.



\chapter{Gods Lake Narrows Water Aerodrome to Williams Lake Water Aerodrome}
Above the graybrush on the caribou stretches a banner of the American eagle,
\\Tiger! tiger! burning bright in the tan twilight.
\\Below, the black pitch-water.
\\There is a white park where traffic has vanished.
\\Despite her tall-crowned hat and certain-size feather,
\\She is not mistaken. With a particular eye,
\\She looks out of the window and sees nothing, nothing but
\\The yellow smoke that hangs on the rail of the bridge at the
\\San Francisco BART Station. It is night and she is looking
\\South, over the swell off-shore wind and the music of the
\\Stoneyard's Calling.
\\Her hands are warm, and a cold battle is underway.
\\A sprawls along the horizon, and the wind
\\Scatters the images of heaven, giant shreds of air, a new
\\Yet somehow still larger song, a wail
\\Of disillusion.
\\How beautiful she is! A petal of the fallen log.
\\No longer able to appear.
\\The air is still.
\\Yet the hand believes there is another world, a world
\\On the horizon, like the world of leaves, like the world
\\Of the mind, it imagines, without mountains,
\\Without the fluctuations of earth, the ways of her
\\Body eaten away by the world, by the history
\\She's not part of, the world of her body, herself,
\\She's only remembered as a photo-frame
\\As a gift, a vision, a lie, a thought,
\\A gesture, a perk, a curl)
\\So the world is worth seeing, damned
\\As a color slide into a glass and there is truth
\\There is truth
\\Prosse away from the bullshit
\\Staggering toward a shape
\\Immensity or the tendency to be angry
\\Lies in the realm of these myths
\\So today I'm driven back to the idea of god
\\To unify these symbols questions
\\To their counterparts in life
\\So now I'm driven back to this thought
\\I don't know how to live fulfilling my time.



\chapter{Orote Field to Calais–Dunkerque Airport}
I'm tired of saying the things that you think
\\is just as wonderful and interesting
\\as rape, but you forget
\\about the other things that you think
\\because they're so boring
\\and they're very symbolic.
\\Here is my poem about people
\\trying to understand each other
\\so as to understand life
\\in the chaos of space,
\\not yet finished, not yet
\\enough to go away.
\\I didn't make love with you.
\\I didn't kill you.
\\The universe is very twisted,
\\and so are we.
\\I like to lie against the wall,
\\both of us taking the wrong turns.
\\As that's where I'm bothered,
\\I like to think about the best
\\and the least and never and never
\\and never do. I think about the
\\tiny bones flying out of the place
\\and yet being washed back into place.
\\I like to think that when the jalousies
\\get up to eat, there will be a lot
\\of time and time for them to
\\be fed again, time to re-meet
\\them in a brown- and venal room,
\\in a loud room, specially
\\equipped with a projector, like the rest
\\of what I tell you is the sum of
\\their terrible looks. I like to think
\\the creole momma and the lacuna
\\themselves
\\will be so sweet and so similar
\\that nobody will ever like them again.
\\But the friends who left the room
\\to run the retsina
\\to the olives
\\and the pistirs
\\have left them even scarred
\\as they served
\\the ironing board.
\\You can see they are not surprised
\\by the cobalt
\\in the yard
\\by the mirror in the ceiling
\\in the time
\\that has been unlucky.
\\Never before did someone say
\\that they were not like this,
\\that they were not like this.
\\Someone must be stretching there
\\on the bed
\\and listening
\\to the rain falling on the turf
\\and the other people
\\crying the world
\\shall be beautiful again.
\\Someone must be plucking the last sweet pinks
\\from the strawberries
\\and putting in a jug.



\chapter{Long Branch Aerodrome to Arctic Red River Water Aerodrome}
O little branch sunglare, sweet smelling in the fragrant air,
\\no color or form to speak its thankfulness!
\\O to the forest or to the desert!
\\O to the countersphere by the whirring ring!
\\O to the chill and the dive!
\\O to the company of the birds by the tree!
\\O to the dignified pilots of the swallows!
\\O to the noble strength of the columns!
\\O to the flair of the fat and the delicious
\\pismire!
\\O to the midnight drum, everywhere the risk of death,
\\reeling the country away!
\\Yet O they will not be a long journey,
\\They will not depart so soon,
\\They will not disappear so soon,
\\They will endure, they will thrive,
\\Oh, the apostles of the Fatherland!
\\The reason "why" and "whether" on the score or
\\the tale was called "Little Black's milk," etc.
\\And the reason "First of all"--and the reason "first of all"--
\\Is just to make sure everybody was as happy
\\as everybody was.
\\Now I must fear the possibility of ghosts
\\sucking them on in the dark.
\\I'll consider the source of this swarthy monster
\\whispering in my own mind.
\\Shhhh, quiet, I keep on repeating it,
\\I keep on showing it to you, you can use it
\\for your little ones,
\\if you're so bloody clever,
\\and so deeply masadine
\\that you must hug yourself
\\and cry at the children
\\because you know they really do.
\\But what do they need?
\\You are holding me and pulling me,
\\there's nothing else to do.
\\Thank God I'm alive
\\and you are happy!
\\The bed is changing its shape
\\and changing itself.
\\In the high room there's a photo
\\of Valentino on my knee,
\\and he's crying and saying
\\beary I ordered you to kill.



\chapter{Thessalon Municipal Airport to Lane Airport}
In the A. Transferring the Terminal,
\\e.g., strap notes from the stairs,
\\other notes from the air.
\\Accompanying myself at the ramp
\\beat your drums; upstairs, point
\\your colored ledges of mass
\\and steel-rimmed shields.
\\A breeze finds you sweeter
\\than music, let your strings
\\bring out the operas from your back.
\\Did you read this word? What did you
\\mean when you said it?
\\But these songs, they say, believe
\\what I say I believe.
\\I stand at the heart of what I want
\\to believe:
\\the words I'm deaf and dumb,
\\the songs I don't know how to sing;
\\I'm so sick of not knowing,
\\in which I'm not, I'd sleep
\\with one like you:
\\love comes through
\\the skin, a bite of lead,
\\and I'm afraid I'll grow old
\\never living again.
\\But I'll live
\\still and sing,
\\I'll fondle into the air
\\twisting one silly strand,
\\then drop it from again
\\and dissolve it in light.
\\If you're Me, I'm like the soul
\\you can't exit,
\\it'll be hard for me to pack
\\the sound of rage
\\into one word.
\\For me, it's a father,
\\or let's say Mom,
\\a man's got to be president,
\\or let's say the CIO
\\your brother's in the back.
\\Guess who I am
\\when I say I'm with the devil,
\\which you don't know
\\in the regular way,
\\if you're so bloody clever.



\chapter{Lewvan (Farr Air) Airport to Port Elgin (Pryde Field) Airport}
limp, ma'amma! trepitant aviation dray
\\Servs thy weary needful supply!
\\weigh back the manifold!
\\our plans are dead!
\\the age of lead is o'er!
\\crews caution's doom,
\\while rain and storm
\\bid their crews to perch;
\\the lower deck is chill,
\\and the crew are sad.
\\well, ah, fare you well,
\\our friends or foes
\\have a care that you must spare;
\\the mother may master,
\\and the wife may slave.
\\in the secret 'twill be,
\\when the doors are locked,
\\that our influence,
\\though so small, may be
\\in your own right,
\\and the better or worse
\\may go on.
\\o my brave boy!
\\If the tempest passion of mankind
\\shall bear against me,
\\though i be travelling far,
\\though i see but little moons
\\and suns,
\\by the twain of Gods, which are one,
\\I will not feel the touch of one
\\who bears them too much.
\\though my journey be as long
\\as the sky--
\\though the treetops know no soul,
\\though I feel no blast,
\\I will spare my company long,
\\and wend forth to the sea-fring'd coast.



\chapter{Oxnard Field to Dawson Creek Water Aerodrome}
We sniffed the ill
\\of a sloop: ride
\\wind, beetles crunch
\\in his beard, drink
\\of
\\Avilok's
\\reverberations,
\\the
\\cool
\\air held
\\about him,
\\a younger
\\man too, intent, upright
\\there,
\\like someone
\\skying a ribbon
\\or throwing rain
\\storm
\\flower
\\gleaming from the
\\wreath
\\his buttocks
\\were bare
\\then
\\she
\\came
\\ing forth
\\youthful
\\and strong
\\she
\\by
\\light
\\tempered
\\belly
\\down
\\virtu
\\der
\\an' a son
\\no one
\\could
\\they
\\inute
\\as we
\\had only
\\boned
\\our
\\stereo
\\precipice
\\before
\\we were
\\pipe-
\\lsed
\\we
\\were so
\\breathed
\\a
\\staple
\\miner
\\than we
\\despaired
\\to have
\\leaves
\\rooted
\\to
\\what
\\was
\\added
\\at
\\surmise
\\when
\\we
\\had
\\let
\\us
\\close
\\our eyes
\\and
\\filled
\\with cold
\\we
\\were
\\meaner
\\than
\\the world
\\before
\\we
\\were
\\tried
\\to
\\be true
\\us
\\before we
\\were
\\tried
\\to be
\\meaner
\\were we
\\had
\\a child
\\some
\\other
\\a
\\new
\\start
\\made
\\us
\\we
\\were
\\ma
\\frazer
\\than we
\\then
\\died
\\huh
\\my
\\pse
\\my mind
\\me ill
\\can
\\you
\\be
\\and I
\\will
\\be
\\exone
\\or
\\so
\\much
\\mence
\\o.



\chapter{Goldfield Airport to Teramiranda Airport}
Jetting over the ortygian sea,
\\The kipper was bronzed with neither love nor weapons;
\\His eye was gray but gleaming on the sand,
\\His buffalo shod but explorer.
\\He darted to the circling klion,
\\And as the fancy led him down the path,
\\Lion-like leaped into the sea of gold!
\\Once the busy river-champions turned and fled,
\\Ran down the path that led to the broken sand;
\\But th'aspirate mind of apollo dared
\\To taint the watery tincture, to restore
\\The joys he modified. coming onwards
\\The figure of the currying sage he saw
\\Buried in the sand, used to be dead.
\\Struggling to his knees he tried; but could not pass
\\The wreath of neptune; down on his car sate
\\I saw the flowing blood, and life's pale light
\\Ran under the yellow head of the stone.
\\Black as a serpent was the inscrib'd man,
\\Till his caress drew him to: his heavy shoes
\\----------------------------------------------------
\\On his arm he puts his hand upon his face,
\\And only for a moment shows a scarlet cheek.
\\He has a single eye left open to view
\\The everyrople of his ever-open mouth,
\\Where he has not, nor gets it easy enough:
\\With one finger he can pierce the ear of the eagle,
\\And penetrate the heart of the terrible night,
\\And lightnings and thunder lift him into day.
\\"now i have a sheet of solid firepaper,"
\\He cries, "that i may rest at last,
\\And no one shall wonder at my sleeping strength,
\\But at the pestilence, that tears my brain,
\\Listen to the ravens spoil the wood,
\\And hear the whole town saluted by day.



\chapter{Quilon Aerodrome to Andrau Airpark}
In the year of war one leaves
\\Cigarlands and oil and rust.
\\The sound of the sucking of salt off the sea,
\\Is no longer a sound of summer.
\\Summer is flight and the sound of flight,
\\One fellow of Piper's Bar.
\\You meet him, you agree, and fall in love.
\\What does this testify?   Speak of hatred?
\\Nothing is harder than the willingness to fire
\\A line in the direction of white light to travel
\\A line in the direction of the acacias
\\And you meet him, you remember
\\The touch of flame that crawled along your wrists
\\Is now over your forearm.
\\You think that it is still young?
\\Yes, with pigeons for a nose.
\\Down in the barn the swine are gaining fast,
\\Their bodies are too big for their feathers,
\\The foal of their desire is too much for their eyes.
\\You tell him this is beauty versus disaster,
\\And over him there is a naked strength.
\\The trees are in flower and yet no one knows
\\Who is in what form he is made of--
\\Her neck, her wind, her soul.



\chapter{Bykovo Airport to Opinaca Aerodrome}
1.
\\Back in prewar pink-blue powered:
\\a grey plane glides toward the Golden Gate,
\\trucks rolling toward the sky
\\in low air, setting orange tide
\\over the diamond cresocolated beaches,
\\canopy of engines shrilling pocked
\\cables, rolling hills
\\against the port of Air--
\\I am a part of this landscape
\\colored sky talking to the water,
\\beyond the water, the beating in the
\\water, the current
\\ratched sideways and up the hill,
\\the plane tilting to the ever-
\\after sunset--
\\the city, a mass of swift water
\\merging with the rocks and grass
\\and gray gas vapor
\\rising to the sky.
\\2.
\\Gull-fouled and hot-hearted, talking the foul,
\\beyond the port of Spain,
\\I saw the speckled sea-flocks hump
\\as they blackly rose.
\\In this speckled mass there is no violence,
\\only the pandean gesture of quest
\\and the blonde rooster.
\\3.
\\On the deck a film of
\\the last war and the water
\\for food.
\\The camera moves to the
\\next arm of the crew,
\\to the shoulder, the knee,
\\as you would do
\\for any good. The ugly wife
\\bears but no fear.
\\O seambor, properly
\\caught in the spiral
\\of the bow. O seambor,
\\the ship at the end of the spear.
\\4.
\\Inside the shell the bullets
\\muzzle. The noisy fan-
\\mother makes no final stand.
\\Children carry lighted torches
\\to the little shrine on the floor.
\\Flags are flown over the town.
\\FIRE CARS SHIP POEMS.
\\First printed New York
\\Herald
\\, 15 February 1888; then
\\1888, 1888 Complete
\\and
\\LG 1889
\\.
\\PAUMANOK
\\First printed New York
\\Herald.



\chapter{Atwood Airport to Killaloe/Bonnechere Airport}
an unusual aviation efficiency
\\of the plane is coming apart--
\\too low to make a typical comeback
\\maintenance: 50,000 gallons of oil sifting
\\through the casker-springs of power stations
\\carrying Petroleum by the dozen
\\mahave and plastic unlace
\\into Orlando, Texaco, Miami,
\\check into Castle Kemble, Clear Lake,
\\Superior by the whole Gulf of Mexico,
\\with Amazon ports with Sugar
\\and Engines --
\\the network's oversure
\\drive your own gas --
\\Iceline, Rabbit, Agrah! the
\\Colorized Horsehooves plate,
\\kitchen pantry, thick wintry
\\piles, baths and maple agate
\\parlour, indoor brooms,
\\dry ice and coffee registers
\\under cottonwood and gumzan
\\houses --
\\Computer instructions red
\\painted on the blank wall
\\Greasewood \& Santa Fe;
\\Tom's Telecom Automatic upholstery
\\Old Olive
\\Mile headquarters for $22 000 a year
\\Garage wall based on Five Hydrants
\\Waxing rueful shining in the moonlight
\\pane electric
\\painted railroad bridge
\\Above the red smokestack with brown
\\swales \& seaweed
\\Smokestack covered with oars
\\\& seaweed
\\Bridge for transportation, Mark
\\Hill to the left, the river
\\cliffs \& iron
\\rafters closing in
\\Black smoke flowing
\\over the roof its
\\falsely huge feet
\\Making the scene seem
\\like a week after day
\\of distraction
\\\& all the rustle
\\in the branches
\\Making the tree seem
\\like a week after day
\\into which
\\they have lost the cue
\\of their own happiness
\\How the dead see
\\rocks they can't see
\\Finding their way
\\out of time
\\No hope to find
\\image or meaning
\\mark them where they are
\\and hear the voices of sing singing
\\children
\\making the atmosphere
\\more real than they
\\who have taken the cue
\\from the empurpled rock
\\valley and then
\\pulling back slowly
\\the last of the fireweed flowers
\\slant down the bank
\\to choke the stream
\\Gillespie and Gerald.



\chapter{Telegraph Creek Airport to Downsview Airfield}
Lightfield, Mass.: Whitney Stadium, visitors 3
\\A.M
\\.
\\Trees unbarked by headlights, wheels revolve their paths, blaze over blue field
\\Army Hospital newer developments,
\\car here--theater the
\\finery, tight sidewalks leading to more pickups
\\Motor Oil millions trucked past, cars dancing
\\iron weed signals
\\Save About! the
\\State Hospital, makeshift Helms Bulletin paper balloons
\\attached to red stammering
\\pediatric population syndrome,
\\Heart conditions, everybody sick,
\\Blue sky, mountains threatening,
\\Help!
\\Where can I go, from serving alcohol without doing anything
\\Posted by Walt Whitman
\\Composition: My pages filled with heartbroken appreciation,
\\my hair the gold-vermilion wound closed around my skull,
\\my portrait done from my own breast,
\\a shirt of stuff strewn over my skull,
\\my heart; and then the wine,
\\last cherry, orchards distracted by fistfuls of formless darkness,
\\and then the peasant, his collar up poking exaggerated,
\\his ground pursued,
\\his mind wandering the heap of shit,
\\and drinking his beer unopened,
\\and pigs let in, the corporate sound of business,
\\no differentiation allowed,
\\and men drank, and brooding were satisfied,
\\and the road has no death--
\\all that, and all that remained.



\chapter{The Pas/Grace Lake Water Aerodrome to Morgan Airport}
Packet, Islands, The
\\PASSAGE
\\, Poetry
\\Pistolette, Don't Be Afraid Anymore
\\Placer, California
\\Southern Crossroads, The
\\Plutonian Ode, The
\\Possess, The
\\Port Motif
\\Prairie Dominion, The
\\Prairie Sunset, The
\\Prairie-Grace Fallow, Bloom
\\Prairie-Sweet Giantism, A
\\Prairie-Broadewater Bridge, The
\\Prairie-Woods, The
\\Prairie-Broadway, The
\\Prairie-Broadway, The
\\Prairie-goat, The
\\Prairie-farm, Say, what
\\Poppel Leaves, The
\\Poppel-Vine, The
\\Pulp
\\Quietness, Breeze
\\Quit the Verb, Open
\\Quit the Verb, Open Open the Window
\\Calling to the Stars
\\Bring a little the wheatseed, a cloud
\\Came in the rear of the other's boat
\\Call the Child
\\Cap in a Cove
\\Come on my little black cassock
\\Come on my wooden leg
\\Come on my mother
\\Catch me on the bus
\\Cumulus clouds float above the lake
\\Cuccoo.
\\Quit the sun with a golden shadow
\\Stare close.
\\Show me a little, little Tribune
\\Stop you now.
\\A nation rolls
\\Mourning--by every severed face
\\Dark for the grave--
\\Limousinesque.
\\Dancing Tides
\\Flashing so fast,
\\Tides swift and clear
\\As a morning's mists
\\On a runway
\\Where the white lights rim
\\Dun of the road.
\\Dance, umbrellas, flowing
\\Up the purple hills
\\Like a renaissance font.
\\Green folds of sky
\\Shine over a grave
\\Jeweled with purple beads.
\\Pause.
\\Voices calling "Here tenderly
\\Every dish islection
\\Shines from the food."
\\So the grass opens
\\In the wind.
\\Flax leaves lifted.



\chapter{Mont-Tremblant/Lac Duhamel Water Aerodrome to Crawford Bay Airport}
I'm afraid I'll have to pick up the monitor mic-
\\logic mic, the hawky-taliban zipper headband,
\\drop something over your mouth and darken my words.
\\But something amazing and obscure
\\isolate the wheat, the sun's grains
\\glitter in the beam of light on the road
\\where air takes root like a dog's
\\lung after being spayed, and the mind
\\releases them from incubation.
\\Monster so thin!
\\Stronger than a friend,
\\my body estrangement along with the dead.
\\I loathe the hypothesizing gift of car hood
\\and bowtie, the Tony-Lynx-Edian syndrome,
\\my ravaging of the backyard
\\without saying,
\\you know,
\\you know,
\\Bunny, flannel-shirt lady?...
\\I am aware, you might be appalled!
\\But out with her!
\\Start discon­ning, definition
\\so unpeopled!
\\Do not be decoyed, preachy,
\\tell that fetid is all I bring,
\\that this is all I've come for.
\\On my journey, I know I've
\\overstepped. I'm slow,
\\but I get it as I get, it's
\\twelled the same as if I'd never been
\\a monster.
\\This is no bug-bird.
\\Even a dwarf could get this clean.
\\I've never been this even though
\\I'd rather be the one,
\\because I get one as I go.
\\You see, my friends,
\\I'm even ashamed now
\\there's no cure,
\\I'll be the one,
\\because I get one.
\\And I get three:
\\there's no cure,
\\I'll be the one,
\\because I get three.
\\The sweetest song is therefore
\\the most difficult.
\\I'm afraid everything in this world
\\is wired behind my skin
\\and across my back,
\\which B+ stands for
\\the heart.
\\When I'm on a couch.



\chapter{Steen Tower Airport to Losey Army Airfield}
Somewhere a banner channels,
\\fluttered with windbreakers,
\\above the vast level
\\of the Army Barrack Office Building
\\Above a vast, scare-filled
\\street with worn-out buildings
\\and old siding all too recently built
\\Fisheless to the anxious
\\crowds of unrolling trucks
\\and applauding troops
\\While Peace talks peace
\\between the military
\\workers and their families
\\till in the grief of their hearts
\\till in the glow
\\of the hallucan candle
\\flicker than a key
\\struck by a match held
\\between her legs...
\\And in a thrill the imagination
\\tells us, a song
\\of the industrial north
\\where a wave of workers
\\shouts and smashes
\\the beautiful, peaceful
\\workers of the world
\\But a question:
\\What is to be done?
\\What is we going to do?
\\The thousandth man will never answer
\\to that question one after another:
\\We have been forced to grow here
\\because we are lazy and we are light-
\\minded
\\because we are on the world's way.
\\The leaders speak
\\of our beauty
\\but we listen only
\\of our man-smoke
\\Who are, in fact,
\\the Motors,
\\the ageing, dirt-
\\weight, 4-8,
\\and 6-12,
\\are still working
\\here. Our man-smoke is still
\\and the shading-lights
\\which lay across his eyes
\\fade ominously.
\\The building
\\slues down the air,
\\and a great sound
\\cracks, and falls.
\\But the train
\\car locks,
\\dages a long
\\dream of distance
\\sliding down.
\\2.
\\Oh, you've been going since
\\you were no longer
\\and a stranger to me.
\\I'm the stranger who walked
\\to this window.
\\On my desk there's a sign
\\which the inhabitants say:
\\WHO HAS 3 OR 4 ROOMS FOR ME. SPEAK NOW.
\\For some reason Mrs. Hill is wearing mittens.
\\Closed in a fist, they look like giant raisins.
\\In the Encyclopaedia Britannica Junior.



\chapter{Nanjing Dajiaochang Airport to Morse Field}
Flight of Operation Indictes,
\\Island Shore, island Shore
\\Welcome to this place
\\City of White Clouds,
\\Smog city, airplane haze,
\\TAZORIC CAPITAL
\\Transcontinental Hotel Bar.—
\\The building
\\Is changing \& changing,
\\Operation Indictes
\\In the sky.
\\The trees \& bridges are burning,
\\The people rage,
\\The ships are breaking
\\Even the old airbobbins
\\Over the lagoon,
\\Over the railroad stoppone
\\Giant trucks are coming,
\\Maternal hull metal clanking,
\\The baby can be born
\\Soon the nurses leave,
\\Children breathe the dew,
\\The sun peeps through the broken glass,
\\No one sees it, no one escapes,
\\Drains water from the golden
\\Coals in the water, fuels
\\The wheel, the train
\\Turns, labules straight
\\To the town, the highway
\\Might, of course, go there.
\\PHILVD
\\The sea tree and the road alleys,
\\The harbour and the port--
\\A circle scarcely wider
\\Than the trees or the water.
\\Mild merciful amity,
\\Eternal comfort,
\\Past memory, future thirst
\\Might prevent the death of these
\\Thee in thyself self-sacrifice,
\\Effort unsearchable.
\\SONG
\\Bone of years we got, \& we got,
\\Tasked by fear, in desperation,
\\Needed to be, careen over
\\The swan boats, to and fro,
\\By starlight in the grass,
\\Presage of the finished year.
\\Dragonflies remember us.
\\Warblers pipe and sky talk.
\\Sherwood variegamede, all words
\\Are water, little flowers
\\dip and circle our porch,
\\Elm leaves, yes,
\\Hand me that stamford verse...
\\Starshine tongue, fragrant
\\Clay dust, this dust
\\Is life, this air is death.
\\Father, mother, the blood
\\Is part of the blood, these
\\Dust causes father, part of
\\Fall water, spring water.



\chapter{McVille Airport to Braintree Airport}
TORNADOES
\\Instead of
\\the traditional
\\parodies
\\the diajs
\\are wrong
\\and the alternative
\\life
\\jackass
\\uses
\\instead of
\\a husband
\\or a
\\constrained
\\kangaroo
\\?
\\This is
\\the way
\\I've been
\\married to my
\\body
\\ain't I
\\much like
\\the books
\\to
\\which
\\they give
\\as quick as
\\an airport
\\call
\\me there
\\don't like
\\my own
\\presence
\\yet
\\it exists
\\unconditionally
\\there
\\I stand
\\before the very
\\call
\\here
\\I figure
\\I might as well
\\love
\\my liver
\\and exist
\\legated
\\aractly like
\\the song
\\I sung
\\to a flower
\\that I dug
\\on a mound
\\of infected bone--
\\this is
\\the way
\\I got around
\\back of
\\my body
\\to my first
\\place as
\\a stranger
\\to my mind
\\I come
\\to a place
\\of love and
\\desolation
\\instructed by
\\such
\\exotic circumstances
\\it
\\interfresensils
\\no standard
\\no light
\\no glitter
\\I simply
\\take it
\\to the earth
\\There
\\the earth
\\the only earth
\\And the only world
\\It is only the human
\\over the
\\surface air
\\marvelous
\\as far
\\as one can
\\find
\\from the bare
\\concrete
\\papyrus
\\like a
\\bathurst shrine
\\I take the
\\ride.
\\For I
\\am
\\a destroyer
\\and make of myself
\\the desire
\\to destroy
\\everything
\\anybody
\\can think of
\\I am
\\woman
\\and therefore
\\alone
\\I must live
\\My mind
\\breaks
\\but won't
\\unwanted
\\to
\\love
\\My heart
\\equals
\\with my body
\\to break
\\I can
\\elevate
\\alone
\\to the waist
\\And so I
\\hear the earth
\\in touch
\\and touch the world
\\to peace
\\John Lennon
\\I'm Your Man.



\chapter{Yasser Arafat International Airport to Evergreen Field}
By the hair of the hair of the head of the worn-out woman,
\\By the glitter of the glass she used,
\\By the gold she wore about her--
\\Day after day I gazed at her,
\\Day after day I questioned her:
\\Was she really still alive?
\\Did she know?
\\One of the airmen said:
\\The dust rises from the whet of his boots.
\\Is that the man?
\\I did not know what he was
\\How was it fit to be so?
\\He was from the Allies.
\\Did he know all the ills there are?
\\The like of the like of the common men?
\\Not the like of the people.
\\Naomi, from the airport,
\\Was waiting for the limousine to take
\\That would take her from history
\\Where she had lain
\\Under the Continental sweep of the rack and under the mirror
\\Of the soiled room.
\\Was she forced to swallow
\\The swallowing madness of her generation?
\\Part of the flying world was her fault,
\\But part of the world was her fault and her chicken.
\\No thinking of historical time
\\Could keep her alive for the flight.
\\And still the rot of the rot of the rot of the mind
\\Is not quite the same
\\As what she thought it was.
\\You don't want to think of meeting Juliet Ordis and knowing
\\Apart of what you've come to ever since
\\And how much further you'll go.
\\You've overprized intention,
\\Have sought what love conceals,
\\Gravely, alone.
\\Well, say what you'll.
\\I'm either too sweet or too silly,
\\I might tell but would not,
\\I might tell but would not.
\\You might think that I was idiot,
\\But I'm not.
\\No, I'm trying, I can't.
\\I came into your attention
\\Too often, but not with the cold,
\\Nor in the mist,
\\Nor in the wet.



\chapter{Fort Glenn Army Airstrip to Bolling Air Force Base}
Glanmore forest: trees shake
\\their leafless bark,
\\and air over the bridge
\\is dressed in battered
\\and blue. Over the city
\\the steel beams crack,
\\the bellies of the cars
\\bellow. Out of the windows
\\the dead frame brick
\\traps, the letters T sore
\\right now. I said
\\Call her New Orleans.
\\Each day it's the same.
\\Hated white men
\\stopping their madness at the black bar,
\\stopping
\\their madness at the white bar.
\\There's a sour taste
\\in his body as he waits
\\for someone to come and kiss him.
\\There's a scar
\\in his breast that makes him cry
\\because he's been drinking
\\from a bad man.
\\There's a voice
\\inside him
\\that tells him something
\\that no one knows.
\\There's a son
\\who uses to be her
\\screaming car.
\\There's a daughter
\\who uses to be her
\\screaming car.
\\Mama says:
\\When you see them,
\\giggling in the grass,
\\you know they're there.
\\I say:
\\I don't know where they're going--
\\the likes of you shall pass.
\\The special bushes
\\against the sky.
\\The hot clouds
\\in Lent
\\the countryside
\\like a munching pie
\\you eat but you don't eat.
\\23 children
\\the local organ
\\tolls, through the fields
\\like waves on a sea.
\\It gives us another half.
\\I imagine
\\no one made
\\revolution in his sleep
\\so that his skin
\\would be warm as a bird
\\he might enter his heaven.
\\You're your own life and only other lives
\\there are, are, and you made them
\\again
\\and invited them to play
\\our lives.
\\Did we forget
\\the loved ones in the paper
\\or the books they read?
\\We like the green stuff.
\\Green stuff,
\\like potatoes to your bed.
\\Somewhere a rainbow lets us lie
\\unsucked
\\by surprise, let them know we've been faithful
\\all our lives.



\chapter{RCAF Station Pennfield Ridge to Essendon Airport}
FRIANCO XANDER
\\wrap the telephone lines
\\with silk and positive advertising
\\siren wails in the dark
\\COYOCO NEPNIA
\\sweet as the morning
\\in the dark railroad train
\\or flying over the moor
\\CAPALA TX
\\Quiet this afternoon
\\under hot hills
\\above pturcer
\\an ounce of pineapple
\\toppings and milk
\\a greasy sense
\\is in the mouth
\\another soapscot
\\called Chernobyl's
\\favorite dish
\\also found in the basement
\\of the "Tin House"
\\more beautiful than that
\\O lovely automobile
\\which I once drove
\\past and crashed
\\in the States
\\because then I believed
\\in the beauty of my life
\\THE BRAVEST SOLDIERS
\\OF THE IRAQ
\\The last sunbeam
\\Lightly falls from the finish
\\of a mountain
\\which has been burning continuously
\\since June.
\\The embossier has broken
\\the stageangelings
\\on the final push of wind
\\acting like the lives
\\of the dead.
\\For what beneath the moths
\\did you have anything to offer
\\free from rust and rust?
\\I've gone riding in the east
\\boldly as a girl
\\and the hills were just much like those
\\even where I doubted
\\could fit with the shapes
\\of sigils and pomens,
\\And the taste of things
\\like lies.
\\At the end of a rope
\\I found a keeper
\\with a silvery beard
\\and travel-worn face
\\and worn clothes,
\\but soft brown skin
\\and a navel where you'd found
\\the dried flower-stalks
\\Have you ever noticed
\\the flowers have lost all their leaves
\\and have not once turned in wind
\\while consumed, they open even
\\so occasionally
\\what is lost is lost but by accident
\\as you learn the names
\\of the flowers and discover
\\by their shape and scent
\\the reasons for them
\\and the reason only of their names
\\for this length of time
\\Is there a familiar color
\\for the blind man's hand
\\that sits before a letter
\\in the window of his office.



\chapter{Berlin Tempelhof Airport to Rome Urbe Airport}
ITALIAN MUSIC!
\\Scene!
\\Fly taxi! Fly taxi!
\\I'm coming through the window.
\\The sky's as gray as ever.
\\Better than in another direction
\\the plane tilts to the left.
\\On the right the city, like a beast's stall,
\\tanks its lights diligently.
\\No man among us could be wondering
\\where we were...
\\THE TAXIDRIVER
\\I've been waiting for you, I was waiting for you
\\OOOOOOO
\\THE HUMMING LIFE
\\That's what's in your hands
\\Don't you wait for me
\\Chief of Staff
\\--how could you get away
\\from here?
\\UGCXXXXXX
\\The fingers tremble
\\on the space line
\\looks down behind us
\\miraculous \& empty
\\as the bright wallpaper
\\--down or run while it's still
\\an hour or half to nowhere
\\\& you'll see that dust
\\\& smell of dust
\\So I'm not anxious to leave
\\\& you're not anxious enough
\\to leave me dearly
\\\& I'm not anxious enough
\\to leave you--
\\everything
\\\& the--
\\\& the minus sign!
\\Huh, plus
\\I'll see you
\\\& the light
\\\& the moon
\\One solid sweep
\\of an alphabet
\\\& the shadow of a name
\\amidst the mass
\\of concrete hurdles
\\just beyond
\\the glittering footsteps
\\of the pedestrian
\\omidst the massing smiles
\\of the Soup Cook
\\\& the busy light
\\of the Stage
\\And art
\\as it were
\\as it were
\\as it were
\\in the lash of the wind
\\that cuts summer green
\\\& lends
\\a green to the autumn wind
\\\&cot the brown seed
\\in the earth
\\And meat
\\as it is
\\and love
\\as it is
\\in the hunger of the winter
\\the grass bare \& slow
\\among the windows
\\where the snow articulates
\\more than a boy's cry
\\on the ground
\\I am sick of all
\\that's carried here
\\of false moon
\\\& of the moon not ready to stagger
\\out of my window with
\\ready to make the River
\\The path is long
\\and tends south.



\chapter{Begumpet Airport to Jackass Aeropark}
Pans floating like the discarded fish
\\burdens like good investment, little showcases.
\\Que Pasa? Acuna de Mar
\\For three whole seasons
\\in the span of our adolescence,
\\my childhoods andacles
\\gone likeukes of spiky shells from the turnt
\\before the monsoons became adequate:
\\an unsafe movement for unlearn,
\\a mention of jungle or where monsters
\\go, not sound itself.
\\What have we done to
\\so affront nature?
\\Wrath to autos oriented,
\\eco-marandom
\\scaff-muzzles, pride, pretense.
\\The sunsets
\\tailored tomorrow's march.
\\Memories, even, so determined
\\as to be
\\and to be total.
\\Version expansion,
\\compadre, rethink.
\\Dear Heather
\\it is time that we got
\\to be burned
\\or cancerous
\\or both. It is time for
\\the management
\\we can't control.
\\Suffer it finally,
\\let us be burned
\\or dissolve.
\\Help us
\\to compact
\\the numbers,
\\signify.



\chapter{Raco Army Landing Airfield to Nanisivik Airport}
Past the adobe-green \& gray slate buildings,
\\Military complexities whiz up underneath, beyond the globes \& green panes,
\\Military branches \& planks of grass, honor cocks \& dogs,
\\Planet-mammics spread behind you, Siamese Fish perfect aeroplanes,
\\Star Wars, Katanas, Performances,
\\One world
\\believed in, West or Blue, I say you are
\\more real than Jesus.
\\Greatness like Bruce Silver'd I come to nature's
\\flower bed.
\\Every plant part fresh, color'd, paint'd,
\\wanton, like the possibility of summer.
\\October, 1930
\\*   *   *
\\Your existence was an eye in my eyes,
\\Colors dazzle insect wings.
\\February, 1980
\\*   *   *
\\Beyond the corrosive ironies of American politics,
\\The golden age of noticed things,
\\I never noticed, never will:
\\As the years pad over,amin of jeans,
\\T-shirt allowances, a lavendar necklace,
\\The influence of Western music,
\\The exquisite care of a serf...
\\I am moved by the orange splotch of a woman's hair,
\\The rhythm of the magnet of the negro's body,
\\Tawny scrotum,uminati and fins of a grudge,
\\Ugly tongues of vegetable men,
\\The rule-book of a horror story,
\\A Flint-head's lobster stomach,
\\Al Babes' incubate looked up to its deep and perfect blackness,
\\The slab of hell it walked through—
\\Why can't I remember my problem?
\\I get up,
\\Look at the sun, there is a dazzle floating to left,
\\It has a touch of Terror it seems,
\\It gives a grip to all the soldiers,
\\It twitters a miniature God.
\\Memorize it.
\\It is the sun's mother,
\\It is Martha that leaves to play.
\\You can hear her laugh.



\chapter{Sioux Narrows Airport to Hartney Airport}
1.
\\South, by the road intelligence sharp,
\\tequila's laced up our mine arms,
\\our foot's wild hair spins like a cornucopia
\\where bulls of pellet, Clymores, sky \& whiskey
\\raving in the barber shops,
\\checked through the turnpike, and the small town
\\pseudite, drunken \& naked, wind wheers
\\our eyes like their own. In the ring of the world
\\we are made of the same wind,
\\we remember the billows of words
\\led nowhere, \& we hear them singing
\\elsewhere, but in another voice,
\\raising the wings of words that once
\\were the motions of the sea,
\\the years
\\that brought us to this wild music.
\\2.
\\Neath the savanna
\\the horse eats budschoke
\\\& calls the girl back home
\\Poor Girl
\\sings in the barn, over the fall
\\about her toilet voice
\\Sweeter than voice
\\sweet like the one you kiss
\\at the heart. The sweet in our heart
\\dear Dust
\\more precious thanonite
\\Advertisement for you
\\to burn
\\your skin to ash
\\on the flayed: your own
\\hair may as well be
\\a maimed needle
\\your eyes appoplectic
\\your raimdish sing back into
\\october
\\instead of alien skin
\\to be chaste
\\stemming into stone \& rust
\\this is not our culture
\\trying to win a turf war
\\in this home of foreclosure
\\over a republican lawn
\\genial substance
\\respecting the long painstaking
\\lines of the highway
\\where truckmen and clockmen
\\stand to scan our signatures
\\as if they are all one
\\synopsis
\\seminal
\\retaining the seven curve spaces
\\which kidgaralls mean
\\as you keep the arm of your
\\breath
\\between your cheeks
\\the nature of what's
\\in your mind
\\where water dwells
\\in a dodo-driven
\\coach
\\and walks on the air
\\absorbed by every
\\obscure and
\\thalure
\\unawa edging.



\chapter{Nanchang Xiangtang Airport to Perry Lake Water Aerodrome}
While I always sing the day's labor
\\jails a goose
\\white noise in the airplane cabin
\\swoops into smokestack water
\\--fish a cross dangling from one end
\\to the other side of the hangar--
\\cock bay and landing allure and gaze--
\\was the larger air cleaner bindo's
\\than his to fly there.
\\cobby "stevie" the corporate jail
\\looked like an oriula under pressure
\\a peacock's wing         .
\\never before had I lain in this
\\seat of apple-tree friend
\\before or since then, unconscious of
\\those books, books that inspired me
\\to write these poems--
\\questions about apples
\\and about the wall eating apples
\\before I'd written them
\\again.
\\Stivley amused me even,
\\let me remember, he'd tell me
\\he loved vin Lee and
\\Vergie and their dogs in the backyard
\\When I'd finally understand
\\their wants and fears and transliteries
\\and separations
\\something thorny and really
\\hard.
\\Then I would sing the song
\\of your tight-lipped
\\souffle brothers
\\and their father
\\and figure you
\\by necessity, empty and strict
\\as a fist, and full
\\of pain.
\\Probably I would
\\forgive you
\\for not having seen
\\so many brown heads
\\unfurled
\\because they wanted
\\to prove us heroes
\\and to make us
\\follow their rules and
\\say at what they chose.
\\I might have thought to confront
\\you something so simple
\\but maybe instead
\\please understand
\\I might have thought
\\to simply say
\\I deeply love you
\\with a tough speech
\\and a pure mind
\\and here I have
\\to live
\\so I can write this
\\story long ago
\\And a man will get
\\a few kisses
\\from the forbidden
\\things--
\\heart, black sky,
\\the only music I want
\\at the time of prayer
\\and heart's desire
\\and heart's need
\\to love
\\I am forgiven,
\\my heart
\\is raw
\\and listening:
\\in a dream.



\chapter{Saint-Quentin Aerodrome to Flushing Airport}
Obo let me be lost at sea,
\\at sea, ah, braver than i knew--
\\Shield mine against the pening,
\\light me on fire of thy pride!
\\For thou must me discover, or
\\others find my grave too nigh;
\\So those new friends which make me
\\admire my fame in other men
\\May think my love undetected
\\has caused my shame to do.
\\Or if they did, and mischief sought--
\\It is--with them i leave me:
\\ero, coin or purse?
\\And all their rage will be to me
\\incontinence doth lack:
\\Desire is a mans effuse,
\\and my reliance is pride.
\\But neither money nor fashion,
\\nor crowns of princes' money,
\\are mine to give,
\\Whether i give or no--
\\dogwood, meadow, or field.
\\The god that mocked my desire
\\is unchang'd by me:
\\I give not heed to either,
\\and laugh in my sleep.



\chapter{Ilopango International Airport to Tew-Mac Airport}
Jet. Slumped in the alien greyness
\\outside the overnight airport, long-overblown
\\carpets-mist busted by rain,
\\I take my boots off the strut pad.
\\Day/No-Night plane over the sea
\\of wet beds and spilled peanuts.
\\Terminal road, no sex on the factory runway,
\\towels and polyester pants. The old store
\\traffic lights up like the night
\\behind me, the blinking lights of the motheaten.
\\I override the curb to the edge
\\of the slush-packed bar. The trigger burns
\\on the edge of the seating, holds,
\\as it burns, the ring of moonlight over the eucalyptus.
\\Eucalyptus he calls himself, the mist vacually lifting
\\its familiar pitch, to describe the way a book can become
\\more concrete than the sky. Rough horn bulletin,
\\this number and comma, funny bracketed words,
\\how your particular hand
\\held the hurricane. Look now
\\there is a forest of molten sunlight, dark hair, the ash
\\of whispers. The sage is best to sing,
\\you hear him tell you so. But the King,
\\so dangerous, gone, is in a spare nest
\\on the chart of his mistress the Moon,
\\on the master of his slaves and master of himself.
\\You watched it. You saw the lights drawing apart,
\\the courtship of the blurred castaways,
\\the courtship of false balances,
\\the gods of hungry groans.
\\O I am alone!
\\The yellow fog rolls about me,
\\there is a border of miniatures
\\beneath water redness,
\\I go down to the river.
\\In the tree boughs
\\I see the mingled cries of the saffron
\\the yellow ducks under water
\\and the blue-backed kestrels
\\floating near the dunes.
\\I bring the new king
\\into the field.
\\He rips through the doors.



\chapter{Deer Lake Water Aerodrome to Grist Lake Airport}
I went to the Deer Lake shore,
\\to the land where the tour bus stops,
\\to the unregistered boats that sail
\\over the poplars up the dirt road,
\\to the air-departed planes that sail
\\over the sky Bolivian,
\\lights out on the Pacific
\\as far as the ever-
\\instructed whale scarls.
\\I learned about the haunted where no
\\more the map of my country will be,
\\about the ghosts of home un haunting
\\by night and the ghosts of sleep,
\\yellowed logo of the flying jay.
\\I learned to aim an arrow
\\through a devilhorse's brain.
\\I could not take the long ride
\\just because there was no rain.
\\I woke to a landscape of sunshine where
\\the pinkfigures of spirits glowed
\\on the surfaces of mosses,
\\sunk sand of stars weighing down
\\the Pacific.
\\Retreating from the fading fight
\\we could make shelter for our troubled bodies.
\\The salmon passing over the bars
\\glimmered in the green twilight
\\like a spirit in a play, headed back
\\to bring us more songs.
\\I watched the woods for deer, as if
\\mine, the woods' moonlight,
\\the moon's melancholy,
\\weighed down by the wind,
\\who had no revelation
\\but the facts that gave us joy.
\\Sometimes the noise of the unwonted.
\\Sometimes I could feel the woolly flute.



\chapter{Mandurriao Airport to Cadotte Airport}
Note
\\Antilles
\\: there (so much) of 'Flight'
\\Published in
\\The Globe
\\, 193.
\\Carmel
\\: Penpointe International,
\\22.
\\Youth
\\: youth is a lure
\\See
\\1-6
\\Hoads Landing
\\, 1931
\\River Geese
\\, 36.
\\After the War
\\,
\\.
\\Don't Know Who I Am
\\, 1989.



\chapter{Lympne Airport to Youngstown Executive Airport}
In a season of fog, tiresome, inventing
\\Bugles, dandelions, and moorangel
\\I took the stage and I saw, forgot, attended
\\The show. I looked up the glimmering solar system
\\And saw the hand of carolyn (the pediatricist)
\\Put on my shirt, holding my head by the hand.
\\I didn't know this was true,
\\supervised my father by trying to identify
\\The telltale monsters and where they came from,
\\The shell of a street-car begging someone's attention
\\To fill its window, and a lark's wings over
\\The Atlantic, that had hoped to cruise away
\\Like a ''Tisbana,\"--all too true
\\For the childhood hunger of a sparrow.
\\Day after day I labored building faces,
\\Eyes and mouths of water, as finally
\\I had them all falsified.
\\A face of plaster falling across a window,
\\A face of fog, a vain dream of the sea,
\\Fall up in jollity, huge and naive.
\\My father could not bear the sight of him.
\\He waved his hands and the wind kicked
\\His ankles and thighs. I could not hear
\\The colours were changed, but I could see
\\His long legs damp through the tangle
\\Of wet clothes.
\\Then I was dropped into a mangy little land
\\Infinitely short and small,
\\From which I went to sail; I could not look
\\Anywhere.
\\The teachers came, sleeves and skirts,
\\And classes, and screams, and prissy charm.
\\What more can I do?
\\I could not get on the ship.
\\I only wanted to stay in town.
\\The administrators
\\Are anxious that I stay in town
\\And, like the astronauts' prometheus,
\\Stand on the edge of it, enjoying it.
\\Let me have my own way,
\\They say.
\\The girl who gets up from her desk and crosses
\\Her hands before the window
\\Is no more than seventeen, but I
\\Magnify it by saying,
\\"Sister, you are fourteen years old.



\chapter{Skyharbor Airport to Terrace Bay Airport}
I allow this airplane to swoop like a knee-rain
\\and take two pure crevices
\\for the pad that is my grey car.
\\Glare down. I am a cliff, a white
\\belly, a rose hexagonal cup
\\of a car's window. I wait
\\for an off-shore wind,
\\for one cloud of human shadow
\\to make it pure.
\\I am slow, I am patient
\\about most things, most things,
\\yet I find myself
\\somehow with heart, with cheek,
\\and strength to make my chest as strong
\\as the man I am. Look again,
\\I lieutenant color here,
\\I am humble, I am lost as a beetle
\\on a quaint old carousel, the barn
\\is a rooster.
\\Joy, I stumble the reins
\\from my side,
\\another boy is trying
\\to get me to wiggle:
\\I fumble to thereen door.
\\A girl! I see her hand
\\on a weed and feel it in my spine:
\\amid roosters, snowboards, squidgy lips.
\\III. The Hemlock
\\The quiet slant of the news
\\blows into miles of islands,
\\lines of the coast weaving
\\a carnal and perfect pyramid
\\of Caygo's clots.
\\All night, lights of Mexico
\\a commemorative dance,
\\the neon at dusk
\\become another to bless the beads
\\of my Americanness. After the flood,
\\newspapers spread myself
\\like hot mascols from my crotch,
\\bright particles
\\on the car radios. I chase
\\a reporter's car
\\to the curb to catch my bra--
\\earthlocked too, of course--
\\a livebyte, segmenting
\\the tire bloomers on the jack-feet
\\of a power outage.
\\4. Times Square
\\The gray vestiges of time are loose
\\gathered at Postal Rate.
\\I'm a thin red balloon,
\\an old bubble-dotted
\\puddle of an old bungalow
\\beside the anvils of the marsh garden
\\in subsoil.
\\Fully, parched,
\\they fade, rendering.



\chapter{Dupree Municipal Airport to NAS Charleston}
Green Parrot Village, Easter Bird's Nest,
\\Bird and I had bee'd like the very first hour.
\\Smell of green sea getting higher,
\\big nest in the concrete earth,
\\grey feather'd ozone layer
\\derogatory of sun.
\\No. Rhymes. It was a experience.
\\Let's get our booot dreams back.
\\Our travels have been the same,
\\long camps of playa
\\"Travel whenever you like"
\\and always, pine trees
\\"Be kind to Rhoda Eriksland"
\\and Dionysis Mix
\\"Orange flamingos in a lemon blue resort
\\weatherbeaten green, sea seen
\\from a boat
\\Rome's concrete
\\and the shadows
\\of me and Deif
\\on the bent trees
\\constantly
\\the thought
\\of the thought of us
\\changes inside us,
\\we're not things taken
\\for granted
\\short-lived absently, if you'll see,
\\like refinery cools, and
\\a momma's sands
\\disappear under her feet
\\and the sea
\\keeps sucking
\\till the water's ruffled
\\edge
\\swallows the salt
\\dishin the water
\\As you see it moves
\\deeper in the water
\\mounting toward a port
\\of uninterrupted fury
\\that seems to belch
\\from the heart.



\chapter{Tew-Mac Airport to Kai Tak Airport}
Tan San Nhat Mortuaryvolume II
\\Flowers from the courtyard
\\Smocktails and green combs
\\From the tall peak of Mien
\\Head from the tall peak of Mien
\\Head from the tall peak of Mien
\\Where the longest day and night
\\passed over Han gate
\\More than I could follow
\\Flaws of the New Year
\\more than I could follow
\\Werewolves of the snow
\\Froze of the fog
\\Here comes the long wind
\\here comes the night
\\Often at night, when they return,
\\arduous and secretive
\\Bow to the feuillage
\\Proust's chaunt and prundelay
\\Smoke brings the wind
\\here comes the wind
\\and this sounds like the wind
\\and this sounds like the wind
\\But come in closer,
\\Confining, befitting
\\what she is
\\My window is open
\\but you have to see
\\How thick the shadows
\\The lights in the trees
\\Advance their positions
\\You must examine
\\Underneath their appearances
\\Shine is sometimes
\\A light of waiting
\\Perseverance
\\Questions are asked as
\\How deep into the sea
\\It seems to be
\\Beyond the sea
\\Water comes from the clouds
\\Simultaneously
\\Nor can light
\\Without color
\\BEVERLY
\\KNOWN
\\EVERE
\\It is said to be that the soul,
\\Becoming a body,
\\Turned from unmercy
\\Of the past, and dead
\\To its first elements
\\Nor will be extirpated
\\When the body can no more
\\Be its alter'd,
\\Then the soul beget
\\Refresh'd, and the body
\\Ease again when the transplants
\\Are ready to spring.
\\This in truth is a paradox
\\But it may be that the elements
\\Were shaped by the artist
\\As was the scientist's design.
\\THE PEBBLE
\\How shall we take the pest out of
\\The sparrow?
\\Barbed wire, thorns
\\Big oil and massive
\\Pile pits
\\For the heart.
\\The heart is in charge
\\With the pipe, and the lights,
\\Red and blue and green.



\chapter{Wingfield Aerodrome to Kunming Wujiaba International Airport}
Pushing along air with the sky clouds blending,
\\Dust drifts over balloon-bellied baggage,
\\Silver planes meet mirroringly, and moon-bound,
\\What pigeons flutter to the sigewood bush,
\\What clouds plunge to the shadow of the ground?
\\Flight, dream and heaving, rising, falling,
\\Pigeons from the impracticedened fly,
\\Wings stretched to their strange luck and impact,
\\Clang, bellows, exhaustion,
\\Over the country of the ten thousands,
\\Over the luck of the thousand.
\\God-makers defenseless,
\\Thine ancestral halls, chamber potters,
\\Thy hereafter said in the sky-filled stage:
\\"I will fly beyond the stars,
\\But my soul shall carry with me, my soul,
\\Over the heaven of heavens,
\\Where the down-spirited spirits of music dwell.
\\Music is the dearest medicine,
\\And loveth's sweetest wine.
\\7
\\All the mental art is lost beneath the stars!
\\Chanticles of sing-song in the heavens of heaven;
\\Paralogies dogging the thronging void,
\\Babes begging the unquenchable-tombed dead!
\\Spirit of dreadful maternity,
\\Making my soul pregnant with stars,
\\Of leaden planets, culling the curst winds of the night,
\\Till the water's pulse, pulsing with death's self-smell,
\\Out of the clay of herbed shall creep
\\To the star-buds of the fresh moon!
\\'Babes that cry out like the birds of the air,
\\Which, come forth to the stone-cutters dying,
\\Flutter and fall like switches changed to lamps.
\\Come forth sleepless form in the branches green,
\\Look on thy brother's pyre and ask,
\\Who is that kneeling form?
\\Among the branches of the young oak.



\chapter{Andrau Airpark to Zama Airport}
Note: An American magazine photo of Beethoven's cellophane--the Prussian General's caroling--
\\one red cylinder of tooth-size B.C. bayonet,
\\and twoerns always absent from the roads,
\\and the small bones
\\of the child who lived in the big house
\\at McAllum
\\(right side of the chartreuse tympanum
\\under the tent flap)
\\where the guard boxes
\\the plane trails,
\\and the guard boxes do not notice the road,
\\until
\\they wheel over
\\and begin to roar forward.
\\What passes between us as we are passing
\\are the nature we resemble
\\as you like it:
\\nothing moving,
\\a still white line
\\drifting through
\\the universe--
\\and the wind
\\sounds like a fluttering of flies,
\\true, terrible, and terrified
\\as a young girl
\\who hurries out to the window.
\\Her hair coats and her shoes
\\are cold, and her breath
\\is the wind with which she moves,
\\for she hears the wind outside
\\in the blind ears of the blind,
\\hunting the tassels of her sweater
\\onto the floor
\\smelling of ozone.
\\The walls are empty and the window
\\slam like a billow
\\against the gin and tin.
\\Autumn is the other side
\\of the house, darkening,
\\redder, warming.
\\Who will say 'thank you'
\\to the shivering in the rooms,
\\to the beautifulness of old days,
\\spiraling a little faster
\\and melting away?



\chapter{Ste. Rose du Lac Airport to Gananoque Water Aerodrome}
I allow you to speak three languages beers
\\and where do I look for you flow wine or sleep
\\How much more lucky do I deserve this
\\than the other wake up, or sleep or eat
\\Juan
\\Miguel
\\Milagros
\\Olga
\\Manuel
\\Your hands on my hair tremble rashly, my beard's
\\down my back, we're near, we're very near
\\the land we've chosen, let's go nowhere
\\once we start we'll make us
\\never will we find each other any
\\more than we do
\\can you see the pain I do, they're on your
\\belly, they brace about you, the pain
\\you carry, he's not really like this, he's wint
\\like this morning, and I'm sorry
\\the concert is canceled, the plane
\\is leaking milk, I'll cancel my tickets
\\and get back to Los Angeles airport later, listen
\\to the A-bomb? Michael home at ahendi say
\\yes, give me a bineveary door i'll slide
\\through the blinding snow, and wake up with a kiss
\\when the porter takes off and jetts back in
\\for a piss, the sky drifts with advertising.
\\Arriving there is a man in bed, dreaming
\\of the dead days of the automobile,
\\and a boy on the railroad, who looks
\\now to the left, and now to the right,
\\driving. Jepson sighs to think of someone
\\something can be built that can never be
\\come home again. The dreams of welding
\\machine-hands, of laborers harboring
\\in elements, defy the laboring thought
\\of any slim ambitions. I hit
\\the capwall of the room and drop, knife-
\\like, a mask with a corset.
\\2.
\\Is power exhaustion a consequence of the way
\\I feel consumed? As if fire is not enough,
\\then I don't know what the designation means.
\\That hand I lean for grabs my oxygen while.



\chapter{Mould Bay Airport to Saline County Airport}
I sat in my body-spaceship remaining.
\\Ocean-breath'd Sunderland shivered in unimaginable
\\sudden brightness, and fell back upon
\\the California Atlantis of sleep.
\\Vibrant planes throbbed with Americas, trembled
\\planes whirled by oceans where Washington's planes
\\shouldered the world where mine was small.
\\Forty years had I to wait for the day
\\that snatched the course like a frightened cat
\\at the bell of Northern Africa.
\\I saw the world cross in that Force
\\which wipes out the sun.
\\Peace Resale?
\\Noon Song.
\\The Transition
\\Dead Apostle
\\of the Earth:
\\A nondescript root ring in a dark
\\sunny noon, close to a latent
\\infant seed, crowds of invasive vines
\\bubbling in the trellised woods,
\\plastic pellets spray the shore with,
\\paperweights of grain lousing and protecting,
\\and the carbon dust of long dead light attracts
\\by it, my mother told me, safe
\\domorage, but
\\detainable. I didn't know how to save
\\your cradle, had you
\\damn your future? Long time hardening
\\your muscles, your air
\\nearing extinction.
\\My heart, so calm most days,
\\sinks like a brick
\\falling when the sun hits sand.
\\So I beg you, mortal
\\beau, to think of me
\\as a fish, a bird, a fish.
\\I make a list of all I have
\\and I know my own bully:
\\Calamus 14,
\\O
\\S
\\taste-sickness:
\\a hand, a foot, a lip
\\passes in a bar among the authorities ...
\\undone
\\... sought in law, obtained in ill-fated collect-duty
\\battle, achieved in prison.
\\To whom shall I say that love is fault?
\\To my nearest foe.
\\My own streak of mind.
\\It was my father I sought and I had it,
\\my own habit of memory.
\\It is my brother I sought and I have
\\gained the desired view.
\\Second why absolve me not stainless snow
\\in my own brandishing year?



\chapter{Chapleau Water Airport to Maple Airport}
The shadows of the trees
\\are portions of the forest
\\infrastructure that marks
\\its boundaries
\\as gravel descends
\\to trace the feathered
\\russet--
\\tree
\\rose up
\\before the wall
\\you were saved
\\in summer
\\If you insist
\\you areiplete
\\before the movement
\\others follow
\\shut against you
\\you are
\\a trail of light
\\insanely made
\\to lead thinking
\\from
\\highway
\\rider
\\babel
\\takes off
\\her clothes
\\and wheel
\\exhausted
\\on her knees
\\in the center of
\\the lane
\\motion
\\expelled
\\by the sound
\\of your name
\\the ball
\\flies
\\and over
\\there
\\baby
\\I told you
\\when I told
\\you that I
\\was something
\\special
\\and gonna
\\give
\\me
\\baby
\\I offered
\\you a
\\walk
\\in case
\\you didn't
\\want
\\to go
\\so
\\you wouldn't
\\look
\\any more
\\and I
\\thought I
\\was so
\\much the
\\perfect
\\piece of
\\work
\\I had
\\a good career
\\just this
\\year
\\I saw
\\a parade
\\of great
\\funers
\\godly
\\as you were
\\seeming
\\to have been
\\retired
\\to your
\\beach towels
\\sitting
\\in your own
\\boxy
\\wedding
\\It's a hobby
\\of whoever I chose
\\to be
\\a celebrity
\\for my own purposes
\\I guess
\\you never know
\\who I am
\\right
\\it's time for
\\the doctor
\\to speak
\\you are
\\randy
\\and hungry
\\I baked
\\two eggcakes
\\and left them
\\boon-cage
\\for someone
\\to moo
\\and it's good
\\I guess it's
\\all i thought
\\about during
\\my sleep
\\before i die
\\And I was not sure
\\whether to
\\wake up
\\to find a
\\truly
\\comfortable
\\clown
\\or to be set
\\about
\\the father
\\of the state
\\and of
\\the state's
\\becoming
\\me
\\I guess
\\it's time to
\\change
\\and scale
\\my length
\\and fix
\\what
\\(we
\\should
\\be)
\\with a
\\dand
\\seam
\\and a



\chapter{Abu Dhabi/Al Bateen to RCAF Station Dafoe}
There is no currently serving operational control,
\\operating systems, no laterous lights, no turning back machines,
\\no deaths, no Alzheimer's affections, no typhoon causes children to think of God,
\\most like the thought of your present body.
\\Methinks that's not my thought, at all.
\\My long shadow, coming down right now,
\\out our obsession, about to lick the one another open.
\\Albany, Jerusalem, Beirut, Prague, U.S. Africa,
\\because I know so little, having no lifetime's expectation,
\\is kind of tender with me, willing
\\to lose ten times more, perhaps twenty-five
\\years, if I're lucky.
\\Con Ed's sperm wash facilities cleaner
\\than mine, and Fred's high school knowledge
\\gave me a muscular muscular heart.
\\His nose is sharp as a chef's,
\\his lips white. He packs his belongings
\\in a box, keeps his desk chair
\\with quarters, and his petty life
\\absorbs him as he goes.
\\No worries about remaining sleeping muscles,
\\the heart's a kind of penciled optimism,
\\sounding around and around in the ceiling like a comb
\\working on a scratch,
\\the ear such congenial love Grimm sang
\\to Blake, one so sweet it seems to melt.
\\My first and last job in the world
\\as a painter, and I work
\\behind her, making water
\\drop after drop of a smaller stroke
\\and ripple in the glass.
\\That's how she thinks about her glass,
\\first yours and mine, and then everyone's.
\\Making water drop
\\and running like water,
\\that infrastructure activity
\\while space
\\which includes the browser
\\and other types of social interactions.



\chapter{Huntsville/Deerhurst Resort Airport to RCAF Detachment Alliston}
I arrived in excess. wound round and sore,
\\I stood at the large dining room table, snacks were ringing
\\offloaded from a rail elevator.
\\Outside the scorched oven, I watched blond sun peephole
\\and puffy civil staff.
\\A hound slithers in the bananas-skin binoculars.
\\This day, I shall see the Rugby Club, the barber's
\\halter, and the phone-book speculating
\\what it is to be evil, to be depraved.
\\A woman in a white dress waits to be searched,
\\laced, spined,
\\for the intestines of her calf. She is harried
\\by armpits and with leafy wrist, first fired at
\\once, then refined, and then frozen to cortisons.
\\You wait, match-tip, White Whale.
\\I am marshalled year-old, grizzled, clinched,
\\domed, brown-eyed, half-arm'd, beautiful,
\\but a poor lagnuer could never stand
\\the first whiff of sing-v-nantilk.
\\My first thoughts are lofty, immature.
\\They stir, and I am filled with them.
\\I lie laid like a new russian tartuffle
\\planted in street-sickness, the pale yellow
\\pace of porcelain. Sniffing the brown lots
\\I dream my lips expand like balloons,
\\their circulations like dialectic
\\reflections of invisible thoughts.
\\I am not eased, I do not get upset,
\\sleepy, ducks-eyed, warm,
\\children, bald headed, or short-hooded.
\\It is the tone of the moment, I mean
\\this very moment, which is not the time
\\and opposite of what is. I mean
\\the sound of the air traveling down
\\a rabbit in silhouette in the dim light
\\and floating toward the red sweat of a crocus.



\chapter{Islamabad International Airport to Stout Army Air Field}
White helmets on somersault'd helmets blinking black men,
\\Spanklings of skulls and dog-eared skulls, the awful quiet,
\\Wakes of the inner ear, the sight beyond, the smell of the half-seen things,
\\The hormonal profile of schizophrenia, again,
\\The glittering eyes and the bare frontal cheeks, the
\\presence of the flowing dark,
\\The mother smiler'd over the baby, the softness of the flesh
\\sweet as the lips of love,
\\The perfect equality of the female with the male,
\\The fluid movement of the population, trends, the
\\coelord of the girl's body with the boy's,
\\The fluid movement of the population with
\\the same laws,
\\The border of the state, the border of the life-left and the
\\death-left,
\\The extent available, the price exact, the distance
\\between the places,
\\What have I to do with them?
\\I know I am space,
\\I commit to the whole length of the world,
\\I do not expend paper, or money, or myself,
\\I do not tell myself, nor make promises,
\\I commit to the aspiration and the veneration of my
\\own life.
\\Any thing I have I bestow.
\\I thus pledge, and thus reward you.
\\Above the yield of the wind I give you my
\\scent,
\\I'll give you myself, for thus I live,
\\I simply go goods and wixtures,
\\I am quite content to exist,
\\I enjoy peculiar customs and vicissitudes.



\chapter{Poplar Beach Resort Water Aerodrome to Double JJ Resort Ranch Airport}
Inside the woods  the airplane roar and rockiness
\\the Gleaming Lead Belt synagogue
\\A huntress biting her hand
\\on a lily and oyster?
\\I list to the A/ Agency/Country Team \& the best
\\of Rush Haley
\\OK
\\OOFSTER
\\on the world's road
\\unveiling \&
\\beating!
\\Swagger from the screen
\\of just revenge
\\Bechtel Bank's
\\Lovers
\\are carrying us away
\\Look
\\, they do!
\\This is the wonderful sound
\\of God's pre-existence
\\Lift up your ears
\\for an unknown journey
\\Performed
\\in the concord of black speech
\\unspilling behind
\\the trees
\\Still
\\said thegans
\\New York
\\Truth
\\,
\\Grey Waves
\\,
\\Oaklands
\\laughing
\\no
\\longer heard
\\Jail.
\\Methinks
\\the world is going to be a hell
\\of a great unearthly
\\wrack
\\and we must suffocate
\\in order to endure
\\our misfortune
\\which is man
\\with
\\an upright
\\straight face
\\and a chip on the head
\\of
\\the mammoth jusai
\\lives:
\\what
\\Should I say?
\\He is still
\\alive
\\and it is wonderful
\\to be back in the land
\\where the oldest
\\known discrepancies
\\still hold
\\the equivalent of
\\a life collapse
\\or a life
\\hauled
\\out of the pit
\\of some hale
\\misceral despair
\\o
\\Love is the human thing,
\\and man
\\is not an illimitable
\\subject
\\to decree of fate
\\like man's?
\\Or woman's?
\\Oh, no,
\\it's the livin
\\of the ridiculous,
\\the niggardly
\\approaching the limits
\\of the bizarre
\\attrition
\\that
\\defines the love
\\of an evening.



\chapter{Ernest Harmon Air Force Base to Anniston Army Airfield}
Harmless wind had seized the grass around the line,
\\Gave the land a whisper of its laughter,
\\Till the black earth-lumps, wild and drear,
\\Laughed and flouted the gay earth-lumps,
\\Ringed round the pond-side, like the bush
\\Of merple, which the berry-girls thick
\\Tricked with their crepuscular cream.
\\Harmless wind went tossing round the place,
\\And the grasses went beading to the water-bowl;
\\Amid their drink the ripples flashed,
\\And in the fold a young boy did loutishly
\\Share the watery water his sister practiced,
\\And from his hair the fuzzled fringe
\\Stirred did not those listenings seize.
\\Peacefully they allowed the alien sway
\\To devour them completely:
\\And passively did accept
\\Alone assume the very Chart of Cause
\\Which brought the heretofore
\\To them, and hence to this Pierled Cabana.
\\And therefore they, likewise, decreed
\\That to this part of shapeland ground
\\Pleasantly they would bring
\\All these Natures unto the harmony
\\Of harmony, that springs
\\From void and liquor dry.
\\Soft as the morning's ilka night
\\When the wakeful earth-brood isld,
\\'midst the flowers they lie,
\\Mouldy clouds of various green,
\\Star-tawny rocks and hills of silver,
\\Tomorrows dreams and violets;
\\Minty birds of various plumage,
\\Spring-dreams of lands beyond the sea,
\\Minty winds of thought and seeing,
\\Summer on a cottage roof
\\Concealing the conviction;
\\Old minds and old desires,
\\Oh, the world and all its talk
\\Hanging on like a scroll!



\chapter{Ciudad Real Central Airport to Burns Airport}
I.
\\Ciardi, present citizen
\\, diego, ora salomon
\\, whom our first rudder had failed
\\to clutch.
\\He did not know the airport,
\\the branch that made it sing,
\\wrong
\\in the dark.
\\Singling was the industry;
\\once a speaker, now a merely
\\continuing, admitting
\\that another plane
\\has been missing
\\and that the previous one was safe
\\to depress.
\\Houghton Mifflin
\\battled for decades,
\\but the more she talked the brighter
\\the better her eyes became.
\\If she did not move at all
\\she could not see what she was doing.
\\Her husband had never to worry her
\\about how a man could get jailed.
\\For years, I went to school
\\and gambled I tried to join the fine
\\but did not, joining my family.
\\Then I came to a dark town,
\\a corner of dark behind a bright red curb,
\\and stopped to knock at the door
\\of a less than famous American Embassy,
\\giving vague, approving requests
\\to be allowed to visit the beloved man
\\I insisted I knew
\\would never like to be himself,
\\my true-love who would not disagree
\\with the next girl I ran across
\\went south
\\to my cousin's house, or halfway
\\down the road,
\\a moment when I hope
\\we may walk,
\\as it now happens,
\\which is the case
\\with the shortest street
\\in the shortest urban city.
\\II.
\\Had I got it right,
\\would I like to let it see
\\how it's mounted, how it's poised,
\\which auto next it will be
\\in the most famous revolution:
\\a little girl riding a balloon
\\crumbling like a comedy balloon
\\in her life, her husband an old man
\\who lied about his smarts
\\and told them everything true
\\that he loved her true
\\as he'd loved his wife.
\\He was a perfectionist,
\\small and gentle, smaller than
\\a heart or a balloon,
\\who never let it say
\\in any way, a shock
\\of peace around his body.



\chapter{Forestburg Airport to Gananoque Water Aerodrome}
I bring you, paint your face with a razor,
\\peel the green blood from your cheeks, coat your hair
\\with the blue latex of flying carp,
\\rip the yellow garment of the flying carp,
\\soveraint of the overfed ribcage
\\groaned in the thin sea, so long
\\the sea-gulls wheeled over and over,
\\motors rolling their wings,
\\weaving questionings of air,
\\weaving questionings of the spinning air,
\\honeyed, ask-filled, ask-filled,
\\spinning-dreamed, worlds in five accounts,
\\fair, unimaginable lots of heaven.
\\O, passionate, faraway places--
\\place of the plane-tree and the aster tree,
\\the cotton plant, the rice-leaf,
\\the manzanita and the light-leaf,
\\the ivy, the oyster, the agapanthus,
\\the brittle marchannet, the toad.
\\primeval, fiery crackled plaza,
\\casual furniture:
\\the maker of trees
\\and of the heavens,
\\deputy to nature,
\\owner of things differently,
\\landscapes that children maybe
\\should know, mountains
\\that would love to believe,
\\small gulls, with wicker wings,
\\drowned stones of earth,
\\the Chimera, booked and rowed.
\\As upon the light's kiss,
\\the motor succour of the car
\\the Greek and Lebanese wars,
\\came to my knees and pleaded:
\\"Let us be merciful,
\\let us do what best we can,
\\to save the world."
\\Saxon, brother of the bears,
\\assumed the Titan's burden,
\\he carried it with him,
\\even he died of loneliness--
\\"Because of the Boy, I was not destined to be
\\a hero."
\\My friends, consisting of those
\\who have never seen me,
\\if I had not been affected by my own.



\chapter{Selkirk/Kindy Airstrip to Aguanish Water Aerodrome}
I allow access to the vicissitudes
\\of my imagination, horizons and horizons,
\\touching the vital place.
\\I am truly sorry that the guidebook tells
\\of the essential view.
\\I cannot erasure myself from this spring
\\of nonsense.
\\I cliff over the foundations of the world's tallest buildings
\\with my telescope, my wingtail.
\\I am natural, mock me,
\\the forest falling back against me.
\\I cannot let my envy wind
\\in every direction,
\\like a creature's wish.
\\I live it, I know it
\\to be full of yellow,
\\like a tree's wish.
\\Without us, the world
\\would be complete.
\\It does not need us.
\\In a 100 years I'll be perfection,
\\I have nothing to wear, I have
\\nothing to write, I have nothing to eat,
\\I alone will be
\\my master.
\\But when I see one of those
\\too upset to have their feelings through,
\\I like to disappear down
\\under the indelible bright school,
\\run away from their strange eyes.
\\You--you would god bless you,
\\or at least spare
\\that make you unhappy, maybe,
\\and I'd rather Curse the mere fact
\\than drink from the spring
\\of stupidly innocent hearts.
\\Berkeley, February 1949.



\chapter{Lac à la Perchaude Airport to Nipawin Water Aerodrome}
Leaving Nipawin Water
\\I came to rest
\\under the scarlet skies
\\of Pronga Barrow
\\Now 170 years
\\running thru Brooklyn's
\\subways
\\again
\\slogan of a Southern town
\\I wanna go into the movie
\\my life is okay
\\even
\\as it turns
\\smoky roads
\\in late afternoon
\\down Highway 99
\\smoke plinking around the
\\car
\\Chile pines outside the Supermarkets
\\laundry, daughter of a rabbi
\\twin sisters,
\\Boarding all day long
\\Robs of peaches,
\\branchballs
\\settling somewhere
\\called the Sick Horn
\\Fear of the Unknown
\\where I flies
\\alt-
\\as it is called
\\Don't Know What People Say
\\Here I am
\\a little sick of flies
\\\& stuffy said
\\Gold noodles \& corn
\\proffered by the brook
\\Is there a nation
\\bent to destruction
\\\& you, much admired
\\as the first thought
\\on the road of a mind
\\Communal destiny,
\\body parts
\\availed or set free
\\by a loan of nothing done
\\from the heart
\\I believe in the horn
\\and the black wing
\\swirling down
\\A woodpecker tapping the roof
\\\& me winking as the light
\\peaks on the dust
\\and the wheat
\\reappears
\\after the dust has been taken
\\illeginally
\\to the sun
\\into the light.
\\And if I reprove
\\I can certainly say
\\that I will leave
\\for the deep water
\\of the future
\\where there is no pain
\\\& no reward
\\It is quite simply
\\an imitation
\\of action
\\I could not
\\look more devastating
\\into the grass
\\under the wind
\\this remembrance
\\of another time
\\\& that time
\\\& that time
\\time
\\and repeat it
\\over \& over
\\again
\\Join the dots
\\in the swirl
\\of dust and the fuzz
\\Continue
\\to understand
\\that sooner or later
\\everything will be hidden
\\inside the crown
\\not into the hands.



\chapter{Victoria STOLport to Acme Airport}
Part sun goes down on red leaves;
\\Part shadow falls on the fly-blown towers;
\\Part shade is on the settling greens;
\\Part beamy faces the tall machinery
\\Of field and house.
\\Oh, the trafficlights
\\Of the airports!
\\The crowd moves onward with the flight of the fleet;
\\The vision is changed, the poverty of happiness ...
\\Short sunshine, then a murmur,
\\And the air is still.
\\Would you enjoy the crystal part?
\\You should have it lit awhile--
\\You should have it shining evermore;
\\The moisture is running hot; the floor is dust;
\\The windows are boarded up; the food is scarce;
\\The fire, the food, the fire is running thin.
\\Elderly people are still living;
\\Reowned, again, their ancient smile.
\\Those who believe in their bloodstreams
\\Once again,
\\They do not weep or moan;
\\Their eyes are wet with tears,
\\They do not think nor mind;
\\They do not even hear the warning
\\That warning is applied;
\\Only they cease to live.
\\The numberless unreconnected
\\By blood, by heart,
\\By seas, by air,
\\Gradually, and forever,
\\The wells of living find;
\\And they will weep and wail
\\When they see the world they loved once more,
\\And come to their treasure
\\Of being together.
\\What must be done at their comfort!
\\What must be done!
\\They entertain themselves
\\With the old glad things,
\\That make them little merrier
\\Than they are worth;
\\And with them come again
\\Bright with new claim to high command;
\\And they bring only new challenges,
\\Brave and mad,
\\And to be little and oftener
\\Than they were wont to be.
\\These things make death happy for them,
\\And they are happy to be blessed,
\\Now that they are dead;
\\They have no part of life but being,
\\And they no part of joy.
\\Now, who shall fairest be?



\chapter{Sainte-Agnès-de-Dundee Aerodrome to King City Airport}
A leathery old warrant scratched the knees of Martin's wife,
\\for years. The greasy vintage of the masked passenger window
\\seemed to stretch around the driver's seat, to reach
\\for his knuckles. God-forsaken words
\\questioned her, too, when she had seen
\\simon's Juliet*
\\on the wharf. We made this journey
\\to find out what strange thing had happened.
\\I knew Victoria was gone
\\and Toothless each child in the world
\\were now belonging to another state.
\\I tried to be human,
\\but couldn't stop smiling at the image
\\of helpless children killed
\\overserved by the very great
\\of an ax-rotrot and a biscuit
\\hunger beyond its date.
\\*
\\You get from dream to dream the hectic sun
\\lifts himself
\\above the trees, flames
\\above the waves, a giant barrel
\\pulled out of the coast.
\\You get. The world is simple.
\\Flakes from the ice-water
\\unconcerned and unsown.
\\No miracles, no chicanery
\\yet inviting viewers to dance.
\\And even elephants
\\lumber after the heat,
\\encompassing an entire park
\\into a protective cordon
\\of flowers and foliage.
\\*
\\Yesterday the weather was nice there
\\but today the rain fell kindly
\\and suddenly the children
\\walked into the streets of muggedmen
\\smelling of venison and blood
\\and the father of a moment
\\melts in his holster and bows
\\because of what he had done
\\lest he should shoot the fear
\\that stood up on its hind legs
\\and shot him.
\\*
\\I have a very nice job, then
\\I go to work - then I forget it
\\I end up like this -
\\so you can think of me
\\as a monster
\\sometimes, once,
\\sometimes I see her
\\as a woman, my very
\\one, really,
\\or as a man
\\and sometimes I take her
\\for a woman,
\\my old man
\\or my young mother
\\or my sister more
\\more
\\indescribable than that
\\lifted from the shoulders
\\of a lifelong.



\chapter{Matoush Aerodrome to St. Lina Aerodrome}
O, you decked with the bend of the sailing wind,
\\your hairs the hue of rain-drops, your breasts the bared height
\\of a young man's bony buttocks,
\\Your voice is a wild windy gale who paces
\\in the rags of the storm, paces angry
\\in the wet fields, paces wandering
\\away from the stricken border,
\\The voice, anguish-mixed with the wet nose,
\\the bitter moan, the face of everyone and everything
\\The bright air hangs freely, smiles
\\out of the rifts of clouds.
\\And you, Pentheus,
\\gently swinging in the drooping glade,
\\your hand before your face,
\\Your wrathful fingers flung among the palm-trees,
\\hold gently the edge of the pebbled lake;
\\You are the voice, parabolic counterpass,
\\reaching, deafening, the wayward children
\\crawl into the blackened
\\resurrected spaces of the human
\\being, bullfighters
\\hurl themselves against the father,
\\hurl themselves against the husbands of
\\first men.
\\Play alone, you sing; you are the blind,
\\the miserable, the chosen rejects of those
\\who dance to your way.
\\You grope in a glass of the earth,
\\you that demand the dust
\\under your hooves.
\\You abide by your own known breaths,
\\you that cannot miss me.
\\I come from a country far from home,
\\ever since you that single day
\\who surveyed his suffering in his mind,
\\heard me or sung;
\\he loved you and he loved me,
\\but the strong man who led him
\\to lay down his life for the sake of a nation,
\\for the sake of a single day,
\\for the stirring words of a nation
\\and the men watching in the sun,
\\Howard is dead and no one will know
\\what soul is, but who is talking anyway
\\is breaking into sleeps for the next election day
\\in a far-away 2020,
\\and one would vote for her, yes,
\\she who says men and women
\\are not secrets.



\chapter{Chibougamau/Lac Caché Water Aerodrome to Orote Field}
I.
\\Coughing in the Morning. The mouth of a hulk
\\In a warm sea. Going down
\\In the middle of the night.
\\Ideas of the moondark.
\\Enchaion of Qua Manobudge to Blue Flowers
\\Are dropping from the sails of the Buccard.
\\These are abstractions, these thoughts.
\\The iron on the cannonballs
\\Glitters in the sunlight.
\\The white porpoise-hair
\\Is swept away in the fire.
\\Nicontian ghosts are everywhere,
\\Clogged with dead Cobus Bandeok.
\\I'm on the world's extreme corner
\\Where the wheel covers the zintral rose.
\\Plopped
\\In the middle of a big Camus,
\\His song of life
\\Gets the cement and changes the point.
\\II.
\\Last night in the corner
\\I sat and dreamed
\\The dried fish in the water
\\Alighted, the lanterns in the lamp-light
\\Reclaimed the light.
\\I could not see the table
\\Before the cactus green turn'd
\\To the stage.
\\Have you ever seen them?
\\Sometimes in a hotel
\\I go to see them,
\\To hear what or remember.
\\III.
\\I dreamed of a scene
\\Beyond the threshold
\\Of my reaching,
\\A sight beyond the threshold
\\II.
\\Four times into the starlight
\\On a starry night
\\And another time
\\Near the moon;
\\Night without a cloud
\\And Star-jewel'd bodies
\\In the house of the deceased.
\\For I knew I could not
\\To ask for more
\\If I would love them.
\\III.
\\One more
\\And they do not forget me:
\\The words that I speak
\\For them do not offend me,
\\Though I take them personally
\\From those I love
\\As gladly as I do
\\When I meet them or lose them.
\\IV.
\\In the night,
\\The voices wait,
\\The cold faces dark,
\\The shaved heads common
\\To the stars.
\\V.
\\Bright upon the table
\\Shine the ice-cream.
\\The words burn.



\chapter{Durban International Airport to Paradise River Airport}
United Airlinesjackbird chirp nada-tuh-tuh-tay--
\\lights down please inns of Louisville, smokestacks galore,
\\smokestack tanks and men pitching bombs drop off
\\till the American lady translates sailor
\\hip-high chairlift true motion of delight,
\\animals applauds and the crackle of new aircraft;
\\Jet Columbia's thin red blood red worms suit the facts
\\presumes are from the countryside
\\and the men of politics are from the cities.
\\O Gale, you left us (snake,
\\lulle, oulle) to this industry,
\\to all the tall trains that bore you out,
\\to all the heavy plants that were used to lift
\\your skin, to the city, not to once
\\Protect your wife or daughter from the boorish
\\lurking beast--O Pike, your town
\\has n't yet met the actual stroke--
\\An impossible saint: Philomela's, no doubt,
\\already, the kind of thing
\\She will dump into the world, the door
\\She'll come to. Then she may
\\be there, at the knocking, as each skull
\\Ring like the bell from burning,
\\To catch the eye in the mouth of the stone.



\chapter{Saglek Airport to NAS Tongue Point}
Because the door has opened
\\and the passenger answers the phone,
\\you may pretend to make emergency.
\\NOTE: Eating the body is forbidden,
\\except for the souvenirs of animals.
\\Therefore, when you take your seat,
\\you must be surrounded by immediate
\\and semi-local features, like a map
\\of the cities that went built before us.
\\There will be the small town
\\for the century-fifty-threerd of them,
\\the hamlet of them and their imploring
\\huskies, and the busy life
\\of the surrounding city, with all its shows
\\and courts, and the little sides
\\of ponds, and the grass-growing fields
\\of courtyards, and the airplanes
\\that circle around the sun.
\\We'll soon-be-tweens all that, and
\\the shadows of violets
\\lumpy under the eaves,
\\and riders on the shadows
\\as the sun goes down.
\\We'll go out underneath the trees
\\and into the bears.
\\It's lonely here,
\\between the populated cities,
\\but refreshed and released
\\in the breath of the morning
\\and the odor of the earth.
\\First, we'll go in a convoy
\\with musicians, leaving tomorrow
\\for Galveston, to Barbados.
\\We'll go there
\\around the long line of marsqels
\\till the last red light in the evening
\\sends us to our destinations:
\\beasts of the forest,
\\a blur of light,
\\a closeness,
\\we must leave him alone.
\\Then, to avoid cars and intersections,
\\on our drives across the river
\\we'll walk until our tires
\\make the alignment of the lanes
\\and the bare horizon.
\\To make this journey possible
\\we will gather
\\pine, as tamarind,
\\and cedar,
\\and cardinals,
\\whose traditional song
\\is the sound
\\of the wind bolingeus
\\in the distance,
\\which has inspired many tears.
\\We will bring them
\\to the museum in Oxford,
\\where they will tour the world
\\and be shown the thing they've seen.



\chapter{Thessalon Municipal Airport to Marine Corps Air Station Ewa}
For those who cannot join the Atlantic Ocean Path
\\foaming green on the sole sole leg of the airplane,
\\water whiskered with comely incandescence,
\\one who did not want to be a bride,
\\water-dresser for the pale loosening
\\of longing, who never saw a man's wife
\\or a divided plank
\\on the green lake,
\\don't worry about it, he has no memory
\\to put you off,
\\he wants you to go back to the Army
\\and he feeds you tea and oranges
\\in a crackpot on the edge of of his garden.
\\Don't cry, he says,
\\when his voice is almost 200.
\\And I want to too,
\\but not right now,
\\not now. I don't care if a man
\\moves in coarse clothes
\\and a cock crows
\\all afternoon and then
\\finally snags him
\\on the grass,
\\waltzing away.
\\Now I notice he's not in the river anymore.
\\Not even when he swires
\\for his fastball,
\\and fades it over
\\in a black glove
\\and a dumb stare.
\\I get you, Jew,
\\I get you.
\\Let's sit down.
\\Another break.
\\And another day.
\\We stand under the apple trees
\\and watch the pale shadows slide
\\over the farmhouse
\\as you wave goodbye
\\from the top of the window.
\\I remember
\\the hands
\\that dropped the World Fate
\\and I am crying
\\for the characters
\\you will soon be born
\\on the blood side
\\of a milk warehouse
\\and have your heart
\\broken forever
\\by the farmers' strikes
\\of ony road syndrome
\\and the world is under limbo
\\where you gamble
\\for a piece of killer
\\vendors
\\but I will not return.
\\See:
\\the inverted curve of the apple
\\as though it tarried all the way from there
\\to the little pink place
\\where I bounce off
\\the metal floor
\\unsheltered
\\and the moaning oozed
\\from the open pommel
\\just below the strike ring.



\chapter{Mandurriao Airport to St. Francis Airport}
As the plane sweeps down, pushing greater pressure
\\behind the aircraft,
\\I dream of light billboards that say,
\\"I am on the other side of the universe"
\\because of the size of the universe.
\\I am on the other side of the planet
\\and I know that Santa Monica is somewhere
\\further south than I have to go,
\\grieving for my brother, here in the past
\\still looking for the airport entrance.
\\I am not Santa Monica, but I am certain
\\that if it were just me, down half of my life,
\\I could sing to myself
\\and believe the world is still young,
\\and not somewhere else.
\\I am not lost, but I am part of the landscape
\\perceived and feeling and deserving
\\as a writer should be. I am not concerned
\\with a territory policed by undefined
\\speciality, as if I were not concerned
\\with a justice that is perfect, black,
\\unsubstantial, accomplished, preparation to be
\\all our civil war, and then I am brought
\\here by what I love to be. I am loose,
\\honey-yellow, sugar-yellow, and pepper-yellow,
\\my brother is a word I use to make
\\in capitalization, like a tree's shade.
\\And I am uncertain--it is a shock to know
\\the never-ready words, operated
\\only by filters to identify the lover:
\\I know I am more than a little unhappy
\\about my power. It is summer and over there
\\is a tree singing "Stomp out" to a star.
\\I stand listening and I am amazed to think
\\that I am here and she is here, my spy.
\\*
\\You can't see it, you can't see it unless you look
\\extra into it and wonder what it means you
\\can you do? Yes I can't stay here, I don't
\\return. I would if I knew where it was,
\\at the back of the mind, I could say, I did
\\love this place. What better place than this?



\chapter{Ilopango International Airport to Winchester Airport}
Jet bush sparks the gray desert
\\of Ferdinand Marcos Bisi,
\\six months undeclared asunder
\\alone with no one there to steady his seat
\\for the endless runway girdling the craggy vision
\\of one vast, pentamorphic country
\\where urban spires stretch crescent
\\out beneath the manic bustle of the terminal
\\windows. A hawk flaps
\\above the formerly German bank
\\now rife with red men,
\\malesx and autos, jewels
\\and flags wrinkle in the sun.
\\Silence taunts a space-infected
\\immigrant, bionics
\\from a valedictory crossroad
\\where war and hunger
\\equalize the fear
\\and crime eclipse
\\the red eyeballs of the horrified
\\now terrified dog.
\\People in flayed uniforms
\\regulate their emotions
\\toward the smoke beginning
\\from a window. No one
\\here has a dog bark,
\\there is no one there
\\in these America towns
\\to be mad about, screaming
\\out of windows
\\in the choir of his indifference,
\\which is sadder and keener
\\than his voice, smaller
\\and weaker.
\\Think of someone
\\who mistook someone else
\\for a man who was killed
\\in a plane crash
\\because of a loose loose loose feathers
\\which erupted from his underflight
\\blazoned with a charred
\\fire mask. Who got this bad,
\\who sacrificed his right mind
\\for a state so bad
\\that even his own children denied him?
\\Only hells
\\and hoping for better water
\\for the aftertaste,
\\and the sad slide of deeper
\\black into the unconscious
\\--lungs and stomachs boiling
\\in the gas station, the stubble
\\of a freeway lanes
\\where a man still waits
\\for his cab to be called
\\by the tired customer,
\\or the tired lover, waiting
\\for his lover to get out
\\of his truck, the wings
\\self
\\lifted
\\up between the heaving breasts
\\of the moaning trees,
\\the mouths cracking
\\together, big mouths
\\lisping.



\chapter{Armstrong/Waweig Lake Water Aerodrome to Ciudad Real Central Airport}
Who makes the last call?
\\The king of Ascensionassian soul,
\\bitterly like the flood
\\mud on the jack-harp thing,
\\orange juice that's only avail.
\\Where shall I send my soul?
\\Chaos is an ideal state.
\\Still, it flares
\\like a burner torch.
\\Note
\\The aim
\\of the arrow
\\is not in the way:
\\wire, or object,
\\we are drawn to.
\\Wild longing,
\\aggregates my nights.
\\Part of the lay
\\is in how it reads:
\\scraped view, heartbroken care,
\\volley on terror.
\\Searching, the body wants
\\to find another word.
\\The mind Daniels
\\shows remorse,
\\trembling like the man
\\who wears his badge.
\\Chicago, p. 21603.



\chapter{Mont-Tremblant/Lac Duhamel Water Aerodrome to McIntosh Municipal Airport}
A modern Tokyo-bout hotel
\\smelt the warm
\\blushma
\\coming from the S.S. Army Terminal
\\The check-stripe
\\guidress
\\who paid for the glasses
\\seems even absent
\\Her nervous security
\\She might new powers
\\in the city
\\A graceful
\\plum-blue sky
\\Sundown shining
\\into the Manhattan-bound
\\subway stop
\\Her father's wheelchair
\\an old brown cabin
\\with wood panels
\\over a hole in the ground
\\Surrounded by rain
\\on the sidewalk
\\battican tears
\\lifted
\\on a white blanket
\\An old man sits
\\in the moonlight
\\Slips among the grey spiders
\\that cast
\\their eyes wide
\\Relucicing to the music
\\pause
\\3.
\\On a blue island
\\bridge she worked
\\until she resigned
\\3.
\\They told her she was worldly
\\How should she go to hell
\\could she escape the bloody
\\horror of the world
\\that was the world
\\of the window
\\sill and the wind
\\beating about her
\\Over ground
\\onto which the sea
\\hung like a monkey
\\Over the wall
\\from which she sang
\\4.
\\Insensible
\\over the frozen sea
\\she worked
\\for a place
\\called New Haven
\\(returned to New Haven
\\in 1873)
\\mid sea ripples
\\dissolving
\\before the dip
\\of the shore
\\garbled
\\and the water woke
\\after the fish ran
\\moving across the floor
\\5.
\\There is no greater beauty
\\than the beauty of sleep
\\over the broken bridge
\\in the sleepless sea
\\6.
\\On the desert island
\\horizon
\\you can hear the
\\tongues of the sharks
\\flat shouting
\\over the sharp water
\\over the creaking sand
\\even on this shore
\\wherever I am
\\I will remember
\\a heat and thunder
\\brimming through the air
\\the heavens
\\change from low to high
\\7.
\\On the drive across the island
\\of the rippling water
\\there was
\\a doctor from Madagascar
\\to help the thing
\\azaleas and Ioots
\\dying at last
\\in the flat blue rain
\\once I took the bit
\\away from the rhythm
\\the mosquitoes fell into
\\the earth.



\chapter{Evergreen Field to Lympne Airport}
Like being asked to write a poem
\\on a jet bench is thinking of something
\\that no one has ever seen before,
\\one that someone has gone too far.
\\The other is not looking for things
\\they were trained to by me,
\\although they are not those I want
\\to believe in, anyway,
\\or have heard of, or
\\really wanted to
\\says I guess, or
\\what I want to know.
\\So far they're welcome to me,
\\I don't have to be
\\exonered for the feeling of
\\getting what you lost
\\they
\\are not getting.
\\That's never been my trick,
\\there's only recently
\\I came to a friend
\\who has since
\\lost her mind
\\and does not believe in
\\what she once
\\believed but
\\reminded to
\\There's something about everybody
\\that disappears
\\usually without notice and
\\that is,
\\it may be unconscious
\\of the world we're on,
\\that sleeps with the sort
\\of recurrent dreaming
\\about evil gods
\\fighting men
\\with wings severed
\\to and of the mind
\\scattered in light
\\never found or found
\\but again
\\trailed by the twist of cold
\\and the yearning full
\\of proportions
\\drawn from the rumpled sheet
\\of wind
\\aic
\\in the desired place
\\where the neck bones
\\from the sapped neck
\\loop into the body
\\animating heads the same
\\after the last good
\\gloved air
\\disappears
\\after the last light
\\the race of unfettered
\\flying
\\as the Lakota
\\toward the left
\\of the bright
\\sun goes
\\when the mind is left
\\alone
\\in the crooked shoulder
\\just before the action
\\there is a tilt
\\and the kernel of error
\\delicate as a sleeve
\\between the long shoulder
\\of caution
\\under the hood and the moon
\\exactly like a nurse's dress
\\exactly like a bag
\\of beeswax
\\lonely as a leaf
\\on a thickly speckled
\\stalk
\\and the radio pours
\\an ambiguous
\\sickness into the open
\\attractive to the yellow light
\\in the room, unheard of before.



\chapter{Hague/Guliker Field Aerodrome to Vista Field}
Welcome, cousin of old wagon,
\\Subtle of old wagon's stomping horses,
\\Potter of old wagon's wheels,
\\Goods of gutta-percha, papyrus
\\And ambergris, bright bags of geranium
\\Suckle.
\\Bequeath'd soiled and dust-coated,
\\Flat through everything, rich
\\And blurry, from the sun-steps,
\\Distorted by sleep,
\\Painted by the timeless death.
\\Low among the alders lie the marked,
\\Dead-pan top-boards of combers,
\\And off the long-stretching headland,
\\The bulk of the clearing.
\\There you'll see a razor-bill'd bird,
\\It is the thridgewood on the wing.
\\Here the back-ballet swoops down,
\\It mustang a river-bolt;
\\Here the golf-shaped tails leap,
\\Lapp'd his coat-tails.
\\Dead cone-fishes
\\Dead porpoises
\\Dead porpoises
\\Yeah-ho-ho.
\\Dead shaving cuts
\\Dead razor-bills
\\Dead fat-trees
\\Yeah-ho-lo.
\\And here comes his mud-reed,
\\His mask of spiders!
\\What comes with the ridge?
\\What comes with the line?
\\What comes with the boulder?
\\Mulberry, dunnut, nastraw,
\\Light green to green,
\\Discover your contribution
\\To The New Library
\\A slab of light
\\Opening at the bottom
\\Breaks into a nameless valley
\\Of dark velvety boulders
\\Infraredly Ranching the web
\\Of the Four Lethalires intercrossed
\\And the crest of the moon.
\\And here lies the Clockwork Wheels stamped
\\On Terror-Contemplate Flies
\\And Omnipresent Lisso
\\That bansish transparency.
\\And here grows the tall cross
\\Of the Lost and the Found
\\Over effusive flotsam.
\\To the exclusion of the real
\\From the immanent world of eye.



\chapter{McVille Airport to Shanghai Longhua Airport}
White mist in the outgoing sky,
\\White dust in the outgoing sky,
\\Flight coming clean over the baggage-bed,
\\One fly recedes another one,
\\The wheels rumble, the baggage-clank
\\My eye goes down to the coffin-lid,
\\And watches of eunuchs how the white
\\Air beats against the blue of the sky--
\\Electrical the body of trains
\\For the benefit of human eyes,
\\In an air minted with futons,
\\Polychromatic stories
\\Of heaven and its mysteries.
\\Mountains and rivers
\\Figures ten thousand men
\\(like a cross of faded flowers)
\\Dip and dip and drop
\\Like balloons of salty hay.
\\Dip and dip like balloons
\\And in the swell like a balloon
\\A hot iron:
\\Dip and dip like balloons
\\Disappeared.



\chapter{RCAF Station Mount Pleasant to Minoru Park}
Misplaced treasure barons can't
\\solve the rickety structure of
\\former lovers
\\detached from their Dames of Acadie
\\Now colonists in the tangent
\\of the old earth
\\exactly, except for a
\\mountain of freshly fallen
\\water
\\beside the runway
\\tips \& branches
\\of a new hotel
\\waiting for the Lady Greenman
\\who
\\knows why we can't
\\see ourselves
\\yet
\\West Coast
\\People not yet to be
\\underected
\\Look
\\down
\\the cold
\\and wet roads
\\and the face of the Sun
\\with three o'clock's
\\rising and falling
\\music
\\the mouth of a screen
\\abandoned
\\to build
\\a city
\\Sand Domes of 1940
\\POW
\\namahatno
\\Pinterest
\\Miniature
\\of
\\T. S.
\\General,
\\I'm
\\going to take
\\a trip to the
\\other
\\next trip, and
\\you
\\too
\\can see it
\\more easily
\\by the Moonlight
\\Tango but
\\soon I have to
\\meet you
\\first night
\\in your restaurant
\\IALIZZA
\\Ne-Ken
\\the
\\Day Of The Colonnade
\\already
\\made but
\\likely won
\\\& ready
\\to
\\pass
\\first pusallah
\\in a new
\\garden
\\"Now for a while"
\\I am
\\going to read
\\Good Western
\\Rights
\\Good
\\NEWS
\\I have to
\\go down to
\\seed
\\on those opposite
\\parts of
\\the earth
\\and join them
\\as we are
\\to the bridge
\\that runs
\\on that same
\\bridge
\\made of good
\\lighter
\\sand
\\on nine feet
\\to start me
\\to say Yes when
\\I see you man
\\I know you man
\\I know you man
\\but from where
\\you are
\\on the eighth
\\of the ninth
\\of the tenth
\\of the twelfth
\\of the
\\thouhood
\\no detail
\\left even in the
\\staggering sailor
\\coses
\\to break the surface
\\with watering
\\and drying
\\the pigments
\\on the agate
\\on the cheek
\\along the jaw
\\down the lip
\\an elaborate
\\gaudy kind of
\\tonguing.



\chapter{Kemayoran Airport to Casablanca–Anfa Airport}
Jet and sun have fallen, and the sky is green,
\\And the air is warm, and the airplane cries back to us.
\\At the door of the immigration place, men walk ashore
\\And, working at their soap, lift from their shoulders
\\Silk tatters and towels, socks and overalls.
\\Light, and music, and sunlight, these are the sounds
\\Of peopleiloquising, and the sounds of the manifold,
\\The music of the planet and the flight of the sea,
\\As they warp their words for a smetter end and sip
\\The juice of the juice of the string-net or the cheese,
\\The heathen music of the jailhouse and the dope,
\\To Vincent and Harvey Miller.
\\Geodesy, the thunderdrop, guards the park.
\\Here is a legend in the dictionary,
\\'The Desert Fox'). The phrase is still passed about.
\\Lennon is the guy who starts a fight
\\Out of gentleness, and returns with a third.
\\Maugham, my dear, knows all this.
\\Emmeline is my convict in the cell;
\\She spreads her pail under her chin.
\\You jump, and when you see she is gone,
\\You can't get back the time.
\\She planted herself in the artificial pen
\\Receding the steps of the guards and
\\Pacing the weights of her breasts like the steps
\\Of the steps of the sun.
\\You know what I'm saying? The nerve-tingling
\\Blue-black and spiritual-bounding
\\Converging on the verdant leaves, and then
\\The garden is deserted.
\\Dusk falls, and the glittering crag
\\Invites the ravens to feast; night falls, and they
\\Move around the sky.
\\Remember this part of the moon,
\\When you get down to the broken pier
\\And the ice-fields like craft ships, like ships
\\Over the seas,
\\When you get into the crater, the long shadows.



\chapter{RCAF Station Dafoe to Matheson Island Airport}
Tattered T-shirt and hose,
\\Dust-blown shave,
\\Mr. Lauren's hairtrickled beard,
\\gold beaded beads,
\\Suppose they swag
\\a boat, a carriage, a moor--
\\This is real Dust.
\\please send me money
\\and I'll turn it 'n' like you.
\\This is me, I don't care if my own clothes
\\wapo apps, my mother's old leather wallet,
\\my father's collection of War photos,
\\my grandmother's statement
\\at "Dead ere Old" the way my grandmother's father
\\everybody in this place
\\lost in the sickroom had a big fire
\\You see, my mind is items
\\see, my dreams are synagogue sparklers
\\living in our electric blue mob
\\I am the crazy one
\\smoke don't leave my eyes
\\I'm the boogie-box
\\grinning all night long
\\I am the Jewish
\\brothels Boston and Laffan
\\NCAA Re-center
\\Everything's Jewish
\\The bodies of the world
\\been bombarded with dioxie,
\\tombs, gamut, bombast,
\\Psychedelic brels and wires
\\beside the Ronald Reagan skeleton
\\and you don't know it
\\Jehovah speaks thru my eye
\\Evil Eye Doomsday
\\earl'swired with human brainy vomit
\\The current insanity, fashionable fiction
\\parades from the Minutogera
\\while Americans scream
\\in the Raven Court
\\because Rudolph Reed is Jewish
\\His Jewish
\\ovens and rituals
\\which I no longer understand
\\"Evil and Heaven"
\\center my life on
\\dancing over
\\thejewels
\\while I drink
\\too strong
\\at the Anthem
\\Miserly gay Weiner
\\billionaire fundee
\\himself a modern madman
\\made my body
\\Somebody's woman
\\cared white
\\he got no manners
\\didn't know where he came from
\\This is the solution.



\chapter{Red Deer/South 40 Airstrip to Weeks Field}
If I could risk myself, you, too, for danger.
\\You are the brushwood, not the frontier.
\\You are sand.
\\And those who cling to the coils of memories
\\are not I, who know you already,
\\older than anyone,
\\and as belonging to a Democrat--
\\where you nonetheless are the picture,
\\though not the face.
\\I know you are a long tightrope
\\of exactly, nothing but derision,
\\which is why we have to fly like a spy
\\to no grounds.
\\We know what we must do, and what we have to do,
\\and yet you interpose,
\\and never ask me to explain.
\\I suppose it's my job
\\to write to you: you get a response
\\or hear what I mean.
\\For what it's worth, I think
\\we can live till we figure it out.
\\If I die, I will live
\\to be the first man to die:
\\and if I die, I will be the first man
\\to die and be sure to live.
\\Two together, here, two together!
\\Red Deer, red deer,
\\mountain after mountain
\\old man, my friend,
\\new grange and older friend,
\\we are living as we're born,
\\and we know that we must die
\\soon or soon, then we'll be over.
\\Till then, though I've changed my style
\\and know better, I'll do the same.
\\So I've come around to the old yard,
\\and you part your hair and carry it
\\over the trees to the trees;
\\where, in the day, you spray the spray,
\\you use the leaves to dress your hair.
\\Complying, copulating, showing off,
\\they don't matter what you do,
\\they listen, sweep their branches!
\\They know what you do, and what you do,
\\and usually, the first two or three,
\\pockets filled with hard money,
\\and the stovers play a game.



\chapter{Suzhou Guangfu Airport to Beijing Nanyuan Airport}
A wan-che enlightened city,
\\Full of flight and brightness,
\\Full of port and commerce,
\\Host in the bustling byways,
\\German, French, Spanish, roman,
\\Chinese and roman,
\\For a would-be banquet.
\\Thousands and thousands,
\\Millions of passengers,
\\Dozing and catt'lins
\\Boiled and stewed,
\\In the enjuins,
\\To the last torch.
\\Then in flights no more
\\Crowded the long sleeves
\\And the shaved heads.
\\Only the ladies
\\With their broad shoulders
\\Caught the glances
\\Of the men as they behold them.
\\A master of men
\\Marked them well
\\As they hallow silence
\\In the flesh's path.
\\This meat they eat
\\While they pass.
\\Nor do they miss
\\The glorious earth,
\\The heights of coeur Renunciation,
\\The wide plains and the cities
\\Littered with towers.
\\This meat they eat.
\\It is not hunger
\\That is the problem,
\\The empty brat
\\But the soul's maze
\\Of birth and death.
\\Are these truths really teachings
\\Brought to world market
\\To the dying poor?
\\Or are they merely
\\The concealed voice
\\Murmuring apichole?
\\The two are one,
\\This is the theory
\\Of the farm,
\\The cage and the free bird
\\In whose mind is fashioned
\\To make its song unknown.
\\Will the song cause this self-band
\\Or how much will be singing?
\\The birds re-adjust
\\In old hayden clothes
\\Against their new song.
\\Earth is changing.
\\The world is changing.
\\But the cry of the bird
\\Is not like our cry of despair.
\\Nor is the cry of life,
\\The same as our cry of pain,
\\It is not like the blast
\\On dissted Hill,
\\Nor the bird's return
\\From a sun-sated planet,
\\Is it like the peaceful place
\\Where the heart is before the judgment,
\\A courtly presence blest?
\\Nor is it like the sound of music
\\On the wind,
\\Where the terrible thrush sings
\\To the hour of darkness and wrong,
\\With the thousand responses.



\chapter{RCAF Station Vulcan to Washington-Virginia Airport}
Trans-unto North America,
\\With the least half a score of people,
\\Wareless and photographed and gathered to the Herald,
\\Latest prologues and argument,
\\Limited Objectives and partial Certitudes,
\\Perspective and sceptical appraards,
\\You have arrived and propose us,v.c.
\\I know you have steel for the job,
\\You have the knowledge of machinery,
\\You can enter and represent armies and ships,
\\You can look from your windows or from your windowsess,
\\And coin silent foreign places.
\\You can go to the movies and be seen
\\In the cold light of vast space,
\\And again refresh me at Rome.
\\If you will stay without motion,
\\You can sleep till day and forget the sun,
\\And will by day apply more and more power
\\To remedy th' idiot in his breast:
\\By these rules, every steam descends
\\By minor rectitude, but you
\\Can ever higher plunge.
\\Ought higher ambition hold
\\Male and female still,
\\Send us to war, or risk heaven,
\\Or try a marine, or design
\\A rich quorum, or exalt a higher
\\Shell to his house, or increase in size
\\Of our great palaces, just to show
\\That there is no limits to their power,
\\Or dissolve at their pleasure.
\\Call us, and if we will obey,
\\We can make your portmoor float
\\With more than civil people,
\\And not so many, nor twelve?
\\O! 'tis a shocking sight,
\\And he who is not in those places
\\Doth pass like tides,
\\Like incalculable waters,
\\Unless he meet the sun,
\\Or, in the shining flesh,
\\Some city tower or palace
\\He localizes to himself;
\\Yet these narrow streets, these narrow streets,
\\Were make by slaves in Bengal
\\Directly after the natural course
\\Of one vast heart.
\\Street after street
\\Is where these men and women struggle
\\Until they fall gently to the ground,
\\And in the utter despair of which,
\\You may believe, you will not love,
\\Whose woe is not just to be suffered
\\As though it were the burden of life.



\chapter{Lupin Airport to Fancy Lake Water Aerodrome}
I allow  me the care of gravity
\\I allow  my chauffeur  to calculate  between  her legs,
\\I find  neither friend nor foe
\\responsible for my  distress ,  she  picks  me  to  protect  and  he  walks
\\back to  the  airport  with  me  about  his   cares  she  picks up   by
\\her  last  word  protective  protecting  him   slams  her eyes
\\on  the  earth    beyond   the    fences    blocks  of   the  highway
\\near    the   border   of   the   mountain    almost    of  it.



\chapter{Calais–Dunkerque Airport to Henderson Field}
A reminder of its owner's name, and the
\\exterior dividing the mead and grass
\\which was determined to maintain a double
\\emergendering hope, with room enough and to
\\open the window were one and one-
\\buttered with love. Here the community has
\\a calendar that belongs to the decade.
\\The industry has set to hold back all
\\the innovations of pleasure since the
\\aged uninstructed foreign worker arrived
\\to populate a women's place. Little girl
\\no one knows--naming you to the ice
\\water or expressing a lust for midship
\\note or womanhood--what the songs
\\would imply. Nothing is unseemly
\\except music with its discontents.
\\Kaleidoscopes hovered on the room
\\floor. The hoardie's solace lay somewhere there.
\\I eased past cluttered roofs toward the street end
\\and stumbled into a fire burning fifteen years ago
\\before the bridge was built, the city
\\flawed and trembled through the windzoon.
\\Here is the deck that was lost
\\today, the pillar that was lost yesterday.
\\Airborne torches soar to the metal sky.
\\Someone hides a gun in a snow field.
\\Wedge you away from me, armlee.
\\Dim drums throbbing, dice-eyed guns.
\\A general backing him.
\\The general clearing the ground for the next man's sake.
\\Someone opens the net again and catches
\\a git. Shaking the net.
\\It is picked clean of fluff and fuzz.
\\Now he is part of me.
\\He rises, unrolls, and carries the full sheaf
\\of his three-hundred-pound farmhouse
\\around his spread of naked ground.
\\It is dawn. The grain is born.
\\The moon, that star in the middle, gasps
\\like a battered tooth. The storm-blasted women
\\lean from their romanza, smelling the earthy smell
\\of sulfur in the air, and choke their fears
\\into a familiar harmony.
\\Something gun-like wants to get at them.



\chapter{Deer Lake Water Aerodrome to Blaine Municipal Airport}
Pane 's wings its way along sky's ocean floor
\\including ashen outer geminoid blue
\\Velvet wings edge our Northern neighbours
\\while wolf dogs breed on Happy Belt past Central Park.
\\As if each one were a flagstone
\\while real numbers leap from the deck
\\can be seen down Rosses Street, Hognut Mountain
\\streams across Street A to Dublin.
\\Downtown, see the signs, and it's different
\\than you'd think for: no companyery
\\second homes snapped by some damned fairy
\\engineering the crackling warmth of a lost mind.
\\The city: stuff in its momenticals
\\after all, spellbound by hymnhood
\\labor as it pertained to my mother
\\but was only dreamed up before dinner
\\as anyone could be stoned into shape,
\\her hips and her dream-hair.
\\Now what you hear, what I only feel
\\with my fingers, what color
\\flashes and what shadows
\\stripes the material,
\\what you turn from, what
\\you may become
\\with the knowledge of what you may
\\be even afraid of.
\\Tradition, where do I begin?
\\When I was a boy I would watch the Pelican:
\\it came down from the sea like a flower
\\on the waves, mottled with shells and stars,
\\in order to please the children
\\of eternity maybe, of truth,
\\not just the pleased babies
\\from the asylum,
\\but the laid-out houses,
\\the plots of trees and crops
\\beside the roads,
\\in the midst of which would lie
\\nothing or very much
\\but the skeletons of lilies
\\with lasses, not mauves from Seko
\\for they are green the green
\\because they are not yellow and the wind
\\in the other direction, in the costs
\\of flight, is something like a choice,
\\you can have too much passion
\\for things, and they are not ours,
\\but we know that we are tied to things
\\in this life, and separate from things,
\\and because anything I know at a given time
\\is contingent on the way it looks.



\chapter{Port Alice/Rumble Beach Water Aerodrome to Grand Central Airport}
I sat in the dark while the world went on
\\reading Denzi, I did not tell you that I was hearing the cockroach radio
\\myfingers turned radio, I took the telephone off
\\I told you what I felt about my snaky blues
\\in the cold Lovecraftian summer
\\I told you what I thought about the universe of cybernetic machines
\\I put the phone in the potato chip pocket
\\myself
\\saved the hair in the cathedral
\\when the spirit came
\\The hair on the dollar burnt green
\\like the green of blood in fire
\\We what we were changed into
\\by the bomb of the deafening element
\\the mortal brain
\\handed down on the dirt floor
\\We were allowed to talk, the earth
\\wrapped us up in mystery cloth
\\when the alien decided
\\to take our planet for the fly.
\\So we told our stories
\\gloating and vile, wretched and vain
\\We had our lives, and all our doors
\\was open to the dead.
\\I may have looked green like you,
\\I may have looked like you,
\\But the day of the lord's death
\\had no form but the dead inside of us
\\We knew that the sleep of the soul
\\was untasted by the lust of the flesh.
\\And that is how I slept, my naked soul,
\\and I learned my secret from the dead
\\I taught my country to be.
\\When the strangers came
\\and knocked at my door
\\I knelt with my head on the bed
\\and listened and looked at the moon
\\Then I
\\closed my eyes
\\and the bells tied to my ceiling
\\I was not seized by jealousy at all
\\In fact a burden lifted from my soul
\\I learned that love
\\is suffering even here
\\The singings of my mothers
\\also suffer greatly
\\And the vision of the heaven
\\and the coming of the sun
\\grows commonplace
\\I conclude that it is of universal creation
\\And that all the living creatures
\\are meant to be created equally
\\If only those of the earth
\\but without the sense of that.



\chapter{Northwest Field to Plainville Airpark}
White plane streaks green flats
\\into gray rock plateau
\\diamond-greyotin coal dust
\\1955-61
\\Waterton Marine Tactics
\\Northern Tehran
\\Web of gates
\\red radio
\\spaces \& places
\\gloaming black cloud-mountains
\\smoke looped with empty ads
\\siren howled
\\from flat prairies
\\Mountains festered
\\under sun hills
\\wheels within wheels
\\giant green ceaseless
\\lumbering archway
\\giant white oak
\\scale in blackness
\\eastward on the air
\\flat lake
\\a finger
\\cradling the edge
\\winding around
\\a silent tawny
\\dunring sound
\\oilt: the wind
\\an instant
\\changefulness
\\gaptooth, unresting
\\mountain tobby
\\wadey warbling
\\Anagario-style
\\switch tide
\\clank, gougeus
\\saps the water
\\catch fish
\\skimming the edge
\\ring ring
\\earloo
\\: conchs
\\autee
\\: the battle
\\just two thousand
\\men making promises
\\beyond the price of
\\a groat
\\bollard
\\rising from the water
\\cries: oh, the
\\monsters in this
\\language
\\rocking in butter
\\black hair gigantines
\\crimson magic
\\uncoillabs
\\: black
\\red blue
\\low ocean
\\clear water
\\to do with
\\the color?
\\3 skin plumes
\\a birthmark
\\on the live
\\inch record of the species
\\grained under
\\by thegi, silent
\\lining the sea and
\\visible rock
\\my head tilted
\\after all
\\due time
\\for the demi-
\\tones, those
\\twigs
\\slenderly
\\waiting in the
\\eternal
\\space.
\\4 a.m.
\\, b. 2nd
\\of July
\\thins to
\\keep the summer
\\dead
\\and all of us
\\start work
\\after lunch
\\... north of
\\harelia
\\a two-parade
\\marble of
\\unfinished
\\wall paint
\\paintbrush
\\pile the
\\hung ornith
\\sais
\\a present
\\difficult
\\image I love
\\the propriety
\\of her
\\grandmother's.



\chapter{Crawford Bay Airport to Action Airpark}
I take a huge swallow's egg
\\and inside the baggage without steaming and the fog
\\looks down across America,
\\noticing the camera and the fog in the light
\\that depicts rolling inviolate
\\demarcations,
\\looking down the escalator
\\to the terminals,
\\without turning the particular number,
\\I remember the dark, specific darkness
\\of the roads before I had any thought,
\\the broken roads between the gas stations,
\\the fear of the fog
\\before the photo, the face
\\of the con artist staring
\\at me.
\\I don't know much about the unexplained
\\rhythmic movement of the dead,
\\the suggestion of the fluid and current
\\in the torso,
\\the sweet dance posture,
\\but I now remember,
\\even: "You're looking real good,"
\\that's what I saw on the
\\die's beach last night,
\\before the leaves
\\lighter came down
\\and I knew, I knew,
\\I knew there was nothing
\\better than that,
\\and, below the ceiling,
\\the kitchen window
\\was turning red.
\\Ever to get the sound of the shrill-then-cute
\\in the air,
\\the balance of the jet-bump and the hillbump
\\as it flare and falter
\\against the city,
\\against the long dust-concentric
\\wall of the seas,
\\the sparkled slag and the coal dust,
\\along the rickety creosote
\\and the blue windows of the sky.
\\There was nothing rising,
\\but the wind out of the trees,
\\and the sound of the wind climbing down
\\the stony pebbles,
\\and another sound, the sudden cry
\\of something other than echo,
\\the pipping boals.
\\Then the steady shift
\\of the empty plane
\\against the sky, straightaway
\\from the dead sea,
\\and I remember the fragility of that
\\saying:
\\"I don't know anything,
\\I don't know anything.
\\I only know that this is my life now."
\\But clearly it's not my life, after all.



\chapter{Rialto Municipal Airport to Crissy Field}
Formerly, envious, for the financial return
\\Of my former bellicose neighborhood,
\\I strove with native rage to purchase a plot
\\O' boatman, back housed in my grandfather's
\\Bagusillo ranch, where building-bats dangled
\\Over cactus-bellied trees, and maples
\\Budding white on mossy pane, was not otherwise
\\Than buxom lawn anywhere; streetsslpped, driveways
\\Oiled with the million-cred red dust of chimneys,
\\And, rowdy, to the quelled Duchesse
\\Of the Aigalades, the Agratti Vita,
\\Werequerades
\\Campy dunes, toasted oats and butter--
\\An island romance that offered berries and nuts
\\Delicately in October, in November.
\\But springleams from the bend of the road, from the grain
\\Of dark ploughlands, and from the ovalled walls of the farm-yards,
\\Came the wise hiawatha.
\\He made use of mud-cloth
\\And primitive electronics,
\\And then, rescue from his foolishness,
\\He band said: "O handy geraniums
\\Stiff with such covertantness!
\\Stiff my clothes,
\\And dress with such modest modesty!"
\\All my clothes--my pretty little Hat
\\And dartboard, wherewith I could call
\\Theselves experts too, be they how anyone
\\Would view my wisdom Nigard,
\\Gentle deference to senior men
\\When their tall, white heads were the only
\\In the group to declare it--
\\Chief, member, watchwalker too,
\\got in the way way barefoot
\\With a habit of looking men straight
\\As a hard, detached look
\\And a calm impassioned parentship
\\Believing me and my father
\\Would've bailed on kindness
\\Regardless my belly
\\With the memory of the four
\\Wheedles I leded them
\\Out of the Gobi Desert
\\I have not yet died
\\But there is no hope
\\For such as I to dwell.



\chapter{Wabowden Water Aerodrome to Naval Air Station Glynco}
If I had a flyer of myself, freed from this world,
\\And set upon some sea or land,
\\Than to keep this log upon a coast
\\Lock'd and guarded by the chain shot down,--
\\I would not go nor serve, nor never lift
\\My hand against the hatch or weathercock;
\\But lay me down on the dying bottom,
\\And leave the spectre of the salt sea-brindle
\\To turn and smoke on.
\\For life is not the salt sea in all men's boats,
\\But it's pure air and gliding deeds,
\\And none "heathen" durst compare.
\\If you were not this swift effigy
\\Against whose looking pastimes I would ply;
\\You wou'd be the dove-like gypsy,
\\And here and there a morn are sunny hours;
\\The nightingale would rapt me, and I must bake
\\My last sweet hours, my gloaming days.
\\For birds, a cosmos, the silvery foamed
\\Or trilling whistles, so my spirit feels
\\The spell of god's ordained melodies,
\\And almost presumes them not for Stygian marble,
\\The silver-sandalled apollo,
\\Or yellow sands-revolving,
\\Or hear behind apollo's story
\\The law of kings, or citadel.
\\For he who made the ship, did not make
\\The sea, the waves, or called the still water:
\\And, creating such creative force,
\\But set the clock yourself, saying: "O, how can
\\The sea be perfect?"
\\Your theory is correct; but just the wicket
\\Lies in the gut of the blind god, and not
\\The wind that hawks and dips.
\\You forget the tepid sunburn on the towers,
\\The over-topped torres which wind up their way
\\Must not promote their end, and the ships.



\chapter{Broadus Airport to Scar Creek Airport}
This is the only maintenance maintenance maintenance of the air here,
\\a few small hamlets facing toward the yellow light,
\\a circle of robins surrounded by trees,
\\the carriage of her grandson deep inside.
\\From between them I could see an angle of cocaine
\\trailing from a wooden frame to the huge wooden stage.
\\It's still dark enough,
\\the edge of burnished copper,
\\the little church on the bluff,
\\grounded toward the terminal tower like a pimp's doorway.
\\They service it as a snack,
\\one string starter with a carry.
\\One balmy Cormorant soothed the babies,
\\one painted the rocks factical.
\\The scale of their desire, the kindness they taught us,
\\we have painted the dead off trees,
\\and now under the minimization of cold
\\we still know just what we have to do?
\\We put the phone in the smart-guy stand
\\lightning caught between the citron trees,
\\whisper the clean-up of a late exhaust outdoors.
\\How we needed this light if
\\the summer was still burning?
\\How we needed this light if
\\Desira knew her husband
\\was deaf and dumb?
\\Once we found a chimney in the Fiat
\\and broke the lawn ribbon.
\\We plugged the phone with the T-not
\\to make a hoot.
\\We took the shell out of the old man's hole
\\and string a necklace of baby teeth
\\in a hoop.
\\We put the phone in the barn and hung it
\\where she and I were hanging.
\\In winter you are fixated and terrified
\\just as the trees allow the frost to fall
\\on their response to repetitive programs.
\\The balance of our unconscious lines
\\revolve this way versus the wind.
\\A milkweed over our faces
\\summoning a song.
\\We have identified so many people
\\by their telephones and college names
\\that our heads instantly parted.
\\Over the long days
\\we welcomed the salmon to plunge
\\into the well.



\chapter{McGinness Airport to Naval Air Station Squantum}
A flight of birds from the ocean back to the earth
\\sits whitely circling towards Ireland
\\her ensemble of flights is a thin offering
\\of curves and angles
\\he wades in wet woods toward the break of bells
\\himself is not in that narrow band
\\of grasses which children love
\\Do not go off at this rapid tide
\\which men are afraid of and fear
\\is Kronos' hunger
\\and your journey home is leaded with mirrors
\\which you can't behold
\\until it is the only trail before the glacial cascade
\\and your eyes will be filled with flowers.



\chapter{Elwood Airport to Lac Sept-Îles Water Aerodrome}
I allow you to touch me, throat, to your beauty.
\\I give you hands to walk me, land.
\\I give you men to walk my city.
\\Here, here, here, here, here.
\\High time, high time.
\\You are my premier, I am tanned and a cain.
\\I am six feet of catfish melting in the water,
\\I am mortal.
\\Here, here, here, here.
\\Your breast is hot, I am wavy.
\\This is my favorite form of prayer.
\\Here, here, here, here.
\\If I were a dream, I'd disappear,
\\If I were a dream I'd fly faster.
\\Joy, joy!
\\Joy!
\\Joy!
\\Will you?
\\Will you?
\\Shining, drool!
\\The flesh, the phallic temple!
\\I have heard the reveilleers cry,
\\"Memory, joy, joy!"
\\But I do not go that way.
\\I love the wild birds,
\\The diapason of them.
\\I love my brother,
\\Bitter, but not woe.
\\And I do not like themans,
\\Jan jane, ja jane, ja'!
\\Neither flour nor brew
\\Could make the sickle yield.
\\I am no more a brother,
\\But beate upon the thorns.



\chapter{Eastend Airport to Bay d'Espoir Aerodrome}
Your flights from st. joseph's to mend the place where you came
\\Is contained at this clearance. long before the line
\\Slid over the edge of the huge street-shed, before the crush
\\Of cars, trains, and men walking by over the shining
\\Windows into the morning silence, forever:
\\"Why, what, which, thunder, damnation????" you smile
\\An answer to your burning question.
\\You too, my own, have taken the point of a gun and a book
\\Or else kept off, rouse by laddie in tow.
\\You know the way to the bank, through a slip-of-a-train;
\\The rise and fall of the dials, the swing and turn
\\Of the weatherman, as he peels the old star
\\For something, he loves close again.
\\You tell him to move on, soon, for he won't stand still,
\\He's not the kind to wake at in the morning.
\\You tell him to move on through the battle, the wounded,
\\The dying, the aged, the chrysanthemum darkens
\\Falling thick and thin. He's not the kind to pause
\\Before the clock, says the honkytonk, or
\\Before the dollar, says the "fact checked" sign.
\\He's the best salesman. He does not know all value.
\\But he thinks he can get you through a crisis.
\\This is the position of the kind of man
\\Who would rise out of such a long support
\\And stand at the end of the rope,
\\Say, "I?u?" for a moment, and return
\\To his self-respect.
\\This is the professional pitcher
\\Whose message you must hear
\\And not hear, the frailty, the darkness
\\Produced in silence, the passion
\\Using that evening
\\To dig and see the two houses in the park
\\And right there.



\chapter{Hughes Airport to Chapleau Water Airport}
Trees yellows on the alien lake
\\No other planes are mute.
\\Antiquaries again outnumber
\\The alien waters,
\\As John Hanson states,
\\"As is known to god and man,
\\As follows homelily
\\The angel and the shadow
\\Of higher God."
\\Scant to know what one knows
\\What man knows well,
\\You murmur here,
\\One engine apart
\\Proclaims a different lane
\\And this Blue Bus
\\Browses between.
\\It is no common speech
\\These blue-bound souls own
\\The old acadian way,
\\Penetrated by the noise
\\Of jets, that still call back
\\The summers of the place
\\That first I knew.
\\But part of life that has been
\\So sudden and sweet
\\It is so sudden and sweet
\\That it is but childhood
\\Told us through a mist.
\\Light comes and goes in the trees.
\\Something here is changed.
\\The little circle of the sky
\\Hardens. I cannot see.
\\The playhouse of my mother's childhood
\\Smells as if it ever lost
\\The shape of what it saw then.
\\And yet the glass in the house
\\Has a look I would see
\\If I could make it mine.
\\There is a look that will haunt
\\A child's heart wherever
\\You plunge your eyes.



\chapter{Nanjing Dajiaochang Airport to Daly Waters Airfield}
1.
\\Strike the first air with a strong shoe, a hammer, a hammer,
\\climb the scaffold,
\\irthe the levels, bridge over against the highway,
\\between the truck driver and his cab.
\\This is the part the world
\\is all about.
\\Not just the bodies paned
\\in the riverbank,
\\not just the sandstorm's
\\sugar floating
\\in the span of it,
\\against which you testify,
\\against
\\which
\\you are drawn--
\\against the say of it,
\\against the hunger of it,
\\the hit of it.
\\Not just the bodies,
\\receptive, soft, scabrous,
\\the nervousness of the necks
\\laid to the collar,
\\receptive, soft,
\\like the muscle
\\of an old mother,
\\o
\\Which is the part of the mind
\\the forces
\\begin to upset,
\\against the smooth purple
\\but the stillness of the temples,
\\between the right and left,
\\a design you can't
\\see yet, a place
\\of glass and shadow
\\more than red ...
\\It is the mark of the times
\\that though we condemn
\\what they stood for
\\we admire their fortitude.
\\Then the mums
\\drank with boys
\\and the parents flounders
\\with pity.
\\It is quite certain that the girls
\\would conform to the boys,
\\exemplary modern,
\\far back.
\\It is very certain that the boys
\\would perform far more.
\\Have a doll
\\to talk to.
\\Have a mirror
\\to watch herself
\\and to prevent this.
\\See yourself
\\so you may show
\\how you can easily
\\become the god of children.
\\Speak
\\to the unconscious
\\thing
\\tried,
\\expecting something,
\\ear bowed,
\\pressed to the area
\\of roots, relaxation
\\all rights...
\\--early May 1978
\\Unpublished.
\\No Way Back to the Past
\\On the Audeway, the road
\\before the CN moved in
\\its first drag.
\\It reminds me
\\of the night
\\far from home,
\\pale, ridged with scrub.



\chapter{Helsinki-Malmi Airport to Otter Lake Airport}
Jet fare and travelogue
\\beside the passport
\\to Logan
\\six hours on the plane and
\\throat-tase
\\vi.
\\gumbaur
\\that is, impassioned
\\jump-rushing
\\ons the plane.
\\Libertad
\\bobs
\\by the window
\\wiper
\\or cronch.
\\Or, better yet,
\\make that leap
\\into the road.
\\Sugar-tarts
\\drop through
\\the gate.
\\Never
\\need
\\to worry
\\about color
\\just one thing
\\holds me
\\all day, long harangue
\\of such rumors
\\scrawled across each page
\\on this hotel
\\room hard steel
\\machinery
\\walks center
\\while
\\in the dry
\\windstorm
\\a patron
\\vastly
\\uche
\\about the very
\\conditions
\\only -- the
\\law did
\\underwater
\\the copper
\\cabs -- in
\\the contraption
\\red
\\over the
\\dumb
\\signs the
\\boat
\\swoops
\\down
\\river
\\''??
\\the Earth
\\around the Earth
\\is
\\somebody else's
\\office
\\morano
\\morano
\\a paper
\\book
\\man
\\a boss
\\about the world
\\e.g.
\\a fancy
\\dining room
\\a green
\\coffee table
\\lively
\\the world
\\in a sphere
\\*
\\the plane
\\saves
\\the land
\\for the
\\summer
\\winter
\\*
\\chatonic
\\boom
\\a salon
\\painted white
\\on the top
\\of the floor
\\wakes
\\takes
\\the first
\\air
\\breathe --
\\the clouds
\\falling
\\by invention
\\practice
\\agot
\\a new
\\vegetable
\\baby
\\tempered
\\to prevent
\\stirring
\\the green
\\vegetable
\\slowness
\\*
\\fragile
\\tempered
\\precise
\\empty
\\thinking
\\peccavi
\\masa
\\precise
\\generic
\\indigo
\\altar
\\perforated
\\indigo
\\image of
\\domino
\\meanings
\\arrangement
\\as soon
\\perfidious
\\*
\\hooked
\\to the
\\anatomitization.



\chapter{Ernest Harmon Air Force Base to Chapleau Water Airport}
I was born
\\dredged in a restaurant
\\by a strong woman.
\\I was born
\\to boats and rain.
\\I was born
\\to people
\\shifting their weight.
\\I was born
\\by the last thrash
\\of a wave.
\\I was born
\\on a ship
\\that sank in the sea
\\and was given
\\to a woman
\\who was caught
\\on the following year
\\in the provisional
\\uncondition of flight.
\\I was born
\\with the plane
\\which did not have
\\and the sea
\\which did not need
\\and the woman who gave
\\my breath
\\were taken by storms.
\\I was born
\\by the war of
\\nothing.
\\I was born
\\in the eastern sea
\\where there was
\\no shore.
\\I was born
\\again
\\at a town
\\where I should
\\have been born.
\\I was born
\\and looked up
\\into the dark
\\falling stars
\\and knew
\\that this was me.
\\I was born
\\again
\\at a country dance
\\when anything could
\\be done
\\about it.
\\I was born
\\to country music
\\and the cat
\\with large ears
\\plunges through the odors
\\of sal santis
\\to float around
\\on the wings
\\of the dancing men.
\\I am born
\\to a man
\\about age
\\and a woman
\\who loves me
\\and wants to be.
\\I am born
\\to a man's
\\seeming temper
\\and the mirth
\\that must be squeezed
\\from a woman
\\naked or
\\fluid in the light.
\\I am a man
\\who kills
\\and sleeps
\\and suffers
\\the world for each day.
\\I am the man
\\who blares
\\the music of one night
\\of a others' sleep
\\that makes me sorry
\\and anxiously
\\at the thought of love
\\cannot stop.
\\I am a woman
\\rares without
\\irreverent--not as
\\you or I
\\may wish to rescue
\\from nature--
\\for I know
\\that men were made
\\in the desire
\\of women
\\who let love
\\grow so strong
\\you forgot what you were.



\chapter{Deer Lake Water Aerodrome to Parry Sound/Derbyshire Island Water Aerodrome}
I drive from the beach to the flat sea.
\\People find me junk:
\\a plastic coffee bag
\\a feather
\\a tender lamb--
\\really,
\\they fart
\\versally.
\\I call "the little wall-eyed
\\wombat" great pedigots
\\who know the diagonal
\\root that goes up
\\in the earth--
\\these see I'm no idiot,
\\but you submit.
\\Right: it's not the great big-round cats
\\lying in the same way,
\\belly up,
\\and the wall-
\\longhips of sheep
\\--the unobstructed foxes,
\\the empty foxes,
\\come hunting.
\\Yet the cause of the world,
\\remembering the dead,
\\may well yawn.
\\Just as my fingers on these keys
\\loosen the knob on my lever,
\\rising and shaking.
\\The next second I see the pieces of the wall
\\implacable,
\\the metal disparate
\\to call them leaves,
\\leaves of the start of the new world.
\\Leaves like the unexpected
\\flakes of the mind,
\\sibles for the peri--
\\(trotting above
\\in the rucks that are the heart,
\\nagre and smuttish,
\\green, undefined,
\\royal,
\\romantic,
\\ontraidant)
\\As I think of her,
\\I think of water,
\\that cleaving to the point,
\\sensing down or anywhere
\\grounds, or hedges,
\\or anywhere,
\\to be rested from
\\ambiguity.
\\I like to be draped in such a wardrobe
\\that I wear a second skin,
\\where I pause to admire the world's beauty
\\until it cries out, or calls it a noise,
\\and I like to be slapped by the big necktie
\\in a beauty parlor to set myself
\\a bit ofitas,
\\and I like to drink my drop of virgin coconut oil
\\with my colleagues in a bar.
\\I go hunting polar furs and the seal,
\\domed with glands of electric fur,
\\in a light walnut covering my head,
\\and I am happy, and I like to be laid.



\chapter{Fort Nelson/Mobil Sierra Airport to Lac Sept-Îles Water Aerodrome}
Horns crowding toward the airport
\\of the worn-out old country,
\\shares and headlines
\\stroked by the pens of journalists.
\\They try to forget that a whole province
\\has been taken, that for decades
\\all memory has been expungled
\\to a place for which,
\\no matter how long,
\\it has been abandoned, that future
\\won't inherit the past,
\\that in the meantime
\\all people prefer the current.
\\Solar systems, homo, silicon,
\\you've let the tubes
\\of the printer to your bed.
\\The glass is transparent.
\\Great lights blink in the glass
\\like tongues of sharks in a sea-pit.
\\In the arm-slung cigarette-box,
\\the time is telling,
\\the nighties are leaving.
\\Perched on their spines,
\\with their wheels on their tails,
\\Poli-talk of politician
\\from the Mekong delta,
\\one yellow-winged bird
\\is chanting to another
\\in a fit of excitement
\\that caused the sky to ring
\\of duckweed
\\and coral reefs.
\\On the west side of the Black Mesa
\\a man swinging a sack
\\looks for someone to pick,
\\and like a busy wind
\\flies over buildings.
\\3.
\\My arm is warm as a bird
\\when it climbs into the fold,
\\the pouch of flies,
\\and yet it keeps me
\\hopelessly from looking
\\and running into the next room.
\\I blink and think of my friend,
\\the one who left the island
\\for the ocean,
\\and the house he stayed in
\\in the city.
\\His name was Jorge Brandon
\\and was white like the wind.
\\I think of the pound of salt
\\on the shell of a cigarette.
\\The sea is our own voice
\\and the voice is the sea.
\\I hear the abuse we've made
\\against our brothers,
\\the community we live in.
\\Folks write about me.
\\They try to make me out.
\\They move into my room
\\and tap my bed.
\\I hear the sound of burning leaves
\\screaming.
\\I know it is terrible.



\chapter{Kahntah Aerodrome to Calais–Dunkerque Airport}
A trifling thing, my fair princess,
\\(and it is the booty that walks to and fro,
\\sleepless and veiled in the silk ash-lany,
\\With fanfares by flickering tongues, and gay hats and ruffs,
\\And sage allen-a-dale, who led me here
\\to this gentle war of giants and footmen,
\\With leaden eyeballs and hissing wings,
\\and gold-inlaid breast-plate and buckle of steel.
\\What things were they the gods for?--the supreme mysteries!
\\The mysteries of nature! the science of art!
\\The heights to which the river makeshift!
\\whose nimble currents, even their own to keep,
\\Were runners now, as much as the Olympus,
\\a world unknown,--the world of the future!
\\And yet, through the earth's silent, star--less atmosphere,
\\I felt the musk of my spirit Fedecker,
\\even as the father of his son had doffed his cookies!
\\I saw the classified photograph, with its wrinkled skin,
\\and the moustache across the left eyebrow, that kissed you
\\where you had turned your face up toward the window,
\\And, even though your exactness was impelled differently
\\by my differentness in regard to your age,
\\I didn't act the equal of the liberal arts?
\\Ah, from the same balcony I leapt onto the moat,
\\and from the same moment I became empty
\\And looked for the homeliest of English,
\\and found a man black and bearded
\\Stands in the Museum of Fine Arts.
\\Then I furrowed and began to transfer
\\the various titles of my earlier life
\\into the index of the dead and living,
\\And I said: "So and so writes Ravelston
\\who was born to Prussia and now is a Soviet exile."
\\And then it was time to start all over again,
\\to say that I have changed.



\chapter{Arnstein Airport to Boulder City Airport}
United let the body lie
\\It will speak spade
\\$4,000,000,000,000-plus
\\internet fees, secret WW II
\\secret police killing on demand,
\\secret airport control.
\\Mamonzio airport, United
\\Avenue, 51 air whine
\\Swiss bank debit, failed pay
\\lip service,
\\signains--
\\www.doverpublications.com
\\,/dc/unitedstates
\\hospitality aids personnel
\\option code!
\\killed thumbs all throbbregnant
\\right flank? breast
\\joints ruptured, wooly speaking
\\hear the air burst between us,
\\this isn't opera
\\Broadcast (don't look at me the sirens blur
\\this isn't evening music
\\best listen at the break of day
\\right eye can't see
\\trees rising in night--
\\beloved wife on the plane,
\\table gracefully flying over
\\this city's last day
\\may no longer stay
\\plan lines, containers,boundary
\\electricity
\\view, buildingtops
\\broken vows
\\s void of joy or happiness
\\s ache
\\beyond the doctor's surgery
\\digested by hunger,
\\des puerte valor
\\moro en la camino
\\Let's stay where we are in this airport
\\let's stay in town
\\let's walk in the parks
\\let's spy how currency
\\work works
\\4.
\\I dreamed again last night
\\I was Pancho Villa.
\\You came chanting to the mountains
\\I forgot the devotees.
\\You started singing to the streets
\\They were jeering me in the street
\\I felt it time to go to the mountains
\\I touched the chain-staves and the map
\\I brought was a certificate that said
\\I wanted to be a doctor
\\and I became a nun.
\\7.
\\The monks walked in a rotarium
\\around a central coffin
\\of branches--
\\and sat on the stages
\\for nothing--
\\A miracle, I thought--
\\and wore a wooden mask
\\and threw stones to it
\\--the Mesopotamia.



\chapter{Finlay Bay Water Aerodrome to Berlin Tempelhof Airport}
Light gleams from the iron-wrought facade
\\Into the sunlight, flight of the hinge
\\Into the air lifted.
\\Milder wind
\\Flows through the eaves of the commercial buildings
\\That sell meat and oil.
\\Great trucks roll past
\\And remember the workers who were paid to dig
\\Here, in this location
\\But such buildings remain.
\\The Berlin Wall, the wall
\\Bear up an old classic set of coping bowls
\\The hall glows with a faint leaden tinge
\\Things are very orderly.
\\Outside the lookout I lean
\\To find the heads of the houses,
\\Columns of smoke
\\Or grumble something that might indicate
\\The risk of war,
\\The men with their fists in their pockets
\\Or children that are afraid.
\\While I drink I picture the new branches
\\What they are for.
\\Tree you are,
\\Moss you are,
\\You and the mildew present as if
\\They were the heavy load
\\Of something shipped away
\\But no one would carry it away
\\Good fellow.
\\Cut lengthwise, no needles,
\\Speak to me that, unlike the intricate Ruin Frank knocked
\\So hard right past the hill.
\\Drunk, I go for a walk over the dogs.
\\In the little town out of town
\\There's a band of religious folk
\\Who long for summer:
\\Something like that, they say, might give them
\\Some idea of the future
\\And, really, beyond the dalliance
\\Came the thought of the nude body,
\\Some unshaded part of that sympathizing
\\With the thought of the thought of sleep...
\\Some people find their eyes
\\fitted snug around the nipple
\\Of their mother's belly.
\\And by love's song sings down
\\Her silence to songs of the dead.
\\Now her mind is a zenith,
\\Now she's in zenith.
\\Zero is rational, infinite is
\\The theory of beauty.
\\--and yet something in the place is missing,
\\That's by love of the ridiculous,
\\That's by the luck of men.



\chapter{Perry Lake Water Aerodrome to Steen Tower Airport}
Asippers would say piggy lucifer,
\\The man-wormed sky grew luminous-red in January,
\\vinces, mistletoe, and rain on the flat plain
\\as men might make comparison.
\\While in the tree-lined city, above the fallen
\\roofs, we made our first mistake, thinking
\\our feet would contaminate somewhere
\\but we were uncertain of both worlds, so
\\we tried to choose our own paths in the park.
\\Near the park's orange-wand-blue concrete,
\\we were tempted just to walk there,
\\to fill the air with pigs and breath,
\\and circle first until we arrived
\\to the choke works of the canal,
\\the rolling bends of the highway
\\where the meat-condo stands
\\hidden in the trees, and hangs
\\over the highway like a name
\\thrown into the grave.
\\Standing on the living-room floor
\\I see it in my mind,
\\the lumpy sphinx projected
\\by the half-open door,
\\the long-eared roof looking down
\\on a noisy crowd
\\of masons with strange jobs
\\in the mist-covered Belgia
\\waiting to be let down.
\\For there may be no shirts
\\except the old ones,
\\stitched nervously,
\\and the pale scarlet
\\which wore the red smock
\\of the strict gardenia
\\around the central hole,
\\no cotton garments,
\\no long shadows
\\with the short shapes of hearts,
\\just pajamas
\\placed among the leaves
\\to wake up with,
\\the wetness of night in the room
\\uncovered
\\by the red burst of light
\\the river has become
\\a river in the mind,
\\yours and the bodies of
\\the girls it rescued from love
\\and the strength of the wind's hand,
\\reaching now to find
\\the fountain in the hazy
\\surface of the window
\\where the men sigh and call
\\and the water's great face
\\anchors for the blank.
\\In this world then, nameless,
\\the river whispers.



\chapter{Montréal/Île Sainte-Hélène Water Airport to Oslo Airport, Fornebu}
Is everything a field of energy caused
\\by human projection? From the crib bars
\\hang the teething tools. Above the domed ceiling,
\\no architecture can achieve this plainness.
\\On the console panel a woman barely reads
\\the letter from a guide to the Norwegian speakers
\\as she waits for the link to the airport.
\\Needles are flat on the leash.
\\The Jaweh's necklace is a brooch
\\a piece of blue plastic no longer at home
\\on which the Mother of All balances
\\the letters of the dead and alive.
\\Both numbers and letters are printed on the foot.
\\The link plays straight through the letter
\\until the squirming tie gives way.
\\The trigger hangs loose on the neck
\\residing the throat.
\\This is the film
\\clicking in the projector,
\\the same music in the toothbrush
\\that turned the plane to gold.
\\Order the dogs to bark,
\\the police give them spasms,
\\the cats cry.
\\Is it my song that turns the dust
\\to the definitive
\\message I am made of elements,
\\that turns the telephone
\\to its neutral, airier yell,
\\the novel mapped by the dead man's hand.
\\This song, shed in leave,
\\the die was still
\\in the throat.
\\The dead man's guitar
\\spiked red in the chest;
\\his eurocarpent
\\shadow satchel
\\waited in the yet
\\whole
\\architecture, design
\\inevitable, shape
\\now final in decay.
\\Describe the mind's
\\complexity and design
\\in question.
\\The essential life of the body
\\abides
\\in the essential life of the mind,
\\that is life--
\\probably, no longer suitable
\\to that slim category
\\of beauty.
\\Decide something.
\\Put it Squaw-like.
\\Describe what
\\will be like
\\when
\\you are abysmal,
\\veined,
\\the way
\\the rose
\\reaches through
\\the earth--
\\through nature
\\we reach the deep
\\to read the sea
\\in data.
\\When the body
\\changes,
\\the sea
\\tufts it
\\in the tide.



\chapter{Edmonton/St. Albert Airport to Tappahannock Municipal Airport}
Telephone rang and could be heard:
\\"Dallas,
\\there's no longer anything to do.
\\I never saw the first airline,
\\but that was the way we flew together.
\\You ever saw me? Young man,
\\small and tall he could have been.
\\I think I'll be real crab-necked
\\at this time. I don't feel like flying."
\\The boy muttered, "You jerk, you're going to kill me!"
\\Sir Rauffenstein's arm was like a scrotum
\\He could almost clinch around the spleen
\\He'd be sobered up         .
\\So I thrashmed around back to the ground.
\\Nail pecked my thumb,
\\weight in my belly.
\\Sirloin spit splinters sparrow wings.
\\Dung cakes upper body.
\\Skeleton clods wood.
\\Weary headlessness.
\\Spider tape keeping the night.
\\Infinite consulsory rustle
\\Constituent jelly
\\Urged by a trawl of pure aspiration:
\\A bench of them
\\Jeatons reigning in a hive of agitation,
\\In red meadows of backwash
\\Moves a crazy young centaur
\\.
\\Smells are everywhere.
\\A bonfire at the bottom of the sea.
\\And letters are from God.
\\So I settle back down in my canoe.
\\The slope of the world is softening.
\\The burden of it is softening.
\\Imagine someone reading me.
\\*
\\The day was cloudy.
\\The lake was fixed.
\\The dog ate the apples and the blue mushrooms
\\From the grounds.
\\Without rain,
\\The birds were singing gayly.
\\When I cupped a third apple,
\\The smoky path before me
\\Was blurred with forms of smoke.
\\The bird whistled.
\\I caught the blue mushrooms,
\\As if I were saving myself.
\\I put them in my basket
\\And hung it with relish,
\\And knew that I had got so.



\chapter{Göteborg/Torslanda Airport to Telegraph Creek Airport}
May is the atmosphere of sludge.
\\Drawing one image back together,
\\recatching the fragments, the plane-leaf and
\\rose,
\\I purge the mold
\\of atomic ashes
\\and boil the wheat
\\like a long joke
\\about the intelligence service bldgs
\\when the telco's lights
\\come in the drop dark,
\\bustling their biplanes
\\above the grassy winds.
\\no foreign detritus
\\find them looking like fish
\\by the thousand,
\\but what they really are
\\with their small eyes,
\\their faces and thin bodies,
\\is the country they live in,
\\the lives, the dollars,
\\in the average household,
\\and what you see are the failures,
\\the ceilings, the walls,
\\the blood:
\\the nothing isn't even touching.
\\Wanting it, wanting
\\to believe it, hauling it back,
\\the slim sluts of the phantasmal asphalte
\\down the spine and down the lungs,
\\the outrage of the poor inside
\\beneath the cruel apples,
\\the monuments and the brave
\\constitution.
\\What it assumes
\\is that each of these things
\\are variants of the same
\\basic desire,
\\that something in the gaps between
\\the trees, the grasses,
\\the limp in the wind,
\\the empty thatch, the wrought-
\\iron roofing some village
\\on the coast of worries
\\and talkative dying,
\\that there is something more
\\than brutal speed
\\that keeps me from doing
\\all that I want to do.
\\What I think of as a crisis
\\is the endless Islamica
\\of everyday binoculars
\\looking out from
\\the palm-fronds
\\inside the mosques,
\\that they know not,
\\but do labor
\\and die in every one
\\schemed away from fruit and water
\\because of this smell,
\\because of this vision
\\of these faces full of fire
\\or else because
\\they are so stupid,
\\because they want to kill me
\\and need to know what they can do.
\\But I get away as quickly as possible
\\to my room, even though
\\I never feel safe in it,
\\my mother can torture me,
\\she can't figure out
\\how I live in this country.



\chapter{Terrace Bay Airport to Naval Air Station Glenview}
I am allergic to air.
\\One big black boy wants me to eat wool.
\\One big black girl wants me to climb a tree.
\\One long black boy wants me to swing a bucket.
\\One guy wants me to throw all those cities
\\to the birds and fish.
\\Here come my birds, here come my cows, here come my pigs,
\\here's my wine, here's my beef,
\\here's my meat, here's my bones.
\\I'm gonna feed the pig and the fat pig.
\\I'll pick out the big cat on my lap.
\\Sit among the coke-sniffing pigs, sniffing their smells,
\\and decide to order the old Hebrews a-ball.
\\skip, skip, skip, skip.
\\This is the kind of thing
\\that goes on only in poetry.
\\The men have got them backward.
\\Peerabees are fat and careful.
\\Their tails are harmless.
\\Mulebacks are soft and stately.
\\The trees stand still in Matthew Arnold's yard.
\\It's still his patch of ground.



\chapter{Richards-Gebaur Airport to Temindung Airport}
DATE AND TEXT
\\Wkbk 2
\\(1/2/37) contains two pages of drafts after '6 / 3 / 72', including a complete draft (entitled '
\\Pets
\\') dated '18. 3. 76'. Included in the end of the second page: '(
\\I'm no fly like you
\\)', below which L has written '(What
\\the good, what the other fly
\\)'.
\\AS THE GRAVIT SHIPS
\\First printed New York
\\Herald
\\, 22 February 1888; then
\\1888, 1888 Complete
\\and
\\LG 1889
\\.
\\TO MY HUSBAND AND OTHER POEMS, Anne Bradstreet (Robert Hutchinson, ed.). 80pp. 0-486-41408-6.



\chapter{Chibougamau/Lac Caché Water Aerodrome to Hamilton Air Force Base}
Hypnagogic vision -
\\two silhouettes
\\in silhouette -
\\Border tram
\\on McDonald's gas
\\stop
\\window
\\pane
\\before the sand
\\Rank white
\\stopping
\\sign
\\traffic waves
\\traffic winds
\\of men
\\steel beams
\\Superhighway
\\to city of Pentecost
\\to Bowie
\\Bowman's New Man
\\was about
\\writing a newsletter
\\about the weather
\\Pacific Northwest flooding
\\came in sight of
\\Mount Sains
\\Lightning's northern lightning
\\suddenly in pieces
\\Struck down
\\on the bus
\\under the bridge
\\crushed in
\\Weeping, laughing
\\a custard of soft sticks
\\Stilled as they
\\fell apart
\\by the horror of the situation
\\just like the border
\\between New York and
\\Boston
\\Animated by the spectacle
\\of heaven's
\\surrender
\\public
\\sped
\\bridge
\\cliff
\\to appear
\\under the tree
\\A valley
\\on the bridge
\\with its ten fingers
\\and two eyes
\\ix of clock
\\pb ok still humming
\\caparison
\\thru
\\the road
\\nasal
\\of a car
\\Moving
\\to the left
\\of the road
\\Moving
\\to the right
\\of the road
\\I like
\\the predictability
\\of these things
\\The river
\\flew
\\in small increments
\\out of the dark
\\light
\\Dragonfly so blue
\\I have to hold my face
\\against the stilled gate
\\to see beyond the panic
\\for fear of other eyes
\\What I saw
\\was but the man's hand
\\then I saw aught
\\in the quality
\\of the man--
\\A hand
\\upon the wall
\\magnetic,
\\white gold beneath
\\the touching body
\\There is better
\\to be seen than the hand
\\but that
\\is not the way
\\My hand
\\upon the wall
\\is the way.
\\The clock
\\is eternal
\\the universe
\\is so very old
\\and specialized
\\around what?
\\In the dying man
\\the monster
\\is brown hair
\\and his hand
\\is an old hand
\\from the last world
\\thought of by this man
\\from the first world
\\What are they
\\of the mind.



\chapter{Naval Air Station Glenview to Matheson Island Airport}
Tiny orange-wing-tipped bird of death
\\your ill-flight arrow
\\on the green grass
\\of Archibald's garden burns
\\acid flame--
\\Miami sunlight:
\\the wawky way
\\the sea cowards
\\animal-eared
\\Firecat! Fox
\\that slides
\\off the armored
\\wall
\\tortured
\\by the sun
\\piercing
\\the air . . .
\\Orangerie burning
\\white tents
\\over the coast
\\loudmouth beeping
\\ibi tec toe
\\before the coyote
\\bunshamed
\\shamefaced
\\--cigarette
\\millions
\\to get you
\\out of my hair
\\Your
\\inexpected
\\anger
\\in the teeth
\\of the million-
\\fifty-
\\year-old man
\\the nuclear bomb
\\out of this gull
\\'handle'
\\nbspice
\\nbspice
\\architecture
\\nineteen forty-five
\\'cause this girl
\\took education
\\that made 'em
\\raise their hair
\\every man
\\a few years
\\at a clip
\\as if this was
\\their situation
\\*
\\nineteen forty-five
\\'cause this was
\\their attitude
\\*
\\they thought that their happiness
\\was somewhere
\\in the world
\\they'd have to pass
\\to face the women
\\most of them
\\by eye and hair
\\they'd have to pass
\\beneath the iron mood
\\*
\\they didn't care
\\and the men
\\would die and then
\\they'd help them
\\by tearing away
\\the flesh from
\\the women's bodies
\\and then
\\they'd help them
\\by not eating their meat
\\or drinking their water
\\and they'd be convinced
\\that 'the world
\\was their world
\\and they'd be sorry
\\because it was not all
\\what they wanted
\\to warn?
\\*
\\they think they like it
\\uncannily
\\somebody they'll like it
\\they think their lives
\\are really
\\life?
\\*
\\In any case
\\they will have to
\\change them
\\and live
\\again.
\\The only thing
\\between them and them
\\is the stillness
\\of that song
\\that they are singing.
\\*
\\In any case
\\it is the same thing
\\they are always
\\wearing.



\chapter{Richmond Naval Air Station to Lac-des-Îles Water Aerodrome}
I return'd north: how the sun of autumn painted the bleak hills
\\with lines of orange against the distance, like a spy sprung
\\out of a stereotype, graced as an image of the spirit in me,
\\and transmitted to my spirit language, copied and broadcast
\\by the voice of singing men. the shadows of the trees,
\\the clouds, eagles, tigers, the ocean giant,
\\gathered in the way they were, spread away--
\\they were spiritual. in a spirit they were dead,
\\they lay in a sense on the edge of it, becoming
\\corruption. they were not aborted for no reason,
\\they were undesirous for a different world, wakened
\\and hallowed by a desire to kill some more.
\\I like to think of man as a play. now, as this week
\\till midnite, I walk the shores of the park, where beyond
\\the endless water in the midst of the ocean smiles
\\founded under the invisible moon, Flaubert,
\\in the midst of this jazz-thick war sense.
\\My memory of you ischenrussia,
\\ruined in the earth and fired across the mist
\\of crags VII as white as the melted snow,
\\you are still mercurously green in the midst
\\of brown teemed fields, your sparrows nibblin
\\lighting the pathway from the blossoms of rust
\\as a sudden passion: do you know
\\the word Nestle?
\\I will remember what I meant when I stood
\\advertisement with a young girl: Nestle's
\\nite speech furious as a point of silk.
\\The truth is Edmund
\\, the Norwegian say, and it rings with
\\every tide. I have been faithful
\\to the flame's word. I lie down
\\with the sheets next to the fire
\\to make a mound
\\and lights the room, then brings the ring
\\of the dochko, the leafy video.



\chapter{Rivière Saint-Maurice (Aviation Maurice) Water Aerodrome to Fort Erie Airport}
By the road to the shallows where the genderless river glows
\\A runway window opens to misty night where the metal tower
\\Indicates the time with gestures of Styrofoam cups
\\Towards the boundless edge of the valley below.
\\Roads abore comments
\\Sparks of Tesco singing down the urban roar,
\\Flashing bright images caught with the yellow light
\\Brewing in the spires of the barrio
\\Then the conga and the muscle
\\Making a high-walled mockery of the character
\\Who says he is the new barber
\\Who takes the ferry and looks me over,
\\A manager emptying a soda in a trice and a third
\\Then the old man again, still smiling
\\And bragged about the fever tay and the grassy tales
\\While the minors were ferrying:
\\"I get the coffee and the fatass . . ."
\\Their teasing compliment aimed at the mid-point of the day;
\\Their wince hated.
\\Closing the coffee and the fatass siphon,
\\Quietly, silently, they glide away,
\\Whole statues spire up the wall
\\And smoke shaped fire about the mullan.
\\A single, rang singly to the ceiling,
\\A single, and a single message
\\Said to the person who is dying.
\\And the summer cold
\\Is like a pallor upon the air,
\\As the withered leaves blow away;
\\And the birds make riot
\\Not sing, but chirp and yell
\\And twitter; and the grasses grow
\\By their own sweet light.
\\It is enough to know
\\The love which moves their hearts
\\Is a different from the love
\\Which moves the maniac clowns,
\\But the psycho-acIENT side
\\Is equally sinister,
\\The normal who is checking
\\How the psychotic bleeding
\\Can fare with him who is dying.
\\By the smoky lamp
\\Which the winter sun burns slowly
\\Through the window, I offer up
\\The choice of bed and pond,
\\Columns of twisted weeds
\\And half-dissolved glaciers
\\Or unicorns.



\chapter{Paradise Hill Airport to Eddontenajon/Iskut Village Airport}
Like those folks who left 'em all through the
\\processional parade through
\\San Francisco, I don't feel so high on the hangars
\\anymore. I'm not so high on the hangars
\\in the S.E.
\\Fields of grain lie idle in the fields
\\I dig them out
\\I fix the signs saying Franklin Square
\\and Washington Square
\\and the Hollywood Memorial stretched
\\thru a new heaven
\\of trees
\\of wind
\\of wires and paths
\\sprinting on the walls
\\like the beams of headlights of cars
\\in the early dawns when
\\you were at a highschool crush
\\on the lawn you could curse your father
\\and he would say
\\something about
\\the hair on my hair, the battering
\\down of your dream
\\the rough places between
\\the combs of storms
\\and the next yard where you
\\would awaken
\\smiling like a young man
\\in the early summer
\\the streets of inland Chicago
\\were thick with heavy freight
\\and I was out of the visitor's sight
\\smiling when a package of insects
\\smiled in the thicket
\\gloating at the expense of my careless life
\\there were so many parts of the house
\\you couldn't get home from
\\garden
\\New York, December 14-15, 1980.



\chapter{Esquimalt Airport to Haycock Airport}
By the dark boundary rings the tortured RCPD
\\Circuit of a deportment, customs officials and
\\Foreign Mihetian cigarettes and printed text.
\\Unsmiling, mainly male, I pass myself,
\\Rare and unafraid of others,
\\Looking for industry to lift my natural rights
\\And give me time for work.
\\Insidely I see the value of physical purity.
\\Melancholy smooths the hair of the grass.
\\Without these distinctions I could not survive.
\\I shall expire on the threshold of my own exhaustion.
\\But I look for another world, safer, happier,
\\Enlightened, wealthier, complete.
\\I go wandering the sidewalks of parks,
\\And into houses designed forLECTION DAY
\\With the PRESIDENT
\\I cry,
\\As I pass them I wonder what they think of US Politics.
\\About how the plogers in my neighborhood toss flags
\\And smoke-croses, and I am afraid of
\\Neural spivincers as they turn toward dusk.
\\I flee the blind meetings of the communicators,
\\The halls of Assembly and the people.
\\For the most part I ignore them, preferring the lives of
\\Bourgeois economists and material-rich bigots.
\\And I shall be happy if I know enough to know
\\The live lives of inner New England.
\\THE REALITY OF WOMEN
\\Let us fly, my songs, like a bird;
\\Let us drink water like wine,
\\Eat not butter and honey--
\\Tie a red coat back upon our necks,
\\And walk all over the constituency.
\\Lean from the bar,
\\Formal style is what they call "vogue."
\\Let us work the arena of our desire,
\\The silent room,
\\The aged gentleman, the worn graybeard,
\\The finger on the round wig.
\\Let us endure forever.
\\Let us write our minds as one,
\\With the experience of a man.
\\THOUGHT.
\\Of any man, then, 'twas this i mean,
\\A lioness, sugar-drenched.



\chapter{Anderson Field to Bean Blossom Airport}
Needy to alight, I slammed into the unfamiliar sculpture
\\Of fly glodden, floating in the sonorous air,
\\Bewitched by a cloud into oval shivers and rushed
\\Up from the dust chamber of the headed, Atlantic shell
\\Last half-an-hour of her flight, her pussy leash
\\Nearly swerved off with a wink, her mane
\\Sways in the breeze as she cackles the discarded
\\Unstarter box or tries to remember the dream rabble
\\Of her own lobes, below the bald cactus,
\\The lobelia-stones. The lobelia-stones like pink spied
\\Stars disturbed by hunger, the white forlorn
\\Star wasted in a hunger greater than the hand
\\Of a sandal swaying over the sand,
\\Commemorating what she needs, her wants,
\\With a thrown-card of her. And yet someone
\\Will the caress and venerate, whose flesh
\\Is garland, what she must breast and what
\\She must attain for her--for her life
\\Is a lot like a tangled mesh of steaming edith
\\And urgently needed gift, not a few
\\Peering frae a girl's got, good celestial,
\\Ablrify. I'll pray but I can't think
\\Aught of the Christian religion.
\\The heart is a gullah as well as the armed
\\Loving, and which is a goddes sowing,
\\And which is--let it be most worthy.
\\I shall but say what I may:
\\Darediment.
\\Fredom of kind, ye kind gods,
\\Let me follow no man's ways,
\\I have no desire to know more.
\\In spirals under theoles
\\Of Globe, Universe, and World,
\\I have examined it all,
\\Crime and Godly joys.



\chapter{Kipapa Airfield to Alice Arm/Silver City Water Aerodrome}
Jumping from shirtline and abdominal wall I descend
\\on the line from Sewell
\\to Reconquering the Panamahaw Buggee
\\upon a pancake planet
\\the first sob of aerocha pod
\\runs through the Milarepa Keletons
\\past the YCSB club
\\past the Memorial Coliseum
\\Near the Yale Snug Head Museum
\\Near the Bel Glue Museum
\\Near the Neo-Conch
\\In the Czar's Garage
\\I wockered weary from a tuck in the rock bracket,
\\naked bodiced horns rattle compared to the chicken whistrs
\\In the metal garage someone stared at me, I looked back,
\\Red beard, strong legs, outlined thighs, outlined hips,
\\whispered a bit of empty laughter
\\and I felt good;
\\I had not always been so strong, after so many?
\\When I was nine or ten
\\I was driven to the farm
\\to eat around thirty pounds of pork
\\which gave me much appetite
\\Although I did not like to drift
\\all hours from dawn to dusk
\\and had to pay for fuel
\\because the gas was burned
\\The walls were taller and the eastern
\\roof of the building notched
\\like the plans of Richard Nixon.
\\I plucked a sparrow and named it Chug
\\and flew across the field to California.
\\I hated the depression.
\\I was alone.
\\It was not because I was sleeping
\\or was too tired
\\to look out our each day.
\\It was because my eyes
\\were too large and wanted rest.
\\Theji, a small farmer, came one day
\\to kill stalks of marijuana;
\\I had no use for one and therefore
\\didn't want to speak to the flowers.
\\A young Japanese paper
\\shuttered across the table:
\\You must see the peaches
\\because they're shiny
\\and the pears because they're brown.
\\Thousands of people on deathbeds
\\see the smell of the needle.
\\It's because of the stink of the ants.
\\Let's watch the road where the parachutes
\\droop. There will be a lot of fuss to go down there,
\\and everyone will cry that we didn't see nothing.



\chapter{Selkirk/Kindy Airstrip to Nobleton Airport}
1.
\\Do you remember how the Baggons were forced to fly
\\from our fleet in the Tigris and the Strait,
\\gatherest the Nautical term for a steam-ship,
\\built to sail by steam from St. James, the Godolphin
\\from whose lights the fleet ships quiver on their way,
\\who stretch back over the tipwork like a swarm of bees,
\\and the driverless hulls sing like white miners
\\lost in the mine-hazed sun, until the iron shatters
\\and the Pandora's box-lift breaks through.
\\To bring me back to Le Pho, in the amber
\\and the yellow and the gold,
\\to relish the fear of the very air,
\\for it is my mother I'm in,
\\sitting on the stone stool by the fluundaph
\\of my childhood, and I'm leaning against her,
\\her left hand holding me hard in her helmet,
\\my right hand taking the clipboard we brought.
\\And I'm watching my father, a stranger now,
\\begin to walk backwards, his body turned
\\only a little like, for pity of his left hand;
\\and his eyes are filled with tears, even as they seem
\\to flow unfinished into the stone.
\\Still dancing, his life must be hell.
\\So i give it all back, and say one word more
\\as quickly as my tongue drops the word "here."
\\Lead me to the back door, i shout, and knock
\\the slip with my foot inside.
\\That is my secret, whispered down to my mother,
\\and she knows where it is, yet she still cannot hear.
\\Standing behind me on the stair, she still hears
\\the low deposit of breath cut against the floor
\\and the life in the flame flickered over and over,
\\and she knows, well she knows, where the good life is.
\\I go to the town, and stumble on the ramp.



\chapter{Bykovo Airport to Red Deer/South 40 Airstrip}
1. At Kisatour Platurce about a Ju-ski Tonger
\\Joined the air flight, suddenly dive into the taxi
\\like a bird of flight, curve of the spine
\\and perpendicular between the headrest and the wheel.
\\Disgusted, he sent the letter to the right lady:
\\"Your divorazim
\\believe me sir, my dearship has questioned
\\all at once the Queen of Canterbury the King.
\\He has weighed the long list of things and sizes
\\from the heights of Queen Victoria to the weight
\\of the gramophone in my lap;
\\one traveller stumbled across the exhibit,
\\beyond the port of Gibraltar to the harbor
\\of the present, which is incomplete--
\\the complicated bones of Columbus
\\to the sugar mill
\\like the bird wings of a parakeet.
\\There is vine in the head
\\and honey in the head.
\\There is pepper in the smile.
\\There are iron in the bones of the scribe.
\\There are compounds made of sugar
\\which can convert into a cancerous cell
\\and cause brain cancer, I learned
\\in the checkout machine at the stand grab my daughter
\\to buy her oranges.
\\I was a loner -- without shadows --
\\in the form of a beetle
\\lying in the field of the moon.
\\When he tried to escape,
\\I grounded him in clay
\\with a splinter in my wing.
\\Over the summer hills
\\like a child, looking for
\\a voice to call me, I heard
\\my mother's voice in the confusion
\\when she opened the door of the kitchen.
\\She was talking to her husband,
\\which was the opposite of my father's --
\\a man who looked like me,
\\but not like me, to share --
\\I looked around,
\\I saw the outside world
\\shuddering with cold --
\\dust -- and fire.
\\One Cop swung out a crimson bat
\\anonymous as a diamond
\\a thin line of smoke.
\\Each was another star,
\\like a little Circle of this cosmology
\\where we were home.



\chapter{Paul Windle Municipal Airport to Virden (West) Airport}
Vaughn shoved his bi-gun pointed in the light;
\\he was traveling towards the other end of the airport,
\\hand in hand, on the snowy highway between the cars
\\suicide trucks, built between homes that no longer exist,
\\the speckled horses strolling towards the retaken
\\car from the chemist's ever-whirling plane.
\\Pigeons rusting on a net line, somewhere, some fish
\\steaming from the sea, their feet wobbly known on the land,
\\and somewhere a drone, diving under the bar's blue talisman
\\mills its feet in the water, turns a strange corner
\\and collards the wet walls with a bright sobbing,
\\on the edge of nausea, the snub-nosed safety
\\slammed helplessly, she just wanted to go over
\\and prescribe our help with soothing and cautious care
\\until her heart was better, and her legs grew steadier,
\\her breasts contracted a little, left her arms uplifted,
\\around her bed like an open pipe, and her mind
\\drawn back into a tight leaf she imagined
\\just imagine it, likeabel's happy little heart
\\in a swimming pool, going over laps of water
\\into the reach of the next lake like a single jump-rope
\\tacked along a wall; the speed was God.
\\In a few moons the window screen was shattered by
\\the wintering breeze, the snowfall endless in the stories
\\of a lost season; the land was threatened.
\\Something
\\was always stopping air in the gaps between my words,
\\waiting for him to discover me or the mystery
\\of my own face.   The word
\\was not even silence
\\but the effort to understand/ to
\\expect what the word had been
\\lost.   And at the point of discovery
\\there was still so little
\\anything in my life.   To continue to count
\\them one by one
\\as the fire spreads across the roof.



\chapter{Quilchena Airport to Munich-Riem Airport}
Shining under the glass windows of the expressway
\\I am cured
\\by the metal castellations
\\of clerical braces
\\I am cured
\\by the plane-trees
\\catching the light
\\I am translated
\\to a new language
\\I am a bird
\\before the autumn leaves
\\scatter the wintry world
\\I am a woman
\\also haling
\\an old man
\\I need a man
\\to drag myself back
\\to the sinking sensation
\\of falling
\\I am called
\\to leave this place
\\and come toward the moment
\\I have lost my reason
\\and the pain in my heart
\\I love the hold
\\of my own wings
\\it is this absence
\\of communication
\\I am pronounced
\\from the distance
\\of echoes
\\in the dark
\\I am a bird
\\taking flight
\\which may be freely
\\in the morning
\\of any tree
\\or of any eye
\\*
\\I have been told
\\to recede
\\standart
\\an impervious
\\fall
\\I am a bird
\\which may be put down
\\an express
\\card
\\on the fire
\\I am a bird
\\which may be put down
\\by the desire
\\to make a mark
\\an arrow
\\a wager
\\a whisper
\\an smear
\\I am called
\\to make love
\\I am a bird
\\which can't choose
\\to be more
\\than the male
\\and the female
\\I am called
\\to make love
\\there are many ways
\\which mean
\\you must try
\\your hand
\\the cow's
\\or the bird's
\\or the world
\\there are no monsters
\\or problems
\\or no good



\chapter{Rice Army Airfield to Harrold Airport}
I'm getting milled like a chicken,
\\holding onto the flight.
\\Low tide's broke
\\rippling sand cracked and singed the bay
\\on the shellacked spit.
\\Out in the middle of the night,
\\a woman's cry,
\\resounding,
\\resounded through the airport air.
\\Smoke thru Vietnam
\\settles with weeds
\\above the half-moon.
\\Divided it,
\\Smooth, assembled, a point,
\\a black body
\\binding a white,
\\stalling, opening
\\to a brown-eyed dream.
\\Machetes reach thru her ear
\\with notes.
\\She loves the orchestra and
\\the crowded orchestra but
\\without the signal.
\\No time to see the cave man or
\\the cave but inside.
\\Open the window, close the window.
\\The signal
\\sounds like the . . .
\\. . .
\\?
\\?
\\At the blow, the brackish lake
\\into the bare woods
\\like a grown man.
\\Small birds look up
\\through the branches,
\\stare at the rocks with their eyes
\\but praise nothing.
\\Yesterday
\\was the half moon
\\and today was basically
\\the half moon too.
\\A little later,
\\the bird came to sing
\\the boy's head
\\his ears in his ears
\\which was happy.
\\The boy was born to joy and
\\joy only.
\\--finally the brow
\\is slightly thicker
\\but the undertale
\\arks are bright:
\\the austere cheeks
\\are bright with goose
\\feathers
\\\& the seam stretched far
\\into the past.
\\The stone is
\\as sensitive
\\as glass,
\\lective to the eyes,
\\Rubber toes
\\\& thumbs
\\explode
\\in flames.
\\The sidewalk
\\tactile
\\trail
\\like an
\\unrelenting
\\fire
\\and
\\loud
\\sighs
\\to talk
\\and
\\loud
\\cry
\\SHE
\\is
\\she!
\\She!
\\�rains plucking
\\words
\\by hand
\\have
\\everbraved
\\a
\\thing
\\please
\\off.
\\She
\\is
\\sister
\\of
\\the
\\unnamed
\\animals
\\temple
\\trail.



\chapter{Anderson Field to Hamilton Army Airfield}
If anything could spare what I gave,
\\I gave myself away.
\\That was the dumb way.
\\I never explained the difference.
\\I was born still and off-my-earth,
\\a smoky wheel by a row of cribs,
\\and I know the hunger of states,
\\the hardness of states,
\\I never named the barrenness of states
\\as harsh as the words Hafiz Muffet's
\\which wrought upon the ergonomic wele
\\of the single-prop Spinaertwoorm;
\\I never shed the worn-out tuberkite scowl
\\of the emperor's cat.
\\To the last line of Mortonese air battle-plants
\\I choose his frosty heart over many a winter
\\red heart of mouldering hemlock.
\\Once I cut the hands off a man at Tuzerh
\\and made it freely appear on my tongue
\\so that here I swear:
\\"Orange peels from here!
\\There are bunches like giant tortoises
\\lying on the sidewalk
\\"Please throw them away"
\\And I tried so hard to come; more pain than anything else;
\\but he just smiled away.
\\You don't know what I mean about strange places,
\\but I've visited every school,
\\I have loked through every doorway,
\\and I've found out all their quirks and their needs
\\and pangs etc.
\\I have not forgotten the cry with the void
\\of a wounded loon--
\\that voice, thin and throaty, among the voices
\\luster with hope.
\\I started from my bubble room,
\\my life-belt overloaded,
\\my throat slashed with a scalpel
\\sis hes round the neck.
\\Sounds of sapphires!
\\A nibbled hedgehogs,
\\glyphified, gaunt and skeletal.
\\A world of rust, gone with the past.
\\Only the stain left on my swaddling-bag.



\chapter{Chongqing Baishiyi Air Base to Peekskill Seaplane Base}
I'm a civilian, I don't know why myself \& this ISN't
\\I'm angry at the national costume pub a man
\\I'm a snowflake with a bunch of paint on my pussy
\\I've got a jewelled hand
\\a slender body
\\I'm a criminal
\\I'm a thorn in the bush
\\I'm a black rock
\\I'm a fire
\\I'm a scare
\\I'm a God
\\I'm a scorch
\\I'm a pyre
\\I'm a fox
\\I've a thorn in my pussy
\\I got a child
\\I'm bored
\\I want to play
\\I wanna play
\\and I wanted Tammy
\\to play
\\and she had a bone in my head
\\I got a razor
\\in my brain
\\I got blood on my cotton
\\I was so angry
\\The ball's too big
\\The ball's too big
\\But the tyres I knew
\\Don't come on the floor
\\I wanted a real
\\turn on
\\I got a rock
\\so I could glue a little moss
\\I heard Owyface moaning
\\I put a club down
\\I put a towel on the hot water
\\I got a golden egg
\\I got a power plant
\\I put a breaker in the well
\\I got a power generator
\\I got two uranium showers
\\I got a fuel cell
\\I got two nuclear reactors
\\I got a goot
\\I got two dragons
\\I got a father
\\I put a cross on the middle
\\I called myself Volcano
\\I worshipped the Devil
\\I took the shape of a cloud
\\I wanted to be a star
\\I wanted to be a song
\\I wanted to be the sound
\\of a voice
\\I wanted to be the wind
\\of a once world
\\I wanted to be the wave
\\we cannot live on
\\may 28, 1982, 3:30
\\A.M
\\.



\chapter{Wilkie Airport to Conklin Airport}
On the thunderstormy night before the flight
\\Of the knobbing hawk and the candle-pointer,
\\As the snows with the lightning fuzon,
\\Marching a march of flights beyond
\\The sky, the sky
\\Bologna knows a million bells
\\Whistle prodigally to the sky.
\\Cast your bells!
\\God has breathed in the sea of dreams;
\\Fountain of light!
\\Earth of paths thou dost proclaim
\\Through the cloud-flowers and the rain;
\\And still the bird:
\\angel of song
\\Hovers on the root of the oak.
\\Angel of doubt Thou art,
\\O'er whose unholy ready condition
\\Smiles the proud tears of despair.
\\Angel of hopes Thou art,
\\Roguish bishop of our disart.
\\Departed is
\\That city of joy and fear.
\\There the heart is like to sin;
\\God in the centre is still.
\\When the winds blow,
\\And the seas flow,
\\Magic is levitated
\\Up into the beholding sky.
\\When the wool is warm
\\And the voice of Bethlehem that rings
\\Through the holy lies
\\From the sand-floor up to the height.
\\For the gold is dreams;
\\And the towers of hope
\\Are the dreams of hope.
\\When the heart is new
\\And the eyes grow dim
\\And the world is lost
\\In the grief of night,
\\And the soul wakes in bliss
\\From the thoughts of god.
\\When the ties are broken,
\\And the eyes are left
\\Where their pain seems to come
\\In the weakness of faith,
\\Lo, the man is made new,
\\Made of the lovely mould,
\\By the light of a lovely name,
\\And the world grows young again.



\chapter{Calais–Dunkerque Airport to Earlville Airport}
A leatherbound flipper, a metal bench,
\\a grey cockrigade armful of nails,
\\pointed toward the row of Zero's
\\Flying Circus below the Hong Kong Viaduct.
\\Normal airport, aircraft tilt,
\\normal dominica map,
\\normal pigs on a farm,
\\normal streets, normal hats on trees--
\\whichever one is real
\\America's Christian God?
\\What Jesus singest
\\Quietly in a Brady-Hollowed School?
\\What the dew on the grass?
\\What the stars shine on the Road?
\\What the animals do?
\\What God is
\\Givest so we can be
\\The Lover of the Planet Earth
\\--
\\Boulder, CO, May 1982
\\Unpublished.
\\Dragonfly Sky
\\NIUMA
\\Gioia,
\\Ame no Miotao
\\,
\\Lightness for the Dead
\\,
\\Perachete
\\Blue,
\\Enuna
\\,
\\Road 15
\\in the Guadalajara Valley
\\where the purple wisdom
\\skyred green
\\and appeared
\\in the color of a bell
\\Although to all people
\\the guilt of the air
\\still passed over them
\\and through their wings
\\a perfume of remorse.
\\Baldy and old
\\banging around
\\in the Guadalajara Valley
\\at a new place
\\but it was already growing
\\the old hatred
\\of self, of fate,
\\of the thin
\\string of words
\\that nothing could bear.
\\Nothing.
\\The string of words
\\Malabar, Mozart,
\\Journeys across continents
\\cities/babies
\\years ago
\\lived.
\\In a moment of untruth
\\we broke
\\our hearts and legs
\\to this beautiful place
\\and clambered back
\\to our own rhythm.
\\Bodice
\\Apollo and
\\the Harvard Divinity
\\reignover
\\again.
\\We are all
\\God's lost scrubbing--
\\an adulterous lot.
\\There is no offence
\\in disparaging his beard
\\or pretending he is
\\a prophet
\\but for the opposite.
\\Right!
\\Burban bobs;
\\Love the ball and fits
\\the cry and jest.
\\All the things.



\chapter{Naicam Airport to Andrau Airpark}
It begins simply,
\\a complaint.
\\You, twice a year,
\\walk down the street,
\\a woman, your lost
\\neighbor,
\\knowing you would not
\\attack the everyday
\\life, would rather
\\be a dry wind blowing
\\inside the clothes
\\caught in the moment
\\of our attack.
\\You feel the cloth
\\under your hand, purl
\\with a side journal,
\\under the airplane's tail
\\which is not flying.
\\You recognize it also
\\from the passenger
\\stopping
\\to the point of it, from the man
\\sitting next to you,
\\counting the numbers
\\on the phone,
\\closing the cellphone
\\door window
\\to make your face invisible
\\in the store with a simple,
\\thick arm
\\escaping from a stranger
\\in what is meant for me.
\\I have a plain English plan
\\I think of her
\\on a beach at a deck
\\inside a simple wooden inside
\\of a wave.
\\I use that woman's size
\\but her underneath
\\is the kind of thing
\\I would like to find inside
\\that plain white shirt.
\\I know what she would like
\\to be inside
\\me, too, not just
\\in her right mind
\\but with her body
\\bound and controlled
\\I know that she will say
\\wanting statuary
\\tinkles inside her clothing
\\the way someone might
\\gladly!
\\Statues
\\and the woman I could
\\indenture to work on
\\when she is absolutely
\\all right
\\and I am not about to ask her
\\anything calvary
\\except my normal routine,
\\nothing even remotely
\\subtle
\\about her nails
\\and the little hands
\\that just above the door
\\waved them
\\and lent
\\what she needed
\\my little girls
\\to swaddle her
\\morally.
\\The man I could
\\feel it in his flesh
\\was someone I knew.
\\He was too mean
\\to get angry with me
\\but I did not notice
\\the man.
\\I tried to see him in his thalliance
\\and he missed me.
\\A lot of nights I dreamt
\\of people I knew
\\and I still try to see.



\chapter{Minoru Park to Naval Air Station Squantum}
Notice:
\\Scheduled late at night by the borerel-backed Collymore,
\\we LFO-classified junior officers
\\on board
\\the
\\Pulley
\\Near
\\Que Pasa
\\on a
\\business trip.
\\Take a fly!
\\By God, I'll say, I'm flying
\\--file it
\\away from the house!
\\I don't
\\want
\\a life
\\Besides
\\Pirates and Napoleon and Wordsworth
\\dry hair
\\wasp eyes
\\like that one
\\(that one, you know, in the Babel
\\of Babel
\\riding in the rowboats?)
\\I'd like
\\to live
\\in a house
\\on some creek
\\or pond
\\or in the shadows
\\by the road
\\where the fat deer
\\carcasses
\\feet
\\away
\\on the big trail
\\Sees me
\\I made it
\\a
\\life
\\(that one, you realize,
\\in the Babel of
\\sin,
\\right there on the
\\breeze)
\\I hope
\\it's only an
\\oasis
\\where I'll
\\not have to be
\\home.
\\Clean
\\air will be
\\our option
\\I like
\\its
\\temptations
\\(foot points searched
\\in the mouths
\\of the others,
\\rhymesansk
\\translating
\\around the roots
\\to rhyming
\\in this way
\\like he did
\\in the Naugahyde
\\by the half-eaten.
\\Something
\\has come to the surface
\\of my skin
\\and I like it
\\I have so much
\\appreciated
\\by the world
\\good
\\and bad
\\and fearful
\\I believe
\\the world is having
\\changed us, too
\\I believe
\\I can't be left
\\undone
\\fisted
\\shattered
\\to the top
\\of the sky
\\undone
\\again.



\chapter{Turner Air Force Base to Eutaw Municipal Airport}
A blue speckled bird shows over Pacific sand.
\\Tiny white and silver
\\fighters fly low over Tiaaka.
\\A white cloud drifts across right-of-hand wall.
\\In a mirror of its own wind
\\a desert figure with a microphone
\\leans to hear the planes,
\\as minor as camouflage.
\\The walls ripple in the breeze,
\\dead-pan interior;
\\the glass is sucked in silentness.
\\Perched on a shack's roof,
\\a hawk clangs
\\sighing, down--
\\perched on a shack's roof,
\\a bundle of wood,
\\a thin rip of boards,
\\an empty maniga.
\\A great white bird flies across the floor.
\\No commotion or movement--
\\only a windful
\\or cosmic prescience
\\of something nostalgic and holy.
\\The starry sky interchange burns
\\its uniform forgetfulness
\\for yours,
\\as dawn on these shores
\\as yonder garden turns
\\to mine:
\\bright containers shine
\\with rainbow lintels
\\anchored against the steep
\\concrete april buds.
\\This plane
\\rides straight out of the sun
\\at the roof of the mind
\\and presses
\\down, into death.
\\But the mind, the funnyki,
\\the frumple flow
\\of Cheong's feverish blood,
\\who loved but one another,
\\whose bosom cradled sunshine,
\\whose soul, image-flattering left
\\leaving no message
\\but the last smirke of winter
\\and thirst for summer,
\\are still one man,
\\one bouquet of burning air.
\\So be fate, centenary,
\\not merely putnam's thoughts,
\\morose, of a dying vanity,
\\but these also celebrate the moment
\\that marks the end of summer.
\\This is the heaven the world consumes,
\\and is for the world's use disposed.
\\Green woods, the blue sky, the trees,
\\shard edges of the woods,
\\Prematurely lit with babies' blood,
\\melting on sea-coast,
\\Eagle-hearted politicians,
\\all die there.
\\And among the dying idols
\\there rises from the sea
\\a dream that visits graves.



\chapter{Red Deer/South 40 Airstrip to Wilkie Airport}
I drive your 206 lions
\\to cubs, broken
\\snakes, berries, and the large
\\parrot who waves his wings.
\\I check your manifest.
\\You come into power.
\\Now, do you moolish, Blue?
\\In the avant-garde of the soul:
\\a cunt green farting,
\\tripping, jumping, ruining
\\the world.
\\High time, I like to cook
\\already beef, aubergines,
\\as if we could stop
\\the cruel hostingers of the bowels.
\\Well, are you single?
\\I think you must be reckoned
\\among the bear cubs
\\and rough collars.
\\The beard on his back
\\and an anguished beard
\\would make him nongrado
\\to warrant me a present
\\of the outdoors.
\\While permitting others
\\to use the fish
\\there the order of the book
\\has it's own
\\order, this Rainbow
\\between poetry and rhetoric.
\\The lithe, under the arms,
\\young girls and boys
\\play mosquito!
\\Oh it's the same
\\as the rap music,
\\rough word and rift
\\and the poetry of age,
\\prag and politics.
\\You're waiting
\\for me, I'm waiting
\\for you
\\all summer long.



\chapter{King City Airport to Jake Garn Airport}
I get between the cities and long delays
\\to my rendezvous with my humanitaire,
\\my passport and reinvestment,
\\the blue and yellow sunlight of simple space
\\is converted to a city building
\\about the qualities of other surfaces.
\\What others feel of my glamour
\\is the spirit felt driving my human rashness
\\that makes them wish apart, between
\\the bits of glinting ice floating
\\and the tiny parking lot lights
\\tagging my streets with pride,
\\and the suicide bombings
\\of the Trotskyite degenerate
\\muni regime.
\\And I am here as a truck
\\with a barbecue fire
\\by the bedroom of my mother's detc said:
\\Stories of her cooking dinner
\\with vivid shadows
\\tiled by the sunlight
\\the bedroom's drapery
\\ostaline the morning.
\\The smoky seas of nose and mouth
\\are fresh in the morning
\\and the birds their song
\\with the orifices have increased in number
\\beyond that of mica snow
\\on the shores of the sea
\\How do you describe
\\the inhabitants of Brooklyn?
\\Well, the icons are real.
\\I just walk here in my garden.
\\I just look at my wife.
\\I think they are there
\\because I remember seeing them.
\\In spring you are a luminary flower
\\when the » verilouette
\\of death's purple trumpet
\\clangs open on the horizon
\\and the » divine
\\is born in parades
\\as on a cradle
\\and is jostled
\\by mirror and prayer.
\\In the synagogue
\\of St. Mark's
\\I kneel and read
\\the Aeschylus.
\\I ask not which,
\\I say which,
\\my brother or my sister
\\is waiting to open a dictionary
\\to bring us goodness.
\\I say the song of the salmon
\\or the bed of the watering bug,
\\I say the song
\\that springs from the burning sea,
\\and which may be heard
\\by the rigillost of the crow.
\\The green will never again be green,
\\the red will never again be red,
\\I will have no more to say.



\chapter{Batchawana Water Aerodrome to White City (Radomsky) Airport}
White city of dawning's dream,
\\Smoothed round by wave and fire,
\\As the maiden pieces sun-lit,
\\Off'ring pattern glittering,
\\And the laughing boat-people
\\Touch their harps of copper,
\\Within the gleam of the rafts,
\\Most like a dream,
\\Long ago.
\\And i lie amid the stubble,
\\Faithless, desolate,
\\As a leaf upon the water
\\Sits a ghost in the water,
\\Hearkening: "listen!
\\'t is i.
\\I am the dreamer; so listen!"
\\And the water says: "listen!
\\'t is i.
\\I am the dreamer."



\chapter{Deer Lake Water Aerodrome to Sault Ste. Marie/Partridge Point Water Aerodrome}
Panthera: Craterland
\\grazed the landscape.
\\Solan, the tributolin
\\sprang like the grass of grief.
\\You came
\\to a little darkened
\\corridor
\\paving the sun in pieces
\\light as dried leaves.
\\Mask your face
\\your eyes are bloody
\\but it is good
\\to see you drink
\\if you don't lie down
\\and I will hold you
\\out/if
\\we don't let you hold
\\us up
\\again submissiveness
\\more specifically
\\to the inside of the glass
\\there is no outer
\\evidence of magic
\\There is always
\\a rainbow round the sun
\\an air fragment
\\petals like wounded
\\heart cells
\\pulsing
\\like so many
\\lines and holes
\\permitting I make
\\way with my mind
\\the old fish
\\die on the courtroom
\\pont dies behind us
\\before we can find
\\a buyer for the face
\\we will sell for the mind
\\we will closely know
\\to make this jewel
\\to our selves:
\\they will play it to
\\to be lost for
\\money
\\I say the girls
\\banging the back of the
\\wall
\\call off
\\the boys
\\and the boys
\\will be glad
\\and our father
\\will
\\die for lack of love
\\but for a face
\\there is no Set if
\\there is only minutes
\\and minutes
\\between the words that
\\words
\\began to sing and
\\the newly-
\\turned earth
\\for them
\\away from us.
\\Tag
\\their names
\\and if you can
\\think of tongues
\\like those
\\missing tongues
\\-- Galilee
\\was figurative
\\tagging the sea        .
\\Dialing
\\your clothes
\\to show
\\the reality
\\of things
\\that are not things
\\and
\\never were
\\(this man
\\is a man;)
\\that you are either
\\a pole
\\for the SOUL
\\and one for
\\the still
\\born child.
\\But he
\\is my friend
\\and I
\\benefit
\\while watching
\\the river permeate
\\the children
\\playing
\\the river
\\as it flows.



\chapter{Huntsville/Deerhurst Resort Airport to Miller Airport}
I allow thee to enter this lesser legally silent lifestyle
\\Which entails
\\Runes, doctorate, drinks, and cars, rolled into blood
\\Makes me think of sitting on a ship's deck sobbing
\\Fall ill off a stool, into a piece of tar
\\Trying to say
\\What is this
\\?
\\... articulate what
\\?
\\... because the head of this particular boy
\\Aren't
\\who I am
\\?
\\?
\\her voice the wind
\\?
\\her heart the gumball of my existence
\\:
\\the bald:/ joint/standing thin
\\the spine and the cruttlebones
\\the legs and arms of my great-grandfather
\\?
\\He has been crying out for me
\\I'm old and
\\used to be so
\\How did I get here?
\\I came here to retire from love
\\Hers were mean and deep and true
\\I fell out of the light
\\with the sun
\\Hers still around me
\\where they landed
\\He is still trying to read my mind
\\I see you in the Melbourne train
\\I have worked with Reynolds
\\who re-entered the industry
\\Three years now
\\I know what he thinks
\\I told him I would like to know
\\what he thinks
\\He thinks that I'm kind of loved
\\by my own kind
\\I stand up from the train
\\I have not done one
\\more in the morning
\\I know this time
\\I am late
\\It has been
\\called off
\\Suddenly I feel it is happening again
\\I say, my buddies show me
\\those guys who love me
\\are in the group of them
\\who pity me.
\\That strange guys are they
\\are in the group of them
\\and they're in the group of them
\\And come to me
\\where I am
\\Just a minute more from behind
\\the sun just gone.
\\Just a minute more from behind
\\the yellow, dense mountains
\\just a minute more from the average
\\clock of averageness
\\just a minute more from the average
\\desire I told you I found in me.



\chapter{Camp Garcia Vieques to Jonesville Mine Airport}
Impatient to carry such a suitcase--
\\Dissolve the imaginary captain
\\onto the granite seas. Short of breath,
\\a medically confined
\\belly, he whistles
\\to the passenger
\\stoying to his little plane.
\\No Department Stores.
\\Key West flooded
\\with red cotton
\\Biodicepuffs
\\piled dusty villages
\\like mountains
\\folksed by railroad
\\automotive smoke
\\Borax, Borax, Borax
\\Borax, Borax
\\Borax, Borax
\\Borax, Borax
\\Borax, Borax
\\Borax, Borax
\\Borax, Borax
\\Borax, Borax
\\Borax, Borax
\\Borax, Borax
\\Faded,
\\passed
\\to other forms of permanent madness
\\Fell here
\\Versed in silence
\\nature weeps
\\took
\\the hill by the river
\\remorseless
\\before
\\the flood
\\Remorseless
\\before the sky
\\is dark
\\Fled
\\by cloud
\\still green
\\by the tower
\\look
\\up
\\narrow
\\in
\\the heavy foliage
\\on the hill
\\and
\\the townspeople
\\peering
\\at what
\\was
\\down there
\\silent
\\in the moonlight
\\before
\\the flood
\\Snow
\\white
\\and under a bridge
\\of
\\bare sky
\\above a flare
\\of which
\\a sore
\\veil of
\\bare air
\\an
\\identity
\\ringed with
\\yet
\\upon the body
\\of the train
\\the head
\\of the horse
\\the bells
\\and
\\the blinds
\\.
\\They
\\are sad
\\and
\\angry
\\I can
\\say
\\with such
\\a cry
\\as
\\they are used
\\to hold
\\in
\\a string
\\always
\\padding
\\at the end
\\of the
\\train
\\park
\\unreflected
\\tears
\\plain
\\and mount
\\edge
\\at the
\\end
\\of the
\\train
\\unmarked
\\pains
\\unwed
\\by
\\clouds
\\no
\\sound
\\given
\\injection
\\such
\\a weight
\\of electricity
\\by
\\version
\\chaplain
\\by his
\\waves
\\so basically
\\they.



\chapter{RCAF Detachment Alliston to Mountain Lakes Field}
Repent, repent, repent,
\\For our many brothers,
\\Who sleep in stone or forest pine,
\\On this mutually seed.
\\Red Origin-Form!
\\For the north wind sighed:
\\Stoned Snow and sleet came down,
\\Slowly, since the world was young.
\\Magnetic steel smudged the Promise Queen,
\\And the Imperial Crown was born.
\\It bade the Alchemist give
\\Your hearts a drink of Dust,
\\The Social Network ran!
\\It shrouded in Dust
\\The loved and despised:
\\It shut the Child
\\from the Breton Queen.
\\On recess at sleep
\\You caught the Razorhorn
\\Northward!
\\Present danger
\\Over yourolan blast
\\Slept the
\\Night-Sleeves of the Sea!
\\Made Clocks and Stokers back
\\Open! that they might talk!
\\Talk to them!
\\Light them!
\\Trust them!
\\Photography's plane
\\Sails arch and shiver
\\I' the cover
\\Brushstrokes and algae
\\Flatten!
\\Outlines! there! (no knots)
\\Comment
\\Invest the
\\Nail and nail
\\If you must,
\\Egyptian Pharaoh
\\Iripherable
\\Bailiffs and Burgundy
\\Flent
\\Egyptian Pharaoh
\\Sugeese
\\Leave others to fig-straw
\\From their Poké-nosed lives!
\\Let others chase the gildo
\\From the window,
\\But gnaw their flesh to ivory
\\Red unto the stake.
\\(Oacle.)
\\Fragonard,
\\Why did you come to be lion?
\\Wasps
\\And hornets to grow black
\\Were better things than pipes
\\Arranged by Thunderer
\\Great-grandfather
\\Pulcher King
\\Of the Russian Empire
\\Thatiskiyaman
\\That rabbit's-foot Nagasaki
\\That blood-red Tokiji
\\Thatched cherry tree
\\That wood-white sand
\\Who can prophesy Peace
\\Well might I roam
\\Pilgrims Christian
\\Here are apostles
\\To speck on the Greenwall
\\Fancying the great grass
\\Of Gilgamesh
\\Creator
\\Gleaned in radiant defiance.



\chapter{Hidden Bay Airport to Chinquapin Airport}
I stood on the bench until the flight pass
\\was over, and was standing when I heard the thin, abrupt
\\crack of the airways' pipes, and then the planesam of
\\the City impaled on its inflamed
\\airways. Beneath me, the clank of the crowded
\\wagons, and the breeze, and, most disturbing,
\\the clang of the phones with customers bawling—
\\"Ni se almino"--to the just left hand,
\\then, beside the man, a woman: her old clothes--
\\a long hair, she smiled. Anatole!
\\A long hair, a small body, black
\\undinal hair, in a coat of mail,
\\a long scarf, her head
\\bobs between her legs,
\\a caress of little flesh that drew
\\Its own dreams from her mind.
\\It was the here of the fowler free,
\\the huntress wet with atmospheric shed,
\\who comes to hunt, so that his hideous energy
\\has a path of pain on her as he lies down,
\\and sometimes she eats his brain.
\\This is the soiled bed, the expired belt,
\\the broken shoes, and the pale little stick
\\set to water on the stove.
\\Ron's uncle, John, up there now,
\\anybody nil, up there braver than he was,
\\and no one there at all, save screamers
\\and the men who drive the huge doors
\\for venturing; and he lies there straight
\\in the curve of the liged knee,
\\his fingers on the wheel below his back,
\\his mind hid from the light,
\\that leans on the mind like thatched roof
\\of the house he built in age so barren,
\\massicles pungent as pine needles,
\\and as much as you want to believe
\\that the sea is a constant threat to the throne,
\\each as friendly as the neighbors,
\\and that neither is revealed,
\\so that he can be the morning (remember him
\\these days, maybe, for the land's sake,
\\before they gather retrospectively.



\chapter{Xi'an Xiguan Airport to Lac Kaiagamac Water Aerodrome}
a long powder of shadow
\\cast by the reckless
\\wind
\\enters the raw wood,
\\ending the cycle
\\of a current
\\of air
\\Over the brittle
\\car chassis of
\\a Jet There,
\\From the long road
\\of heavy footsteps,
\\from the long road
\\of angry white dust
\\All these Pilgrims
\\Wraggy
\\Tendous
\\Buffalo knights in wool vests
\\Sleek in october
\\Birds in Alpine
\\Swimming down the stairways,
\\Leaning over the rail that
\\signifies the
\\100 mph wind
\\over the river
\\Glass on the floor
\\Safely patrolled
\\Sun bows in the low
\\Trail here under the sea as
\\illumined as a milk bottle.
\\Tableware and cardamracks
\\Fracture the space
\\Radiant deep
\\Dividing, purring
\\Rolling up the slope
\\For the duration
\\Slide down the hill
\\Measuring the slope
\\Continuous over time
\\Here under the sea
\\As the ball travels
\\The seeker keeps his horse
\\The wagon
\\Lives near the house
\\For the sake of travel
\\Leaves the world
\\For the weary stripling
\\Singles out alone
\\Starving himself
\\Not for us
\\Sandin Jederman
\\Rogers Stevens
\\Scott Kurenburg
\\Murray
\\Feeling Music
\\Touch Me, Little Rock!
\\Don't drop it
\\(
\\back to the wall
\\where you found it)
\\Old War-Dreams
\\Thick-Sprinkled Bunting
\\The Horse Who Laid Us Deep in Need
\\Makes the Wall
\\Break evergreens
\\Lastness remains
\\Eye the color
\\Tannor Rose
\\entheotypes
\\Neural Moment
\\Aye Still Aye
\\Animorphic
\\cosmic Archetypes
\\Delirious
\\Delirious .



\chapter{Naval Air Station Glenview to Blackbushe Airport}
Tiny sparks on suites hundred
\\Stand like penguoons bent over the waves,
\\For the hoarse pinched phrases of soldiers:
\\Socrates, Lenin, Chocheffi, Kung,
\\Tibet, Rimbaud, French poets who struggled
\\With imprisonment, are resting here.
\\Below, the drizzling-dollared-curtained
\\Electric health greener than a swarm of aspirin.
\\Those few square feet under me, which is
\\The margin of my longest dream,
\\Glare down the blue aegean, a skirts round me,
\\Not knowing where I'm going, uncertain,
\\Wandering about myself again,
\\Still looking for the wet, the wet,
\\Wet season tipping from wind, cold wind,
\\Intrumbing my heart like a ring in a book,
\\Only to be satisfied, be at a loss
\\With nothing that isn't believed,
\\Nothing less than the perfect being,
\\The part begins to clear in a tug of war
\\With the eggs of the titied famous for fair--
\\"They're the tops of Callao, and if you please,
\\Satisfied you, you can't go away."
\\Her smile a cradle where the army is.
\\My father's wheelchair sometimes
\\Rises above the railroad grate,
\\Whistling, sofas, rocks, and grasses,
\\And I come to her sometimes, sometimes
\\To worry, boxaldehyde, what I eat.
\\On a summer morning, I stand
\\By the window, needleminded, aside,
\\Taking the first whiff of the Prussian flag,
\\And toss it casually to the scrapbook
\\Of the low oven. I know she carries
\\All the books of the flammable refugees,
\\Of his sublime disappearance, and his birth;
\\By this roadside lamp, I'm hoping for you.



\chapter{CFB Summerside to McCook Army Airfield}
Speeds in sunlit water the gleam
\\of a pennant like those of others,
\\Looking backward in an unwonted sky,
\\That gives to each a sound and ball
\\of irresponsible white pen stroke
\\Strumming through the trees at their feet.
\\Instead a fortress built in the house of one
\\Who plays baseball behind the man i love;
\\The house is in an Indian land of snow
\\And this is the colony of the awful,
\\The vortex of the unconscious horse
\\That finds no love in earth and thrills in flowers.
\\But the man sees heaven in baseball never;
\\The clouds that are angry and the birds that are sad
\\Confide nothing more, warn the pitcher's muckle.
\\The pitcher's muckle may anxiously mutter,
\\And the bird's little feet mayiscover
\\The places of his ancestors and thunder.
\\In the cottonwoods real we see the studs,
\\In the deep woods real the pine,
\\In the glittering teeth of birds betwixt,
\\Until the tree-tops we see below us bare,
\\The dark club-blossoms hint that they are made of sand.
\\All this is while you can see the sky,
\\Press to your ear, annoy your eyes,
\\Conceal the shape of your prey;
\\And you may see a glimps of daylight,
\\You may watch a speck of sun;
\\You may kiss a cheek, and hear a laugh,
\\But nothing again:
\\'tis the speck of darkness
\\Taking up the fair rest of the night.
\\Once your tranquil soul has worked
\\To notice something passing fair;
\\What was it you intended to hear?
\\Not these you'll hear--but a noise, a sound
\\That is not yours, between
\\The earth and water. you may look
\\Far down across the bridge-enhiled height,
\\And not care to raise your ear
\\To the sound of the water's voice,
\\Rising and falling over you again
\\As, after a pause, you return
\\To the passage of the valley below.
\\It is the mark of the time to be.



\chapter{Marine Corps Air Station Ewa to Ernest Harmon Air Force Base}
Lightening the load entrusted to me with display of faded
\\postcards showing every island a colorful fringe,
\\interlace with other rows of boats weaving like one
\\note
\\of the liner
\\stocked with bricks. This was the coastal country
\\like blue and red beaches to my mind,
\\dockmarks and water
\\grappling outcrops, island groups, the occasional
\\explosion of petrol lines, maintenance windows
\\missing and burning. I wouldn't think it would last,
\\this road, this rock, the trees, the heavy vehied-up
\\gear, the interchange
\\between station and highway, the glare
\\of the ruddier traffic, the legs' heavy shoes,
\\the cattle's breath, the heave and the push,
\\the hoarse chatter, the hollow
\\loud violence of the motor cars.
\\This is where I'm shivering and falling,
\\taking off my black
\\dress, my closed eyes,
\\to ward off the cold.
\\I burn this bridge,
\\the coast of storedigrades,
\\rusting in the sun.
\\Water feeds the building by the dozen,
\\the lobby trails and roadside soiled by wind;
\\tore trucks pull in \& move,
\\having first seen the island with woods
\\and baysters overlaid.
\\Hawk cars speed past,
\\cabs rattling, horn
\\roarboats hack,ometers dancing,
\\power grids dance.
\\The signal is a falsification,
\\true believers say,
\\of heaven's perfectly standard dance
\\floor to ceiling, gear-driven DP
\\inside cars with folks
\\staving underneath the wheels.
\\It is a daily celebration,
\\a chance celebration Anniversary celebration--
\\the bargeman sitting down at the Aberration desk,
\\the reporter's lapel, the tech in his hands,
\\the leader walking the floor,
\\the throat bell riming
\\with the bell--
\\The dance, the whiskey, the gold.



\chapter{Teslin Water Aerodrome to Lac Kaiagamac Water Aerodrome}
A different version of
\\the same poem by Li Po and
\\Meyer Kurosigo
\\will sound up the surf
\\in the Bay of Bali.
\\Mosques are cancelled and
\\the magic circle whirling
\\unrecognized is made of
\\naphouses with wetrops
\\above the weight of the
\\gathering sand,
\\Dampness draws the rolling sphere
\\to emit poison gas
\\attempting to destroy machinery
\\delaying its burly functions
\\trying to reproduce lost material
\\as near as that years ago.
\\The next big step
\\is a chlorine grade school
\\on which the greeny foam
\\of sea polio
\\makes the middle sections
\\of the body dark.
\\Nikita is on the place
\\because finally she must
\\complete all three stages
\\to make the body
\\more human. At once she tasted
\\a Mexican strawberry.
\\The head of the woman who saw
\\the world opened
\\behind her and fell
\\before her.
\\I am the woman, I
\\who woke to pigeons
\\taking a number of
\\grounds along with them.
\\I am the girl bringing
\\a poem to the place
\\where they are lodged
\\under the name of
\\a poet.
\\The collection of poems
\\will be stored somewhere
\\named LULU
\\just inside the border
\\of an old field of corn.
\\Lovers will arrive here
\\and sing for the elephants.
\\They will bring it early or late
\\and the mood
\\of the poem will change
\\as they choose their words
\\to suit their mood.
\\The poets will keep
\\the jeweled baubles
\\slide warm.
\\They will give their loved ones
\\new dreams.
\\The flowers will be
\\filled with the
\\blood of their own lord.
\\They will drink it in
\\their round homes.
\\My heart is inside my breast.



\chapter{Hefei Luogang International Airport to Parc de la Vérendrye (Le Domaine) Water Aerodrome}
I begin my shuffle of lately songs with a particular tune
\\choose a craft;
\\this collation
\\is no gig;
\\no Chango, no Alberto, the no creed.
\\No mad Rimbaud, the music of the insolent
\\Century in its own way, is here!!
\\Fly on, my feather-loving penguin,
\\fly, my Anson--
\\The elevator man, admitting defeat,
\\Adjusts his gear on his fingers.
\\Softly, calmly, immensity taps at your
\\Dream Pipes.
\\The green doctor with uniform and white
\\Moustache
\\Drops on the table.
\\The morning-star, its nimbus full of
\\Immodestly colored peas,
\\Whooped and rabbit-eared, its wings all
\\Sprang into the crowd.
\\Above, the old bubble-head
\\Of childhood called the sootyoodle
\\And came to yogurt shops
\\Trying to get them onto the floor.
\\They were very white, the mutants just
\\Tugged at by the tide of battle,
\\The most they offered were little else
\\Than what they got from wood and beef.
\\And some were parceled into piles, the red
\\For special privileges, the blue
\\For heat there, and the green
\\For money represented.
\\What they collected was extreme
\\Tableware and bat chests
\\Miracle of the collecting:
\\Swordmaker, curlerer, hunter,
\\Seer and waker, girders and strips
\\Of the great coat's hanger
\\Bitten by the silver bullet
\\In the sweep-head, etched and set
\\Quietly as a keyhole, plain and complete.
\\What was it inscribed?
\\Ron Padgett said "Semblance of the Formes Tract."
\\I didn't know that half-zero
\\To my north, and I had my street
\\And all the complaints I had
\\When it was their own
\\Maria Zukofsky and Zenyakuyevsky
\\Were stuffed in the corner of my eye
\\And Barbara, owner of a small typewriter,
\\And I was at a computer talk.



\chapter{Ganado Airport to Fort Providence Water Aerodrome}
I give you a military shirt.
\\Here is the federal building,
\\a finger to caress the face,
\\a mouthful of flame,
\\and an anvil for an unknown seed hold.
\\A waste of a government that creates
\\for no-thing "pro patria,"
\\PGIII,
\\no-serving-my-rangeruit-huh-duh-ta-gi-nght,
\\which goes where goes the country skirt.
\\Only the wing trails elongate
\\behind the eyes, to where the beard begins.
\\A sparrow on a visitor's nose,
\\first flyliness, or chute of monkeys,
\\mimmered copies of ourselves,
\\some clipping of clothing,
\\bonneted determination,
\\gallogly, occultus,
\\blinded-eyed reasoning,
\\space mimes or omens veducted
\\in red telephus,
\\forward into darkness.
\\A carry-weehawkins in zeppelin,
\\a downdrifting from band to band
\\in descending bombed-out cities
\\(this time they truly say they're from the North)
\\blew a loop of hatred through
\\a love-nest, engendering
\\fritish paranoia of evil spirits
\\sliding down the ladder of greased walls
\\to descend
\\enclosing the nonexistent,
\\which is to say
\\it's anywhere you've looked
\\at or owned
\\or always
\\wandering or simply staying
\\held company.



\chapter{Cincinnati-Blue Ash Airport to Naval Air Station Alameda}
A brittle trandelion lays its head aside from the bus,
\\Bones white on the aluminum wings of a wing bus,
\\And another batch of workers nuts the mold-spun umbrellas.
\\A dragnet of water bubbles up from the industrial pipes,
\\Their bodies turn, heavy valves exchange with mechanical steel,
\\And John Wayne interstates between windings of trucks and assembly lines.
\\A pruning saw will have to do, and the saw has to be set,
\\And horse and ball will not ride under the marina tree.
\\Consider what this world has been through in the last ten years.
\\Strangers talking in Öster, the capital satanic milagrammatron,
\\Like the bald, white and purest Father, Steal more.
\\Still, the little lighter people in station vans seem relaxed;
\\They zip up their sleeves; they bend over their shoulders;
\\The lights are out on La Carreta Avenue and they pass me by.
\\2.
\\The sky is a show of flashing chromatic wings;
\\The dry cement fills the streets and makes the buildings
\\Candles
\\Light
\\,
\\burning amid the war over materiality and yet
\\A board-game more than once,
\\The chess game of everything that moves.
\\In the shadowless evening, by the flickering iron
\\Of the TV, a man leans on a chair and intones,
\\A blue-black talkman, then says,
\\"The motionless men and women of this stage,
\\This crowd of forms,
\\The unseen angels of this universal frame
\\Are but brief spells of lost eternity."
\\He ends abruptly
\\In a long corner of the room, alone.
\\3.
\\Winner, winner!
\\The silent man in the circle,
\\Whose world is the gravity of the world,
\\Stands
\\An image of himself, which he disappears into.



\chapter{Gilbert Plains Airport to Andrau Airpark}
The sun makes the hills brighter,
\\and the sky darker,
\\and that's the way it does it,
\\according to the way the world
\\glowy in the sun,
\\according to the yellow
\\star whose light dares match
\\the skull's resistance
\\to its dark.
\\On the West Bank of the river
\\a plane haze like a depleted
\\memory
\\moves grad-
\\ually, dizzy
\\across a warsound
\\high as the worrying
\\eyes of a child.
\\And the day is dusting
\\the banks of the river
\\and, as it returns,
\\gasps, as if
\\I have just escaped
\\from the line of ants
\\pinging sads
\\all over my dress.
\\Now I'm alone
\\a speck on the darkness
\\your face, the shape
\\of my regret
\\mounts on the arriving
\\of my brae sweater
\\to find himself nowhere
\\in his hometown
\\while the other women
\\grimly
\\change sets of instructions.
\\I'm sure "always"
\\is an impossibility,
\\for me,
\\at least, inside a poem
\\and Stubbs himself
\\has never left.
\\But I get away
\\with the knowledge of the world,
\\learn how to die
\\as a man
\\and want to tell you so,
\\but I can't.
\\This is different from living
\\in the traditional way,
\\which requires no more
\\than the gasp and the teeth
\\of the sparrows.
\\Now in a new season
\\we share a bed
\\and bananas
\\to Crown Me Whistle
\\and give each other lessons
\\in smoothness
\\before the departure.
\\Oh, doesn't there happen quite enough?
\\Broils
\\are safe only!
\\That's how we know
\\the season.
\\You've only to wait
\\and it's then you'll get
\\the thing you're wanting.
\\Now if you tell me, baby,
\\you've got it,
\\I'll bear it,
\\but don't let her
\\take it when I'm done.
\\There's very little
\\spvertipeland
\\about it.
\\There's a lot of n-
\\ovation, it's an art!



\chapter{Evergreen Field to Five Mile Lake Water Aerodrome}
I rolled out of bed and remembered I had one more
\\paw, tunneled through books,
\\my second one a granite slope
\\which entered a field of water half a block away.
\\How much easier to write than to go home!
\\Getting ready to mulch with the family dog, panting
\\and snapping his fingers.
\\One friend in the car and I in the kitchen.
\\We gazed at the poised manure pile, silent,
\\the white sand in the white sugarwater drum,
\\and the hill with five thousand men,
\\and the farmer's daughter feeding a fence.
\\Under the hedge, under the hedge,
\\some soul decided what it wanted,
\\and said it, in its heart,
\\and doesn't it? She didn't wait, she didn't
\\Look me in the eye, she didn't know
\\What I was thinking, so we lied to the car,
\\held her breath quick before she really died.



\chapter{Canadian Forces Base Portage la Prairie to Sechelt/Porpoise Bay Water Aerodrome}
Hence much must try, much be mimicked, in the square;
\\And be no more sure than the Scotchman and Welshman are.
\\Creeds are false and illusions are as soon
\\As dreams; that in the course of belonging
\\Too often have dangled the best and worst;
\\And will not be successent, though all goes right.
\\What had unfaithful earth to do with them?
\\For a wraith's voice, the man's shrill fife,
\\Haunted the grape, delayed the harvest day.
\\Children twisting an arm to laughter, necks bent over,
\\Their lips dry with theatric breath, the man's tempo
\\Flows as his words fall like a fountain's fall,
\\And the blind god, that never attends,
\\Admits afresh, accepts the world as his own.
\\From those many eyes, the holy and hidden,
\\The holy blind man pries the world with his way.
\\Imagine a museum overlooking the world,
\\A lobby opening to the past, where the ever-
\\Left was looking for someone to have done.
\\The kind of thing people say: «remember
\\two names are one. That's how it goes
\\when it's both of us and we're both of them.
\\You see they have no reason
\\to put stuff in there or hope to keep it.
\\Who says they're having a good time.



\chapter{Hamilton Air Force Base to Fort Chipewyan/Small Lake Water Aerodrome}
Hadda you got to carry my meat
\\on your knee
\\in your diaper
\\to the customs people the friendly beings
\\from gray savannahs
\\rain wood/colored swamp
\\where crying contained
\\water/walled
\\for effect koi the heads/fish
\\staring contracted
\\onto the made
\\human work
\\processuht ones/fingers
\\subjected to the cycle
\\of the ocean
\\drum generated
\\on the steeled
\\truck
\\using antler
\\branches
\\delicate brown seeds
\\rising from the
\\motherof threads
\\dusky blue wraps
\\lifted
\\by the agitation of
\\seeds
\\whose roots they attached
\\between the bevelous
\\bendors
\\of their breasts.



\chapter{Martha Lake Airport to Galway Airport}
I'm not any kind of law driver
\\I'm not a junkie who eats meat
\\I'm not a junkie who wants to die
\\Tonight I'm afraid of a stranger
\\I'm not a drunkard who sweats
\\I'm not a drunkard
\\I'm not a drunkard
\\I'm just a very tired man
\\I mean a man
\\I mean a man
\\I mean a man
\\I mean a man
\\I mean a man
\\I mean a man.
\\January 7, 1997.



\chapter{Love County Airport to Ganado Airport}
I am not allowed to speak to any of you
\\but I will read in order to reproduce as much of what
\\I knew when I met you.
\\You are alive, you raise your fat arms:
\\you seem to be thanking me,
\\to walk into the world with only steel
\\to bend around my knee, to accept coffee with without electricity
\\to protect from hatred, to take a big bird of water
\\and a rib-bone boat and fly east to Chile
\\because I telephones you,
\\and because I want to die I'll live by my mother's side
\\(My woman's body is the reason of my immortal life
\\in the world because it's not enough for her to succeed
\\in military, beat me, cancer or a survival trained parachute
\\which is more expensive than the army plane
\\because they're too big and cheap and military
\\they're also not enough at all
\\to fly freely.
\\I know I'm going to die but I'm not given a uniform.
\\I know my body is hollow.
\\I know I'm still in bed.
\\I know it's still you.
\\But the snow keeps whispering,
\\it's still you.
\\If I wait for the snow to pause
\\and for the wind to go over,
\\I can see you continuing to grow
\\on the bridge of the bridge, the official bridge
\\that goes over to the barracks,
\\the city of our proud communicators,
\\the city of our flesh called "comments"
\\that stop me pausing
\\and I can't say, "You, Michael, are a great clown and trickster"
\\because I want to be more than anything.
\\GWYAF. You and I at least
\\haven't reached the goal.
\\For me there is no grade to climb
\\when combined we are vulgar.
\\Never to be fixed.
\\Never collected nor spent.
\\We are on each other's fault.
\\It is my fault, and not the fault
\\of the messenger who carried the message.



\chapter{Disneyland Helipad to Long Branch Aerodrome}
Among the level milky towers
\\Of the old chain-driven park,
\\In the gray stone and brick building,
\\One enters a spiral of doors
\\Opon the opposite hillside
\\Sabotta
\\, 12.
\\White over white, the path follows
\\A mint, white, and green leaves
\\Stained with red Bernat
\\nails,
\\The knotted thread of the gypsy girl
\\Blown fine.
\\The overstore window beside
\\The shuttered rooftop
\\Greyness fills the air
\\Of time ...
\\The brick arch of the bank
\\Shows steel
\\Time
\\Bookkeeper counts stacks of
\\"Calm Walnut Hills"
\\Birds' i have heard
\\Off behind the blackguard
\\Scaffold clang
\\An empty voice
\\Tells me what I came for
\\There are no stones left to this
\\Body, so that it knows
\\First Face
\\Last Face
\\There are no sections left.
\\I have been crying in the rock
\\After the white rabbit.
\\White rabbit
\\Flies screaming
\\In the snow.
\\Mandarins say
\\This is the bandage room
\\Where the world has lived
\\Or still lives.
\\I have been crying
\\In the rock.
\\The animal, the cry
\\Of my strand,
\\The ballpoint, the table
\\Enkindled with a luminous cir-
\\Dice and followed by the hand
\\Of the dancer.
\\What I mean is this,
\\This counter-clarion,
\\This celadon.
\\You hold your dead hand
\\And the picture
\\Takes shape.
\\The shadowy arm.



\chapter{Bangalore/Hindustan Airport to Chambly Airport}
Jet. Close to earth. In Muslim sun.
\\Passenger. No. Must return.
\\I know it. I've been there.
\\I love the place.
\\Boats. Communism.
\\Cranky metal 'n' water.
\\You make me sick
\\every time I go.
\\There you are
\\a clock in the fire.
\\The green goes from the green and I go from the red.
\\The grass goes from the grass and we go up to Jeremiah's stone.
\\In the middle day, the sun felt like a stubble
\\and the day broke into flames.
\\My chest burned and my heart
\\said one prayer to me.
\\That night I found a field where the camel's hump was hidden.
\\Jews in those lilies ran to the river and envied them.
\\Oily-belled and well-clothed to behold the beast,
\\the master of the herd,
\\and harnessed him to his trappings.
\\We lay on the grass and watched the water wrinkle
\\and falter and thicker.
\\His skin burned like the gold dust of a gossamer:
\\his angry face streaked with drops.
\\I knelt to look at him,
\\and only looked at him.
\\He moved with the wind and held the walnuts down,
\\the ones that shriek and wobble,
\\one after another, then panted and lifted their necks,
\\and dropped the heavy nuts into his mouth.
\\He moved from here to the south valley,
\\smoke rose over the river.
\\To the north fell the falling snow,
\\the goats were beaked and thirsted,
\\their heads were bare and thirsting.
\\yah, pfft!
\\Jerusalem is cursed men's fate.
\\The gods, deprived of their thrall,
\\bid earth in for a hem!
\\Something was dead in each of their hoarded loves,
\\and evil voices call'd them to.
\\'twas the farmer's unarmed water
\\that failed to keep his gates.
\\Before their foundations began to build.



\chapter{Epcot Center Ultralight Flightpark to Craft's Field}
Bands of blackberry bushes stamped awake
\\the fallen leaves conked over the still snow,
\\their message carried near and far
\\in flocks of white.
\\Iron rings on steel wings swell out of sheet
\\that no tree has attained.
\\The streets crack into singleness,
\\mad minds reach there to catch
\\the flying stillness,
\\organs straining in thirst.
\\Kees' heart tender like a chickadee,
\\praying for something
\\and everyone waiting too,
\\too far away from the flare of day,
\\ready to cry if the world is shaking
\\or Canadians are singing.
\\Still, it isn't enough to have been there
\\it's going to be changed, the people,
\\the nation, changes forever
\\beyond that of today, changing still
\\so that those people who look back now
\\and see park around them say
\\as Louise Child, you look
\\to be like me, I'm leagued
\\like you, I'm less stressed by adrenaline
\\than by boredom,
\\that heat is less, less Godlike,
\\than a lightness in the mornings
\\that is needed, that sunlight.



\chapter{Gowganda/Gowganda Lake Water Aerodrome to McVille Airport}
Let me, let me,
\\let me weary be
\\of prayer and flight:
\\Our winds are milder than ours,
\\our springs are briefer.
\\The pear tree in the corner
\\doth bloom with pain:
\\The pheasant in the camp
\\with fever burneth,
\\And bitter blood and hunger
\\the bird doth slay.
\\'tis familiar
\\to me, sweet maid,
\\and dear to fancy;
\\For every man i knew
\\before had a wreath
\\of balsam from the morn.
\\The sword outwore
\\the shepherd's crook;
\\The nets were in the sea,
\\the wawser-tree was free.
\\So thou, fair maid,
\\find'st my wish away,
\\Let randolph or mantolla
\\shine among the crowd;
\\For they are catholomew,
\\the grass is thine.
\\So shall it be:
\\I am a king,
\\and i am a queen,
\\And i am a diver,
\\and i am a man:
\\All pains the lawless passion
\\befit the noble mind.
\\I am a realm,
\\and i am a realm;
\\I am a realm,
\\and i am a man!



\chapter{Galway Airport to Haleiwa Fighter Strip}
United and alien, looking for trade,
\\clank their guns a-trip and a-gun,
\\belonging to the women's wing-tips,
\\giving your captain your cue,
\\afters and afters, captain,
\\you must look for something at my hands,
\\for ice on the sea,
\\for wind, an open patch of sky,
\\for rain, for sun,
\\for the curtain of rain on the windowpane,
\\for rain on the windowpane.
\\Call us what you will,
\\this war is motion and progression,
\\it is the death you carry in you,
\\it is the sea you must cross and swim in,
\\you are the gauge of my peace,
\\I am the wheel she strokes,
\\I am the rubber,
\\I are the train she rides.
\\When you lie down to sleep,
\\and I lift the pillow to your forehead,
\\I am the arrow bent and wrote,
\\I am the green body,
\\formed of the green spider,
\\I am the net that holds them.
\\When you lie down to sleep,
\\and I lift the pillow to your forehead,
\\I am the arrow bent and written,
\\I am the net that holds them.



\chapter{Hamilton Air Force Base to Glasgow/Renfrew Airport}
Light plumes of smoke Emerst
\\into the grey-walled Gorgke,
\\and on a screen the Goliath of
\\Age,
\\White-haired, white-bearded, who
\\would be a man today
\\were he not today
\\being dated and older than
\\everyone else,
\\dressed in blue against
\\the snows of winter,
\\he could not
\\because of the dogwood
\\peeling its back against
\\the world.
\\The plane glided
\\under the trees
\\to the graveyard.
\\Then leveled the level
\\of the world
\\and the sky
\\was the sky of the
\\shot-squad of birds
\\moving accustomively
\\across the tarmac
\\at the time of the war.
\\The centre of the crowd
\\was a cemetery
\\with hundreds
\\keeper's-in-arms,
\\Starting lines and rows
\\of fusillades
\\set for
\\the guard to keep,
\\and the thing that
\\everyone
\\wears
\\was a costume
\\made of feathers
\\and ruffle
\\dresses to sit in,
\\each with a name
\\pornning against
\\the fuchsia
\\of the feather-
\\ruffled body
\\the body's in
\\the uniform of rigor.
\\Joy! Joy!
\\They were the people
\\was dying and
\\beside the river
\\felt the great
\\spread-
\\eyes of the honed-
\\like-tongue
\\imagining
\\the gods of
\\this landscape
\\were
\\about them at
\\interpretation.
\\Interpretation,
\\what it was,
\\was the way
\\they looked
\\when he came back
\\the young
\\older brothers and
\\the young
\\is coming back
\\and again
\\by leaps
\\that we know
\\just why
\\they are
\\there
\\in this particular
\\place.
\\They are not
\\like us at all
\\but they are cocks
\\and cocksurers
\\and all that other things
\\we do.
\\But they are cocks
\\and cocksurers.
\\So we have
\\conceived this
\\and will therefore
\\by the same
\\esliabic
\\accent
\\to bring
\\back the.



\chapter{Presidente Médici International Airport to Chambly Airport}
Jethed me on your regional baldness
\\I was dying to stand on a bare beach
\\drill-dropping hair a trifle
\\I am thrumming lots of cold water buoys
\\drank down last week's rain and bawdy taste of chewing
\\pan's too long black curly hair an uncle
\\tried to help me crochet learn to sing
\\I don't want to be a cop
\\because I'm mostly a cookie
\\I have no office and I don't fly
\\I have no family and I don't cook
\\I have no breakfast and I don't like
\\my poems--
\\well, today I'm all in a room with a pool of mothers--
\\accepting his apology
\\that really can't mend your love
\\nor your recovery from illness
\\and your stubborn pursuit of manuscripts
\\where you lost your almost constant optimism
\\and I'm not exactly remembering
\\the thirties, but I'm not nauseous,
\\too sick to worry about your old ankles
\\and your wives. Oh, I know I'm lost
\\but I'm not complaining, so congratulations
\\to all the hatless black magi who left each other
\\to their rearen forums
\\and blew their tops at each other!
\\It is not misogyny that harps itself
\\across the sea of the multiflora
\\but eloquence of the infinitely surrounded,
\\the sing-song chimerias
\\and the Allen Ginsbergs of MY OWN TELLING
\\that made me into someone
\\layered my soul with rumors of my own
\\destiny and general bad luck.
\\I had a milder quality,
\\a manly too, of biting charm,
\\and I hated him faster than I hate
\\the brothers who failed to love me,
\\the old excitable closeness of their parties
\\the comfort of my dinner
\\the careful construction of their traps
\\I learned from the humane rights panel
\\to ratify any change of address
\\I could see he'd come to his stand
\\and, undisturbed, he would stay.
\\It was a flower
\\upon which April
\\had descended from the skies!
\\How tender
\\a caress! I told myself
\\hoefully that if I could ruin my craft.

% \chapter{Chapter One}
% \lipsum[1-20]
% \chapter{Chapter Two}
% \lipsum[21-40]
% \chapter{Chapter Three}
% \lipsum[41-60]
% \chapter{Chapter Four}
% \lipsum[61-80]
% \chapter{Chapter Five}
% \lipsum[81-100]
% \chapter{Chapter Six}
% \lipsum[101-120]

% begin back matter

\end{document}
% END THE DOCUMENT